### 2023-08-21 analysis/checkData.Rmd
Create checkData.Rmd

---
title: "checkData"
output: html_document
date: "2023-08-21"
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
```

# Load data

```{r}
# article data (random)
d_articles_random <- read_csv(here('data','raw','articles (random) - Sheet1.csv')) %>%
  filter(!is.na(`primary coder initials`) & !is.na(`secondary coder initials`)) # we only need articles that we're coded by someone

# article data (prominent)
d_articles_prominent <- read_csv(here('data','raw','articles (prominent) - Sheet1.csv'))  %>%
  filter(!is.na(`primary coder initials`) & !is.na(`secondary coder initials`)) # we only need articles that we're coded by someone

# journal data (random and prominent sample)
d_journals <- read_csv(here('data','raw','Data Extraction Form (policy) (Responses) - Form Responses 1.csv'))

# list of journals in random sample
journal_list_random <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv')) %>%
  slice_head(n = 108) %>%
  select(`Journal`)

# list of journals in prominent sample
journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv')) %>%
  slice_head(n = 114) %>%
  select('Journal' = `Journal name`)
```

# Journals data

Remove pilot journals

```{r}
d_journals <- d_journals %>%
  filter(`Are you piloting?` == "No") %>%
  select(-`Are you piloting?`)
```

Change two journal names entered incorrectly so they match names in sample.

```{r}
d_journals <- d_journals %>% mutate(`Journal Name` = fct_recode(`Journal Name`, 
                                         "MEMORY & COGNITION" = "Memory & Cognition",
                                         "JOURNAL OF COUPLE & RELATIONSHIP THERAPY-INNOVATIONS IN CLINICAL AND EDUCATIONAL INTERVENTIONS" = "Journal of Couple & Relationship Therapy"))
```

```{r}
d2 <- d %>%
  mutate(
    sample_journal_prominent = `Journal Name` %in% journal_list_prominent$Journal,
    sample_journal_random = `Journal Name` %in% journal_list_random$Journal,
    sample_journal_both = sample_journal_prominent & sample_journal_random,
    sample_journal_error = !sample_journal_prominent & !sample_journal_random
  )
```

```{r}
d %>% 
  count(`Journal Name`) %>%
  filter(n > 2)
```

```{r}
d %>% filter(`Journal Name` == "CLINICAL PSYCHOLOGY-SCIENCE AND PRACTICE")
```

# Articles data

Find cases where primary and secondary coder disagreed on whether to exclude.

```{r}
d_articles_random %>%
  count(`1_exclusion`, `2_exclusion`)
```

On first pass, it looks like we have some exclusion disagreements. Let's identify the relevant papers:

```{r}
d_articles_random %>%
  filter(`1_exclusion` != `2_exclusion`)
```

Find cases where primary and secondary coder disagreed on whether to exclude.

```{r}
d_articles_prominent %>%
  count(`1_exclusion`, `2_exclusion`)
```

On first pass, it looks like we have some exclusion disagreements. Let's identify the relevant papers:

```{r}
d_articles_prominent %>%
  filter(`1_exclusion` != `2_exclusion`)
```

### 2023-08-21 analysis/checkData.Rmd
Update checkData.Rmd

@@
 ---
+
+# Load packages
 
@@
 ```
+# Rename colums
 
-# Journals data
+Rename some columns for easier reference.
+
+```{r}
+d_journals <- d_journals %>%
+  select(coder_id = `Coder's Initials`,
+         pilot = `Are you piloting?`,
+         journal = `Journal Name`,
+         journal_empirical = `Does the journal publish empirical research?`,
+         web_comments = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
+         ppc_name_A = `A. Enter the name of the PPC type offered by the journal:`,
+         ppc_name_B = `B. Enter the name of the PPC type offered by the journal:`,
+         ppc_name_C = `C. Enter the name of the PPC type offered by the journal:`,
+         ppc_description_A = `A. Enter the verbatim description of this type of PPC provided by the journal`,
+         ppc_description_B = `B. Enter the verbatim description of this type of PPC provided by the journal`,
+         ppc_description_C = `C. Enter the verbatim description of this type of PPC provided by the journal`,
+         ppc_length_A = `A. Are there any length limits for this type of PPC?`,
+         ppc_length_B = `B. Are there any length limits for this type of PPC?`,
+         ppc_length_C = `C. Are there any length limits for this type of PPC?`,
+         ppc_time_A = `A. Are there any time limits for submission of this type of PPC?`,
+         ppc_time_B = `B. Are there any time limits for submission of this type of PPC?`,
+         ppc_time_C = `C. Are there any time limits for submission of this type of PPC?`,
+         ppc_ref_A = `A. Are there any reference limits for this type of PPC?`,
+         ppc_ref_B = `B. Are there any reference limits for this type of PPC?`,
+         ppc_ref_C = `C. Are there any reference limits for this type of PPC?`,
+         ppc_review_A = `A. Is this type of PPC sent for independent external peer review?`,
+         ppc_review_B = `B. Is this type of PPC sent for independent external peer review?`,
+         ppc_review_C = `C. Is this type of PPC sent for independent external peer review?`,
+         ppc_note_A = `A. Anything additional, unusual, or interesting to note?`,
+         ppc_note_B = `B. Anything additional, unusual, or interesting to note?`,
+         ppc_note_C = `C. Anything additional, unusual, or interesting to note?`,
+         general_note = `Anything additional, unusual, or interesting to note?`,
+         -starts_with("D. "), 
+         -ends_with("Are there any other types of PPC in this journal? (Remember to check for web comments!)`"))
+
+d_articles_random <- d_articles_random %>%
+  select(
+    article_id = `article id`,
+    coder_id_primary = `primary coder initials`,
+    coder_id_secondary = `secondary coder initials`,
+    exclusion_primary = `1_exclusion`,
+    exclsion_reason_primary = `1_exclusionReason`,
+    ppc_linked_primary = `1_Is article linked to PPC`,
+    notes_primary = `1_Additional notes`,
+    exclusion_secondary = `2_exclusion`,
+    exclsion_reason_secondary = `2_exclusionReason`,
+    ppc_linked_secondary = `2_Is article linked to PPC`,
+    notes_secondary = `2_Additional notes`
+  )
+
+d_articles_prominent <- d_articles_prominent %>%
+  select(
+    article_id = `article id`,
+    coder_initials_primary = `primary coder initials`,
+    coder_initials_secondary = `secondary coder initials`,
+    exclusion_primary = `1_exclusion`,
+    exclsion_reason_primary = `1_exclusionReason`,
+    ppc_linked_primary = `1_Is article linked to PPC`,
+    notes_primary = `1_Additional notes`,
+    exclusion_secondary = `2_exclusion`,
+    exclsion_reason_secondary = `2_exclusionReason`,
+    ppc_linked_secondary = `2_Is article linked to PPC`,
+    notes_secondary = `2_Additional notes`
+  )
+```
+
+# Inspect journals data
 
@@
 ```{r}
-d2 <- d %>%
+d2 <- d_journals %>%
   mutate(
@@
 ```{r}
-d %>% 
+d_journals %>% 
   count(`Journal Name`) %>%
@@
 ```{r}
-d %>% filter(`Journal Name` == "CLINICAL PSYCHOLOGY-SCIENCE AND PRACTICE")
+d_journals %>% filter(`Journal Name` == "CLINICAL PSYCHOLOGY-SCIENCE AND PRACTICE")
 ```
 
-# Articles data
+# Inspect articles data
 
@@
 ```
+
+Our procedure is for TEH for resolve disagreements between the primary and secondary coders.
+
+```{r}
+
+```

### 2023-08-22 analysis/checkData.Rmd
new prepare sample folders

@@
 ```
+
 # Rename colums
@@
 
-# Inspect journals data
+# Inspect journal's data
 
@@
 d_journals <- d_journals %>%
-  filter(`Are you piloting?` == "No") %>%
-  select(-`Are you piloting?`)
+  filter(pilot == "No") %>%
+  select(-pilot)
 ```
 
-Change two journal names entered incorrectly so they match names in sample.
+Adjust two journal names entered incorrectly so they match names in sample.
 
 ```{r}
-d_journals <- d_journals %>% mutate(`Journal Name` = fct_recode(`Journal Name`, 
+d_journals <- d_journals %>% mutate(journal = fct_recode(journal, 
                                          "MEMORY & COGNITION" = "Memory & Cognition",
@@
 ```{r}
-d2 <- d_journals %>%
+d_journals <- d_journals %>%
   mutate(
-    sample_journal_prominent = `Journal Name` %in% journal_list_prominent$Journal,
-    sample_journal_random = `Journal Name` %in% journal_list_random$Journal,
+    sample_journal_prominent = journal %in% journal_list_prominent$Journal,
+    sample_journal_random = journal %in% journal_list_random$Journal,
     sample_journal_both = sample_journal_prominent & sample_journal_random,
@@
 d_journals %>% 
-  count(`Journal Name`) %>%
+  count(journal) %>%
   filter(n > 2)

### 2023-08-23 analysis/checkData.Rmd
Update checkData.Rmd
created singlge sampleID column
and removed now obsolete 4x sample_journal_xx columns

Also changed name 'web_comments' to 'anyPPC' to more accurately reflect values and added some descriptive annotations

@@
          journal_empirical = `Does the journal publish empirical research?`,
-         web_comments = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
+         anyPPC = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
          ppc_name_A = `A. Enter the name of the PPC type offered by the journal:`,
@@
 ```
-
+Create sample ID column(s) to indicate whether in prominent, random, or both samples
 ```{r}
@@
   )
+
+#Creates sampleID column denoting; prominent, random, or both to replace the 4 specified columns above
+d_journals %>% 
+  mutate(sample_journal_prominent = ifelse(sample_journal_prominent, "prominent", "random")) %>%
+  mutate(sample_journal_both = ifelse(sample_journal_both, "both", "na")) %>%
+  mutate(sampleID = case_when(
+    sample_journal_both == "both" ~ "both",
+    sample_journal_both == "na" ~ sample_journal_prominent,
+    TRUE ~ sample_journal_both
+  )) %>%
+  select(-c(sample_journal_prominent, sample_journal_random, sample_journal_both, sample_journal_error))
+
 ```
 
+Check entries to ensure secondary coding and identify anomalous entries
 ```{r}

### 2023-08-23 analysis/checkData.Rmd
applies sampleID change to tibble

@@
 library(here)
+library(tidylog)
 ```
@@
 #Creates sampleID column denoting; prominent, random, or both to replace the 4 specified columns above
-d_journals %>% 
+d_journals <- d_journals %>% 
   mutate(sample_journal_prominent = ifelse(sample_journal_prominent, "prominent", "random")) %>%

### 2023-08-24 analysis/checkData.Rmd
Update checkData.Rmd

@@
   select('Journal' = `Journal name`)
+
+# list of all prominent journals (some not in sample)
+journal_list_prominent_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'))
+
+# list of all random journals (some not in sample)
+journal_list_random_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'))
 ```
@@
 d_journals <- d_journals %>%
-  select(coder_id = `Coder's Initials`,
+  select(timestamps = Timestamp,
+         coder_id = `Coder's Initials`,
          pilot = `Are you piloting?`,
@@
   select(-c(sample_journal_prominent, sample_journal_random, sample_journal_both, sample_journal_error))
-
 ```
 
-Check entries to ensure secondary coding and identify anomalous entries
+Get JIFs for journals
+
 ```{r}
-d_journals %>% 
+d_journals_prominent <- d_journals %>%
+  filter(sampleID %in% c('prominent', 'both'))
+
+d_journals_random <- d_journals %>%
+  filter(sampleID == 'random')
+
+journal_list_prominent_all <- journal_list_prominent_all %>% 
+  select(journal = `Journal name`, `2021 JIF`, WOS_first_psych_category)
+
+d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal')
+
+journal_list_random_all <- journal_list_random_all %>%
+  select(journal = Journal, WOS_first_psych_category)
+
+d_journals_random <- left_join(d_journals_random, journal_list_random_all, by = 'journal')
+
+journal_list_prominent_all <- journal_list_prominent_all %>%
+  select(-WOS_first_psych_category)
+
+d_journals_random <- left_join(d_journals_random, journal_list_prominent_all, by = 'journal')
+
+tmp <- d_journals_random %>% filter(is.na(`2021 JIF`)) %>% distinct(journal, .keep_all = T)
+write_csv(tmp,here('data', 'prepareSample', 'journals', '02 - modified', 'we_need_jifs.csv'))
+```
+
+Check journals where we have more than 2 entries
+
+```{r}
+d_journals_prominent %>% 
   count(journal) %>%
@@
 
+For the journal HUMAN ARENAS, RTT coded twice, first entry was an error and needs to be removed.
 ```{r}
-d_journals %>% filter(`Journal Name` == "CLINICAL PSYCHOLOGY-SCIENCE AND PRACTICE")
+d_journals_random <- d_journals_random %>%
+  filter(!(journal == "HUMAN ARENAS" & timestamps == "8/6/2023 3:37:26"))
+```
+
+For the journal INFANTS & YOUNG CHILDREN, MN coded twice, first entry was an error and needs to be removed.
+```{r}
+d_journals_random <- d_journals_random %>%
+  filter(!(journal == "INFANTS & YOUNG CHILDREN" & timestamps == "7/15/2023 18:51:15"))
+```
+For the journal EDUCATIONAL PSYCHOLOGIST, AW coded twice, first entry was an error and needs to be removed.
+```{r}
+d_journals_prominent <- d_journals_prominent %>%
+  filter(!(journal == "EDUCATIONAL PSYCHOLOGIST" & timestamps == "6/29/2023 14:06:13"))
+```
+
+For the journal EUROPEAN JOURNAL OF PERSONALITY, journal is in both samples so AW coded twice, entries are substantively the same, removing first entry.
+
+```{r}
+d_journals_prominent <- d_journals_prominent %>%
+  filter(!(journal == "EUROPEAN JOURNAL OF PERSONALITY" & timestamps == "6/29/2023 22:01:35"))
+```
+For the journal PERSONALITY AND SOCIAL PSYCHOLOGY REVIEW, two entries from NM, first entry was an error.
+
+```{r}
+d_journals_prominent <- d_journals_prominent %>%
+  filter(!(journal == "PERSONALITY AND SOCIAL PSYCHOLOGY REVIEW" & timestamps == "7/3/2023 18:34:38"))
+```
+
+For the journal PSYCHOLOGICAL MEDICINE, two entries from RTT, first entry was an error.
+
+```{r}
+d_journals_prominent <- d_journals_prominent %>%
+  filter(!(journal == "PSYCHOLOGICAL MEDICINE" & timestamps == "8/6/2023 9:49:10"))
 ```

### 2023-08-24 analysis/prepareSamples/assignCoders.R
Create assignCoders.R

@@ -1,0 +1,18 @@
+library(tidyverse)
+library(here)
+d <- read_csv(here('data','journal_rand.csv'))
+d <- d %>%
+  filter(`eligible (T = publishes empirical, F = no empirical)` %in% c(T,F))
+
+d_shuffle <- d %>%
+  filter(`eligible (T = publishes empirical, F = no empirical)` == T) %>%
+  slice_sample(n = 100) %>%
+  mutate(coder = ifelse(row_number()<=40, "RT", "SV")) %>%
+  mutate(coder = ifelse(row_number()>=81, "TEH", coder)) %>%
+  select(journal_name, coder)
+
+d <- d %>% left_join(d_shuffle, by = 'journal_name')
+
+coders <- d %>% select(coder)
+
+write_csv(coders, 'coders.csv')

### 2023-08-24 analysis/prepareSamples/randShuffleProminent.R
Create randShuffleProminent.R

@@ -1,0 +1,16 @@
+# randomly shuffle prominent journal list to disrupt coder drift
+
+library(tidyverse)
+library(here)
+
+d <- read_csv(here('data','tmp2.csv'))
+
+d_coded <- d %>% filter(!is.na(primary_coder))
+d_not_coded <- d %>% filter(is.na(primary_coder))
+
+set.seed(42)
+d_shuffle <- d_coded %>% slice_sample(n = nrow(d_coded))
+
+d_out <- bind_rows(d_shuffle,d_not_coded)
+  
+write_csv(d_out, 'prom_journals_shuffled.csv')

### 2023-08-25 analysis/checkData.Rmd
Update checkData.Rmd

@@
 ```{r setup, include=FALSE}
-library(tidyverse)
-library(here)
-library(tidylog)
+library(tidyverse) # for various tasks including munging and plotting
+library(here) # for easier file path access
+library(tidylog) # for inline programming reporting
+library(assertthat) # for testing
+`%notin%` <- Negate(`%in%`) # for identifying when values are not in a vector of expected values
 ```
@@
 
+Load the extracted (i.e., manually coded) data.
+
 ```{r}
 # article data (random)
-d_articles_random <- read_csv(here('data','raw','articles (random) - Sheet1.csv')) %>%
-  filter(!is.na(`primary coder initials`) & !is.na(`secondary coder initials`)) # we only need articles that we're coded by someone
+d_articles_random <- read_csv(here('data','raw','articles (random) - Sheet1.csv'), show_col_types = F) %>%
+  filter(!is.na(`primary coder initials`) & !is.na(`secondary coder initials`)) # we only need articles that were coded by someone
 
 # article data (prominent)
-d_articles_prominent <- read_csv(here('data','raw','articles (prominent) - Sheet1.csv'))  %>%
-  filter(!is.na(`primary coder initials`) & !is.na(`secondary coder initials`)) # we only need articles that we're coded by someone
+d_articles_prominent <- read_csv(here('data','raw','articles (prominent) - Sheet1.csv'), show_col_types = F)  %>%
+  filter(!is.na(`primary coder initials`) & !is.na(`secondary coder initials`)) # we only need articles that were coded by someone
 
 # journal data (random and prominent sample)
-d_journals <- read_csv(here('data','raw','Data Extraction Form (policy) (Responses) - Form Responses 1.csv'))
+d_journals <- read_csv(here('data','raw','Data Extraction Form (policy) (Responses) - Form Responses 1.csv'), show_col_types = F)
+```
 
+There is some information about the sample that isn't included in the extracted data files (e.g., JIFs, Web of Science subject category), so we need to load some of that information from the original sample files.
+
+```{r}
 # list of journals in random sample
-journal_list_random <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv')) %>%
+journal_list_random <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F) %>%
   slice_head(n = 108) %>%
@@
 # list of journals in prominent sample
-journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv')) %>%
+journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F) %>%
   slice_head(n = 114) %>%
@@
 # list of all prominent journals (some not in sample)
-journal_list_prominent_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'))
+journal_list_prominent_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F)
 
 # list of all random journals (some not in sample)
-journal_list_random_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'))
+journal_list_random_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F)
 ```
@@
     exclusion_primary = `1_exclusion`,
-    exclsion_reason_primary = `1_exclusionReason`,
+    exclusion_reason_primary = `1_exclusionReason`,
     ppc_linked_primary = `1_Is article linked to PPC`,
@@
     exclusion_secondary = `2_exclusion`,
-    exclsion_reason_secondary = `2_exclusionReason`,
+    exclusion_reason_secondary = `2_exclusionReason`,
     ppc_linked_secondary = `2_Is article linked to PPC`,
@@
     article_id = `article id`,
-    coder_initials_primary = `primary coder initials`,
-    coder_initials_secondary = `secondary coder initials`,
+    coder_id_primary = `primary coder initials`,
+    coder_id_secondary = `secondary coder initials`,
     exclusion_primary = `1_exclusion`,
-    exclsion_reason_primary = `1_exclusionReason`,
+    exclusion_reason_primary = `1_exclusionReason`,
     ppc_linked_primary = `1_Is article linked to PPC`,
@@
 
-# Inspect journal's data
+# Remove non-relevant rows
 
-Remove pilot journals
+## Remove pilot journals
+
+Removing all rows that were entered during piloting and therefore not part of the main sample.
 
@@
 
-Adjust two journal names entered incorrectly so they match names in sample.
+## Remove erroneous rows
+
+Occasionally coders entered data for the same journal twice. Below we remove the erroneous rows, using the journal name and data entry timestamp to identify the relevant rows.
+
+For the journal HUMAN ARENAS, RTT coded twice, first entry was an error and needs to be removed.
 
 ```{r}
-d_journals <- d_journals %>% mutate(journal = fct_recode(journal, 
-                                         "MEMORY & COGNITION" = "Memory & Cognition",
-                                         "JOURNAL OF COUPLE & RELATIONSHIP THERAPY-INNOVATIONS IN CLINICAL AND EDUCATIONAL INTERVENTIONS" = "Journal of Couple & Relationship Therapy"))
+d_journals <- d_journals %>%
+  filter(!(journal == "HUMAN ARENAS" & timestamps == "8/6/2023 3:37:26"))
 ```
+
+For the journal INFANTS & YOUNG CHILDREN, MN coded twice, first entry was an error and needs to be removed.
+
+```{r}
+d_journals <- d_journals %>%
+  filter(!(journal == "INFANTS & YOUNG CHILDREN" & timestamps == "7/15/2023 18:51:15"))
+```
+
+For the journal EDUCATIONAL PSYCHOLOGIST, AW coded twice, first entry was an error and needs to be removed.
+
+```{r}
+d_journals <- d_journals %>%
+  filter(!(journal == "EDUCATIONAL PSYCHOLOGIST" & timestamps == "6/29/2023 14:06:13"))
+```
+
+For the journal EUROPEAN JOURNAL OF PERSONALITY, journal is in both samples so AW coded twice, entries are substantively the same, removing first entry.
+
+```{r}
+d_journals <- d_journals %>%
+  filter(!(journal == "EUROPEAN JOURNAL OF PERSONALITY" & timestamps == "6/29/2023 22:01:35"))
+```
+
+For the journal PERSONALITY AND SOCIAL PSYCHOLOGY REVIEW, two entries from NM, first entry was an error.
+
+```{r}
+d_journals <- d_journals %>%
+  filter(!(journal == "PERSONALITY AND SOCIAL PSYCHOLOGY REVIEW" & timestamps == "7/3/2023 18:34:38"))
+```
+
+For the journal PSYCHOLOGICAL MEDICINE, two entries from RTT, first entry was an error.
+
+```{r}
+d_journals <- d_journals %>%
+  filter(!(journal == "PSYCHOLOGICAL MEDICINE" & timestamps == "8/6/2023 9:49:10"))
+```
+
+# Perform initial tests and fix issues
+
+Let's check a few columns to see if they contain what we expect.
+
+## Journals
+
+Check every row has an entry in `timestamps`.
+
+```{r}
+assert_that(
+  all(!is.na(d_journals$timestamps)),
+  msg = "Found missing timestamps"
+)
+```
+
+Check we have the expected coder initials in `coder_id` and convert column to factor.
+
+```{r}
+expected_coders <- c("AW", "NM", "SV", "RTT", "TEH", "SS", "BC")
+
+assert_that(
+  all(d_journals$coder_id %in% expected_coders),
+  msg = "Found unexpected values in the coder_id column"
+)
+
+d_journals$coder_id = factor(d_journals$coder_id) # make this column a factor
+```
+
+Check every row has a `journal`.
+
+```{r}
+assert_that(
+  all(!is.na(d_journals$journal)),
+  msg = "Found missing journal name"
+)
+```
+
+Check every row has a `journal` that appears in the original random or prominent sample lists.
+We initially get an error for this test because some journal names were entered in the extraction form with incorrect formatting.
+Correct this below before running the test.
+
+```{r}
+d_journals <- d_journals %>% 
+  mutate(journal = fct_recode(journal,
+                              "MEMORY & COGNITION" = "Memory & Cognition","JOURNAL OF COUPLE & RELATIONSHIP THERAPY-INNOVATIONS IN CLINICAL AND EDUCATIONAL INTERVENTIONS" = "Journal of Couple & Relationship Therapy"))
+```
+
+```{r}
+assert_that(
+  all(d_journals$journal %in% c(journal_list_prominent$Journal, journal_list_random$Journal)),
+  msg = "Found journal names that do not match sample"
+)
+```
+
+That fixed the problem, now all journal names in the extracted data match journal names in the sample files.
+
+We can't run any more useful tests at this point because in many columns coders have used entered free text to explain cases that were unclear.
+So we will run tests again later after coding discrepancies have been resolved.
+
+## Articles
+
+Firstly let's join the prominent and random articles together (with a new column identifying which sample they are in) to streamline some testing.
+
+```{r}
+d_articles <- bind_rows(
+  d_articles_random %>% mutate(sampleID = "random"),
+  d_articles_prominent %>% mutate(sampleID = "prominent")
+)
+```
+
+Check every row has an entry in `article_id`.
+
+```{r}
+assert_that(
+  all(!is.na(d_articles$article_id)),
+  msg = "Found missing article ids"
+)
+```
+
+Check we have the expected coder initials in `coder_id_primary` and `coder_id_secondary` columns and convert columns to factor.
+
+```{r}
+assert_that(
+  all(d_articles$coder_id_primary %in% expected_coders),
+  msg = "Found unexpected values in the coder_id_primary column"
+)
+
+assert_that(
+  all(d_articles$coder_id_secondary %in% expected_coders),
+  msg = "Found unexpected values in the coder_id_primary column"
+)
+
+# make these columns factors
+d_articles$coder_id_primary = factor(d_articles$coder_id_primary)
+d_articles$coder_id_secondary = factor(d_articles$coder_id_secondary)
+
+```
+
+Now check we only have expected values in the `exclusion_primary` column.
+
+```{r}
+assert_that(
+  all(d_articles$exclusion_primary %in% c("RETAIN", "EXCLUDE")),
+  msg = "Found unexpected values in the exclusion_primary column"
+)
+```
+Now check we only have expected values in the `exclusion_secondary` column.
+
+```{r}
+assert_that(
+  all(d_articles$exclusion_secondary %in% c("RETAIN", "EXCLUDE")),
+  msg = "Found unexpected values in the exclusion_primary column"
+)
+```
+
+Now check that when `exclusion_primary` is "RETAIN" `exclusion_reason` is NA.
+
+```{r}
+d_articles <- d_articles %>%
+  mutate(exc_col_check = ifelse(exclusion_primary == "RETAIN" & is.na(exclusion_reason_primary), T, F)) # if we are retaining there should be an NA in the reason column
+
+assert_that(all(d_articles$exc_col_check == F), msg = "Found unexpected value in exclusion reason column when it should be NA")
+```
+
+# Attach sample information to extracted data
+
+## Identify sample for journals
+
+The `d_journals` dataset does not identify whether journals were in the prominent sample, random sample, or both.
+So we need to get the sample ID retroactively using the files containing all journals included in the sample.
+
 Create sample ID column(s) to indicate whether in prominent, random, or both samples
+
 ```{r}
@@
 
-Get JIFs for journals
+## Identify JIFs for journals
 
@@
 
-Check journals where we have more than 2 entries
-
-```{r}
-d_journals_prominent %>% 
-  count(journal) %>%
-  filter(n > 2)
-```
-
-For the journal HUMAN ARENAS, RTT coded twice, first entry was an error and needs to be removed.
-```{r}
-d_journals_random <- d_journals_random %>%
-  filter(!(journal == "HUMAN ARENAS" & timestamps == "8/6/2023 3:37:26"))
-```
-
-For the journal INFANTS & YOUNG CHILDREN, MN coded twice, first entry was an error and needs to be removed.
-```{r}
-d_journals_random <- d_journals_random %>%
-  filter(!(journal == "INFANTS & YOUNG CHILDREN" & timestamps == "7/15/2023 18:51:15"))
-```
-For the journal EDUCATIONAL PSYCHOLOGIST, AW coded twice, first entry was an error and needs to be removed.
-```{r}
-d_journals_prominent <- d_journals_prominent %>%
-  filter(!(journal == "EDUCATIONAL PSYCHOLOGIST" & timestamps == "6/29/2023 14:06:13"))
-```
-
-For the journal EUROPEAN JOURNAL OF PERSONALITY, journal is in both samples so AW coded twice, entries are substantively the same, removing first entry.
-
-```{r}
-d_journals_prominent <- d_journals_prominent %>%
-  filter(!(journal == "EUROPEAN JOURNAL OF PERSONALITY" & timestamps == "6/29/2023 22:01:35"))
-```
-For the journal PERSONALITY AND SOCIAL PSYCHOLOGY REVIEW, two entries from NM, first entry was an error.
-
-```{r}
-d_journals_prominent <- d_journals_prominent %>%
-  filter(!(journal == "PERSONALITY AND SOCIAL PSYCHOLOGY REVIEW" & timestamps == "7/3/2023 18:34:38"))
-```
-
-For the journal PSYCHOLOGICAL MEDICINE, two entries from RTT, first entry was an error.
-
-```{r}
-d_journals_prominent <- d_journals_prominent %>%
-  filter(!(journal == "PSYCHOLOGICAL MEDICINE" & timestamps == "8/6/2023 9:49:10"))
-```
-
 # Inspect articles data
@@
 d_articles_random %>%
-  count(`1_exclusion`, `2_exclusion`)
+  count(exclusion_primary)
 ```
@@
 ```
+
+# Final tests
+
+Now check that `journal_empirical` contains only 'Yes' or 'No'. When we first run the test we get unexpected values.
+
+and convert these to `TRUE` and `FALSE` respectively.
+
+```{r}
+assert_that(
+  all(d_journals$journal_empirical %in% c("Yes", "No")),
+  msg = "Found unexpected values in journal_empirical column"
+)
+```

### 2023-08-25 analysis/checkData.Rmd
Update checkData.Rmd

@@
 
-Now check that when `exclusion_primary` is "RETAIN" `exclusion_reason` is NA.
+Now check that when `exclusion_primary` and `exclusion_secondary` are "EXCLUDE" then we have reasons in the reason columns. When they are "RETAIN" the reason columns should be NA.
 
 ```{r}
-d_articles <- d_articles %>%
-  mutate(exc_col_check = ifelse(exclusion_primary == "RETAIN" & is.na(exclusion_reason_primary), T, F)) # if we are retaining there should be an NA in the reason column
-
-assert_that(all(d_articles$exc_col_check == F), msg = "Found unexpected value in exclusion reason column when it should be NA")
+# primary_exclusions <- d_articles %>% 
+#   count(exclusion_primary, exclusion_reason_primary) %>%
+#   mutate(expected_values = case_when(
+#     exclusion_primary == "RETAIN" & is.na(exclusion_reason_primary) ~ T,
+#     exclusion_primary == "EXCLUDE" & exclusion_reason_primary %in% c("NO ACCESS", "NON-ENGLISH", "NOT EMPIRICAL", "RETRACTED", "IS ITSELF PPC", "OTHER") ~ T,
+#     TRUE ~ "criteria not met"
+#   ))
+# 
+# secondary_exclusions <- d_articles %>% 
+#   count(exclusion_secondary, exclusion_reason_secondary) %>%
+#   
+# 
+# 
+# assert_that(, msg = "Found unexpected value in exclusion reason column when it should be NA")
 ```
@@
 
+```{r}
+
+```
+
 Find cases where primary and secondary coder disagreed on whether to exclude.
@@
 ```{r}
-d_articles_random %>%
-  count(exclusion_primary)
+d_articles %>%
+  count(exclusion_primary, exclusion_secondary)
+```
+
+Random ID 37 — TEH decides to go with primary coder and retain.
+Random ID 41 - TEH decides to go with primary coder and retain.
+Random ID 68 - TEH decides to go with secondary coder and exclude.
+Random ID 95 - TEH decides to go with secondary coder and retain.
+Random ID 103 — TEH decides to go with primary coder and exclude.
+Random ID 120 — TEH decides to go with primary coder and retain.
+
+```{r}
+d_articles %>%
+  filter(exclusion_primary != exclusion_secondary)
 ```

### 2023-08-25 analysis/checkData.Rmd
Update checkData.Rmd

@@
 
-```{r}
-
-```
-
 Find cases where primary and secondary coder disagreed on whether to exclude.
-
-```{r}
-d_articles %>%
-  count(exclusion_primary, exclusion_secondary)
-```
-
-Random ID 37 — TEH decides to go with primary coder and retain.
-Random ID 41 - TEH decides to go with primary coder and retain.
-Random ID 68 - TEH decides to go with secondary coder and exclude.
-Random ID 95 - TEH decides to go with secondary coder and retain.
-Random ID 103 — TEH decides to go with primary coder and exclude.
-Random ID 120 — TEH decides to go with primary coder and retain.
 
@@
 
-On first pass, it looks like we have some exclusion disagreements. Let's identify the relevant papers:
+Following protocol, coding discrepancies are resolved by TEH.
+We now create an `exclusion_final` column which represents the resolved coding.
+TEH decides to either go with the primary or secondary coder's verdict.
+For other articles, we use the primary coder's verdict (which is the same as the secondary coder).
 
 ```{r}
-d_articles_random %>%
-  filter(`1_exclusion` != `2_exclusion`)
+# create exclusion_final column
+d_articles <- d_articles %>%
+  mutate(exclusion_final = case_when(
+    sampleID == 'random' & article_id == '37' ~ exclusion_primary,
+    sampleID == 'random' & article_id == '41' ~ exclusion_primary,
+    sampleID == 'random' & article_id == '68' ~ exclusion_secondary,
+    sampleID == 'random' & article_id == '95' ~ exclusion_secondary,
+    sampleID == 'random' & article_id == '103' ~ exclusion_primary,
+    sampleID == 'random' & article_id == '120' ~ exclusion_primary,
+    sampleID == 'prominent' & article_id == '30' ~ exclusion_secondary,
+    sampleID == 'prominent' & article_id == '49' ~ exclusion_primary,
+    sampleID == 'prominent' & article_id == '66' ~ exclusion_primary,
+    sampleID == 'prominent' & article_id == '98' ~ exclusion_primary,
+    TRUE ~ exclusion_primary
+  ))
+
+# create exclusion_reason_final column
+d_articles <- d_articles %>%
+  mutate(exclusion_reason_final = case_when(
+    sampleID == 'random' & article_id == '37' ~ exclusion_reason_primary,
+    sampleID == 'random' & article_id == '41' ~ exclusion_reason_primary,
+    sampleID == 'random' & article_id == '68' ~ exclusion_reason_secondary,
+    sampleID == 'random' & article_id == '95' ~ exclusion_reason_secondary,
+    sampleID == 'random' & article_id == '103' ~ exclusion_reason_primary,
+    sampleID == 'random' & article_id == '120' ~ exclusion_reason_primary,
+    sampleID == 'prominent' & article_id == '30' ~ exclusion_reason_secondary,
+    sampleID == 'prominent' & article_id == '49' ~ exclusion_reason_primary,
+    sampleID == 'prominent' & article_id == '66' ~ exclusion_reason_primary,
+    sampleID == 'prominent' & article_id == '98' ~ exclusion_reason_primary,
+    TRUE ~ exclusion_reason_primary
+  ))
 ```
 
-Find cases where primary and secondary coder disagreed on whether to exclude.
+Find cases where primary and secondary coder disagreed on why to exclude.
 
 ```{r}
-d_articles_prominent %>%
-  count(`1_exclusion`, `2_exclusion`)
+# we've already dealt with cases where the decision to exclude differs, so we're not looking only at cases where the decision to exclude matches, but the reason for exclusion differs
+d_articles %>%
+  filter(exclusion_primary == exclusion_secondary, 
+         exclusion_reason_primary != exclusion_reason_secondary) %>%
+  select(article_id, sampleID, exclusion_reason_primary, exclusion_reason_secondary)
+```
+We will resolve these by applying the exclusion criteria hierarchically. In other words, we use the highest level of exclusion criteria assigned by one of the two coders.
+1. Access
+2. English
+3. Retracted 
+4. Non-empirical
+
+```{r}
+# update exclusion_reason_final column when primary and secondary coder disagree on reason to exclude.
+d_articles <- d_articles %>%
+  mutate(exclusion_reason_final = case_when(
+    sampleID == 'random' & article_id == '14' ~ exclusion_reason_primary,
+    sampleID == 'random' & article_id == '35' ~ exclusion_reason_primary,
+    sampleID == 'random' & article_id == '54' ~ exclusion_reason_secondary,
+    sampleID == 'random' & article_id == '73' ~ exclusion_reason_primary,
+    sampleID == 'random' & article_id == '78' ~ exclusion_reason_primary,
+    sampleID == 'prominent' & article_id == '29' ~ "RETRACTED", # the article was withdrawn, retracted seems like the closest fit among out labels
+    sampleID == 'prominent' & article_id == '37' ~ exclusion_reason_primary,
+    sampleID == 'prominent' & article_id == '39' ~ exclusion_reason_primary,
+    sampleID == 'prominent' & article_id == '46' ~ exclusion_reason_primary,
+    sampleID == 'prominent' & article_id == '54' ~ exclusion_reason_secondary,
+    TRUE ~ exclusion_reason_final # if none of the above, retain whatever is in this column already
+  ))
+```
+Finally, let's check anything that was excluded with the reason "OTHER".
+
+```{r}
+d_articles %>% filter(exclusion_reason_final == "OTHER") %>% select(article_id, sampleID)
+```
+Article ID 68 can reclassifed as "NO ACCESS" and for the other three articles we can create a new post-hoc exclusion category "CONFERENCE ABSTRACT".
+
+```{r}
+d_articles <- d_articles %>%
+  mutate(exclusion_reason_final = case_when(
+    sampleID == 'random' & article_id == '68' ~ "NO ACCESS",
+    sampleID == 'prominent' & article_id == '2' ~ "CONFERENCE ABSTRACT",
+    sampleID == 'prominent' & article_id == '56' ~ "CONFERENCE ABSTRACT",
+    sampleID == 'prominent' & article_id == '85' ~ "CONFERENCE ABSTRACT",
+    TRUE ~ exclusion_reason_final # if none of the above, retain whatever is in this column already
+  ))
+```
+We should now have resolved coding for all exclusion decisions and exclusion reasons in d_articles
+
+```{r}
+d_articles %>%
+  count(exclusion_final, exclusion_reason_final)
 ```
 
-On first pass, it looks like we have some exclusion disagreements. Let's identify the relevant papers:
+Now for articles that are retained, we need to check if they have the same classification in `ppc_linked`.
 
 ```{r}
-d_articles_prominent %>%
-  filter(`1_exclusion` != `2_exclusion`)
+d_articles %>%
+  filter(exclusion_final == "RETAIN",
+         ppc_linked_primary != ppc_linked_secondary)
 ```
 
-Our procedure is for TEH for resolve disagreements between the primary and secondary coders.
+There appears to be one case where the primary coder did not identify any PPC links, but the secondary coder did.
+After review, TEH determines that there is a linked PPC for this article.
+Thus for this article, the final coding is the same as the secondary coder's classification, and for all other articles we use the primary coder's classification (which is the same as the secondary coders in those cases).
 
 ```{r}
-
+d_articles <- d_articles %>%
+  mutate(ppc_linked_final = case_when(
+    exclusion_final == "EXCLUDE" ~ NA_character_, # if article is excluded, use NA
+    sampleID == 'prominent' & article_id == '38' ~ ppc_linked_secondary,
+    exclusion_final == "RETAIN" & exclusion_primary == "RETAIN" ~ ppc_linked_primary,
+    exclusion_final == "RETAIN" & exclusion_secondary == "RETAIN" ~ ppc_linked_secondary,
+    TRUE ~ "ERROR" # if none of the above, retain whatever is in this column already
+  ))
+```
+```{r}
+d_articles %>%
+  count(exclusion_final,ppc_linked_final,sampleID)
 ```

### 2023-08-25 analysis/checkData.Rmd
Update checkData.Rmd

@@
 ```
+
+After removing excluded articles, there should be
+
 ```{r}
 d_articles %>%
-  count(exclusion_final,ppc_linked_final,sampleID)
+  filter(exclusion_final == "RETAIN") %>%
+  count(sampleID, coder_id_primary)
 ```

### 2023-08-25 analysis/checkData.Rmd
Update checkData.Rmd

--- 2023-08-25 analysis/checkData.Rmd
@@
 
-# Inspect articles data
+# Resolve coding disagreements in articles data
 
@@
 ```
+# Resolve coding disagreements in journals data
+
 ```{r}
-d_articles %>%
-  count(exclusion_final,ppc_linked_final,sampleID)
+d_journals %>%
+  group_by(journal) %>%
+  summarise(num_unique_emp = n_distinct(anyPPC), unique_emp = toString(unique(anyPPC))) %>%
+  filter(num_unique_prices > 1)
+
 ```

### 2023-08-25 analysis/checkData.Rmd
Update checkData.Rmd

@@
   group_by(journal) %>%
-  summarise(num_unique_emp = n_distinct(anyPPC), unique_emp = toString(unique(anyPPC))) %>%
-  filter(num_unique_prices > 1)
+  summarise(unique_responses = n_distinct(anyPPC)) %>% # get the number of unique responses to this Q (should be 1 if they match)
+  filter(unique_responses > 1)
 

### 2023-08-29 analysis/practiceCoding_AW.Rmd
AW practice code

---
title: "Results from Primary Coding"
author: "Annie Whamond"
date: "2023-08-28"
output: html_document
---

#Prelim results and visualisations for d_journals

```{r}
#Genarate table to assess anyPPC

d_primaryONLY <- d_journals %>%
  filter(coder_id == "AW" | coder_id == "NM") %>%
  filter(journal_empirical == "Yes") %>%
  group_by(journal) %>%
  distinct(journal, .keep_all = TRUE)

 table(d_primaryONLY$sampleID, d_primaryONLY$anyPPC)

 table(d_primaryONLY$sampleID)
```

#Look at limitations for anyPPC = YES
```{r}

 d_PPConly <- d_primaryONLY %>%
   filter(anyPPC == "YES")

#Look at stated length limits
PPC_length <- d_PPConly %>%
  filter(ppc_length_A != "NO") %>%
  filter(ppc_length_A != "NOT STATED")

table(PPC_length$ppc_length_A)
table(PPC_length$ppc_length_B)

#Look at stated time limits

PPC_time <- d_PPConly %>%
  filter(ppc_time_A != "NOT STATED")

table(PPC_time$ppc_time_A)

```

#Add COPE status
```{r}
dj_random <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F) %>%
  slice_head(n = 108) %>%
  select(`Journal`, 'COPE' = 'COPE (T = member; F = not a member)')

dj_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F) %>%
  slice_head(n = 114) %>%
  select('Journal' = `Journal name`, 'COPE' = 'COPE (T = member; F = not a member)' )

dj_cope <- left_join()

#Code from checkData.RMD for extracting JIFs
d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal')

journal_list_random_all <- journal_list_random_all %>%
  select(journal = Journal, WOS_first_psych_category)

d_journals_random <- left_join(d_journals_random, journal_list_random_all, by = 'journal')

journal_list_prominent_all <- journal_list_prominent_all %>%
  select(-WOS_first_psych_category)

d_journals_random <- left_join(d_journals_random, journal_list_prominent_all, by = 'journal')

tmp <- d_journals_random %>% filter(is.na(`2021 JIF`)) %>% distinct(journal, .keep_all = T)
write_csv(tmp,here('data', 'prepareSample', 'journals', '02 - modified', 'we_need_jifs.csv'))

```

### 2023-08-29 analysis/checkData.Rmd
Update checkData.Rmd

--- 2023-08-25 analysis/checkData.Rmd
@@
          anyPPC = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
-         ppc_name_A = `A. Enter the name of the PPC type offered by the journal:`,
-         ppc_name_B = `B. Enter the name of the PPC type offered by the journal:`,
-         ppc_name_C = `C. Enter the name of the PPC type offered by the journal:`,
-         ppc_description_A = `A. Enter the verbatim description of this type of PPC provided by the journal`,
-         ppc_description_B = `B. Enter the verbatim description of this type of PPC provided by the journal`,
-         ppc_description_C = `C. Enter the verbatim description of this type of PPC provided by the journal`,
-         ppc_length_A = `A. Are there any length limits for this type of PPC?`,
-         ppc_length_B = `B. Are there any length limits for this type of PPC?`,
-         ppc_length_C = `C. Are there any length limits for this type of PPC?`,
-         ppc_time_A = `A. Are there any time limits for submission of this type of PPC?`,
-         ppc_time_B = `B. Are there any time limits for submission of this type of PPC?`,
-         ppc_time_C = `C. Are there any time limits for submission of this type of PPC?`,
-         ppc_ref_A = `A. Are there any reference limits for this type of PPC?`,
-         ppc_ref_B = `B. Are there any reference limits for this type of PPC?`,
-         ppc_ref_C = `C. Are there any reference limits for this type of PPC?`,
-         ppc_review_A = `A. Is this type of PPC sent for independent external peer review?`,
-         ppc_review_B = `B. Is this type of PPC sent for independent external peer review?`,
-         ppc_review_C = `C. Is this type of PPC sent for independent external peer review?`,
-         ppc_note_A = `A. Anything additional, unusual, or interesting to note?`,
-         ppc_note_B = `B. Anything additional, unusual, or interesting to note?`,
-         ppc_note_C = `C. Anything additional, unusual, or interesting to note?`,
+         A_ppc_name = `A. Enter the name of the PPC type offered by the journal:`,
+         B_ppc_name = `B. Enter the name of the PPC type offered by the journal:`,
+         C_ppc_name = `C. Enter the name of the PPC type offered by the journal:`,
+         A_ppc_description = `A. Enter the verbatim description of this type of PPC provided by the journal`,
+         B_ppc_description = `B. Enter the verbatim description of this type of PPC provided by the journal`,
+         C_ppc_description = `C. Enter the verbatim description of this type of PPC provided by the journal`,
+         A_ppc_length = `A. Are there any length limits for this type of PPC?`,
+         B_ppc_length = `B. Are there any length limits for this type of PPC?`,
+         C_ppc_length = `C. Are there any length limits for this type of PPC?`,
+         A_ppc_time = `A. Are there any time limits for submission of this type of PPC?`,
+         B_ppc_time = `B. Are there any time limits for submission of this type of PPC?`,
+         C_ppc_time = `C. Are there any time limits for submission of this type of PPC?`,
+         A_ppc_ref = `A. Are there any reference limits for this type of PPC?`,
+         B_ppc_ref = `B. Are there any reference limits for this type of PPC?`,
+         C_ppc_ref = `C. Are there any reference limits for this type of PPC?`,
+         A_ppc_review = `A. Is this type of PPC sent for independent external peer review?`,
+         B_ppc_review = `B. Is this type of PPC sent for independent external peer review?`,
+         C_ppc_review = `C. Is this type of PPC sent for independent external peer review?`,
+         A_ppc_note = `A. Anything additional, unusual, or interesting to note?`,
+         B_ppc_note = `B. Anything additional, unusual, or interesting to note?`,
+         C_ppc_note = `C. Anything additional, unusual, or interesting to note?`,
          general_note = `Anything additional, unusual, or interesting to note?`,
@@
 
-Check every row has an entry in `timestamps`.
-
-```{r}
-assert_that(
-  all(!is.na(d_journals$timestamps)),
-  msg = "Found missing timestamps"
-)
-```
-
 Check we have the expected coder initials in `coder_id` and convert column to factor.
@@
 ```{r}
-expected_coders <- c("AW", "NM", "SV", "RTT", "TEH", "SS", "BC")
+expected_coders <- c("AW", "NM", "SV", "RTT", "TEH", "SS", "BC", "FINAL (TEH)")
 
@@
 
+Note — its easier to do this in the original spreadsheet — for each journal I've added a new row with coder initials "FINAL (TEH)".
+If primary and secondary coding are aligned I just copied their coding into this row.
+If there were differences, I resolved them and entered the final decision into the new row.
+
+Make a tibble containing only the final coding for journals.\
+
 ```{r}
-d_journals %>%
-  group_by(journal) %>%
-  summarise(num_unique_emp = n_distinct(anyPPC), unique_emp = toString(unique(anyPPC))) %>%
-  filter(num_unique_prices > 1)
+d_journals_final <- d_journals %>%
+  filter(coder_id == "FINAL (TEH)") %>% # select only the final coding
+  select(-coder_id, -timestamps) # drop the coder_id and timestamps columns
+```
+# Journals data - exclusions
 
+```{r}
+d_journals_final_eligible <- d_journals_final %>%
+  filter(journal_empirical == "Yes") %>%
+  select(-journal_empirical)
 ```
+
+# Journals data — reorganise
+
+Currently we have one row per journal, and sometimes more than one PPC per journal.
+To make analysis easier, let's switch the data frame from wide to long format (i.e., switch to one row per PPC instead of one row per journal).
+
+```{r}
+d_journals_final_eligible <- d_journals_final_eligible %>%
+  pivot_longer( # pivot to long format
+    cols = c(-journal,-sampleID, -anyPPC,-general_note),
+    names_to = c("PPC_type", ".value"), 
+    names_sep = "_ppc_"
+  )
+```
+
+# Journals data — Harmonization
+
+# Harmonize length limits
+
+Journals used different units to report length limits (e.g., pages, lines, characters, words). We will convert these various units to words using the following approximations.
+
+```{r}
+pageToWord <- 500 # using our own recent papers as a guide, we estimate one page to be approximately 500 words. Thus, any limits stated with page units need to be multiplied by 500 to convert to words
+charToWord <- 6 # using our own recent papers as a guide, we estimate an average of 6 characters per word. Thus, any limits stated with character units need to be divided by 6 to convert to words
+linesToWord <- 10 # after inspecting articles published by journals that use line units, we estimate an average of 10 words per line.
+Thus any limits stated with line units need to be multiplied by ten to convert to words
+```
+
+We will also harmonize differences in data entry formatting, e.g., some coders used quotation marks, commas etc. Any qualitative limits will be designated as such.
+
+```{r}
+d_journals_final_eligible <- d_journals_final_eligible %>% 
+  mutate(length_harmonized = str_remove_all(length, pattern = '"'), #  remove any quotation marks
+         length_harmonized = str_remove(wordLimits, pattern = fixed("YES (copy and paste the limits in the 'other' section below), "))), # remove data entry question text
+```
+
+policyData <- policyData %>%
+  mutate(wordLimits = str_remove_all(wordLimits, pattern = '"'), #  remove any quotation marks
+         wordLimits = str_remove(wordLimits, pattern = fixed('YES (provide number of words/comments below), ')), # remove option text
+         wordLimits = case_when(
+           wordLimits == 'not more than 1000 words and 2 pages' ~ as.character(2*pageToWord),
+
+# Harmonize PPC names
+
+Currently the PPC names are copied verbatim from the journal websites but many of them are basically the same name with small grammatical differences (e.g., letters, letter to the editor etc.).
+For analysis, we need to harmonize these names.
+
+Firstly, we will harmonize names that are grammatically similar.
+We will then examine conceptual similarity and see if we can summarise the types into a few high level categories.
+A guiding assumption here is that we can capture most PPC types with three categories (based on personal experience and empirical data, Hardwicke et al.
+2022):
+
+* letters to the editor - tend to be shorter articles
+* commentaries - tend to be longer articles
+* web comments - tend be to be short informal comments, usually appearing below articles on the journal website
+
+If PPCs we have identified clearly do not fit into these categories, we will categorize them as "OTHER".
+
+Firstly, specify PPC names that we want to convert to different haromized names.
+
+```{r}
+commentaries <- c("Brief comment", "Brief Comment")
+letters <- c(
+
+)
+web_comments <- c()
+```
+
+```{r}
+d_journals_final_eligible %>%
+  mutate(name_harmonized = )
+```
+
+In Emotion, one line seems to be about ten words. So 260 lines is 2600 words.
 

### 2023-08-29 analysis/practiceCoding_AW.Rmd
Added descriptive labels

@@
 
-#Prelim results and visualisations for d_journals
+#Prelim results and visualisations for d_journals using Primary coding data only
 
@@
 d_primaryONLY <- d_journals %>%
-  filter(coder_id == "AW" | coder_id == "NM") %>%
-  filter(journal_empirical == "Yes") %>%
+  filter(coder_id == "AW" | coder_id == "NM") %>% #keeps only entries with primary coder initials from main data tibble d_journals
+  filter(journal_empirical == "Yes") %>%          #removes ineligible journals (not empirical)
   group_by(journal) %>%
-  distinct(journal, .keep_all = TRUE)
+  distinct(journal, .keep_all = TRUE)             #keeps only distinct journal entries
 
@@
 
+# Removes journals that do not offer any PPC 
  d_PPConly <- d_primaryONLY %>%
@@
 ```{r}
-dj_random <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F) %>%
+# Load googlesheet data
+
+dj_prominent <- read_csv(here('data','raw', 'journalList_PROMINENT.csv')) %>% #loads csv of googlesheet data of prominent journals
+  slice_head(n = 114) %>%
+  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
+
+dj_random <- read_csv(here('data','raw', 'journalList_RANDOM.csv')) %>% #loads csv of googlesheet data of random journals
   slice_head(n = 108) %>%
-  select(`Journal`, 'COPE' = 'COPE (T = member; F = not a member)')
+  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
 
-dj_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F) %>%
-  slice_head(n = 114) %>%
-  select('Journal' = `Journal name`, 'COPE' = 'COPE (T = member; F = not a member)' )
+# Combine above CSVs to one tibble
 
-dj_cope <- left_join()
+dj_cope <- bind_rows(dj_prominent, dj_random)
 
-#Code from checkData.RMD for extracting JIFs
+# Identify duplicate rows
+duplicates <- duplicated(dj_cope)
+
+# Select the duplicate rows
+duplicate_rows <- dj_cope[duplicates, ]
+
+# Check if duplicate rows have the same COPE values for journals
+for (i in seq_len(nrow(duplicate_rows))) {
+  row <- duplicate_rows[i, ]
+  id <- row$ID
+  value <- row$Value
+  same_values <- all(duplicate_rows$Value[duplicate_rows$ID == id] == value)
+
+  if (same_values) {
+    cat("Row", i, "with ID =", id, "has the same values in both columns.\n")
+  } else {
+    cat("Row", i, "with ID =", id, "has different values in both columns.\n")
+  }
+}
+
+#All 14 duplicated (both sample) journals had consistent COPE status, join with main data tibble:
+d_cope <- left_join(d_journals, dj_cope, by = 'journal')
+
+```
+
+#join() Code from checkData.RMD for importing JIFs and category
+
 d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal')

### 2023-08-29 analysis/checkData.Rmd
Update checkData.Rmd

@@
 
-# Harmonize length limits
+## Harmonize length limits
 
@@
   mutate(length_harmonized = str_remove_all(length, pattern = '"'), #  remove any quotation marks
-         length_harmonized = str_remove(wordLimits, pattern = fixed("YES (copy and paste the limits in the 'other' section below), "))), # remove data entry question text
+         length_harmonized = str_remove(length_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
+         length_harmonized = case_when(
+           length_harmonized == "1,000 words" ~ "1000",
+           length_harmonized == "1,500 words (one figure and/or one table allowed within word count)" ~ "1500",
+           length_harmonized == "1000 words" ~ "1000",
+           length_harmonized == "16 pages" ~ as.character(16*pageToWord),
+           length_harmonized == "2000 words" ~ "2000",
+           length_harmonized == "265 lines of text including references" ~ as.character(265*linesToWord),
+           length_harmonized == "3500 words (title page and references included)" ~ "3500",
+           length_harmonized == "400 words" ~ "400",
+           length_harmonized == "5 pages, including abstract, references, tables, and figures." ~ as.character(5*pageToWord),
+           length_harmonized == "500 words" ~ "500",
+           length_harmonized == "600-800 words" ~ "800",
+           length_harmonized == "750 words" ~ "750",
+           length_harmonized == "Approx. 1,000 words" ~ "1000",
+           length_harmonized == "approximately 1,000 words" ~ "1000",
+           length_harmonized == "as concise as possible, and ideally not exceed 1,200 words" ~ "1200",
+           length_harmonized == "at maximum half the length of the target article." ~ "Qualitative",
+           length_harmonized == "Maximum length: 1100 words." ~ "1100",
+           length_harmonized == "short" ~ "Qualitative",
+           length_harmonized == "up to 2,000 words counting 500 words per table and figure" ~ "2000",
+           TRUE ~ length_harmonized
+         )) 
 ```
 
-policyData <- policyData %>%
-  mutate(wordLimits = str_remove_all(wordLimits, pattern = '"'), #  remove any quotation marks
-         wordLimits = str_remove(wordLimits, pattern = fixed('YES (provide number of words/comments below), ')), # remove option text
-         wordLimits = case_when(
-           wordLimits == 'not more than 1000 words and 2 pages' ~ as.character(2*pageToWord),
+## Harmonize time-to-submit limits
 
-# Harmonize PPC names
+Journals used different units to report time limits (e.g., weeks, months, years). We will convert these various units to weeks using the following approximations.
+
+```{r}
+monthToWeek <- 4.35 # number to multiply months by to get weeks
+yearToWeek <- 52 # number to multiply years by to get weeks
+```
+
+We will also harmonize differences in data entry formatting, e.g., some coders used quotation marks, commas etc. Any qualitative limits will be designated as such.
+
+```{r}
+d_journals_final_eligible <- d_journals_final_eligible %>% 
+  mutate(time_harmonized = str_remove_all(time, pattern = '"'), #  remove any quotation marks
+         time_harmonized = str_remove(time_harmonized, pattern = fixed("YES (provide detail of time limits below), ")),# remove data entry question text
+         time_harmonized = case_when(
+           time_harmonized == "3 months" ~ as.character(3*monthToWeek),
+           time_harmonized == "6 months" ~ as.character(6*monthToWeek),
+           time_harmonized == "9 months" ~ as.character(9*monthToWeek),
+           time_harmonized == "Draft proposed comments will be due on a tight time- line (i.e., 2– 4 weeks after solicitation), to be determined by the Editor." ~ "4",
+           time_harmonized == "he Commentary mechanism is most effective when used to address a contemporary publication" ~ "Qualitative",
+           time_harmonized == "Matters Arising articles are interesting and timely scientific or academic comments" ~ "Qualitative",
+           time_harmonized == "recent" ~ "Qualitative",
+           time_harmonized == "recently published" ~ "Qualitative",
+           time_harmonized == "UNCLEAR (provide detail in the 'other' section below), recently published" ~ "Qualitative",
+           time_harmonized == "YES (copy and paste the limits in the 'other' section below), 1-year (except for a test of replication)" ~ as.character(1*yearToWeek),
+           TRUE ~ time_harmonized
+         )) 
+```
+
+## Harmonize PPC names
 

### 2023-08-29 analysis/checkData.Rmd
Code to COPE status
currently alters primary coded values only

--- 2023-08-29 analysis/checkData.Rmd
@@
 
+#Add COPE status FROM PRACTICE CODING, does not alter main d_journals tibble
+```{r}
+# Load googlesheet data
+
+dj_prominent <- read_csv(here('data','raw', 'journalList_PROMINENT.csv')) %>% #loads csv of googlesheet data of prominent journals
+  slice_head(n = 114) %>%
+  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
+
+dj_random <- read_csv(here('data','raw', 'journalList_RANDOM.csv')) %>% #loads csv of googlesheet data of random journals
+  slice_head(n = 108) %>%
+  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
+
+# Combine above CSVs to one tibble
+
+dj_cope <- bind_rows(dj_prominent, dj_random)
+
+# Identify duplicate rows
+duplicates <- duplicated(dj_cope)
+
+# Select the duplicate rows
+duplicate_rows <- dj_cope[duplicates, ]
+
+# Check if duplicate rows have the same COPE values for journals
+for (i in seq_len(nrow(duplicate_rows))) {
+  row <- duplicate_rows[i, ]
+  id <- row$ID
+  value <- row$Value
+  same_values <- all(duplicate_rows$Value[duplicate_rows$ID == id] == value)
+
+  if (same_values) {
+    cat("Row", i, "with ID =", id, "has the same values in both columns.\n")
+  } else {
+    cat("Row", i, "with ID =", id, "has different values in both columns.\n")
+  }
+}
+
+#All 14 duplicated (both sample) journals had consistent COPE status, remove duplicates
+dj_cope <- distinct(dj_cope, journal, .keep_all = T)
+
+#join with main data tibble:
+d_primaryONLY <- left_join(d_primaryONLY, dj_cope, by = 'journal')
+
+```
+
 # Resolve coding disagreements in articles data

### 2023-08-29 analysis/checkData.Rmd
corrected csv names

@@
 
-dj_prominent <- read_csv(here('data','raw', 'journalList_PROMINENT.csv')) %>% #loads csv of googlesheet data of prominent journals
+dj_prominent <- read_csv(here('data','raw', 'journals-prominent.csv')) %>% #loads csv of googlesheet data of prominent journals
   slice_head(n = 114) %>%
@@
 
-dj_random <- read_csv(here('data','raw', 'journalList_RANDOM.csv')) %>% #loads csv of googlesheet data of random journals
+dj_random <- read_csv(here('data','raw', 'journals-random.csv')) %>% #loads csv of googlesheet data of random journals
   slice_head(n = 108) %>%

### 2023-08-29 analysis/checkData.Rmd

--- 2023-08-29 analysis/checkData.Rmd
@@
 
+#Add COPE status FROM PRACTICE CODING, does not alter main d_journals tibble
+```{r}
+# Load googlesheet data
+
+dj_prominent <- read_csv(here('data','raw', 'journals-prominent.csv')) %>% #loads csv of googlesheet data of prominent journals
+  slice_head(n = 114) %>%
+  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
+
+dj_random <- read_csv(here('data','raw', 'journals-random.csv')) %>% #loads csv of googlesheet data of random journals
+  slice_head(n = 108) %>%
+  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
+
+# Combine above CSVs to one tibble
+
+dj_cope <- bind_rows(dj_prominent, dj_random)
+
+# Identify duplicate rows
+duplicates <- duplicated(dj_cope)
+
+# Select the duplicate rows
+duplicate_rows <- dj_cope[duplicates, ]
+
+# Check if duplicate rows have the same COPE values for journals
+for (i in seq_len(nrow(duplicate_rows))) {
+  row <- duplicate_rows[i, ]
+  id <- row$ID
+  value <- row$Value
+  same_values <- all(duplicate_rows$Value[duplicate_rows$ID == id] == value)
+
+  if (same_values) {
+    cat("Row", i, "with ID =", id, "has the same values in both columns.\n")
+  } else {
+    cat("Row", i, "with ID =", id, "has different values in both columns.\n")
+  }
+}
+
+#All 14 duplicated (both sample) journals had consistent COPE status, remove duplicates
+dj_cope <- distinct(dj_cope, journal, .keep_all = T)
+
+#join with main data tibble:
+d_primaryONLY <- left_join(d_primaryONLY, dj_cope, by = 'journal')
+
+```
+
 # Resolve coding disagreements in articles data

### 2023-08-29 analysis/checkData.Rmd
Update checkData.Rmd

@@
 
-#Add COPE status FROM PRACTICE CODING, does not alter main d_journals tibble
-```{r}
-# Load googlesheet data
-
-dj_prominent <- read_csv(here('data','raw', 'journals-prominent.csv')) %>% #loads csv of googlesheet data of prominent journals
-  slice_head(n = 114) %>%
-  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
-
-dj_random <- read_csv(here('data','raw', 'journals-random.csv')) %>% #loads csv of googlesheet data of random journals
-  slice_head(n = 108) %>%
-  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
-
-# Combine above CSVs to one tibble
-
-dj_cope <- bind_rows(dj_prominent, dj_random)
-
-# Identify duplicate rows
-duplicates <- duplicated(dj_cope)
-
-# Select the duplicate rows
-duplicate_rows <- dj_cope[duplicates, ]
-
-# Check if duplicate rows have the same COPE values for journals
-for (i in seq_len(nrow(duplicate_rows))) {
-  row <- duplicate_rows[i, ]
-  id <- row$ID
-  value <- row$Value
-  same_values <- all(duplicate_rows$Value[duplicate_rows$ID == id] == value)
-
-  if (same_values) {
-    cat("Row", i, "with ID =", id, "has the same values in both columns.\n")
-  } else {
-    cat("Row", i, "with ID =", id, "has different values in both columns.\n")
-  }
-}
-
-#All 14 duplicated (both sample) journals had consistent COPE status, remove duplicates
-dj_cope <- distinct(dj_cope, journal, .keep_all = T)
-
-#join with main data tibble:
-d_primaryONLY <- left_join(d_primaryONLY, dj_cope, by = 'journal')
-
-```
-
 # Resolve coding disagreements in articles data
@@
 
+## Harmonize reference limits
+
+For reference limits we need to harmonize differences in data entry formatting.
+Additionally, when references are included in the overall length limit, we will re-code these as "NOT STATED", because no specific reference limit has been stated.
+
+```{r}
+d_journals_final_eligible <- d_journals_final_eligible %>% 
+  mutate(ref_harmonized = str_remove_all(ref, pattern = '"'), #  remove any quotation marks
+         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (provide number of references below), ")),# remove data entry question text
+         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
+         ref_harmonized = case_when(
+           ref_harmonized == "20 not hard-and-fast limits" ~ "20",
+           ref_harmonized == "265 lines of text including references" ~ "NOT STATED",
+           ref_harmonized == "contributions may have up to 15 references" ~ "15",
+           ref_harmonized == "Included in 16 page overall limit" ~ "NOT STATED",
+           ref_harmonized == "No more than 5 references" ~ "5",
+           ref_harmonized == "overall limit is 265 lines of text including references" ~ "NOT STATED",
+           TRUE ~ ref_harmonized
+         )) 
+```
+
 ## Harmonize PPC names
@@
 
-Firstly, specify PPC names that we want to convert to different haromized names.
+Firstly, specify PPC names that we want to convert to different harmonized names.
 
 ```{r}
-commentaries <- c("Brief comment", "Brief Comment")
-letters <- c(
-
-)
-web_comments <- c()
+commentaries <- c("Brief comment", "Brief Comment", "commentaries", "Commentaries", "Commentary", "Comments", "Matters Arising", "Observations & Commentaries", "Open peer commentaries", "Short Communications and Commentaries", "Short Research Notes", "Text review")
+letters <- c("Letter", "Letters", "Letter to the editor", "Letters to the editor", "letters to the editor", "Letters to the Editor.", "letters to the editors", "Letters to the Editors")
+# web_comments <- c()
+other <- c("Verification reports")
 ```
@@
 ```{r}
-d_journals_final_eligible %>%
-  mutate(name_harmonized = )
+d_journals_final_eligible <- d_journals_final_eligible %>%
+  mutate(name_harmonized = case_when(
+    name %in% commentaries ~ "Commentary",
+    name %in% letters ~ "Letters",
+    name %in% other ~ "Other"
+  ))
 ```
-
-In Emotion, one line seems to be about ten words. So 260 lines is 2600 words.
 

### 2023-08-29 analysis/checkData.Rmd
Update checkData.Rmd

@@
 
-## Identify JIFs for journals
-
-```{r}
-d_journals_prominent <- d_journals %>%
-  filter(sampleID %in% c('prominent', 'both'))
-
-d_journals_random <- d_journals %>%
-  filter(sampleID == 'random')
-
-journal_list_prominent_all <- journal_list_prominent_all %>% 
-  select(journal = `Journal name`, `2021 JIF`, WOS_first_psych_category)
-
-d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal')
-
-journal_list_random_all <- journal_list_random_all %>%
-  select(journal = Journal, WOS_first_psych_category)
-
-d_journals_random <- left_join(d_journals_random, journal_list_random_all, by = 'journal')
-
-journal_list_prominent_all <- journal_list_prominent_all %>%
-  select(-WOS_first_psych_category)
-
-d_journals_random <- left_join(d_journals_random, journal_list_prominent_all, by = 'journal')
-
-tmp <- d_journals_random %>% filter(is.na(`2021 JIF`)) %>% distinct(journal, .keep_all = T)
-write_csv(tmp,here('data', 'prepareSample', 'journals', '02 - modified', 'we_need_jifs.csv'))
-```
-
-#Add COPE status FROM PRACTICE CODING, does not alter main d_journals tibble
-```{r}
-# Load googlesheet data
-
-dj_prominent <- read_csv(here('data','raw', 'journals-prominent.csv')) %>% #loads csv of googlesheet data of prominent journals
-  slice_head(n = 114) %>%
-  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
-
-dj_random <- read_csv(here('data','raw', 'journals-random.csv')) %>% #loads csv of googlesheet data of random journals
-  slice_head(n = 108) %>%
-  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
-
-# Combine above CSVs to one tibble
-
-dj_cope <- bind_rows(dj_prominent, dj_random)
-
-# Identify duplicate rows
-duplicates <- duplicated(dj_cope)
-
-# Select the duplicate rows
-duplicate_rows <- dj_cope[duplicates, ]
-
-# Check if duplicate rows have the same COPE values for journals
-for (i in seq_len(nrow(duplicate_rows))) {
-  row <- duplicate_rows[i, ]
-  id <- row$ID
-  value <- row$Value
-  same_values <- all(duplicate_rows$Value[duplicate_rows$ID == id] == value)
-
-  if (same_values) {
-    cat("Row", i, "with ID =", id, "has the same values in both columns.\n")
-  } else {
-    cat("Row", i, "with ID =", id, "has different values in both columns.\n")
-  }
-}
-
-#All 14 duplicated (both sample) journals had consistent COPE status, remove duplicates
-dj_cope <- distinct(dj_cope, journal, .keep_all = T)
-
-#join with main data tibble:
-d_primaryONLY <- left_join(d_primaryONLY, dj_cope, by = 'journal')
-
-```
-
 # Resolve coding disagreements in articles data
@@
 ```
+
 Finally, let's check anything that was excluded with the reason "OTHER".
@@
 ```
+
 Article ID 68 can reclassifed as "NO ACCESS" and for the other three articles we can create a new post-hoc exclusion category "CONFERENCE ABSTRACT".
@@
 ```
+
 We should now have resolved coding for all exclusion decisions and exclusion reasons in d_articles
@@
 ```
+
 # Resolve coding disagreements in journals data
@@
 ```
+
 # Journals data - exclusions
@@
 
+## Harmonize peer review polic
+
+For PPC peer review policy we need to harmonize differences in data entry formatting.
+
+```{r}
+d_journals_final_eligible <- d_journals_final_eligible %>% 
+  mutate(review_harmonized = str_remove_all(review, pattern = '"'), #  remove any quotation marks
+         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (provide number of references below), ")),# remove data entry question text
+         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
+         ref_harmonized = case_when(
+           ref_harmonized == "20 not hard-and-fast limits" ~ "20",
+           ref_harmonized == "265 lines of text including references" ~ "NOT STATED",
+           ref_harmonized == "contributions may have up to 15 references" ~ "15",
+           ref_harmonized == "Included in 16 page overall limit" ~ "NOT STATED",
+           ref_harmonized == "No more than 5 references" ~ "5",
+           ref_harmonized == "overall limit is 265 lines of text including references" ~ "NOT STATED",
+           TRUE ~ ref_harmonized
+         )) 
+```
+
 ## Harmonize PPC names
@@
 
+# Journals data — add JIF and COPE
+
+## Identify JIFs for journals
+
+For the random journals we can find the JIFs in the prominent journal sample.
+Some journals do not have a JIF because they haven't been indexed long enough.
+We manually checked all of these journals.
+One JIF needed to be added manually for the journal "Journal of Psychology and Theology".
+The 2021 JIF for this journal is .80.
+
+```{r}
+d_journals_prominent <- d_journals %>%
+  filter(sampleID %in% c('prominent', 'both'))
+
+d_journals_random <- d_journals %>%
+  filter(sampleID == 'random')
+
+journal_list_prominent_all <- journal_list_prominent_all %>% 
+  select(journal = `Journal name`, `2021 JIF`, WOS_first_psych_category)
+
+d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal')
+
+journal_list_random_all <- journal_list_random_all %>%
+  select(journal = Journal, WOS_first_psych_category)
+
+d_journals_random <- left_join(d_journals_random, journal_list_random_all, by = 'journal')
+
+journal_list_prominent_all <- journal_list_prominent_all %>%
+  select(-WOS_first_psych_category)
+
+d_journals_random <- left_join(d_journals_random, journal_list_prominent_all, by = 'journal')
+
+tmp <- d_journals_random %>% filter(is.na(`2021 JIF`)) %>% distinct(journal, .keep_all = T)
+write_csv(tmp,here('data', 'prepareSample', 'journals', '02 - modified', 'we_need_jifs.csv'))
+```
+
+#Add COPE status FROM PRACTICE CODING, does not alter main d_journals tibble
+```{r}
+# Load googlesheet data
+
+dj_prominent <- read_csv(here('data','raw', 'journals-prominent.csv')) %>% #loads csv of googlesheet data of prominent journals
+  slice_head(n = 114) %>%
+  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
+
+dj_random <- read_csv(here('data','raw', 'journals-random.csv')) %>% #loads csv of googlesheet data of random journals
+  slice_head(n = 108) %>%
+  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
+
+# Combine above CSVs to one tibble
+
+dj_cope <- bind_rows(dj_prominent, dj_random)
+
+# Identify duplicate rows
+duplicates <- duplicated(dj_cope)
+
+# Select the duplicate rows
+duplicate_rows <- dj_cope[duplicates, ]
+
+# Check if duplicate rows have the same COPE values for journals
+for (i in seq_len(nrow(duplicate_rows))) {
+  row <- duplicate_rows[i, ]
+  id <- row$ID
+  value <- row$Value
+  same_values <- all(duplicate_rows$Value[duplicate_rows$ID == id] == value)
+
+  if (same_values) {
+    cat("Row", i, "with ID =", id, "has the same values in both columns.\n")
+  } else {
+    cat("Row", i, "with ID =", id, "has different values in both columns.\n")
+  }
+}
+
+#All 14 duplicated (both sample) journals had consistent COPE status, remove duplicates
+dj_cope <- distinct(dj_cope, journal, .keep_all = T)
+
+#join with main data tibble:
+d_primaryONLY <- left_join(d_primaryONLY, dj_cope, by = 'journal')
+
+```
+
 # Final tests

### 2023-08-29 analysis/checkData.Rmd
Update checkData.Rmd

@@
 
-## Harmonize peer review polic
+## Harmonize peer review policies
 
@@
 d_journals_final_eligible <- d_journals_final_eligible %>% 
-  mutate(review_harmonized = str_remove_all(review, pattern = '"'), #  remove any quotation marks
-         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (provide number of references below), ")),# remove data entry question text
-         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
-         ref_harmonized = case_when(
-           ref_harmonized == "20 not hard-and-fast limits" ~ "20",
-           ref_harmonized == "265 lines of text including references" ~ "NOT STATED",
-           ref_harmonized == "contributions may have up to 15 references" ~ "15",
-           ref_harmonized == "Included in 16 page overall limit" ~ "NOT STATED",
-           ref_harmonized == "No more than 5 references" ~ "5",
-           ref_harmonized == "overall limit is 265 lines of text including references" ~ "NOT STATED",
-           TRUE ~ ref_harmonized
+  mutate(review_harmonized = case_when(
+           review_harmonized == "NO, This correspondence is published at the discretion of the Editor-in-Chief and the Associate Editors" ~ "NO",
+           review_harmonized == "NOT STATED, The guidelines discuss peer review, but it appears that this discussion isn't relevant to commentary articles." ~ "NOT STATED",
+           review_harmonized == "UNCLEAR (provide detail in the 'other' section below), It 'may' be sent for independent review: 'Matters Arising submissions that meet the journal’s criteria are sent to the authors of the original paper for a formal response.
+The comments and formal response may then be sent to independent referees.'" ~ "YES",
+           TRUE ~ review_harmonized
          )) 

### 2023-08-29 analysis/checkData.Rmd
Update checkData.Rmd

@@
 d_journals <- read_csv(here('data','raw','Data Extraction Form (policy) (Responses) - Form Responses 1.csv'), show_col_types = F)
-```
-
-There is some information about the sample that isn't included in the extracted data files (e.g., JIFs, Web of Science subject category), so we need to load some of that information from the original sample files.
-
-```{r}
-# list of journals in random sample
-journal_list_random <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F) %>%
-  slice_head(n = 108) %>%
-  select(`Journal`)
-
-# list of journals in prominent sample
-journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F) %>%
-  slice_head(n = 114) %>%
-  select('Journal' = `Journal name`)
-
-# list of all prominent journals (some not in sample)
-journal_list_prominent_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F)
-
-# list of all random journals (some not in sample)
-journal_list_random_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F)
 ```
@@
   mutate(review_harmonized = case_when(
-           review_harmonized == "NO, This correspondence is published at the discretion of the Editor-in-Chief and the Associate Editors" ~ "NO",
-           review_harmonized == "NOT STATED, The guidelines discuss peer review, but it appears that this discussion isn't relevant to commentary articles." ~ "NOT STATED",
-           review_harmonized == "UNCLEAR (provide detail in the 'other' section below), It 'may' be sent for independent review: 'Matters Arising submissions that meet the journal’s criteria are sent to the authors of the original paper for a formal response.
+           review == "NO, This correspondence is published at the discretion of the Editor-in-Chief and the Associate Editors" ~ "NO",
+           review == "NOT STATED, The guidelines discuss peer review, but it appears that this discussion isn't relevant to commentary articles." ~ "NOT STATED",
+           review == "UNCLEAR (provide detail in the 'other' section below), It 'may' be sent for independent review: 'Matters Arising submissions that meet the journal’s criteria are sent to the authors of the original paper for a formal response.
 The comments and formal response may then be sent to independent referees.'" ~ "YES",
-           TRUE ~ review_harmonized
+           TRUE ~ review
          )) 
@@
 # Journals data — add JIF and COPE
+
+There is some information about the sample that isn't included in the extracted data files (e.g., JIFs, Web of Science subject category), so we need to load some of that information from the original sample files.
+
+```{r}
+# list of journals in random sample
+journal_list_random <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F) %>%
+  slice_head(n = 108) %>%
+  select(`Journal`)
+
+# list of journals in prominent sample
+journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F) %>%
+  slice_head(n = 114) %>%
+  select('Journal' = `Journal name`)
+
+# list of all prominent journals (some not in sample)
+journal_list_prominent_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F)
+
+# list of all random journals (some not in sample)
+journal_list_random_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F)
+```
 

### 2023-08-29 analysis/checkData.Rmd
Update checkData.Rmd
moved initial processing of raw data files to raw_to_primary.R
this script now loads in the primary data files

@@
 ```{r}
-# article data (random)
-d_articles_random <- read_csv(here('data','raw','articles (random) - Sheet1.csv'), show_col_types = F) %>%
-  filter(!is.na(`primary coder initials`) & !is.na(`secondary coder initials`)) # we only need articles that were coded by someone
-
-# article data (prominent)
-d_articles_prominent <- read_csv(here('data','raw','articles (prominent) - Sheet1.csv'), show_col_types = F)  %>%
-  filter(!is.na(`primary coder initials`) & !is.na(`secondary coder initials`)) # we only need articles that were coded by someone
-
-# journal data (random and prominent sample)
-d_journals <- read_csv(here('data','raw','Data Extraction Form (policy) (Responses) - Form Responses 1.csv'), show_col_types = F)
+d_articles <- read_csv(here('data','primary','articles.csv'), show_col_types = F) # article data 
+d_journals <- read_csv(here('data','primary','journals.csv'), show_col_types = F) # journal data 
 ```
@@
 
-d_articles_random <- d_articles_random %>%
-  select(
-    article_id = `article id`,
-    coder_id_primary = `primary coder initials`,
-    coder_id_secondary = `secondary coder initials`,
-    exclusion_primary = `1_exclusion`,
-    exclusion_reason_primary = `1_exclusionReason`,
-    ppc_linked_primary = `1_Is article linked to PPC`,
-    notes_primary = `1_Additional notes`,
-    exclusion_secondary = `2_exclusion`,
-    exclusion_reason_secondary = `2_exclusionReason`,
-    ppc_linked_secondary = `2_Is article linked to PPC`,
-    notes_secondary = `2_Additional notes`
-  )
-
-d_articles_prominent <- d_articles_prominent %>%
+d_articles <- d_articles %>%
   select(
@@
 
-Check every row has a `journal` that appears in the original random or prominent sample lists.
-We initially get an error for this test because some journal names were entered in the extraction form with incorrect formatting.
-Correct this below before running the test.
+Some journal names were entered in the extraction form with incorrect formatting. Correct this below before running the test.
 
@@
 
-```{r}
-assert_that(
-  all(d_journals$journal %in% c(journal_list_prominent$Journal, journal_list_random$Journal)),
-  msg = "Found journal names that do not match sample"
-)
-```
-
-That fixed the problem, now all journal names in the extracted data match journal names in the sample files.
-
 We can't run any more useful tests at this point because in many columns coders have used entered free text to explain cases that were unclear.
@@
 ## Articles
-
-Firstly let's join the prominent and random articles together (with a new column identifying which sample they are in) to streamline some testing.
-
-```{r}
-d_articles <- bind_rows(
-  d_articles_random %>% mutate(sampleID = "random"),
-  d_articles_prominent %>% mutate(sampleID = "prominent")
-)
-```
 

### 2023-08-29 analysis/raw_to_primary.R
Create raw_to_primary.R

@@ -1,0 +1,26 @@
+# loads the raw data, filters out irrelevant rows, saves data to the primary folder
+
+library(tidyverse) # for various tasks including munging and plotting
+library(here) # for easier file path access
+
+# load article data (random)
+d_articles_random <- read_csv(here('data','raw','articles (random) - Sheet1.csv'), show_col_types = F) %>%
+  filter(!is.na(`primary coder initials`) & !is.na(`secondary coder initials`)) # we only need articles that were coded by someone
+
+# load article data (prominent)
+d_articles_prominent <- read_csv(here('data','raw','articles (prominent) - Sheet1.csv'), show_col_types = F)  %>%
+  filter(!is.na(`primary coder initials`) & !is.na(`secondary coder initials`)) # we only need articles that were coded by someone
+
+# join the prominent and random articles together (with a new column identifying which sample they are in) to streamline some testing.
+
+d_articles <- bind_rows(
+  d_articles_random %>% mutate(sampleID = "random"),
+  d_articles_prominent %>% mutate(sampleID = "prominent")
+)
+
+# load journal data (random and prominent sample)
+d_journals <- read_csv(here('data','raw','Data Extraction Form (policy) (Responses) - Form Responses 1.csv'), show_col_types = F)
+
+# save as primary data
+write_csv(d_journals, here('data','primary','journals.csv'))
+write_csv(d_articles, here('data','primary','articles.csv'))

### 2023-08-29 analysis/raw_to_primary.R
Update raw_to_primary.R

@@ -19,7 +19,9 @@ d_articles <- bind_rows(
 )
 
 # load journal data (random and prominent sample)
-d_journals <- read_csv(here('data','raw','Data Extraction Form (policy) (Responses) - Form Responses 1.csv'), show_col_types = F)
+d_journals <- read_csv(here('data','raw','Data Extraction Form (policy) (Responses) - Form Responses 1.csv'), show_col_types = F) %>%
+  filter(`Are you piloting?` == "No") %>% # remove pilot journals
+  select(-`Are you piloting?`)
 
 # save as primary data
 write_csv(d_journals, here('data','primary','journals.csv'))

### 2023-08-29 analysis/preprocessing.Rmd
Create preprocessing.Rmd
Update preprocessing.Rmd

--- 2023-08-29 analysis/checkData.Rmd
@@
 ---
-title: "checkData"
+title: "Preprocessing"
 output: html_document
@@
   )
-```
-
-# Remove non-relevant rows
-
-## Remove pilot journals
-
-Removing all rows that were entered during piloting and therefore not part of the main sample.
-
-```{r}
-d_journals <- d_journals %>%
-  filter(pilot == "No") %>%
-  select(-pilot)
 ```

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

@@
 library(assertthat) # for testing
-`%notin%` <- Negate(`%in%`) # for identifying when values are not in a vector of expected values
+source(here('analysis','functions.R')) # load custom functions
 ```

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

@@
 source(here('analysis','functions.R')) # load custom functions
+```
+
+# Convert raw data to primary data
+
+This will be moved to master script later.
+
+```{r}
+source(here('analysis','raw_to_primary.R')) # converts raw data to primary data
 ```
@@
          coder_id = `Coder's Initials`,
-         pilot = `Are you piloting?`,
          journal = `Journal Name`,

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

@@
 
-Some journal names were entered in the extraction form with incorrect formatting. Correct this below before running the test.
+Some journal names were entered in the extraction form with incorrect formatting. Correct this below.
 
@@
 
+There is some information about the sample that isn't included in the extracted data files (sampleID, JIFs, Web of Science subject category, COPE status), so we need to load some of that information from the original sample files and attached it to the extracted data
+
+```{r}
+# list of journals in random sample
+journal_list_random <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F) %>%
+  slice_head(n = 108) %>%
+  select(`Journal`)
+
+# list of journals in prominent sample
+journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F) %>%
+  slice_head(n = 114) %>%
+  select('Journal' = `Journal name`)
+
+# list of all prominent journals (some not in sample)
+journal_list_prominent_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F)
+
+# list of all random journals (some not in sample)
+journal_list_random_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F)
+```
 ## Identify sample for journals
@@
 
-# Resolve coding disagreements in articles data
+## Identify JIFs for journals
+
+For the random journals we can find the JIFs in the prominent journal sample.
+Some journals do not have a JIF because they haven't been indexed long enough.
+We manually checked all of these journals on Journal Citation Reports to see if they had been assigned JIFs.
+One JIF needs to be added manually for the journal "Journal of Psychology and Theology".
+The 2021 JIF for this journal is .80.
+
+```{r}
+# first split d_journals into two data frames based on sample ID
+d_journals_prominent <- d_journals %>%
+  filter(sampleID %in% c('prominent', 'both'))
+
+d_journals_random <- d_journals %>%
+  filter(sampleID == 'random')
+
+# get JIF and WOS subject category for prominent journals
+journal_list_prominent_all <- journal_list_prominent_all %>%
+  select(journal = `Journal name`, `2021 JIF`, WOS_first_psych_category) # identify the columns we need from the sample data
+
+d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal') # attach info to extracted data
+
+# get WOS subject category for random journals
+journal_list_random_all <- journal_list_random_all %>%
+  select(journal = Journal, WOS_first_psych_category) # identify the columns we need from the sample data
+
+d_journals_random <- left_join(d_journals_random, journal_list_random_all, by = 'journal') # attach info to extracted data
+
+# get JIFs for randomly selected journals by extracting them from the list of prominent journals (in the original download, not the sample)
+journal_list_prominent_all <- journal_list_prominent_all %>%
+  select(-WOS_first_psych_category) # we don't this column
+
+d_journals_random <- left_join(d_journals_random, journal_list_prominent_all, by = 'journal') # attach info to extracted data
+
+d_journals_random <- d_journals_random %>%
+  mutate(`2021 JIF` = ifelse(
+    journal == "JOURNAL OF PSYCHOLOGY AND THEOLOGY", # for one journal,
+    .80, # manually add its JIF
+    `2021 JIF`)) # otherwise keep whatever is already in the JIF column
+
+# reunite d_journals_random and d_journals_prominent
+d_journals <- bind_rows(
+  d_journals_random %>% mutate(sampleID = "random"),
+  d_journals_prominent %>% mutate(sampleID = "prominent")
+)
+rm(d_journals_random)
+rm(d_journals_prominent)
+```
+
+#Add COPE status FROM PRACTICE CODING, does not alter main d_journals tibble
+```{r}
+# Load googlesheet data
+
+dj_prominent <- read_csv(here('data','raw', 'journals-prominent.csv')) %>% #loads csv of googlesheet data of prominent journals
+  slice_head(n = 114) %>%
+  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
+
+dj_random <- read_csv(here('data','raw', 'journals-random.csv')) %>% #loads csv of googlesheet data of random journals
+  slice_head(n = 108) %>%
+  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
+
+# Combine above CSVs to one tibble
+
+dj_cope <- bind_rows(dj_prominent, dj_random)
+
+# Identify duplicate rows
+duplicates <- duplicated(dj_cope)
+
+# Select the duplicate rows
+duplicate_rows <- dj_cope[duplicates, ]
+
+# Check if duplicate rows have the same COPE values for journals
+for (i in seq_len(nrow(duplicate_rows))) {
+  row <- duplicate_rows[i, ]
+  id <- row$ID
+  value <- row$Value
+  same_values <- all(duplicate_rows$Value[duplicate_rows$ID == id] == value)
+
+  if (same_values) {
+    cat("Row", i, "with ID =", id, "has the same values in both columns.\n")
+  } else {
+    cat("Row", i, "with ID =", id, "has different values in both columns.\n")
+  }
+}
+
+#All 14 duplicated (both sample) journals had consistent COPE status, remove duplicates
+dj_cope <- distinct(dj_cope, journal, .keep_all = T)
+
+#join with main data tibble:
+d_primaryONLY <- left_join(d_primaryONLY, dj_cope, by = 'journal')
+
+```
+
+# Articles data — Resolve coding disagreements
 
@@
 ```
+
 We will resolve these by applying the exclusion criteria hierarchically. In other words, we use the highest level of exclusion criteria assigned by one of the two coders.
@@
 
-# Journals data — add JIF and COPE
-
-There is some information about the sample that isn't included in the extracted data files (e.g., JIFs, Web of Science subject category), so we need to load some of that information from the original sample files.
-
-```{r}
-# list of journals in random sample
-journal_list_random <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F) %>%
-  slice_head(n = 108) %>%
-  select(`Journal`)
-
-# list of journals in prominent sample
-journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F) %>%
-  slice_head(n = 114) %>%
-  select('Journal' = `Journal name`)
-
-# list of all prominent journals (some not in sample)
-journal_list_prominent_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F)
-
-# list of all random journals (some not in sample)
-journal_list_random_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F)
-```
-
-## Identify JIFs for journals
-
-For the random journals we can find the JIFs in the prominent journal sample.
-Some journals do not have a JIF because they haven't been indexed long enough.
-We manually checked all of these journals.
-One JIF needed to be added manually for the journal "Journal of Psychology and Theology".
-The 2021 JIF for this journal is .80.
-
-```{r}
-d_journals_prominent <- d_journals %>%
-  filter(sampleID %in% c('prominent', 'both'))
-
-d_journals_random <- d_journals %>%
-  filter(sampleID == 'random')
-
-journal_list_prominent_all <- journal_list_prominent_all %>% 
-  select(journal = `Journal name`, `2021 JIF`, WOS_first_psych_category)
-
-d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal')
-
-journal_list_random_all <- journal_list_random_all %>%
-  select(journal = Journal, WOS_first_psych_category)
-
-d_journals_random <- left_join(d_journals_random, journal_list_random_all, by = 'journal')
-
-journal_list_prominent_all <- journal_list_prominent_all %>%
-  select(-WOS_first_psych_category)
-
-d_journals_random <- left_join(d_journals_random, journal_list_prominent_all, by = 'journal')
-
-tmp <- d_journals_random %>% filter(is.na(`2021 JIF`)) %>% distinct(journal, .keep_all = T)
-write_csv(tmp,here('data', 'prepareSample', 'journals', '02 - modified', 'we_need_jifs.csv'))
-```
-
-#Add COPE status FROM PRACTICE CODING, does not alter main d_journals tibble
-```{r}
-# Load googlesheet data
-
-dj_prominent <- read_csv(here('data','raw', 'journals-prominent.csv')) %>% #loads csv of googlesheet data of prominent journals
-  slice_head(n = 114) %>%
-  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
-
-dj_random <- read_csv(here('data','raw', 'journals-random.csv')) %>% #loads csv of googlesheet data of random journals
-  slice_head(n = 108) %>%
-  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
-
-# Combine above CSVs to one tibble
-
-dj_cope <- bind_rows(dj_prominent, dj_random)
-
-# Identify duplicate rows
-duplicates <- duplicated(dj_cope)
-
-# Select the duplicate rows
-duplicate_rows <- dj_cope[duplicates, ]
-
-# Check if duplicate rows have the same COPE values for journals
-for (i in seq_len(nrow(duplicate_rows))) {
-  row <- duplicate_rows[i, ]
-  id <- row$ID
-  value <- row$Value
-  same_values <- all(duplicate_rows$Value[duplicate_rows$ID == id] == value)
-
-  if (same_values) {
-    cat("Row", i, "with ID =", id, "has the same values in both columns.\n")
-  } else {
-    cat("Row", i, "with ID =", id, "has different values in both columns.\n")
-  }
-}
-
-#All 14 duplicated (both sample) journals had consistent COPE status, remove duplicates
-dj_cope <- distinct(dj_cope, journal, .keep_all = T)
-
-#join with main data tibble:
-d_primaryONLY <- left_join(d_primaryONLY, dj_cope, by = 'journal')
-
-```
-
 # Final tests

### 2023-08-29 analysis/raw_to_primary.R
Update raw_to_primary.R

@@ -14,8 +14,8 @@ d_articles_prominent <- read_csv(here('data','raw','articles (prominent) - Sheet
 # join the prominent and random articles together (with a new column identifying which sample they are in) to streamline some testing.
 
 d_articles <- bind_rows(
-  d_articles_random %>% mutate(sampleID = "random"),
-  d_articles_prominent %>% mutate(sampleID = "prominent")
+  d_articles_random %>% mutate(sample_id = "random"),
+  d_articles_prominent %>% mutate(sample_id = "prominent")
 )
 
 # load journal data (random and prominent sample)
@@ -23,6 +23,99 @@ d_journals <- read_csv(here('data','raw','Data Extraction Form (policy) (Respons
   filter(`Are you piloting?` == "No") %>% # remove pilot journals
   select(-`Are you piloting?`)
 
+# Some journal names were entered in the extraction form with incorrect formatting. Correct this below.
+
+
+d_journals <- d_journals %>% 
+  mutate(`Journal Name` = fct_recode(`Journal Name`,
+                              "MEMORY & COGNITION" = "Memory & Cognition","JOURNAL OF COUPLE & RELATIONSHIP THERAPY-INNOVATIONS IN CLINICAL AND EDUCATIONAL INTERVENTIONS" = "Journal of Couple & Relationship Therapy"))
+
+
+# Attach sample information to extracted data
+
+# There is some information about the sample that isn't included in the extracted data files (sample_id, JIFs, Web of Science subject category, COPE status), so we need to load some of that information from the original sample files and attached it to the extracted data
+
+# load journal information
+d_journals_prominent_info <- read_csv(here('data','raw','journal_prominent_information.csv')) 
+
+d_journals_prominent_info_sample <- d_journals_prominent_info %>%
+  filter(!is.na(journal_website)) # select only journals included in the sample
+
+d_journals_random_info <- read_csv(here('data','raw','journal_random_information.csv')) 
+
+d_journals_random_info_sample <- d_journals_random_info %>%
+  filter(!is.na(journal_website)) # select only journals included in the sample
+
+# Identify sample for journals
+
+# The `d_journals` dataset does not identify whether journals were in the prominent sample, random sample, or both. So we need to get the sample ID retroactively using the files containing all journals included in the sample.
+
+# Create sample ID column(s) to indicate whether in prominent, random, or both samples
+
+d_journals <- d_journals %>%
[…]

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

--- 2023-08-29 analysis/preprocessing.Rmd
@@
   select(timestamps = Timestamp,
+         sample_id,
          coder_id = `Coder's Initials`,
@@
   select(
+    sample_id,
     article_id = `article id`,
@@
 
-Some journal names were entered in the extraction form with incorrect formatting. Correct this below before running the test.
-
-```{r}
-d_journals <- d_journals %>% 
-  mutate(journal = fct_recode(journal,
-                              "MEMORY & COGNITION" = "Memory & Cognition","JOURNAL OF COUPLE & RELATIONSHIP THERAPY-INNOVATIONS IN CLINICAL AND EDUCATIONAL INTERVENTIONS" = "Journal of Couple & Relationship Therapy"))
-```
-
 We can't run any more useful tests at this point because in many columns coders have used entered free text to explain cases that were unclear.
@@
 
-# Attach sample information to extracted data
-
-## Identify sample for journals
-
-The `d_journals` dataset does not identify whether journals were in the prominent sample, random sample, or both.
-So we need to get the sample ID retroactively using the files containing all journals included in the sample.
-
-Create sample ID column(s) to indicate whether in prominent, random, or both samples
-
-```{r}
-d_journals <- d_journals %>%
-  mutate(
-    sample_journal_prominent = journal %in% journal_list_prominent$Journal,
-    sample_journal_random = journal %in% journal_list_random$Journal,
-    sample_journal_both = sample_journal_prominent & sample_journal_random,
-    sample_journal_error = !sample_journal_prominent & !sample_journal_random
-  )
-
-#Creates sampleID column denoting; prominent, random, or both to replace the 4 specified columns above
-d_journals <- d_journals %>% 
-  mutate(sample_journal_prominent = ifelse(sample_journal_prominent, "prominent", "random")) %>%
-  mutate(sample_journal_both = ifelse(sample_journal_both, "both", "na")) %>%
-  mutate(sampleID = case_when(
-    sample_journal_both == "both" ~ "both",
-    sample_journal_both == "na" ~ sample_journal_prominent,
-    TRUE ~ sample_journal_both
-  )) %>%
-  select(-c(sample_journal_prominent, sample_journal_random, sample_journal_both, sample_journal_error))
-```
-
-# Resolve coding disagreements in articles data
+# Articles data — Resolve coding disagreements
 
@@
   mutate(exclusion_final = case_when(
-    sampleID == 'random' & article_id == '37' ~ exclusion_primary,
-    sampleID == 'random' & article_id == '41' ~ exclusion_primary,
-    sampleID == 'random' & article_id == '68' ~ exclusion_secondary,
-    sampleID == 'random' & article_id == '95' ~ exclusion_secondary,
-    sampleID == 'random' & article_id == '103' ~ exclusion_primary,
-    sampleID == 'random' & article_id == '120' ~ exclusion_primary,
-    sampleID == 'prominent' & article_id == '30' ~ exclusion_secondary,
-    sampleID == 'prominent' & article_id == '49' ~ exclusion_primary,
-    sampleID == 'prominent' & article_id == '66' ~ exclusion_primary,
-    sampleID == 'prominent' & article_id == '98' ~ exclusion_primary,
+    sample_id == 'random' & article_id == '37' ~ exclusion_primary,
+    sample_id == 'random' & article_id == '41' ~ exclusion_primary,
+    sample_id == 'random' & article_id == '68' ~ exclusion_secondary,
+    sample_id == 'random' & article_id == '95' ~ exclusion_secondary,
+    sample_id == 'random' & article_id == '103' ~ exclusion_primary,
+    sample_id == 'random' & article_id == '120' ~ exclusion_primary,
+    sample_id == 'prominent' & article_id == '30' ~ exclusion_secondary,
+    sample_id == 'prominent' & article_id == '49' ~ exclusion_primary,
+    sample_id == 'prominent' & article_id == '66' ~ exclusion_primary,
+    sample_id == 'prominent' & article_id == '98' ~ exclusion_primary,
     TRUE ~ exclusion_primary
@@
   mutate(exclusion_reason_final = case_when(
-    sampleID == 'random' & article_id == '37' ~ exclusion_reason_primary,
-    sampleID == 'random' & article_id == '41' ~ exclusion_reason_primary,
-    sampleID == 'random' & article_id == '68' ~ exclusion_reason_secondary,
-    sampleID == 'random' & article_id == '95' ~ exclusion_reason_secondary,
-    sampleID == 'random' & article_id == '103' ~ exclusion_reason_primary,
-    sampleID == 'random' & article_id == '120' ~ exclusion_reason_primary,
-    sampleID == 'prominent' & article_id == '30' ~ exclusion_reason_secondary,
-    sampleID == 'prominent' & article_id == '49' ~ exclusion_reason_primary,
-    sampleID == 'prominent' & article_id == '66' ~ exclusion_reason_primary,
-    sampleID == 'prominent' & article_id == '98' ~ exclusion_reason_primary,
+    sample_id == 'random' & article_id == '37' ~ exclusion_reason_primary,
+    sample_id == 'random' & article_id == '41' ~ exclusion_reason_primary,
+    sample_id == 'random' & article_id == '68' ~ exclusion_reason_secondary,
+    sample_id == 'random' & article_id == '95' ~ exclusion_reason_secondary,
+    sample_id == 'random' & article_id == '103' ~ exclusion_reason_primary,
+    sample_id == 'random' & article_id == '120' ~ exclusion_reason_primary,
+    sample_id == 'prominent' & article_id == '30' ~ exclusion_reason_secondary,
+    sample_id == 'prominent' & article_id == '49' ~ exclusion_reason_primary,
+    sample_id == 'prominent' & article_id == '66' ~ exclusion_reason_primary,
+    sample_id == 'prominent' & article_id == '98' ~ exclusion_reason_primary,
     TRUE ~ exclusion_reason_primary
@@
          exclusion_reason_primary != exclusion_reason_secondary) %>%
-  select(article_id, sampleID, exclusion_reason_primary, exclusion_reason_secondary)
+  select(article_id, sample_id, exclusion_reason_primary, exclusion_reason_secondary)
 ```
+
 We will resolve these by applying the exclusion criteria hierarchically. In other words, we use the highest level of exclusion criteria assigned by one of the two coders.
@@
   mutate(exclusion_reason_final = case_when(
-    sampleID == 'random' & article_id == '14' ~ exclusion_reason_primary,
-    sampleID == 'random' & article_id == '35' ~ exclusion_reason_primary,
-    sampleID == 'random' & article_id == '54' ~ exclusion_reason_secondary,
-    sampleID == 'random' & article_id == '73' ~ exclusion_reason_primary,
-    sampleID == 'random' & article_id == '78' ~ exclusion_reason_primary,
-    sampleID == 'prominent' & article_id == '29' ~ "RETRACTED", # the article was withdrawn, retracted seems like the closest fit among out labels
-    sampleID == 'prominent' & article_id == '37' ~ exclusion_reason_primary,
-    sampleID == 'prominent' & article_id == '39' ~ exclusion_reason_primary,
-    sampleID == 'prominent' & article_id == '46' ~ exclusion_reason_primary,
-    sampleID == 'prominent' & article_id == '54' ~ exclusion_reason_secondary,
+    sample_id == 'random' & article_id == '14' ~ exclusion_reason_primary,
+    sample_id == 'random' & article_id == '35' ~ exclusion_reason_primary,
+    sample_id == 'random' & article_id == '54' ~ exclusion_reason_secondary,
+    sample_id == 'random' & article_id == '73' ~ exclusion_reason_primary,
+    sample_id == 'random' & article_id == '78' ~ exclusion_reason_primary,
+    sample_id == 'prominent' & article_id == '29' ~ "RETRACTED", # the article was withdrawn, retracted seems like the closest fit among out labels
+    sample_id == 'prominent' & article_id == '37' ~ exclusion_reason_primary,
+    sample_id == 'prominent' & article_id == '39' ~ exclusion_reason_primary,
+    sample_id == 'prominent' & article_id == '46' ~ exclusion_reason_primary,
+    sample_id == 'prominent' & article_id == '54' ~ exclusion_reason_secondary,
     TRUE ~ exclusion_reason_final # if none of the above, retain whatever is in this column already
@@
 ```{r}
-d_articles %>% filter(exclusion_reason_final == "OTHER") %>% select(article_id, sampleID)
+d_articles %>% filter(exclusion_reason_final == "OTHER") %>% select(article_id, sample_id)
 ```
@@
   mutate(exclusion_reason_final = case_when(
-    sampleID == 'random' & article_id == '68' ~ "NO ACCESS",
-    sampleID == 'prominent' & article_id == '2' ~ "CONFERENCE ABSTRACT",
-    sampleID == 'prominent' & article_id == '56' ~ "CONFERENCE ABSTRACT",
-    sampleID == 'prominent' & article_id == '85' ~ "CONFERENCE ABSTRACT",
+    sample_id == 'random' & article_id == '68' ~ "NO ACCESS",
+    sample_id == 'prominent' & article_id == '2' ~ "CONFERENCE ABSTRACT",
+    sample_id == 'prominent' & article_id == '56' ~ "CONFERENCE ABSTRACT",
+    sample_id == 'prominent' & article_id == '85' ~ "CONFERENCE ABSTRACT",
     TRUE ~ exclusion_reason_final # if none of the above, retain whatever is in this column already
@@
     exclusion_final == "EXCLUDE" ~ NA_character_, # if article is excluded, use NA
-    sampleID == 'prominent' & article_id == '38' ~ ppc_linked_secondary,
+    sample_id == 'prominent' & article_id == '38' ~ ppc_linked_secondary,
     exclusion_final == "RETAIN" & exclusion_primary == "RETAIN" ~ ppc_linked_primary,
@@
   pivot_longer( # pivot to long format
-    cols = c(-journal,-sampleID, -anyPPC,-general_note),
+    cols = c(-journal,-sample_id, -anyPPC,-general_note),
     names_to = c("PPC_type", ".value"), 

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

@@
 
-# Perform initial tests and fix issues
+# Perform initial tests and fix some issues
 
@@
 
-## Journals
+## Journal data initial tests
 
@@
 
-## Articles
+## Articles data initial tests
 
@@
 
-Now check that when `exclusion_primary` and `exclusion_secondary` are "EXCLUDE" then we have reasons in the reason columns. When they are "RETAIN" the reason columns should be NA.
-
-```{r}
-# primary_exclusions <- d_articles %>% 
-#   count(exclusion_primary, exclusion_reason_primary) %>%
-#   mutate(expected_values = case_when(
-#     exclusion_primary == "RETAIN" & is.na(exclusion_reason_primary) ~ T,
-#     exclusion_primary == "EXCLUDE" & exclusion_reason_primary %in% c("NO ACCESS", "NON-ENGLISH", "NOT EMPIRICAL", "RETRACTED", "IS ITSELF PPC", "OTHER") ~ T,
-#     TRUE ~ "criteria not met"
-#   ))
-# 
-# secondary_exclusions <- d_articles %>% 
-#   count(exclusion_secondary, exclusion_reason_secondary) %>%
-#   
-# 
-# 
-# assert_that(, msg = "Found unexpected value in exclusion reason column when it should be NA")
-```
-
 # Articles data — Resolve coding disagreements
@@
 ```{r}
-d_articles %>%
-  filter(exclusion_primary != exclusion_secondary)
+# NOT RUN — used to identify cases where primary and secondary coder disagreed on whether to exclude.
+# d_articles %>%
+#   filter(exclusion_primary != exclusion_secondary)
 ```
@@
 # we've already dealt with cases where the decision to exclude differs, so we're not looking only at cases where the decision to exclude matches, but the reason for exclusion differs
-d_articles %>%
-  filter(exclusion_primary == exclusion_secondary, 
-         exclusion_reason_primary != exclusion_reason_secondary) %>%
-  select(article_id, sample_id, exclusion_reason_primary, exclusion_reason_secondary)
+# d_articles %>% # NOT RUN
+#   filter(exclusion_primary == exclusion_secondary, 
+#          exclusion_reason_primary != exclusion_reason_secondary) %>%
+#   select(article_id, sample_id, exclusion_reason_primary, exclusion_reason_secondary)
 ```
@@
 ```{r}
-d_articles %>% filter(exclusion_reason_final == "OTHER") %>% select(article_id, sample_id)
+d_articles %>% 
+  filter(exclusion_reason_final == "OTHER") %>% 
+  select(article_id, sample_id)
 ```
@@
 
-# Resolve coding disagreements in journals data
+# Journals data — Resolve coding disagreements
 
@@
 
-Make a tibble containing only the final coding for journals.\
+Make a tibble containing only the final coding for journals.
 
@@
 ```
+
+Now check that when `exclusion_primary` and `exclusion_secondary` are "EXCLUDE" then we have reasons in the reason columns. When they are "RETAIN" the reason columns should be NA.
+
+```{r}
+# primary_exclusions <- d_articles %>% 
+#   count(exclusion_primary, exclusion_reason_primary) %>%
+#   mutate(expected_values = case_when(
+#     exclusion_primary == "RETAIN" & is.na(exclusion_reason_primary) ~ T,
+#     exclusion_primary == "EXCLUDE" & exclusion_reason_primary %in% c("NO ACCESS", "NON-ENGLISH", "NOT EMPIRICAL", "RETRACTED", "IS ITSELF PPC", "OTHER") ~ T,
+#     TRUE ~ "criteria not met"
+#   ))
+# 
+# secondary_exclusions <- d_articles %>% 
+#   count(exclusion_secondary, exclusion_reason_secondary) %>%
+#   
+# 
+# 
+# assert_that(, msg = "Found unexpected value in exclusion reason column when it should be NA")
+```

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

@@
 
-# Journals data - exclusions
-
-```{r}
-d_journals_final_eligible <- d_journals_final %>%
-  filter(journal_empirical == "Yes") %>%
-  select(-journal_empirical)
-```
-
 # Journals data — reorganise
@@
 ```{r}
-d_journals_final_eligible <- d_journals_final_eligible %>%
+d_journals_final <- d_journals_final %>%
   pivot_longer( # pivot to long format
-    cols = c(-journal,-sample_id, -anyPPC,-general_note),
+    cols = c(-journal,-journal_empirical,-sample_id,-anyPPC,-general_note),
     names_to = c("PPC_type", ".value"), 
@@
 ```{r}
-d_journals_final_eligible <- d_journals_final_eligible %>% 
+d_journals_final <- d_journals_final %>% 
   mutate(length_harmonized = str_remove_all(length, pattern = '"'), #  remove any quotation marks

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

@@
 
-Make a tibble containing only the final coding for journals.
+Retain only the final coding for journals.
 
 ```{r}
-d_journals_final <- d_journals %>%
+d_journals <- d_journals %>%
   filter(coder_id == "FINAL (TEH)") %>% # select only the final coding
@@
 ```{r}
-d_journals_final <- d_journals_final %>%
+d_journals <- d_journals %>%
   pivot_longer( # pivot to long format
@@
 ```{r}
-d_journals_final <- d_journals_final %>% 
+d_journals <- d_journals %>% 
   mutate(length_harmonized = str_remove_all(length, pattern = '"'), #  remove any quotation marks
@@
 ```{r}
-d_journals_final_eligible <- d_journals_final_eligible %>% 
+d_journals <- d_journals %>% 
   mutate(time_harmonized = str_remove_all(time, pattern = '"'), #  remove any quotation marks
@@
 ```{r}
-d_journals_final_eligible <- d_journals_final_eligible %>% 
+d_journals <- d_journals %>% 
   mutate(ref_harmonized = str_remove_all(ref, pattern = '"'), #  remove any quotation marks
@@
 ```{r}
-d_journals_final_eligible <- d_journals_final_eligible %>% 
+d_journals <- d_journals %>% 
   mutate(review_harmonized = case_when(
@@
 ```{r}
-d_journals_final_eligible <- d_journals_final_eligible %>%
+d_journals <- d_journals %>%
   mutate(name_harmonized = case_when(
@@
 ```
+# Reclassify and reformat
+
+Reclassify some values like "Yes" and "No" into logicals, format some columns, and select only columns we need for data analysis.
+
+```{r}
+d_journals <- d_journals %>%
+  mutate(sample_id = factor(sample_id),
+         journal_name = factor(journal),
+         is_empirical = fct_recode(journal_empirical, T = "Yes", F = "No"),
+         has_ppc = fct_recode(anyPPC, 
+                             "ARCHIVE" = "ARCHIVE ONLY", 
+                             "NO IMPLICIT" = "NO (there are no PPC options)",
+                             "NO EXPLICIT" = "NO (explicit statement that PPC is not accepted)")) %>%
+  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized)
+```
+
+```{r}
+d_articles <- d_articles %>%
+  mutate(sample_id = factor(sample_id),
+         article_id = factor(article_id),
+         exclude = factor(exclusion_final),
+         exclude_reason = factor(exclusion_reason_final),
+         ppc_linked = fct_recode(ppc_linked_final, T = "NO", F = "YES")) %>%
+  select(sample_id, article_id, exclude, exclude_reason, ppc_linked)
+```
 
 # Final tests
+
+We'll run some final tests in this section to make sure we have what we expect in each column.
 
@@
 ```
+
+# Export files to processed data folder
+
+The data is now ready for analysis! Let's export it to the 'processed' data folder.
+
+```{r}
+write_csv(d_articles, here('data','processed','d_articles.csv'))
+write_csv(d_journals, here('data','processed','d_journals.csv'))
+```

### 2023-08-29 analysis/raw_to_primary.R
Update raw_to_primary.R

@@ -109,10 +109,7 @@ d_journals_random <- d_journals_random %>%
     jif)) # otherwise keep whatever is already in the JIF column
 
 # reunite d_journals_random and d_journals_prominent
-d_journals <- bind_rows(
-  d_journals_random %>% mutate(sample_id = "random"),
-  d_journals_prominent %>% mutate(sample_id = "prominent")
-)
+d_journals <- bind_rows(d_journals_random,d_journals_prominent)
 
 # save as primary data
 write_csv(d_journals, here('data','primary','journals.csv'))

### 2023-08-31 analysis/practiceCoding_AW.Rmd
Replaced primary with FINAL coding

@@
 
-#Prelim results and visualisations for d_journals using Primary coding data only
+#Prelim results and visualisations for d_journals using FINAL coding data only
 
@@
 
-d_primaryONLY <- d_journals %>%
-  filter(coder_id == "AW" | coder_id == "NM") %>% #keeps only entries with primary coder initials from main data tibble d_journals
+d_FINAL <- d_journals %>%
+  filter(coder_id == "FINAL (TEH)") %>% #keeps only FINAL coded by TEH
   filter(journal_empirical == "Yes") %>%          #removes ineligible journals (not empirical)
   group_by(journal) %>%
-  distinct(journal, .keep_all = TRUE)             #keeps only distinct journal entries
+#  distinct(journal, .keep_all = TRUE) %>%        #keeps only distinct journal entries
+    mutate(anyPPC = case_when(
+    anyPPC == 'Unclear' | anyPPC == 'UNSURE' | anyPPC == 'Unclear type' ~ 'UNCLEAR',
+    anyPPC == 'NO (explicit statement that PPC is not accepted)' | anyPPC == 'NO (there are no PPC options)' ~ 'NO',
+    TRUE ~ anyPPC
+    ))
 
- table(d_primaryONLY$sampleID, d_primaryONLY$anyPPC)
+ table(d_FINAL$sampleID, d_FINAL$anyPPC)
 
- table(d_primaryONLY$sampleID)
+ table(d_FINAL$sampleID)
+```
+
+# Calculate CIs for YES 
+```{r}
+library(binom)
+
+# Prominent Sample data
+prominentSuccess <- 47
+randomSuccess <- 29
+totalSuccess <- 72
+
+sample_size <- 100
+totalSample <- 189
+confidence_level <- 0.95
+
+# Calculate the Wilson confidence interval
+ci_prominent <- binom.confint(prominentSuccess, sample_size, method = "wilson", conf.level = confidence_level)
+ci_random <- binom.confint(randomSuccess, sample_size, method = "wilson", conf.level = confidence_level)
+ci_total <- binom.confint(totalSuccess, totalSample, method = "wilson", conf.level = confidence_level)
+
+# Print the confidence interval
+print(ci_prominent)
+print(ci_random)
+print(ci_total)
 ```
@@
 # Removes journals that do not offer any PPC 
- d_PPConly <- d_primaryONLY %>%
+ d_PPConly <- d_FINAL %>%
    filter(anyPPC == "YES")
@@
 
-#All 14 duplicated (both sample) journals had consistent COPE status, join with main data tibble:
-d_cope <- left_join(d_journals, dj_cope, by = 'journal')
+#All 14 duplicated (both sample) journals had consistent COPE status, remove duplicates
+dj_cope <- distinct(dj_cope, journal, .keep_all = T)
+
+#join with main data tibble:
+d_FINAL <- left_join(d_FINAL, dj_cope, by = 'journal')
 
@@
 
+# Bar graph of PPC by COPE
+
+```{r}
+
+# Create bar plot
+d_FINAL %>%  
+  ggplot() +
+geom_bar(
+  mapping = aes(x=anyPPC, fill = COPE),
+  stat = "count",
+  position = "stack",
+  colour = "black",
+  just = 0.5,
+  width = 0.7,
+  na.rm = FALSE,
+  orientation = NA,
+  show.legend = TRUE,
+  inherit.aes = TRUE
+) +
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues")
+ # facet_wrap(~field) +
+  labs(title = "Journal PPC Acceptance by COPE membership", x = "Accepts PPC", y = "Count")
 ```

### 2023-08-31 analysis/preprocessing.Rmd
Update preprocessing.Rmd

@@
            length_harmonized == "up to 2,000 words counting 500 words per table and figure" ~ "2000",
+           length_harmonized == " Rebuttals and peer commentaries should not exceed 1000 words. Exceptions to these length guidelines can be granted in special cases." ~ "1000",
+           length_harmonized == "1,200 words" ~ "1200",
+           length_harmonized == "1200 words (main text)" ~ "1200",
+           length_harmonized == "2,000 words (excluding abstract, references). Abstract: 200 words" ~ "2000",
+           length_harmonized == "5 pages" ~ as.character(5*pageToWord),
+           length_harmonized == "no more than 1000 words" ~ "1000",
+           length_harmonized == "no more than half the length of the original article" ~ "Qualitative",
+           length_harmonized == "not exceed 500 words" ~ "500",
+           length_harmonized == "Such manuscripts should normally be between 3,000 to 5,000 words, all inclusive (i.e., abstract, text, figures, tables, and references)." ~ "5000",
+           length_harmonized == "typically 1,500 words, excluding references.​" ~ "1500",
+           length_harmonized == "up to 3,000 words" ~ "3000",
+           length_harmonized == "3000 words" ~ "3000",
            TRUE ~ length_harmonized

### 2023-08-31 analysis/preprocessing.Rmd
Update preprocessing.Rmd

@@
 
+d_journals %>%
+  group_by(journal) %>%
+  mutate(has_final = any(coder_id == "FINAL (TEH)"))
+
 # Journals data — reorganise
@@
            time_harmonized == "recent" ~ "Qualitative",
+           time_harmonized == "timely" ~ "Qualitative",
+           time_harmonized == "UNCLEAR (provide detail in the 'other' section below), timely scientific comments" ~ "Qualitative",
            time_harmonized == "recently published" ~ "Qualitative",
@@
            ref_harmonized == "No more than 5 references" ~ "5",
+           ref_harmonized == "a maximum of 5 references" ~ "5",
            ref_harmonized == "overall limit is 265 lines of text including references" ~ "NOT STATED",
@@
 d_journals <- d_journals %>% 
-  mutate(review_harmonized = case_when(
+  mutate(review_harmonized = str_remove_all(review, pattern = '"'), #  remove any quotation marks
+         review_harmonized = case_when(
            review == "NO, This correspondence is published at the discretion of the Editor-in-Chief and the Associate Editors" ~ "NO",
@@
 The comments and formal response may then be sent to independent referees.'" ~ "YES",
+           review == "NO, Strongly implied not, by this: \"The decision to publish is made by the Editors, in order to ensure a timely appearance in print. \"" ~ "NO",
+           review == "YES, ...published work and may, after peer review, be published online as Matters Arising" ~ "YES",
+           review == "YES, Commentaries will be subjected to peer-review and will be held to the same standards of providing a notable contribution to our field to warrant publication." ~ "YES",
            TRUE ~ review
@@
          journal_name = factor(journal),
-         is_empirical = fct_recode(journal_empirical, T = "Yes", F = "No"),
+         is_empirical = as.logical(fct_recode(journal_empirical, T = "Yes", F = "No")),
          has_ppc = fct_recode(anyPPC, 
@@
          exclude_reason = factor(exclusion_reason_final),
-         ppc_linked = fct_recode(ppc_linked_final, T = "NO", F = "YES")) %>%
+         ppc_linked = as.logical(fct_recode(ppc_linked_final, T = "NO", F = "YES"))) %>%
   select(sample_id, article_id, exclude, exclude_reason, ppc_linked)
@@
 assert_that(
-  all(d_journals$journal_empirical %in% c("Yes", "No")),
-  msg = "Found unexpected values in journal_empirical column"
+  all(d_journals$is_empirical %in% c(T,F)),
+  msg = "Found unexpected values in is_empirical column"
 )

### 2023-08-31 analysis/preprocessing.Rmd
Update preprocessing.Rmd

@@
 d_journals <- d_journals %>%
-  filter(!(journal == "HUMAN ARENAS" & timestamps == "8/6/2023 3:37:26"))
+  filter(!(journal == "HUMAN ARENAS" & timestamps == "8/6/2023 3:37:26" & coder_id != "FINAL (TEH)"))
 ```
@@
 d_journals <- d_journals %>%
-  filter(!(journal == "INFANTS & YOUNG CHILDREN" & timestamps == "7/15/2023 18:51:15"))
+  filter(!(journal == "INFANTS & YOUNG CHILDREN" & timestamps == "7/15/2023 18:51:15" & coder_id != "FINAL (TEH)"))
 ```
@@
 d_journals <- d_journals %>%
-  filter(!(journal == "EDUCATIONAL PSYCHOLOGIST" & timestamps == "6/29/2023 14:06:13"))
+  filter(!(journal == "EDUCATIONAL PSYCHOLOGIST" & timestamps == "6/29/2023 14:06:13" & coder_id != "FINAL (TEH)"))
 ```
@@
 d_journals <- d_journals %>%
-  filter(!(journal == "EUROPEAN JOURNAL OF PERSONALITY" & timestamps == "6/29/2023 22:01:35"))
+  filter(!(journal == "EUROPEAN JOURNAL OF PERSONALITY" & timestamps == "6/29/2023 22:01:35" & coder_id != "FINAL (TEH)"))
 ```
@@
 d_journals <- d_journals %>%
-  filter(!(journal == "PERSONALITY AND SOCIAL PSYCHOLOGY REVIEW" & timestamps == "7/3/2023 18:34:38"))
+  filter(!(journal == "PERSONALITY AND SOCIAL PSYCHOLOGY REVIEW" & timestamps == "7/3/2023 18:34:38" & coder_id != "FINAL (TEH)"))
 ```
@@
 d_journals <- d_journals %>%
-  filter(!(journal == "PSYCHOLOGICAL MEDICINE" & timestamps == "8/6/2023 9:49:10"))
+  filter(!(journal == "PSYCHOLOGICAL MEDICINE" & timestamps == "8/6/2023 9:49:10" & coder_id != "FINAL (TEH)"))
 ```
@@
   group_by(journal) %>%
-  mutate(has_final = any(coder_id == "FINAL (TEH)"))
+  mutate(has_final = any(coder_id == "FINAL (TEH)")) %>%
+  filter(has_final == F) %>% View()
 

### 2023-09-01 analysis/raw_to_primary.R
Update raw_to_primary.R

@@ -24,12 +24,9 @@ d_journals <- read_csv(here('data','raw','Data Extraction Form (policy) (Respons
   select(-`Are you piloting?`)
 
 # Some journal names were entered in the extraction form with incorrect formatting. Correct this below.
-
-
 d_journals <- d_journals %>% 
   mutate(`Journal Name` = fct_recode(`Journal Name`,
                               "MEMORY & COGNITION" = "Memory & Cognition","JOURNAL OF COUPLE & RELATIONSHIP THERAPY-INNOVATIONS IN CLINICAL AND EDUCATIONAL INTERVENTIONS" = "Journal of Couple & Relationship Therapy"))
-
 
 # Attach sample information to extracted data
 
@@ -59,6 +56,8 @@ d_journals <- d_journals %>%
     sample_journal_both = sample_journal_prominent & sample_journal_random,
     sample_journal_error = !sample_journal_prominent & !sample_journal_random
   )
+
+
 
 #Creates sample_id column denoting; prominent, random, or both to replace the 4 specified columns above
 d_journals <- d_journals %>% 

### 2023-09-07 analysis/preprocessing.Rmd
Added columns: cope, field, jif
Also added additional variations of 'commentaries' and 'letters' chunk ~507

@@
          general_note = `Anything additional, unusual, or interesting to note?`,
+         cope, field, jif,
          -starts_with("D. "),
@@
 
-d_journals %>%
-  group_by(journal) %>%
-  mutate(has_final = any(coder_id == "FINAL (TEH)")) %>%
-  filter(has_final == F) %>% View()
-
 # Journals data — reorganise
@@
   pivot_longer( # pivot to long format
-    cols = c(-journal,-journal_empirical,-sample_id,-anyPPC,-general_note),
+    cols = c(-journal,-journal_empirical, -sample_id,-anyPPC,-general_note, -cope, -field, -jif),
     names_to = c("PPC_type", ".value"), 
@@
 ```{r}
-commentaries <- c("Brief comment", "Brief Comment", "commentaries", "Commentaries", "Commentary", "Comments", "Matters Arising", "Observations & Commentaries", "Open peer commentaries", "Short Communications and Commentaries", "Short Research Notes", "Text review")
-letters <- c("Letter", "Letters", "Letter to the editor", "Letters to the editor", "letters to the editor", "Letters to the Editor.", "letters to the editors", "Letters to the Editors")
+commentaries <- c("Brief comment", "Brief Comment", "Brief empirical notes", "brief peer commentaries or rebuttals", "commentaries", "Commentaries", "Commentary", "Comments", "Commentry", "commentary", "Commentary articles", "Matters Arising", "Observations & Commentaries", "Open peer commentaries", "Short Communications and Commentaries", "Short Research Notes", "Text review")
+letters <- c("Letter", "Letters", "Letter to the editor", "Letters to the editor", "letters to the editor", "Letters to the Editor.", "letters to the editors", "Letters to the Editors", "Letters to the Editor", "Letter to the Editor")
 # web_comments <- c()
@@
 ```
+
 # Reclassify and reformat
@@
                              "NO EXPLICIT" = "NO (explicit statement that PPC is not accepted)")) %>%
-  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized)
+  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized, cope, field, jif)
 ```

### 2023-09-07 analysis/preprocessing.Rmd
Harmonized final ppc names
Includes a chunk at 540 to harmonize name with problematic quotation marks in raw data for JOURNAL OF CLINICAL PSYCHIATRY

@@
 commentaries <- c("Brief comment", "Brief Comment", "Brief empirical notes", "brief peer commentaries or rebuttals", "commentaries", "Commentaries", "Commentary", "Comments", "Commentry", "commentary", "Commentary articles", "Matters Arising", "Observations & Commentaries", "Open peer commentaries", "Short Communications and Commentaries", "Short Research Notes", "Text review")
-letters <- c("Letter", "Letters", "Letter to the editor", "Letters to the editor", "letters to the editor", "Letters to the Editor.", "letters to the editors", "Letters to the Editors", "Letters to the Editor", "Letter to the Editor")
+letters <- c("Letter", "Letters", "Letter to the editor", "Letters to the editor", "letters to the editor", "Letters to the Editor.", "letters to the editors", "Letters to the Editors", "Letters to the Editor", "Letter to the Editor", "Responses", "Correspondence")
 # web_comments <- c()
@@
   select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized, cope, field, jif)
+```
+#Reclassify PPC name in JOURNAL OF CLINICAL PSYCHIATRY due to quotation marks in raw data name impeding inclusion above
+
+```{r}
+d_journals <- d_journals %>%
+  mutate(ppc_name = ifelse(is.na(ppc_name) & journal_name == "JOURNAL OF CLINICAL PSYCHIATRY" & ppc_type == "A", "Letters", ppc_name))
 ```

### 2023-09-07 analysis/preprocessing.Rmd
Update preprocessing.Rmd

--- 2023-09-07 analysis/preprocessing.Rmd
@@
     sample_id == 'prominent' & article_id == '98' ~ exclusion_primary,
+    sample_id == 'prominent' & article_id == '123' ~ exclusion_primary,
+    sample_id == 'prominent' & article_id == '124' ~ exclusion_primary,
+    sample_id == 'prominent' & article_id == '130' ~ exclusion_secondary,
+    sample_id == 'prominent' & article_id == '132' ~ exclusion_primary,
     TRUE ~ exclusion_primary
@@
     sample_id == 'prominent' & article_id == '98' ~ exclusion_reason_primary,
+    sample_id == 'prominent' & article_id == '130' ~ exclusion_reason_secondary,
     TRUE ~ exclusion_reason_primary
@@
  #          exclusion_reason_primary != exclusion_reason_secondary) %>%
-#   select(article_id, sample_id, exclusion_reason_primary, exclusion_reason_secondary)
+ #   select(article_id, sample_id, exclusion_reason_primary, exclusion_reason_secondary, exclusion_reason_final)
 ```

### 2023-09-08 analysis/preprocessing.Rmd
Added 1 length harmonisation

--- 2023-09-07 analysis/preprocessing.Rmd
@@
            length_harmonized == "3000 words" ~ "3000",
+           length_harmonized == "1500 words" ~ "1500",
            TRUE ~ length_harmonized

### 2023-09-08 analysis/practiceCoding_AW.Rmd
Cleaned up analysis

--- 2023-08-29 analysis/practiceCoding_AW.Rmd
@@
 ---
-title: "Results from Primary Coding"
+title: "Results Coding"
 author: "Annie Whamond"
@@
 ---
+# Load processed data files
+```{r}
 
-#Prelim results and visualisations for d_journals
+d_journals <- read_csv(here('data','processed','d_journals.csv'))
+d_articles <- read_csv(here('data','processed','d_articles.csv'))
 
-```{r}
-#Genarate table to assess anyPPC
-
-d_primaryONLY <- d_journals %>%
-  filter(coder_id == "AW" | coder_id == "NM") %>%
-  filter(journal_empirical == "Yes") %>%
-  group_by(journal) %>%
-  distinct(journal, .keep_all = TRUE)
-
- table(d_primaryONLY$sampleID, d_primaryONLY$anyPPC)
-
- table(d_primaryONLY$sampleID)
 ```
 
-#Look at limitations for anyPPC = YES
+# Journal Policy Overview
 ```{r}
 
- d_PPConly <- d_primaryONLY %>%
-   filter(anyPPC == "YES")
+d_journals_anyPPC <- d_journals %>%
+  filter(ppc_type == "A") %>%
+  filter(is_empirical == "TRUE")
+
+table(d_journals_anyPPC$sample_id)
+table(d_journals_anyPPC$has_ppc)
+table(d_journals_anyPPC$has_ppc, d_journals_anyPPC$sample_id)
+
+```
+
+# Calculate CIs for YES 
+```{r}
+library(binom)
+
+# Prominent Sample data
+prominentSuccess <- 38
+randomSuccess <- 23
+totalSuccess <- 57
+
+sample_size <- 100
+totalSample <- 189
+confidence_level <- 0.95
+
+# Calculate the Wilson confidence interval
+ci_prominent <- binom.confint(prominentSuccess, sample_size, method = "wilson", conf.level = confidence_level)
+ci_random <- binom.confint(randomSuccess, sample_size, method = "wilson", conf.level = confidence_level)
+ci_total <- binom.confint(totalSuccess, totalSample, method = "wilson", conf.level = confidence_level)
+
+# Print the confidence interval
+print(ci_prominent)
+print(ci_random)
+print(ci_total)
+```
+# Look at PPC names
+```{r}
+
+table(d_journals$ppc_name)
+
+```
+
+# Look at PPC length limitations
+```{r}
+
+# Removes journals that do not offer any PPC 
+ d_PPConly <- d_journals %>%
+   filter(has_ppc == "YES")
 
@@
 PPC_length <- d_PPConly %>%
-  filter(ppc_length_A != "NO") %>%
-  filter(ppc_length_A != "NOT STATED")
+  filter(!is.na(ppc_length)) %>%
+  filter(ppc_length != "NO") %>%
+  filter(ppc_length != "NOT STATED")
 
-table(PPC_length$ppc_length_A)
-table(PPC_length$ppc_length_B)
+table(PPC_length$ppc_length, PPC_length$ppc_name)
+```
 
-#Look at stated time limits
+# Look at PPC time limitations
+``` {r}
+PPC_time <- d_PPConly %>%
+  filter(!is.na(ppc_time)) %>%
+  filter(ppc_time != "NOT STATED")
 
-PPC_time <- d_PPConly %>%
-  filter(ppc_time_A != "NOT STATED")
-
-table(PPC_time$ppc_time_A)
+table(PPC_time$ppc_time, PPC_time$ppc_name)
 
@@
 
-#Add COPE status
+# Bar graph of PPC by COPE
+
 ```{r}
-dj_random <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F) %>%
-  slice_head(n = 108) %>%
-  select(`Journal`, 'COPE' = 'COPE (T = member; F = not a member)')
+library(ggplot2)
+library(RColorBrewer)
 
-dj_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F) %>%
-  slice_head(n = 114) %>%
-  select('Journal' = `Journal name`, 'COPE' = 'COPE (T = member; F = not a member)' )
-
-dj_cope <- left_join()
-
-#Code from checkData.RMD for extracting JIFs
-d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal')
-
-journal_list_random_all <- journal_list_random_all %>%
-  select(journal = Journal, WOS_first_psych_category)
-
-d_journals_random <- left_join(d_journals_random, journal_list_random_all, by = 'journal')
-
-journal_list_prominent_all <- journal_list_prominent_all %>%
-  select(-WOS_first_psych_category)
-
-d_journals_random <- left_join(d_journals_random, journal_list_prominent_all, by = 'journal')
-
-tmp <- d_journals_random %>% filter(is.na(`2021 JIF`)) %>% distinct(journal, .keep_all = T)
-write_csv(tmp,here('data', 'prepareSample', 'journals', '02 - modified', 'we_need_jifs.csv'))
-
+# Create bar plot
+d_journals %>%  
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'YES',
+    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
+    TRUE ~ has_ppc
+    )) %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES" | has_ppc == "NO") %>%
+  ggplot() +
+geom_bar(
+  mapping = aes(x=has_ppc, fill = cope),
+  stat = "count",
+  position = "stack",
+  colour = "black",
+  just = 0.5,
+  width = 0.7,
+  na.rm = FALSE,
+  orientation = NA,
+  show.legend = TRUE,
+  inherit.aes = TRUE
+) +
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues") +
+  labs(title = "Journal PPC Acceptance by COPE membership", x = "Accepts PPC", y = "Count")
 ```

### 2023-09-14 analysis/preprocessing.Rmd
Harmonized fields

@@
 ```
+# Harmonize field names deferring to WoS category
+```{r}
+
+d_journals <- d_journals %>% 
+  mutate(field_harmonized = case_when(
+           field == "Psychology | Sport" ~ "Sport",
+           field == "Psychology, Applied" ~ "Applied",
+           field == "PSYCHOLOGY, APPLIED" ~ "Applied",
+           field == "Psychology, Biological" ~ "Biological",
+           field == "PSYCHOLOGY, BIOLOGICAL" ~ "Biological",
+           field == "Psychology, Clinical" ~ "Clinical",
+           field == "PSYCHOLOGY, CLINICAL" ~ "Clinical",
+           field == "Psychology, Development" ~ "Developmental",
+           field == "PSYCHOLOGY, DEVELOPMENTAL" ~ "Developmental",
+           field == "Psychology, Educational" ~ "Educational",
+           field == "PSYCHOLOGY, EDUCATIONAL" ~ "Educational",
+           field == "Psychology, Experimental" ~ "Experimental",
+           field == "PSYCHOLOGY, EXPERIMENTAL" ~ "Experimental",
+           field == "Psychology, Mathematical" ~ "Mathematical",
+           field == "Psychology, Multidisciplinary" ~ "Multidisciplinary",
+           field == "PSYCHOLOGY, MULTIDISCIPLINARY" ~ "Multidisciplinary",
+           field == "Psychology, Social" ~ "Social",
+           field == "PSYCHOLOGY, SOCIAL" ~ "Social",
+           field == "Psychology" ~ "General",
+           field == "PSYCHOLOGY - SCIE" ~ "General",
+           TRUE ~ field
+         ))
+
+```
 
@@
                              "NO EXPLICIT" = "NO (explicit statement that PPC is not accepted)")) %>%
-  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized, cope, field, jif)
+  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized, cope, field = field_harmonized, jif)
 ```

### 2023-10-25 analysis/practiceCoding_AW.Rmd
Article exclusion & ref harmonise
Added group_by(sample_id) for article exclusion reasons to easily see reasons in both samples.

Added one additional argument to harmonise a reference statement

@@
 ---
+
+# Load libraries
+
+```{r}
+library(tidyverse)
+library(ggplot2)
+library(RColorBrewer)
+library(dplyr)
+library(kableExtra) # for tables
+library(knitr) # for literate programming
+library(janitor) # for data munging
+library(tidylog) # for inline code feedback
+library(here) # for finding files
+library(validate) # for data validation and testing
+#library(ggthemr) # for ggplot theme
+library(ggrepel) # for ggplot text labels
+library(scales) # to wrap text on axis labels
+library(ggdist) # for plotting distributions
+library(patchwork) # for multipanel plot layouts
+library(ggbeeswarm) # for dotplots
+```
+
 # Load processed data files
@@
 
+``` {r}
+
+d_journalsEmp <- d_journals %>%
+  filter(is_empirical == "TRUE") %>%
+  filter(ppc_type == "A")
+
+table(d_journalsEmp$field, d_journalsEmp$sample_id)
+
+```
+
+# Create tibbles for prominent and random journal samples
+```{r}
+dj_prom <- d_journalsEmp %>%
+  mutate(sample_id = case_when(
+    sample_id == "both" ~ "prominent",
+    TRUE ~ sample_id
+  )) %>%
+  filter(sample_id == "prominent")
+
+dj_random <- d_journalsEmp %>%
+  mutate(sample_id = case_when(
+    sample_id == "both" ~ "random",
+    TRUE ~ sample_id
+  )) %>%
+  filter(sample_id == "random")
+```
+
+# Descriptives for each journal sample 
+```{r}
+table(dj_prom$field, dj_prom$has_ppc)
+table(dj_random$field, dj_random$has_ppc)
+
+table(dj_prom$field, dj_prom$cope)
+table(dj_random$field, dj_random$cope)
+```
+
+# Plot sample id by field
+```{r}
+
+d_journals %>%
+  ggplot() +
+  geom_bar(
+    mapping = aes(x = field, fill = sample_id),
+    stat = "count",
+    position = "stack",
+    colour = "black",
+    just = 0.5,
+    width = 0.7,
+    na.rm = FALSE,
+    orientation = NA,
+    show.legend = TRUE,
+    inherit.aes = TRUE
+  ) +
+  theme_bw() +
+  scale_fill_brewer(palette = "Oranges") +
+  labs(title = "Sample ID by Field", x = "Field", y = "Count")
+
+```
+
+# CHAT GPT TEST
+```{r}
+library(dplyr)
+library(ggplot2)
+
+d_journals %>%
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'YES',
+    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
+    TRUE ~ has_ppc
+  )) %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc %in% c("YES", "NO")) %>%
+  filter(sample_id == 'both' | sample_id == 'random') %>%
+  group_by(field, has_ppc) %>%  # Group by field and has_ppc
+  summarise(count = n()) %>%   # Calculate counts for each combination
+  group_by(field) %>%           # Group by field only
+  mutate(percentage = round(count / sum(count) * 100)) %>%  # Calculate percentages within each field and round
+  ggplot() +
+  geom_bar(
+    mapping = aes(x = field, y = count, fill = has_ppc),
+    stat = "identity",  # Use "identity" for y values
+    position = "stack",
+    colour = "black",
+    width = 0.7,
+    na.rm = FALSE,
+    orientation = NA,
+    show.legend = TRUE,
+    inherit.aes = TRUE
+  ) +
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues") +
+  labs(title = "Random Journal PPC Acceptance by Field", x = "Field", y = "Count")
+
+```
+
+# Create bar plot of PPC policy by Field
+```{r}
+
+# Creates bar graph for Prominent journals
+
+d_journals %>%  
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'YES',
+    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
+    TRUE ~ has_ppc
+    )) %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES" | has_ppc == "NO") %>%
+  filter(sample_id == 'both' | sample_id == 'prominent') %>%
+  ggplot() +
+geom_bar(
+  mapping = aes(x=field, fill = has_ppc),
+  stat = "count",
+  position = "stack",
+  colour = "black",
+  just = 0.5,
+  width = 0.7,
+  na.rm = FALSE,
+  orientation = NA,
+  show.legend = TRUE,
+  inherit.aes = TRUE
+) +
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues") +
+  labs(title = "Prominent Journal PPC Acceptance by Field", x = "Field", y = "Count")
+```
+
+# Creates bar graph for Random journals
+``` {r}
+d_journals %>%  
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'YES',
+    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
+    TRUE ~ has_ppc
+    )) %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES" | has_ppc == "NO") %>%
+  filter(sample_id == 'both' | sample_id == 'random') %>%
+  ggplot() +
+geom_bar(
+  mapping = aes(x=field, fill = has_ppc),
+  stat = "count",
+  position = "stack",
+  colour = "black",
+  just = 0.5,
+  width = 0.7,
+  na.rm = FALSE,
+  orientation = NA,
+  show.legend = TRUE,
+  inherit.aes = TRUE
+) +
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues") +
+  labs(title = "Random Journal PPC Acceptance by Field", x = "Field", y = "Count")
+```
+
+# Plot PPC length limits by Field and COPE
+```{r}
+d_length <- d_journals %>%
+  select(has_ppc, journal_name, jif, cope, ppc_length, ppc_time, ppc_ref, field) %>%
+  filter(has_ppc=="YES") %>%
+  filter(ppc_length !="NOT STATED") %>%
+  filter(ppc_length !="Qualitative limit")
+
+d_length$ppc_length <- as.numeric(d_length$ppc_length)
+
+d_length %>%
+ggplot() +
+  geom_point(aes(x = ppc_length, 
+                               y = jif,
+                              shape = cope, 
+                              colour = field,
+                              size=1, 
+                              alpha = 0.7, 
+                              show.legend = FALSE,
+                              inherit.aes = FALSE)) +
+  theme_grey() +
+  labs(title = "Word Limits by JIF where PPC Accepted", x = "Word Limits", y = "Journal Impact Factor") +
+  scale_fill_brewer(palette="Accent") 
+```
+
 # Calculate CIs for YES 
+Not sure if this makes sense to do for Prominent and Total, as these are not random samples
 ```{r}
@@
 # Prominent Sample data
-prominentSuccess <- 38
+prominentSuccess <- 1
 randomSuccess <- 23
@@
 ```
+
+# Calculate CIs for NO 
+```{r}
+library(binom)
+
+# Prominent Sample data
+prominentNO <- 77
+randomNO <- 74
+totalNO <- 123
+
+# Calculate the Wilson confidence interval
+ci_prominentNO <- binom.confint(prominentNO, sample_size, method = "wilson", conf.level = confidence_level)
+ci_randomNO <- binom.confint(randomNO, sample_size, method = "wilson", conf.level = confidence_level)
+ci_totalNO <- binom.confint(totalNO, totalSample, method = "wilson", conf.level = confidence_level)
+
+# Print the confidence interval
+print(ci_prominentNO)
+print(ci_randomNO)
+print(ci_totalNO)
+```
+
 # Look at PPC names
@@
 
-table(d_journals$ppc_name)
+table(d_journals$ppc_name)  #PPCnames
+table(d_journals$sample_id, d_journals$ppc_name) #lists journals with PPC types
 
 ```
+Total = 63, 5 journals offering 2 types
 
@@
 
-table(PPC_length$ppc_length, PPC_length$ppc_name)
+dj_prominent <- d_journals %>%
+  filter(sample_id != "random")
+
+dj_random <- d_journals %>%
+  filter(sample_id != "prominent")
+
+#table_length <- table(PPC_length$ppc_length, PPC_length$ppc_name)
+table(dj_prominent$ppc_length, dj_prominent$ppc_name)
+table(dj_random$ppc_length, dj_random$ppc_name)
+```
+
+# Mean JIF by field and sample
+```{r}
+
+dj_prom %>%
+  filter(ppc_type == "A") %>%
+  group_by(field) %>%
+  summarise(mnJIF = mean(jif)) %>%
+  ungroup()
+
+dj_prom %>%
+  filter(ppc_type == "A") %>%
+  mutate(jif = round(jif, 2)) %>%
+  summarise(mean(jif), median(jif))
+
+```
+
+```{r}
+dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(!is.na(jif)) %>%
+  group_by(field) %>%
+  summarise(mnJIF = mean(jif)) %>%
+  ungroup()
+
+dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(!is.na(jif)) %>%
+  mutate(jif = round(jif, 2)) %>%
+  summarise(mean(jif), median(jif))
+```
+# PPC and COPE
+```{r}
+
+table(dj_prom$has_ppc, dj_prom$cope)
+
+dj_rand <- dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(is_empirical == TRUE)
+
+table(dj_rand$has_ppc, dj_rand$cope)
+
 ```
@@
 ``` {r}
-PPC_time <- d_PPConly %>%
+
+table(dj_prominent$ppc_time, dj_prominent$ppc_name)
+table(dj_random$ppc_time, dj_random$ppc_name)
+
+```
+CREATE FIGURES FOR TYPES OF RESTRICTION STATEMENTS
+
+# FIGURE of PROMINENT length limits
+```{r}
+
+dj_prominent %>%
+  filter(!is.na(ppc_length)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_length = case_when(
+    ppc_length %in% c(1000, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ "Quantitative",
+    ppc_length == "NOT STATED" ~ "Not Stated",
+    TRUE ~ as.character(ppc_length)
+  )) %>%
+  ggplot(mapping = aes(x = ppc_length, fill = ppc_name)) +
+  geom_bar(position = "stack",
+           colour = "black",
+           width = 0.5) +
+  theme_bw() +
+  coord_flip() +
+  scale_y_continuous(limits = c(0, 41)) +
+  scale_fill_brewer(palette = "Blues") +
+  theme(legend.position = c(0.9, 0.5)) +
+  labs(x = "Length Limit Statement", y = "Count", fill = "PPC Type")
+
+ggsave(filename = "Prominent_length.png", plot = last_plot(), device = "png")
+```
+# FIGURE of PROMINENT time limits
+```{r}
+
+dj_prominent %>%
   filter(!is.na(ppc_time)) %>%
-  filter(ppc_time != "NOT STATED")
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_time = case_when(
+    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ "Quantitative",
+    ppc_time == "NOT STATED" ~ "Not Stated",
+    TRUE ~ as.character(ppc_time)  # Keep other values as they are
+  )) %>%
+  ggplot(mapping = aes(x = ppc_time, fill = ppc_name)) +
+  geom_bar(position = "stack",
+           colour = "black",
+           width = 0.5,
+           ) +
+  theme_bw() +
+  coord_flip() +
+  scale_y_continuous(limits = c(0, 41)) +
+  scale_fill_brewer(palette = "Blues") +
+  theme(legend.position = c(0.9, 0.5)) +
+  labs(x = "Time-to-Submit Limit Statement", y = "Count", fill = "PPC Type")
 
-table(PPC_time$ppc_time, PPC_time$ppc_name)
+ggsave(filename = "Prominent_time.png", plot = last_plot(), device = "png")
+```
+# FIGURE of PROMINENT reference limits
+```{r}
+
+dj_prominent %>%
+  filter(!is.na(ppc_ref)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_ref = case_when(
+    ppc_ref %in% c(10, 15, 20, 5, "max 20") ~ "Quantitative",
+    ppc_ref == "NOT STATED" ~ "Not Stated",
+    TRUE ~ as.character(ppc_ref)  # Keep other values as they are
+  )) %>%
+  ggplot(mapping = aes(x = ppc_ref, fill = ppc_name)) +
+  geom_bar(position = "stack",
+           colour = "black",
+           width = 0.5,
+           ) +
+  theme_bw() +
+  coord_flip() +
+  scale_y_continuous(limits = c(0, 41)) +
+  scale_fill_brewer(palette = "Blues") +
+  theme(legend.position = c(0.9, 0.5)) +
+  labs(x = "Reference Limit Statement", y = "Count", fill = "PPC Type")
+
+ggsave(filename = "Prominent_ref.png", plot = last_plot(), device = "png")
+```
+# FIGURE of PROMINENT Peer-Review 
+```{r}
+
+dj_prominent %>%
+  filter(!is.na(ppc_review)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+ mutate(ppc_review = fct_relevel(
+    case_when(
+      ppc_review == "YES" ~ "Yes",
+      ppc_review == "NO" ~ "No",
+      ppc_review == "NOT STATED" ~ "Not Stated",
+      TRUE ~ as.character(ppc_review)  # Keep other values as they are
+    ),
+    c("Not Stated", "No", "Yes")  # Specify the desired order
+  )) %>%
+  ggplot(mapping = aes(x = ppc_review, fill = ppc_name)) +
+  geom_bar(position = "stack",
+           colour = "black",
+           width = 0.5,
+           ) +
+  theme_bw() +
+  coord_flip() +
+  scale_y_continuous(limits = c(0, 41)) +
+  scale_fill_brewer(palette = "Blues") +
+  theme(legend.position = c(0.9, 0.5)) +
+  labs(x = "PPC Sent for Peer-review", y = "Count", fill = "PPC Type")
+
+ggsave(filename = "Prominent_review.png", plot = last_plot(), device = "png")
+```
+
+# FIGURE of RANDOM Length Limits
+```{r}
+
+dj_random %>%
+  filter(!is.na(ppc_length)) %>%
+  mutate(ppc_length = case_when(
+    ppc_length %in% c(1000, 1100, 1200, 2000, 2500, 2650, 500) ~ "Quantitative",
+    ppc_length == "NOT STATED" ~ "Not Stated",
+    TRUE ~ as.character(ppc_length)  # Keep other values as they are
+  )) %>%
+  ggplot(mapping = aes(x = ppc_length, fill = ppc_name)) +
+  geom_bar(position = "stack",
+           colour = "black",
+           width = 0.5,
+           ) +
+  theme_bw() +
+  coord_flip() +
+  scale_y_continuous(limits = c(0, 25)) +
+  scale_fill_brewer(palette = "Blues") +
+  theme(legend.position = c(0.9, 0.7)) +
+  labs(x = "Length Limit Statement", y = "Count", fill = "PPC Type")
+
+ggsave(filename = "Random_length.png", plot = last_plot(), device = "png")
+```
+
+# FIGURE of RANDOM time limits
+```{r}
+
+dj_random %>%
+  filter(!is.na(ppc_time)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_time = case_when(
+    ppc_time %in% 39.15 ~ "Quantitative",
+    ppc_time == "NOT STATED" ~ "Not Stated",
+    TRUE ~ as.character(ppc_time)  # Keep other values as they are
+  )) %>%
+  ggplot(mapping = aes(x = ppc_time, fill = ppc_name)) +
+  geom_bar(position = "stack",
+           colour = "black",
+           width = 0.5,
+           ) +
+  theme_bw() +
+  coord_flip() +
+  scale_y_continuous(limits = c(0, 25)) +
+  scale_fill_brewer(palette = "Blues") +
+  theme(legend.position = c(0.9, 0.7)) +
+  labs(x = "Time-to-Submit Limit Statement", y = "Count", fill = "PPC Type")
+
+ggsave(filename = "Random_time.png", plot = last_plot(), device = "png")
+```
+# FIGURE of PROMINENT reference limits
+```{r}
+
+dj_random %>%
+  filter(!is.na(ppc_ref)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_ref = case_when(
+    ppc_ref %in% c(10, 15, 5) ~ "Quantitative",
+    ppc_ref == "NOT STATED" ~ "Not Stated",
+    TRUE ~ as.character(ppc_ref)  # Keep other values as they are
+  )) %>%
+  ggplot(mapping = aes(x = ppc_ref, fill = ppc_name)) +
+  geom_bar(position = "stack",
+           colour = "black",
+           width = 0.5,
+           ) +
+  theme_bw() +
+  coord_flip() +
+  scale_y_continuous(limits = c(0, 25)) +
+  scale_fill_brewer(palette = "Blues") +
+  theme(legend.position = c(0.9, 0.7)) +
+  labs(x = "Reference Limit Statement", y = "Count", fill = "PPC Type")
+
+ggsave(filename = "Random_ref.png", plot = last_plot(), device = "png")
+```
+# FIGURE of RANDOM Peer-Review 
+```{r}
+
+dj_random %>%
+  filter(!is.na(ppc_review)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+ mutate(ppc_review = fct_relevel(
+    case_when(
+      ppc_review == "YES" ~ "Yes",
+      ppc_review == "NO" ~ "No",
+      ppc_review == "NOT STATED" ~ "Not Stated",
+      TRUE ~ as.character(ppc_review)  # Keep other values as they are
+    ),
+    c("Not Stated", "No", "Yes")  # Specify the desired order
+  )) %>%
+  ggplot(mapping = aes(x = ppc_review, fill = ppc_name)) +
+  geom_bar(position = "stack",
+           colour = "black",
+           width = 0.5,
+           ) +
+  theme_bw() +
+  coord_flip() +
+  scale_y_continuous(limits = c(0, 25)) +
+  scale_fill_brewer(palette = "Blues") +
+  theme(legend.position = c(0.9, 0.7)) +
+  labs(x = "PPC Sent for Peer-review", y = "Count", fill = "PPC Type")
+
+ggsave(filename = "Random_review.png", plot = last_plot(), device = "png")
+```
+
+# PPC Reference limits
+```{r}
+table(dj_prominent$ppc_ref, dj_prominent$ppc_name)
+table(dj_random$ppc_ref, dj_random$ppc_name)
+
+```
+# PPC Peer Review
+```{r}
+table(dj_prominent$ppc_review, dj_prominent$ppc_name)
+table(dj_random$ppc_review, dj_random$ppc_name)
 
@@
 
-# Create bar plot
+# Overall
 d_journals %>%  
@@
   labs(title = "Journal PPC Acceptance by COPE membership", x = "Accepts PPC", y = "Count")
+
 ```
+
+``` {r}
+# Prominent Sample
+d_journals %>%  
+  filter(sample_id == "prominent" | sample_id == "both") %>%
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'NO',
+    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
+    TRUE ~ has_ppc
+    )) %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES" | has_ppc == "NO") %>%
+  ggplot() +
+geom_bar(
+  mapping = aes(x=has_ppc, fill = cope),
+  stat = "count",
+  position = "stack",
+  colour = "black",
+  just = 0.5,
+  width = 0.7,
+  na.rm = FALSE,
+  orientation = NA,
+  show.legend = TRUE,
+  inherit.aes = TRUE
+) +
+  theme_bw() +
+  scale_fill_brewer(palette = "Oranges") +
+  labs(title = "Prominent Journal PPC Acceptance by COPE membership", x = "Accepts PPC", y = "Count", fill = "COPE")
+
+ggsave(filename= "ProminentPPC_policyByCope.png", device= "png")
+```
+
+``` {r}
+# Random Sample
+d_journals %>%  
+  filter(sample_id == "random" | sample_id == "both") %>%
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'YES',
+    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
+    TRUE ~ has_ppc
+    )) %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES" | has_ppc == "NO") %>%
+  ggplot() +
+geom_bar(
+  mapping = aes(x=cope, fill = has_ppc),
+  stat = "count",
+  position = "stack",
+  colour = "black",
+  just = 0.5,
+  width = 0.7,
+  na.rm = FALSE,
+  orientation = NA,
+  show.legend = TRUE,
+  inherit.aes = TRUE
+) +
+  theme_bw() +
+  scale_fill_brewer(palette = "Oranges") +
+  labs(title = "Random Journal PPC Acceptance by COPE membership", x = "COPE Member", y = "Count", fill = "PPC")
+
+ggsave(filename= "RandomPPC_policyByCope.png", device= "png")
+```
+
+# Presentation Graph of PPC by Sample
+
+```{r}
+
+library(dplyr)
+library(ggplot2)
+library(forcats)
+
+library(dplyr)
+
+# Duplicate rows with sample_id "both" and rename the duplicates as "Prominent"
+duplicated_prominent_rows <- d_journals %>%
+    mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
+    TRUE ~ has_ppc
+  )) %>%
+  filter(ppc_type == "A") %>%
+  filter(is_empirical == TRUE) %>%
+  filter(sample_id == "both") %>%
+  mutate(sample_id = "prominent")
+
+# Combine the duplicated "Prominent" rows with the original data
+d_journals_processed <- bind_rows(d_journals, duplicated_prominent_rows) %>%
+  mutate(sample_id = recode(sample_id, "prominent" = "Prominent", "random" = "Random"))
+
+# Now, the dataset contains the original "both" rows and their duplicates as "Prominent"
+
+d_journals_processed %>%
+   mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
+    TRUE ~ has_ppc
+  )) %>%
+  filter(ppc_type == "A") %>%
+  filter(is_empirical == TRUE) %>%
+  mutate(sample_id = ifelse(sample_id == "both", "Random", sample_id)) %>%
+  ggplot() +
+  geom_bar(
+    mapping = aes(x = has_ppc, fill = sample_id),
+    stat = "count",
+    position = position_dodge(width = 0.8),  # Use position = "dodge" to create side-by-side bars
+    colour = "black",
+    alpha = 0.7,
+    width = 0.7,
+    na.rm = FALSE,
+    orientation = "vertical",
+    show.legend = TRUE,
+    inherit.aes = TRUE
+  ) +
+  geom_text(
+    aes(x = has_ppc, y = ..count.., label = ..count.., group = sample_id),
+    stat = "count",
+    position = position_dodge(width = 0.8),
+    vjust = -0.5,  # Adjust the vertical position of the labels
+    size = 6
+  ) +
+  theme_bw() +
+  ylim(0, 100) +
+  scale_fill_brewer(palette = "Set2") +
+  labs(title = "Journal PPC Acceptance by Sample",
+       x = "Accepts PPC",
+       y = "Count",
+       fill = "Sample"  # Customize the legend title here
+  ) + 
+  theme(
+    text = element_text(size = 18)  # Increase the font size here
+  )
+
+ggsave(filename = "PPCbySample.png", plot = last_plot(), device = "png")
+```
+
+# Articles and Prevalence
+
+# Calculate CIs for NO 
+```{r}
+library(binom)
+
+# Prominent Sample data for linked
+plPPCsuccess <- 1
+rlPPCsuccess <- 0
+linkedSample <- 101
+
+confidence_level <- 0.95
+
+# Calculate the Wilson confidence interval
+ci_plPPC <- binom.confint(plPPCsuccess, linkedSample, method = "wilson", conf.level = confidence_level)
+ci_rlPPC <- binom.confint(rlPPCsuccess, linkedSample, method = "wilson", conf.level = confidence_level)
+
+# Print the confidence interval
+print(ci_plPPC)
+print(ci_rlPPC)
+
+```
+```{r}
+library(dplyr)
+library(ggplot2)
+library(forcats)
+
+# Modify the dataset to ensure "both" values are included in both "Prominent" and "Random"
+d_journals_processed <- d_journals %>%
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
+    TRUE ~ has_ppc
+  )) %>%
+  filter(ppc_type == "A") %>%
+  filter(is_empirical == TRUE) %>%
+  mutate(sample_id = fct_recode(sample_id, 
+                                "Prominent" = "prominent", 
+                                "Random" = "random",
+                                "Both" = "both"))
+
+# Create a summary dataset to count "both" values in both "Prominent" and "Random"
+summary_data <- d_journals_processed %>%
+  filter(sample_id %in% c("Prominent", "Random")) %>%
+  group_by(has_ppc, sample_id) %>%
+  summarise(count = sum(count)) %>%
+  ungroup()
+
+# Create the ggplot with count labels
+ggplot(data = summary_data) +
+  geom_bar(
+    mapping = aes(x = has_ppc, y = count, fill = sample_id),
+    stat = "identity",  # Use stat = "identity" to specify y as the count values
+    position = position_dodge(width = 0.8),
+    colour = "black",
+    alpha = 0.7,
+    width = 0.7,
+    na.rm = FALSE,
+    orientation = "vertical",
+    show.legend = TRUE,
+    inherit.aes = TRUE
+  ) +
+  geom_text(
+    aes(x = has_ppc, y = count, label = count, group = sample_id),
+    position = position_dodge(width = 0.8),
+    vjust = -0.5,
+    size = 4
+  ) +
+  theme_bw() +
+  scale_fill_brewer(palette = "Set2") +
+  labs(title = "Journal PPC Acceptance by Sample",
+       x = "Accepts PPC",
+       y = "Count",
+       fill = "Sample Type"
+  ) + 
+  theme(
+    text = element_text(size = 18)
+  )
+
+# Save the plot
+ggsave(filename = "PPCbySample.png", plot = last_plot(), device = "png")
+
+```
+# Restriction Statements Graph
+```{r}
+
+table(dj_prominent$ppc_ref)
+table(dj_prominent$ppc_review)
+
+table(dj_random$ppc_ref)
+table(dj_random$ppc_review)
+```
+
+# Check median and IQR for each field
+```{r}
+
+# Group the tibble by the 'field' column
+prom_grouped <- dj_prom %>% group_by(field)
+
+# Compute summary statistics for 'jif' within each group
+promJIF_stats <- prom_grouped %>%
+  mutate(jif = round(jif, 2)) %>%
+  summarize(
+    mean_jif = mean(jif),
+    median_jif = median(jif),
+    q1_jif = quantile(jif, 0.25),
+    q3_jif = quantile(jif, 0.75),
+    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
+    count = n()
+  )
+
+# View the summary statistics
+print(promJIF_stats)
+```
+
+#For randomly sampled journals 
+``` {r}
+# Group the tibble by the 'field' column
+rand_grouped <- dj_rand %>% filter(!is.na(jif)) %>% group_by(field)
+
+# Compute summary statistics for 'jif' within each group
+randJIF_stats <- rand_grouped %>%
+  filter(ppc_type == "A") %>%
+  filter(is_empirical == "TRUE") %>%
+  mutate(jif = round(jif, 2)) %>%
+  summarize(
+    mean_jif = mean(jif),
+    median_jif = median(jif),
+    q1_jif = quantile(jif, 0.25),
+    q3_jif = quantile(jif, 0.75),
+    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
+    count = n()
+  )
+
+# View the summary statistics
+print(randJIF_stats)
+
+dj_rand %>%
+   filter(!is.na(jif)) %>%
+  mutate(jif = round(jif, 2)) %>%
+  summarize(
+    mean_jif = mean(jif),
+    median_jif = median(jif),
+    q1_jif = quantile(jif, 0.25),
+    q3_jif = quantile(jif, 0.75),
+    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
+    count = n()
+  )
+
+```
+```{r}
+count_non_missing <- sum(!is.na(dj_prominent$ppc_length))
+cat("Count of non-missing values in ppc_length:", count_non_missing, "\n")
+```
+
+# View median and IQR for quantitavtive 'Commentary' limits in prominent journals
+```{r}
+
+promCom_stats <- dj_prominent %>%
+  filter(ppc_name == "Commentary") %>%
+  mutate(
+    ppc_length = as.numeric(replace(ppc_length, ppc_length %in% c("Qualitative", "NOT STATED"), NA)),
+    ppc_time = as.numeric(replace(ppc_time, ppc_time %in% c("Qualitative", "NOT STATED"), NA)),
+    ppc_ref = as.numeric(replace(ppc_ref, ppc_ref %in% c("Qualitative", "NOT STATED"), NA))
+  ) %>%
+  summarize(
+    mdLength = median(ppc_length, na.rm = TRUE),
+    mdTime = median(ppc_time, na.rm = TRUE),
+    mdRef = median(ppc_ref, na.rm = TRUE),
+    q1_length = quantile(ppc_length, 0.25, na.rm = TRUE),
+    q3_length = quantile(ppc_length, 0.75, na.rm = TRUE),
+    iqr_length = quantile(ppc_length, 0.75, na.rm = TRUE) - quantile(ppc_length, 0.25, na.rm = TRUE),
+    q1_time = quantile(ppc_time, 0.25, na.rm = TRUE),
+    q3_time = quantile(ppc_time, 0.75, na.rm = TRUE),
+    iqr_time = quantile(ppc_time, 0.75, na.rm = TRUE) - quantile(ppc_time, 0.25, na.rm = TRUE),
+    q1_ref = quantile(ppc_ref, 0.25, na.rm = TRUE),
+    q3_ref = quantile(ppc_ref, 0.75, na.rm = TRUE),
+    iqr_ref = quantile(ppc_ref, 0.75, na.rm = TRUE) - quantile(ppc_ref, 0.25, na.rm = TRUE),
+    peer_rev = sum(ppc_review == "YES"),
+    COPE = sum(cope == "TRUE")
+  )
+
+print(promCom_stats)
+
+```
+# View median and IQR for quantitavtive 'Letters' limits in prominent journals
+```{r}
+promLet_stats <- dj_prominent %>%
+  filter(ppc_name == "Letters") %>%
+  mutate(
+    ppc_length = as.numeric(ppc_length),  # Convert ppc_length to numeric
+    ppc_time = as.numeric(ppc_time),      # Convert ppc_time to numeric
+    ppc_ref = as.numeric(ppc_ref)         # Convert ppc_ref to numeric
+  ) %>%
+  summarize(
+    mdLength = median(ppc_length, na.rm = TRUE),
+    mdTime = median(ppc_time, na.rm = TRUE),
+    mdRef = median(ppc_ref, na.rm = TRUE),
+    q1_length = quantile(ppc_length, 0.25, na.rm = TRUE),
+    q3_length = quantile(ppc_length, 0.75, na.rm = TRUE),
+    iqr_length = quantile(ppc_length, 0.75, na.rm = TRUE) - quantile(ppc_length, 0.25, na.rm = TRUE),
+    q1_time = quantile(ppc_time, 0.25, na.rm = TRUE),
+    q3_time = quantile(ppc_time, 0.75, na.rm = TRUE),
+    iqr_time = quantile(ppc_time, 0.75, na.rm = TRUE) - quantile(ppc_time, 0.25, na.rm = TRUE),
+    q1_ref = quantile(ppc_ref, 0.25, na.rm = TRUE),
+    q3_ref = quantile(ppc_ref, 0.75, na.rm = TRUE),
+    iqr_ref = quantile(ppc_ref, 0.75, na.rm = TRUE) - quantile(ppc_ref, 0.25, na.rm = TRUE),
+    peer_rev = sum(ppc_review == "YES"),
+    COPE = sum(cope == "TRUE")
+  )
+
+print(promLet_stats)
+```
+# View median and IQR for ALL quantitavtive limits in PROMINENT journals
+```{r}
+
+promAll_stats <- dj_prominent %>%
+  filter(ppc_name == "Commentary" | ppc_name == "Letters") %>%
+  mutate(
+    ppc_length = as.numeric(replace(ppc_length, ppc_length %in% c("Qualitative", "NOT STATED"), NA)),
+    ppc_time = as.numeric(replace(ppc_time, ppc_time %in% c("Qualitative", "NOT STATED"), NA)),
+    ppc_ref = as.numeric(replace(ppc_ref, ppc_ref %in% c("Qualitative", "NOT STATED"), NA))
+  ) %>%
+  summarize(
+    mdLength = median(ppc_length, na.rm = TRUE),
+    mdTime = median(ppc_time, na.rm = TRUE),
+    mdRef = median(ppc_ref, na.rm = TRUE),
+    q1_length = quantile(ppc_length, 0.25, na.rm = TRUE),
+    q3_length = quantile(ppc_length, 0.75, na.rm = TRUE),
+    iqr_length = quantile(ppc_length, 0.75, na.rm = TRUE) - quantile(ppc_length, 0.25, na.rm = TRUE),
+    q1_time = quantile(ppc_time, 0.25, na.rm = TRUE),
+    q3_time = quantile(ppc_time, 0.75, na.rm = TRUE),
+    iqr_time = quantile(ppc_time, 0.75, na.rm = TRUE) - quantile(ppc_time, 0.25, na.rm = TRUE),
+    q1_ref = quantile(ppc_ref, 0.25, na.rm = TRUE),
+    q3_ref = quantile(ppc_ref, 0.75, na.rm = TRUE),
+    iqr_ref = quantile(ppc_ref, 0.75, na.rm = TRUE) - quantile(ppc_ref, 0.25, na.rm = TRUE),
+    peer_rev = sum(ppc_review == "YES"),
+    COPE = sum(cope == "TRUE"),
+    count = n()
+  )
+
+print(promAll_stats)
+
+```
+
+# View median and IQR for quantitavtive 'Commentary' limits in Random journals
+```{r}
+
+randCom_stats <- dj_random %>%
+  filter(ppc_name == "Commentary") %>%
+  mutate(
+    ppc_length = as.numeric(replace(ppc_length, ppc_length %in% c("Qualitative", "NOT STATED"), NA)),
+    ppc_time = as.numeric(replace(ppc_time, ppc_time %in% c("Qualitative", "NOT STATED"), NA)),
+    ppc_ref = as.numeric(replace(ppc_ref, ppc_ref %in% c("Qualitative", "NOT STATED"), NA))
+  ) %>%
+ summarize(
+    mdLength = median(ppc_length, na.rm = TRUE),
+    mdTime = median(ppc_time, na.rm = TRUE),
+    mdRef = median(ppc_ref, na.rm = TRUE),
+    q1_length = quantile(ppc_length, 0.25, na.rm = TRUE),
+    q3_length = quantile(ppc_length, 0.75, na.rm = TRUE),
+    iqr_length = quantile(ppc_length, 0.75, na.rm = TRUE) - quantile(ppc_length, 0.25, na.rm = TRUE),
+    q1_time = quantile(ppc_time, 0.25, na.rm = TRUE),
+    q3_time = quantile(ppc_time, 0.75, na.rm = TRUE),
+    iqr_time = quantile(ppc_time, 0.75, na.rm = TRUE) - quantile(ppc_time, 0.25, na.rm = TRUE),
+    q1_ref = quantile(ppc_ref, 0.25, na.rm = TRUE),
+    q3_ref = quantile(ppc_ref, 0.75, na.rm = TRUE),
+    iqr_ref = quantile(ppc_ref, 0.75, na.rm = TRUE) - quantile(ppc_ref, 0.25, na.rm = TRUE),
+    peer_rev = sum(ppc_review == "YES"),
+    COPE = sum(cope == "TRUE")
+  )
+
+print(randCom_stats)
+
+```
+
+# View median and IQR for quantitavtive 'Letters' limits in RANDOM journals
+```{r}
+randLet_stats <- dj_random %>%
+  filter(ppc_name == "Letters") %>%
+  mutate(
+    ppc_length = as.numeric(ppc_length),  # Convert ppc_length to numeric
+    ppc_time = as.numeric(ppc_time),      # Convert ppc_time to numeric
+    ppc_ref = as.numeric(ppc_ref)         # Convert ppc_ref to numeric
+  ) %>%
+ summarize(
+    mdLength = median(ppc_length, na.rm = TRUE),
+    mdTime = median(ppc_time, na.rm = TRUE),
+    mdRef = median(ppc_ref, na.rm = TRUE),
+    q1_length = quantile(ppc_length, 0.25, na.rm = TRUE),
+    q3_length = quantile(ppc_length, 0.75, na.rm = TRUE),
+    iqr_length = quantile(ppc_length, 0.75, na.rm = TRUE) - quantile(ppc_length, 0.25, na.rm = TRUE),
+    q1_time = quantile(ppc_time, 0.25, na.rm = TRUE),
+    q3_time = quantile(ppc_time, 0.75, na.rm = TRUE),
+    iqr_time = quantile(ppc_time, 0.75, na.rm = TRUE) - quantile(ppc_time, 0.25, na.rm = TRUE),
+    q1_ref = quantile(ppc_ref, 0.25, na.rm = TRUE),
+    q3_ref = quantile(ppc_ref, 0.75, na.rm = TRUE),
+    iqr_ref = quantile(ppc_ref, 0.75, na.rm = TRUE) - quantile(ppc_ref, 0.25, na.rm = TRUE),
+    peer_rev = sum(ppc_review == "YES"),
+    COPE = sum(cope == "TRUE")
+  )
+
+print(randLet_stats)
+```
+
+# View median and IQR for ALL quantitavtive limits in RANDOM journals
+```{r}
+
+randAll_stats <- dj_random %>%
+  filter(ppc_name == "Commentary" | ppc_name == "Letters" | ppc_name == "Other") %>%
+  mutate(
+    ppc_length = as.numeric(replace(ppc_length, ppc_length %in% c("Qualitative", "NOT STATED"), NA)),
+    ppc_time = as.numeric(replace(ppc_time, ppc_time %in% c("Qualitative", "NOT STATED"), NA)),
+    ppc_ref = as.numeric(replace(ppc_ref, ppc_ref %in% c("Qualitative", "NOT STATED"), NA))
+  ) %>%
+  summarize(
+    mdLength = median(ppc_length, na.rm = TRUE),
+    mdTime = median(ppc_time, na.rm = TRUE),
+    mdRef = median(ppc_ref, na.rm = TRUE),
+    q1_length = quantile(ppc_length, 0.25, na.rm = TRUE),
+    q3_length = quantile(ppc_length, 0.75, na.rm = TRUE),
+    iqr_length = quantile(ppc_length, 0.75, na.rm = TRUE) - quantile(ppc_length, 0.25, na.rm = TRUE),
+    q1_time = quantile(ppc_time, 0.25, na.rm = TRUE),
+    q3_time = quantile(ppc_time, 0.75, na.rm = TRUE),
+    iqr_time = quantile(ppc_time, 0.75, na.rm = TRUE) - quantile(ppc_time, 0.25, na.rm = TRUE),
+    q1_ref = quantile(ppc_ref, 0.25, na.rm = TRUE),
+    q3_ref = quantile(ppc_ref, 0.75, na.rm = TRUE),
+    iqr_ref = quantile(ppc_ref, 0.75, na.rm = TRUE) - quantile(ppc_ref, 0.25, na.rm = TRUE),
+    peer_rev = sum(ppc_review == "YES"),
+    COPE = sum(cope == "TRUE"),
+    count = n()
+  )
+
+print(randAll_stats)
+
+```
+
+COMPARING SAMPLES TO EACH OTHER ON PPC ACCEPTANCE
+```{r}
+
+dj_prom %>%
+mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
+    TRUE ~ has_ppc
+  ))
+
+dj_rand %>%
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
+    TRUE ~ has_ppc
+  ))
+
+chisq.test(x=dj_prom$has_ppc, y=dj_rand$has_ppc)
+
+prop.test()
+
+```
+```{r}
+# Sample data
+yes_prom <- 38  # Number of "yes" responses in Sample 1 (dj_prom)
+yes_rand <- 23  # Number of "yes" responses in Sample 2 (dj_rand)
+
+# Total number of observations in each sample (assuming 100)
+n_prom <- 100
+n_rand <- 100
+
+# Perform the proportion test
+test_result <- prop.test(x = c(yes_prom, yes_rand), n = c(n_prom, n_rand), alternative = "two.sided")
+
+# Print the test result
+print(test_result)
+
+```

### 2023-10-25 analysis/preprocessing.Rmd
Article exclusion & ref harmonise
Added group_by(sample_id) for article exclusion reasons to easily see reasons in both samples.

Added one additional argument to harmonise a reference statement

@@
 d_articles %>%
-  count(exclusion_final, exclusion_reason_final)
+  group_by(sample_id) %>%
+  count(exclusion_final, exclusion_reason_final) %>%
+  ungroup()
 ```
@@
            ref_harmonized == "a maximum of 5 references" ~ "5",
+           ref_harmonized == "max 20" ~ "20",
            ref_harmonized == "overall limit is 265 lines of text including references" ~ "NOT STATED",

### 2023-12-07 analysis/practiceCoding_AW.Rmd
Code update
Also, corrected readme file for prominent article sample instructions

@@
 ```
+```{r}
+
+d_journals %>%  
+  filter(sample_id == "prominent" | sample_id == "both") %>%
+  filter(ppc_type == "A") %>%
+  filter(!is.na(has_ppc)) %>%
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'Archive',
+    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
+      has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
+    has_ppc == 'YES' ~ 'Yes',
+    TRUE ~ has_ppc
+    )) %>%
+  group_by(has_ppc) %>%
+  summarise(count = n()) %>%
+  mutate(percentage = count / sum(count) * 100) %>%
+  ggplot(aes(x = "has_ppc", y = count, fill = has_ppc)) +
+  geom_bar(stat = "identity") +
+  theme_bw() +
+  scale_fill_brewer(palette = "Oranges") +
+  labs(title = "Prominent Journal PPC Acceptance", x = "Accepts PPC", y = "Percentage", fill = "PPC Policy")
+
+```
+```{r}
+library(dplyr)
+library(ggplot2)
+
+# Filter and process data for ppc_length
+ppc_length_data <- d_journals %>%
+  filter(sample_id %in% c("prominent", "both")) %>%
+  filter(!is.na(ppc_name)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_length = case_when(
+    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
+    ppc_length == "NOT STATED" ~ "Not Stated",
+    TRUE ~ 'Qualitative'
+  )) %>%
+  group_by(ppc_length) %>%
+  summarise(count = n())
+
+# Filter and process data for ppc_time
+ppc_time_data <- d_journals %>%
+  filter(sample_id %in% c("prominent", "both")) %>%
+  filter(!is.na(ppc_name)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_time = case_when(
+    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
+    ppc_time == "NOT STATED" ~ "Not Stated",
+    TRUE ~ 'Qualitative'
+  )) %>%
+  group_by(ppc_time) %>%
+  summarise(count = n())
+
+# Combine the data and unite the columns
+combined_data <- bind_rows(
+  ppc_length_data %>% mutate(Code = "Length"),
+  ppc_time_data %>% mutate(Code = "Time-to-submit")
+) %>%
+unite(limits, ppc_length, ppc_time) %>%
+  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
+                   limits == "Qualitative_NA" ~ "Qualitative",
+                   limits == "Quantitative_NA" ~ "Quantitative",
+                   limits == "NA_Not Stated" ~ "Not Stated",
+                   limits == "NA_Qualitative" ~ "Qualitative",
+                   limits == "NA_Quantitative" ~ "Quantitative",
+                   TRUE ~ as.character(limits)
+                   ))
+
+# Create a stacked bar chart
+ggplot(combined_data, aes(x = Code, y = count, fill = limits)) +
+  geom_bar(stat = "identity", 
+           position = "stack",
+           colour = "black") +
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues") +
+  labs( x = "Restriction Type", y = "Count", fill = "Restriction")
+
+```
+# COMBINED GRAPHS OF PPC POLICY AND RESTRICTIONS (PROMINENT)
+```{r}
+
+# Create the first graph
+graph1 <- ggplot(combined_data, aes(x = Code, y = count, fill = limits)) +
+  geom_bar(stat = "identity", 
+           position = "stack",
+           colour = "black") +
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues") +
+  labs(x = "Restriction Type", y = "Count", fill = "Restrictions")
+
+# Create the second graph
+graph2 <- d_journals %>%
+  filter(sample_id == "prominent" | sample_id == "both") %>%
+  filter(ppc_type == "A") %>%
+  filter(!is.na(has_ppc)) %>%
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'Archive',
+    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
+    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
+    has_ppc == 'YES' ~ 'Yes',
+    TRUE ~ has_ppc
+  )) %>%
+  group_by(has_ppc) %>%
+  summarise(count = n()) %>%
+  mutate(percentage = count / sum(count) * 100) %>%
+  ggplot(aes(x = "", y = count, fill = has_ppc)) +
+  geom_bar(stat = "identity",
+           colour = "black") +
+  theme_bw() +
+  scale_fill_brewer(palette = "Oranges") +
+  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")
+
+# Arrange both graphs in the same figure
+combined_plots <- graph2 + graph1
+combined_plots
+
+ggsave(filename = "Prominent_statements.png", plot = last_plot(), device = "png")
+```
+# COMBINED GRAPHS OF PPC POLICY AND RESTRICTIONS (RANDOM)
+```{r}
+
+# Filter and process data for ppc_length
+ppc_length_random <- d_journals %>%
+  filter(sample_id %in% c("random", "both")) %>%
+  filter(!is.na(ppc_name)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_length = case_when(
+    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
+    ppc_length == "NOT STATED" ~ "Not Stated",
+    TRUE ~ 'Qualitative'
+  )) %>%
+  group_by(ppc_length) %>%
+  summarise(count = n())
+
+# Filter and process data for ppc_time
+ppc_time_random<- d_journals %>%
+  filter(sample_id %in% c("random", "both")) %>%
+  filter(!is.na(ppc_name)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_time = case_when(
+    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
+    ppc_time == "NOT STATED" ~ "Not Stated",
+    TRUE ~ 'Qualitative'
+  )) %>%
+  group_by(ppc_time) %>%
+  summarise(count = n())
+
+# Combine the data and unite the columns
+combined_data_random <- bind_rows(
+  ppc_length_random %>% mutate(Code = "Length"),
+  ppc_time_random %>% mutate(Code = "Time-to-submit")
+) %>%
+unite(limits, ppc_length, ppc_time) %>%
+  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
+                   limits == "Qualitative_NA" ~ "Qualitative",
+                   limits == "Quantitative_NA" ~ "Quantitative",
+                   limits == "NA_Not Stated" ~ "Not Stated",
+                   limits == "NA_Qualitative" ~ "Qualitative",
+                   limits == "NA_Quantitative" ~ "Quantitative",
+                   TRUE ~ as.character(limits)
+                   ))
+
+# Create the first graph
+graph4 <- ggplot(combined_data_random, aes(x = Code, y = count, fill = limits)) +
+  geom_bar(stat = "identity", 
+           position = "stack",
+           colour = "black") +
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues") +
+  labs(x = "Restriction Type", y = "Count", fill = "Restrictions")
+
+# Create the second graph
+graph3 <- d_journals %>%
+  filter(sample_id == "random" | sample_id == "both") %>%
+  filter(ppc_type == "A") %>%
+  filter(!is.na(has_ppc)) %>%
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'Archive',
+    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
+    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
+    has_ppc == 'YES' ~ 'Yes',
+    TRUE ~ has_ppc
+  )) %>%
+  group_by(has_ppc) %>%
+  summarise(count = n()) %>%
+  mutate(percentage = count / sum(count) * 100) %>%
+  ggplot(aes(x = "", y = count, fill = has_ppc)) +
+  geom_bar(stat = "identity",
+           colour = "black") +
+  theme_bw() +
+  scale_fill_brewer(palette = "Oranges") +
+  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")
+
+# Arrange both graphs in the same figure
+combined_plots <- graph3 + graph4
+combined_plots
+
+ggsave(filename = "Random_statements.png", plot = last_plot(), device = "png")
+
+```
+
+```{r}
+library(dplyr)
+library(ggplot2)
+
+d_journals %>%
+  filter(sample_id %in% c("prominent", "both")) %>%
+  filter(ppc_type == "A") %>%
+  filter(!is.na(has_ppc) & !is.na(ppc_length)) %>%
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'Archive',
+    has_ppc %in% c('NO EXPLICIT', 'NO IMPLICIT') ~ 'No',
+    has_ppc == 'Yes' ~ 'Yes',
+    TRUE ~ as.character(has_ppc)
+  )) %>%
+  mutate(ppc_length = case_when(
+    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
+    ppc_length == "NOT STATED" ~ "Not Stated",
+    TRUE ~ as.character(ppc_length)
+  )) %>%
+  group_by(category = c("has_ppc", "ppc_length"), variable = case_when(
+    category == "has_ppc" ~ has_ppc,
+    category == "ppc_length" ~ ppc_length
+  )) %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  mutate(percentage = count / sum(count) * 100) %>%
+  ggplot(aes(x = category, y = percentage, fill = variable)) +
+  geom_bar(stat = "identity") +
+  facet_wrap(~category, scales = "free") +
+  theme_bw() +
+  scale_fill_brewer(palette = "Oranges") +
+  labs(title = "Prominent Journal PPC Acceptance", x = "Accepts PPC", y = "Percentage", fill = "Variable")
+
+```
 
@@
 CREATE FIGURES FOR TYPES OF RESTRICTION STATEMENTS
+
+#TEST CHATGPT
+```{r}
+
+# Reshape the data to long format
+my_tibble_long <- dj_prominent %>%
+  gather(variable, category, has_ppc, ppc_length, ppc_time)
+
+# Create the bar graph
+my_tibble_long %>%
+  filter(!is.na(ppc_length)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_length = case_when(
+    ppc_length %in% c(1000, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ "Quantitative",
+    ppc_length == "NOT STATED" ~ "Not Stated",
+    TRUE ~ as.character(ppc_length)
+  )) %>%
+ggplot(aes(x = category, fill = variable)) +
+  geom_bar(position = "dodge") +
+  labs(x = "Categories", y = "Count") +
+  theme_minimal()
+
+```
 
@@
   theme_bw() +
-  coord_flip() +
   scale_y_continuous(limits = c(0, 41)) +
@@
 ```
+ #Coder Disagreements
+```{r}
+
+d_journals %>%
+  filter(coder_id != "FINAL (TEH)") %>%
+
+```

### 2023-12-11 analysis/practiceCoding_AW.Rmd
Code cleaning
removed redundant and irrelevant code chunks and reorganised into more logical sequence

--- 2023-10-25 analysis/practiceCoding_AW.Rmd
@@
 ```
+# Create separate tibbles for Prominent and Randomly-selected journal samples
+```{r}
+dj_prominent <- d_journals %>%
+  filter(sample_id != "random") %>%
+  filter(is_empirical == TRUE)
 
-# Journal Policy Overview
+dj_random <- d_journals %>%
+  filter(sample_id != "prominent") %>%
+  filter(is_empirical == TRUE)
+```
+# DESCRIPTIVE STATISTICS
+
+# JIF median and IQR (prominent sample)
+```{r}
+
+# Calculate mean and median JIF for entire prominent sample
+dj_prominent %>%
+  filter(ppc_type == "A") %>%
+  mutate(jif = round(jif, 2)) %>%
+  summarise(mean(jif), median(jif))
+```
+
+# JIF median and IQR by subfield (prominent sample)
+```{r}
+# Group the tibble by the 'field' column
+prom_grouped <- dj_prominent %>% 
+  filter(ppc_type == "A") %>%
+  group_by(field)
+
+# Compute summary statistics for 'jif' within each group
+promJIF_stats <- prom_grouped %>%
+  mutate(jif = round(jif, 2)) %>%
+  summarize(
+    mean_jif = mean(jif),
+    median_jif = median(jif),
+    q1_jif = quantile(jif, 0.25),
+    q3_jif = quantile(jif, 0.75),
+    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
+    count = n()
+  )
+
+# View the summary statistics
+print(promJIF_stats)
+```
+
+# JIF median and IQR (random sample)
+``` {r}
+# Calculate mean and median JIF for entire random sample
+dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(!is.na(jif)) %>%
+  mutate(jif = round(jif, 2)) %>%
+  summarise(mean(jif), median(jif))
+```
+
+# JIF median and IQR by subfield (random sample)
+```{r}
+# Group the tibble by the 'field' column
+rand_grouped <- dj_random %>% 
+  filter(ppc_type == "A") %>%
+  filter(!is.na(jif)) %>% 
+  group_by(field)
+
+# Compute summary statistics for 'jif' within each group
+randJIF_stats <- rand_grouped %>%
+  filter(ppc_type == "A") %>%
+  filter(is_empirical == "TRUE") %>%
+  mutate(jif = round(jif, 2)) %>%
+  summarize(
+    mean_jif = mean(jif),
+    median_jif = median(jif),
+    q1_jif = quantile(jif, 0.25),
+    q3_jif = quantile(jif, 0.75),
+    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
+    count = n()
+  )
+
+# View the summary statistics
+print(randJIF_stats)
+
+dj_random %>%
+   filter(!is.na(jif)) %>%
+  mutate(jif = round(jif, 2)) %>%
+  summarize(
+    mean_jif = mean(jif),
+    median_jif = median(jif),
+    q1_jif = quantile(jif, 0.25),
+    q3_jif = quantile(jif, 0.75),
+    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
+    count = n()
+  )
+
+```
+
+# Journal PPC Policy Overview
 ```{r}
@@
 d_journals_anyPPC <- d_journals %>%
-  filter(ppc_type == "A") %>%
-  filter(is_empirical == "TRUE")
+  filter(ppc_type == "A") %>% # Filters to a single row for each journal
+  filter(is_empirical == "TRUE") # Remove excluded journals
 
@@
 
-``` {r}
+# PPC policy by COPE membership status (prominent sample)
+```{r}
 
-d_journalsEmp <- d_journals %>%
-  filter(is_empirical == "TRUE") %>%
-  filter(ppc_type == "A")
+table_PPCbyCOPEprom <- dj_prominent %>%
+  filter(ppc_type == "A" & is_empirical == TRUE) %>%
+  count(has_ppc, cope)
 
-table(d_journalsEmp$field, d_journalsEmp$sample_id)
+print(table_PPCbyCOPEprom)
 
@@
 
-# Create tibbles for prominent and random journal samples
+# PPC policy by COPE membership status (random sample)
 ```{r}
-dj_prom <- d_journalsEmp %>%
-  mutate(sample_id = case_when(
-    sample_id == "both" ~ "prominent",
-    TRUE ~ sample_id
-  )) %>%
-  filter(sample_id == "prominent")
 
-dj_random <- d_journalsEmp %>%
-  mutate(sample_id = case_when(
-    sample_id == "both" ~ "random",
-    TRUE ~ sample_id
-  )) %>%
-  filter(sample_id == "random")
+table_PPCbyCOPErand <- dj_random %>%
+  filter(ppc_type == "A" & is_empirical == TRUE) %>%
+  count(has_ppc, cope)
+
+print(table_PPCbyCOPErand)
+
 ```
 
-# Descriptives for each journal sample 
+# Descriptives for each journal sample [**EDIT so these tables show ppc_type == "A" only**]
 ```{r}
-table(dj_prom$field, dj_prom$has_ppc)
+table(dj_prominent$field, dj_prominent$has_ppc)
 table(dj_random$field, dj_random$has_ppc)
 
-table(dj_prom$field, dj_prom$cope)
+table(dj_prominent$field, dj_prominent$cope)
 table(dj_random$field, dj_random$cope)
@@
 
-# Plot sample id by field
-```{r}
+# ANALYSIS
 
-d_journals %>%
-  ggplot() +
-  geom_bar(
-    mapping = aes(x = field, fill = sample_id),
-    stat = "count",
-    position = "stack",
-    colour = "black",
-    just = 0.5,
-    width = 0.7,
-    na.rm = FALSE,
-    orientation = NA,
-    show.legend = TRUE,
-    inherit.aes = TRUE
-  ) +
-  theme_bw() +
-  scale_fill_brewer(palette = "Oranges") +
-  labs(title = "Sample ID by Field", x = "Field", y = "Count")
-
-```
-
-# CHAT GPT TEST
-```{r}
-library(dplyr)
-library(ggplot2)
-
-d_journals %>%
-  mutate(has_ppc = case_when(
-    has_ppc == 'ARCHIVE' ~ 'YES',
-    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
-    TRUE ~ has_ppc
-  )) %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc %in% c("YES", "NO")) %>%
-  filter(sample_id == 'both' | sample_id == 'random') %>%
-  group_by(field, has_ppc) %>%  # Group by field and has_ppc
-  summarise(count = n()) %>%   # Calculate counts for each combination
-  group_by(field) %>%           # Group by field only
-  mutate(percentage = round(count / sum(count) * 100)) %>%  # Calculate percentages within each field and round
-  ggplot() +
-  geom_bar(
-    mapping = aes(x = field, y = count, fill = has_ppc),
-    stat = "identity",  # Use "identity" for y values
-    position = "stack",
-    colour = "black",
-    width = 0.7,
-    na.rm = FALSE,
-    orientation = NA,
-    show.legend = TRUE,
-    inherit.aes = TRUE
-  ) +
-  theme_bw() +
-  scale_fill_brewer(palette = "Blues") +
-  labs(title = "Random Journal PPC Acceptance by Field", x = "Field", y = "Count")
-
-```
-
-# Create bar plot of PPC policy by Field
-```{r}
-
-# Creates bar graph for Prominent journals
-
-d_journals %>%  
-  mutate(has_ppc = case_when(
-    has_ppc == 'ARCHIVE' ~ 'YES',
-    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
-    TRUE ~ has_ppc
-    )) %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "YES" | has_ppc == "NO") %>%
-  filter(sample_id == 'both' | sample_id == 'prominent') %>%
-  ggplot() +
-geom_bar(
-  mapping = aes(x=field, fill = has_ppc),
-  stat = "count",
-  position = "stack",
-  colour = "black",
-  just = 0.5,
-  width = 0.7,
-  na.rm = FALSE,
-  orientation = NA,
-  show.legend = TRUE,
-  inherit.aes = TRUE
-) +
-  theme_bw() +
-  scale_fill_brewer(palette = "Blues") +
-  labs(title = "Prominent Journal PPC Acceptance by Field", x = "Field", y = "Count")
-```
-
-# Creates bar graph for Random journals
-``` {r}
-d_journals %>%  
-  mutate(has_ppc = case_when(
-    has_ppc == 'ARCHIVE' ~ 'YES',
-    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
-    TRUE ~ has_ppc
-    )) %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "YES" | has_ppc == "NO") %>%
-  filter(sample_id == 'both' | sample_id == 'random') %>%
-  ggplot() +
-geom_bar(
-  mapping = aes(x=field, fill = has_ppc),
-  stat = "count",
-  position = "stack",
-  colour = "black",
-  just = 0.5,
-  width = 0.7,
-  na.rm = FALSE,
-  orientation = NA,
-  show.legend = TRUE,
-  inherit.aes = TRUE
-) +
-  theme_bw() +
-  scale_fill_brewer(palette = "Blues") +
-  labs(title = "Random Journal PPC Acceptance by Field", x = "Field", y = "Count")
-```
-
-# Plot PPC length limits by Field and COPE
-```{r}
-d_length <- d_journals %>%
-  select(has_ppc, journal_name, jif, cope, ppc_length, ppc_time, ppc_ref, field) %>%
-  filter(has_ppc=="YES") %>%
-  filter(ppc_length !="NOT STATED") %>%
-  filter(ppc_length !="Qualitative limit")
-
-d_length$ppc_length <- as.numeric(d_length$ppc_length)
-
-d_length %>%
-ggplot() +
-  geom_point(aes(x = ppc_length, 
-                               y = jif,
-                              shape = cope, 
-                              colour = field,
-                              size=1, 
-                              alpha = 0.7, 
-                              show.legend = FALSE,
-                              inherit.aes = FALSE)) +
-  theme_grey() +
-  labs(title = "Word Limits by JIF where PPC Accepted", x = "Word Limits", y = "Journal Impact Factor") +
-  scale_fill_brewer(palette="Accent") 
-```
-
-# Calculate CIs for YES 
+# Calculate CIs for YES [**EDIT TO DERIVE NUMBERS FROM DATA**]
 Not sure if this makes sense to do for Prominent and Total, as these are not random samples
@@
 
-# Calculate CIs for NO 
+# Calculate CIs for NO [**EDIT TO DERIVE NUMBERS FROM DATA**]
 ```{r}
@@
 
-table(d_journals$ppc_name)  #PPCnames
-table(d_journals$sample_id, d_journals$ppc_name) #lists journals with PPC types
+table(d_journals$ppc_name)  #PPC names from all entries
+table(d_journals$sample_id, d_journals$ppc_name) #PPC names from each sample
 
@@
 
-# Look at PPC length limitations
+# PPC length limitations (Prominent)
 ```{r}
 
-# Removes journals that do not offer any PPC 
- d_PPConly <- d_journals %>%
-   filter(has_ppc == "YES")
+table(dj_prominent$ppc_length, dj_prominent$ppc_name)
 
-#Look at stated length limits
-PPC_length <- d_PPConly %>%
-  filter(!is.na(ppc_length)) %>%
-  filter(ppc_length != "NO") %>%
-  filter(ppc_length != "NOT STATED")
-
-dj_prominent <- d_journals %>%
-  filter(sample_id != "random")
-
-dj_random <- d_journals %>%
-  filter(sample_id != "prominent")
-
-#table_length <- table(PPC_length$ppc_length, PPC_length$ppc_name)
-table(dj_prominent$ppc_length, dj_prominent$ppc_name)
-table(dj_random$ppc_length, dj_random$ppc_name)
 ```
-
-# Mean JIF by field and sample
+# PPC length limitations (Random)
 ```{r}
 
-dj_prom %>%
-  filter(ppc_type == "A") %>%
-  group_by(field) %>%
-  summarise(mnJIF = mean(jif)) %>%
-  ungroup()
+table(dj_random$ppc_length, dj_random$ppc_name)
 
-dj_prom %>%
-  filter(ppc_type == "A") %>%
-  mutate(jif = round(jif, 2)) %>%
-  summarise(mean(jif), median(jif))
+```
+# PPC time limitations (Prominent)
+``` {r}
+
+table(dj_prominent$ppc_time, dj_prominent$ppc_name)
 
@@
 
-```{r}
-dj_random %>%
-  filter(ppc_type == "A") %>%
-  filter(!is.na(jif)) %>%
-  group_by(field) %>%
-  summarise(mnJIF = mean(jif)) %>%
-  ungroup()
-
-dj_random %>%
-  filter(ppc_type == "A") %>%
-  filter(!is.na(jif)) %>%
-  mutate(jif = round(jif, 2)) %>%
-  summarise(mean(jif), median(jif))
-```
-# PPC and COPE
+# PPC time limitations (Random)
 ```{r}
 
-table(dj_prom$has_ppc, dj_prom$cope)
-
-dj_rand <- dj_random %>%
-  filter(ppc_type == "A") %>%
-  filter(is_empirical == TRUE)
-
-table(dj_rand$has_ppc, dj_rand$cope)
+table(dj_random$ppc_time, dj_random$ppc_name)
 
@@
 
-# Look at PPC time limitations
-``` {r}
-
-table(dj_prominent$ppc_time, dj_prominent$ppc_name)
-table(dj_random$ppc_time, dj_random$ppc_name)
-
-```
-CREATE FIGURES FOR TYPES OF RESTRICTION STATEMENTS
-
-# FIGURE of PROMINENT length limits
+# Create and combine restiction statement graphs with ppc acceptance (prominent sample)
 ```{r}
 
-dj_prominent %>%
-  filter(!is.na(ppc_length)) %>%
+# Filter and transform restrictions for ppc_length
+ppc_length_data <- dj_prominent %>%
+  filter(!is.na(ppc_name)) %>%
+  filter(has_ppc != "ARCHIVE") %>% # removes Archive Only PPC types
+  mutate(ppc_length = case_when(
+    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
+    ppc_length == "NOT STATED" ~ "Not Stated",
+    TRUE ~ 'Qualitative' # Summarises all length limits as 'Quantitative', 'Qualitative', or 'Not Stated'
+  )) %>% 
+  group_by(ppc_length) %>%
+  summarise(count = n())
+
+# Filter and transform restrictions for ppc_time
+ppc_time_data <- dj_prominent %>%
+  filter(!is.na(ppc_name)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_time = case_when(
+    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
+    ppc_time == "NOT STATED" ~ "Not Stated",
+    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
+  )) %>%
+  group_by(ppc_time) %>%
+  summarise(count = n())
+
+# Combine the data and unite the columns
+combined_data <- bind_rows(
+  ppc_length_data %>% mutate(Code = "Length"),
+  ppc_time_data %>% mutate(Code = "Time-to-submit")
+) %>%
+unite(limits, ppc_length, ppc_time) %>%
+  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
+                   limits == "Qualitative_NA" ~ "Qualitative",
+                   limits == "Quantitative_NA" ~ "Quantitative",
+                   limits == "NA_Not Stated" ~ "Not Stated",
+                   limits == "NA_Qualitative" ~ "Qualitative",
+                   limits == "NA_Quantitative" ~ "Quantitative",
+                   TRUE ~ as.character(limits)
+                   ))
+
+# Create the first graph
+graph1 <- ggplot(combined_data, aes(x = Code, y = count, fill = limits)) +
+  geom_bar(stat = "identity", 
+           position = "stack",
+           colour = "black") +
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues") +
+  labs(x = "Restriction Type", y = "Count", fill = "Restrictions")
+
+# Create the second graph
+graph2 <- dj_prominent %>%
+  filter(ppc_type == "A") %>% # Keeps only first PPC row for each journal
+  filter(!is.na(has_ppc)) %>%
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'Archive',
+    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
+    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
+    has_ppc == 'YES' ~ 'Yes',
+    TRUE ~ has_ppc
+  )) %>%
+  group_by(has_ppc) %>%
+  summarise(count = n()) %>%
+  mutate(percentage = count / sum(count) * 100) %>%
+  ggplot(aes(x = "", y = count, fill = has_ppc)) +
+  geom_bar(stat = "identity",
+           colour = "black") +
+  theme_bw() +
+  scale_fill_brewer(palette = "Oranges") +
+  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")
+
+# Arrange both graphs in the same figure
+combined_plots <- graph2 + graph1
+combined_plots
+
+ggsave(filename = "Prominent_statements.png", plot = last_plot(), device = "png")
+```
+# Create and combine restiction statement graphs with ppc acceptance (random sample)
+```{r}
+
+# Filter and process data for ppc_length
+ppc_length_random <- d_journals %>%
+  filter(sample_id %in% c("random", "both")) %>%
+  filter(!is.na(ppc_name)) %>%
   filter(has_ppc != "ARCHIVE") %>%
   mutate(ppc_length = case_when(
-    ppc_length %in% c(1000, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ "Quantitative",
+    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
     ppc_length == "NOT STATED" ~ "Not Stated",
-    TRUE ~ as.character(ppc_length)
+    TRUE ~ 'Qualitative'
   )) %>%
-  ggplot(mapping = aes(x = ppc_length, fill = ppc_name)) +
-  geom_bar(position = "stack",
-           colour = "black",
-           width = 0.5) +
-  theme_bw() +
-  coord_flip() +
-  scale_y_continuous(limits = c(0, 41)) +
-  scale_fill_brewer(palette = "Blues") +
-  theme(legend.position = c(0.9, 0.5)) +
-  labs(x = "Length Limit Statement", y = "Count", fill = "PPC Type")
+  group_by(ppc_length) %>%
+  summarise(count = n())
 
-ggsave(filename = "Prominent_length.png", plot = last_plot(), device = "png")
-```
-# FIGURE of PROMINENT time limits
-```{r}
-
-dj_prominent %>%
-  filter(!is.na(ppc_time)) %>%
+# Filter and process data for ppc_time
+ppc_time_random<- d_journals %>%
+  filter(sample_id %in% c("random", "both")) %>%
+  filter(!is.na(ppc_name)) %>%
   filter(has_ppc != "ARCHIVE") %>%
   mutate(ppc_time = case_when(
-    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ "Quantitative",
+    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
     ppc_time == "NOT STATED" ~ "Not Stated",
-    TRUE ~ as.character(ppc_time)  # Keep other values as they are
+    TRUE ~ 'Qualitative'
   )) %>%
-  ggplot(mapping = aes(x = ppc_time, fill = ppc_name)) +
-  geom_bar(position = "stack",
-           colour = "black",
-           width = 0.5,
-           ) +
+  group_by(ppc_time) %>%
+  summarise(count = n())
+
+# Combine the data and unite the columns
+combined_data_random <- bind_rows(
+  ppc_length_random %>% mutate(Code = "Length"),
+  ppc_time_random %>% mutate(Code = "Time-to-submit")
+) %>%
+unite(limits, ppc_length, ppc_time) %>%
+  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
+                   limits == "Qualitative_NA" ~ "Qualitative",
+                   limits == "Quantitative_NA" ~ "Quantitative",
+                   limits == "NA_Not Stated" ~ "Not Stated",
+                   limits == "NA_Qualitative" ~ "Qualitative",
+                   limits == "NA_Quantitative" ~ "Quantitative",
+                   TRUE ~ as.character(limits)
+                   ))
+
+# Create the first graph
+graph4 <- ggplot(combined_data_random, aes(x = Code, y = count, fill = limits)) +
+  geom_bar(stat = "identity", 
+           position = "stack",
+           colour = "black") +
   theme_bw() +
-  coord_flip() +
-  scale_y_continuous(limits = c(0, 41)) +
   scale_fill_brewer(palette = "Blues") +
-  theme(legend.position = c(0.9, 0.5)) +
-  labs(x = "Time-to-Submit Limit Statement", y = "Count", fill = "PPC Type")
+  labs(x = "Restriction Type", y = "Count", fill = "Restrictions")
 
-ggsave(filename = "Prominent_time.png", plot = last_plot(), device = "png")
-```
-# FIGURE of PROMINENT reference limits
-```{r}
+# Create the second graph
+graph3 <- d_journals %>%
+  filter(sample_id == "random" | sample_id == "both") %>%
+  filter(ppc_type == "A") %>%
+  filter(!is.na(has_ppc)) %>%
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'Archive',
+    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
+    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
+    has_ppc == 'YES' ~ 'Yes',
+    TRUE ~ has_ppc
+  )) %>%
+  group_by(has_ppc) %>%
+  summarise(count = n()) %>%
+  mutate(percentage = count / sum(count) * 100) %>%
+  ggplot(aes(x = "", y = count, fill = has_ppc)) +
+  geom_bar(stat = "identity",
+           colour = "black") +
+  theme_bw() +
+  scale_fill_brewer(palette = "Oranges") +
+  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")
 
-dj_prominent %>%
-  filter(!is.na(ppc_ref)) %>%
-  filter(has_ppc != "ARCHIVE") %>%
-  mutate(ppc_ref = case_when(
-    ppc_ref %in% c(10, 15, 20, 5, "max 20") ~ "Quantitative",
-    ppc_ref == "NOT STATED" ~ "Not Stated",
-    TRUE ~ as.character(ppc_ref)  # Keep other values as they are
-  )) %>%
-  ggplot(mapping = aes(x = ppc_ref, fill = ppc_name)) +
-  geom_bar(position = "stack",
-           colour = "black",
-           width = 0.5,
-           ) +
-  theme_bw() +
-  coord_flip() +
-  scale_y_continuous(limits = c(0, 41)) +
-  scale_fill_brewer(palette = "Blues") +
-  theme(legend.position = c(0.9, 0.5)) +
-  labs(x = "Reference Limit Statement", y = "Count", fill = "PPC Type")
+# Arrange both graphs in the same figure
+combined_plots <- graph3 + graph4
+combined_plots
 
-ggsave(filename = "Prominent_ref.png", plot = last_plot(), device = "png")
-```
-# FIGURE of PROMINENT Peer-Review 
-```{r}
+ggsave(filename = "Random_statements.png", plot = last_plot(), device = "png")
 
-dj_prominent %>%
-  filter(!is.na(ppc_review)) %>%
-  filter(has_ppc != "ARCHIVE") %>%
- mutate(ppc_review = fct_relevel(
-    case_when(
-      ppc_review == "YES" ~ "Yes",
-      ppc_review == "NO" ~ "No",
-      ppc_review == "NOT STATED" ~ "Not Stated",
-      TRUE ~ as.character(ppc_review)  # Keep other values as they are
-    ),
-    c("Not Stated", "No", "Yes")  # Specify the desired order
-  )) %>%
-  ggplot(mapping = aes(x = ppc_review, fill = ppc_name)) +
-  geom_bar(position = "stack",
-           colour = "black",
-           width = 0.5,
-           ) +
-  theme_bw() +
-  coord_flip() +
-  scale_y_continuous(limits = c(0, 41)) +
-  scale_fill_brewer(palette = "Blues") +
-  theme(legend.position = c(0.9, 0.5)) +
-  labs(x = "PPC Sent for Peer-review", y = "Count", fill = "PPC Type")
-
-ggsave(filename = "Prominent_review.png", plot = last_plot(), device = "png")
-```
-
-# FIGURE of RANDOM Length Limits
-```{r}
-
-dj_random %>%
-  filter(!is.na(ppc_length)) %>%
-  mutate(ppc_length = case_when(
-    ppc_length %in% c(1000, 1100, 1200, 2000, 2500, 2650, 500) ~ "Quantitative",
-    ppc_length == "NOT STATED" ~ "Not Stated",
-    TRUE ~ as.character(ppc_length)  # Keep other values as they are
-  )) %>%
-  ggplot(mapping = aes(x = ppc_length, fill = ppc_name)) +
-  geom_bar(position = "stack",
-           colour = "black",
-           width = 0.5,
-           ) +
-  theme_bw() +
-  coord_flip() +
-  scale_y_continuous(limits = c(0, 25)) +
-  scale_fill_brewer(palette = "Blues") +
-  theme(legend.position = c(0.9, 0.7)) +
-  labs(x = "Length Limit Statement", y = "Count", fill = "PPC Type")
-
-ggsave(filename = "Random_length.png", plot = last_plot(), device = "png")
-```
-
-# FIGURE of RANDOM time limits
-```{r}
-
-dj_random %>%
-  filter(!is.na(ppc_time)) %>%
-  filter(has_ppc != "ARCHIVE") %>%
-  mutate(ppc_time = case_when(
-    ppc_time %in% 39.15 ~ "Quantitative",
-    ppc_time == "NOT STATED" ~ "Not Stated",
-    TRUE ~ as.character(ppc_time)  # Keep other values as they are
-  )) %>%
-  ggplot(mapping = aes(x = ppc_time, fill = ppc_name)) +
-  geom_bar(position = "stack",
-           colour = "black",
-           width = 0.5,
-           ) +
-  theme_bw() +
-  coord_flip() +
-  scale_y_continuous(limits = c(0, 25)) +
-  scale_fill_brewer(palette = "Blues") +
-  theme(legend.position = c(0.9, 0.7)) +
-  labs(x = "Time-to-Submit Limit Statement", y = "Count", fill = "PPC Type")
-
-ggsave(filename = "Random_time.png", plot = last_plot(), device = "png")
-```
-# FIGURE of PROMINENT reference limits
-```{r}
-
-dj_random %>%
-  filter(!is.na(ppc_ref)) %>%
-  filter(has_ppc != "ARCHIVE") %>%
-  mutate(ppc_ref = case_when(
-    ppc_ref %in% c(10, 15, 5) ~ "Quantitative",
-    ppc_ref == "NOT STATED" ~ "Not Stated",
-    TRUE ~ as.character(ppc_ref)  # Keep other values as they are
-  )) %>%
-  ggplot(mapping = aes(x = ppc_ref, fill = ppc_name)) +
-  geom_bar(position = "stack",
-           colour = "black",
-           width = 0.5,
-           ) +
-  theme_bw() +
-  coord_flip() +
-  scale_y_continuous(limits = c(0, 25)) +
-  scale_fill_brewer(palette = "Blues") +
-  theme(legend.position = c(0.9, 0.7)) +
-  labs(x = "Reference Limit Statement", y = "Count", fill = "PPC Type")
-
-ggsave(filename = "Random_ref.png", plot = last_plot(), device = "png")
-```
-# FIGURE of RANDOM Peer-Review 
-```{r}
-
-dj_random %>%
-  filter(!is.na(ppc_review)) %>%
-  filter(has_ppc != "ARCHIVE") %>%
- mutate(ppc_review = fct_relevel(
-    case_when(
-      ppc_review == "YES" ~ "Yes",
-      ppc_review == "NO" ~ "No",
-      ppc_review == "NOT STATED" ~ "Not Stated",
-      TRUE ~ as.character(ppc_review)  # Keep other values as they are
-    ),
-    c("Not Stated", "No", "Yes")  # Specify the desired order
-  )) %>%
-  ggplot(mapping = aes(x = ppc_review, fill = ppc_name)) +
-  geom_bar(position = "stack",
-           colour = "black",
-           width = 0.5,
-           ) +
-  theme_bw() +
-  coord_flip() +
-  scale_y_continuous(limits = c(0, 25)) +
-  scale_fill_brewer(palette = "Blues") +
-  theme(legend.position = c(0.9, 0.7)) +
-  labs(x = "PPC Sent for Peer-review", y = "Count", fill = "PPC Type")
-
-ggsave(filename = "Random_review.png", plot = last_plot(), device = "png")
 ```
@@
 
-# Presentation Graph of PPC by Sample
-
-```{r}
-
-library(dplyr)
-library(ggplot2)
-library(forcats)
-
-library(dplyr)
-
-# Duplicate rows with sample_id "both" and rename the duplicates as "Prominent"
-duplicated_prominent_rows <- d_journals %>%
-    mutate(has_ppc = case_when(
-    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
-    TRUE ~ has_ppc
-  )) %>%
-  filter(ppc_type == "A") %>%
-  filter(is_empirical == TRUE) %>%
-  filter(sample_id == "both") %>%
-  mutate(sample_id = "prominent")
-
-# Combine the duplicated "Prominent" rows with the original data
-d_journals_processed <- bind_rows(d_journals, duplicated_prominent_rows) %>%
-  mutate(sample_id = recode(sample_id, "prominent" = "Prominent", "random" = "Random"))
-
-# Now, the dataset contains the original "both" rows and their duplicates as "Prominent"
-
-d_journals_processed %>%
-   mutate(has_ppc = case_when(
-    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
-    TRUE ~ has_ppc
-  )) %>%
-  filter(ppc_type == "A") %>%
-  filter(is_empirical == TRUE) %>%
-  mutate(sample_id = ifelse(sample_id == "both", "Random", sample_id)) %>%
-  ggplot() +
-  geom_bar(
-    mapping = aes(x = has_ppc, fill = sample_id),
-    stat = "count",
-    position = position_dodge(width = 0.8),  # Use position = "dodge" to create side-by-side bars
-    colour = "black",
-    alpha = 0.7,
-    width = 0.7,
-    na.rm = FALSE,
-    orientation = "vertical",
-    show.legend = TRUE,
-    inherit.aes = TRUE
-  ) +
-  geom_text(
-    aes(x = has_ppc, y = ..count.., label = ..count.., group = sample_id),
-    stat = "count",
-    position = position_dodge(width = 0.8),
-    vjust = -0.5,  # Adjust the vertical position of the labels
-    size = 6
-  ) +
-  theme_bw() +
-  ylim(0, 100) +
-  scale_fill_brewer(palette = "Set2") +
-  labs(title = "Journal PPC Acceptance by Sample",
-       x = "Accepts PPC",
-       y = "Count",
-       fill = "Sample"  # Customize the legend title here
-  ) + 
-  theme(
-    text = element_text(size = 18)  # Increase the font size here
-  )
-
-ggsave(filename = "PPCbySample.png", plot = last_plot(), device = "png")
-```
-
-# Articles and Prevalence
-
-# Calculate CIs for NO 
-```{r}
-library(binom)
-
-# Prominent Sample data for linked
-plPPCsuccess <- 1
-rlPPCsuccess <- 0
-linkedSample <- 101
-
-confidence_level <- 0.95
-
-# Calculate the Wilson confidence interval
-ci_plPPC <- binom.confint(plPPCsuccess, linkedSample, method = "wilson", conf.level = confidence_level)
-ci_rlPPC <- binom.confint(rlPPCsuccess, linkedSample, method = "wilson", conf.level = confidence_level)
-
-# Print the confidence interval
-print(ci_plPPC)
-print(ci_rlPPC)
-
-```
-```{r}
-library(dplyr)
-library(ggplot2)
-library(forcats)
-
-# Modify the dataset to ensure "both" values are included in both "Prominent" and "Random"
-d_journals_processed <- d_journals %>%
-  mutate(has_ppc = case_when(
-    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
-    TRUE ~ has_ppc
-  )) %>%
-  filter(ppc_type == "A") %>%
-  filter(is_empirical == TRUE) %>%
-  mutate(sample_id = fct_recode(sample_id, 
-                                "Prominent" = "prominent", 
-                                "Random" = "random",
-                                "Both" = "both"))
-
-# Create a summary dataset to count "both" values in both "Prominent" and "Random"
-summary_data <- d_journals_processed %>%
-  filter(sample_id %in% c("Prominent", "Random")) %>%
-  group_by(has_ppc, sample_id) %>%
-  summarise(count = sum(count)) %>%
-  ungroup()
-
-# Create the ggplot with count labels
-ggplot(data = summary_data) +
-  geom_bar(
-    mapping = aes(x = has_ppc, y = count, fill = sample_id),
-    stat = "identity",  # Use stat = "identity" to specify y as the count values
-    position = position_dodge(width = 0.8),
-    colour = "black",
-    alpha = 0.7,
-    width = 0.7,
-    na.rm = FALSE,
-    orientation = "vertical",
-    show.legend = TRUE,
-    inherit.aes = TRUE
-  ) +
-  geom_text(
-    aes(x = has_ppc, y = count, label = count, group = sample_id),
-    position = position_dodge(width = 0.8),
-    vjust = -0.5,
-    size = 4
-  ) +
-  theme_bw() +
-  scale_fill_brewer(palette = "Set2") +
-  labs(title = "Journal PPC Acceptance by Sample",
-       x = "Accepts PPC",
-       y = "Count",
-       fill = "Sample Type"
-  ) + 
-  theme(
-    text = element_text(size = 18)
-  )
-
-# Save the plot
-ggsave(filename = "PPCbySample.png", plot = last_plot(), device = "png")
-
-```
 # Restriction Statements Graph
@@
 
-# Check median and IQR for each field
-```{r}
-
-# Group the tibble by the 'field' column
-prom_grouped <- dj_prom %>% group_by(field)
-
-# Compute summary statistics for 'jif' within each group
-promJIF_stats <- prom_grouped %>%
-  mutate(jif = round(jif, 2)) %>%
-  summarize(
-    mean_jif = mean(jif),
-    median_jif = median(jif),
-    q1_jif = quantile(jif, 0.25),
-    q3_jif = quantile(jif, 0.75),
-    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
-    count = n()
-  )
-
-# View the summary statistics
-print(promJIF_stats)
-```
-
-#For randomly sampled journals 
-``` {r}
-# Group the tibble by the 'field' column
-rand_grouped <- dj_rand %>% filter(!is.na(jif)) %>% group_by(field)
-
-# Compute summary statistics for 'jif' within each group
-randJIF_stats <- rand_grouped %>%
-  filter(ppc_type == "A") %>%
-  filter(is_empirical == "TRUE") %>%
-  mutate(jif = round(jif, 2)) %>%
-  summarize(
-    mean_jif = mean(jif),
-    median_jif = median(jif),
-    q1_jif = quantile(jif, 0.25),
-    q3_jif = quantile(jif, 0.75),
-    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
-    count = n()
-  )
-
-# View the summary statistics
-print(randJIF_stats)
-
-dj_rand %>%
-   filter(!is.na(jif)) %>%
-  mutate(jif = round(jif, 2)) %>%
-  summarize(
-    mean_jif = mean(jif),
-    median_jif = median(jif),
-    q1_jif = quantile(jif, 0.25),
-    q3_jif = quantile(jif, 0.75),
-    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
-    count = n()
-  )
-
-```
 ```{r}
@@
 
-COMPARING SAMPLES TO EACH OTHER ON PPC ACCEPTANCE
+#Coder Disagreements
 ```{r}
 
-dj_prom %>%
+d_journals %>%
+  filter(coder_id != "FINAL (TEH)") %>%
+
+```
+
+# PREVALENCE ESTIMATES
+
+# Calculate CIs for preavalence [**EDIT TO IMPORT VALUES FROM DATA**]
+```{r}
+library(binom)
+
+# Prominent Sample data for linked
+plPPCsuccess <- 1 #PPC events in prominent sample
+rlPPCsuccess <- 0 #PPC events in random sample
+linkedSample <- 101 #total sample size
+
+confidence_level <- 0.95
+
+# Calculate the Wilson confidence interval
+ci_plPPC <- binom.confint(plPPCsuccess, linkedSample, method = "wilson", conf.level = confidence_level)
+ci_rlPPC <- binom.confint(rlPPCsuccess, linkedSample, method = "wilson", conf.level = confidence_level)
+
+# Print the confidence interval
+print(ci_plPPC)
+print(ci_rlPPC)
+
+```
+
+# GRAPH FOR PRESENTATION
+# PPC Policy by Sample
+
+```{r}
+
+library(dplyr)
+library(ggplot2)
+library(forcats)
+
+library(dplyr)
+
+# Duplicate rows with sample_id "both" and rename the duplicates as "Prominent"
+duplicated_prominent_rows <- d_journals %>%
     mutate(has_ppc = case_when(
@@
     TRUE ~ has_ppc
-  ))
+  )) %>%
+  filter(ppc_type == "A") %>%
+  filter(is_empirical == TRUE) %>%
+  filter(sample_id == "both") %>%
+  mutate(sample_id = "prominent")
 
-dj_rand %>%
+# Combine the duplicated "Prominent" rows with the original data
+d_journals_processed <- bind_rows(d_journals, duplicated_prominent_rows) %>%
+  mutate(sample_id = recode(sample_id, "prominent" = "Prominent", "random" = "Random"))
+
+# Now, the dataset contains the original "both" rows and their duplicates as "Prominent"
+
+d_journals_processed %>%
    mutate(has_ppc = case_when(
@@
     TRUE ~ has_ppc
-  ))
+  )) %>%
+  filter(ppc_type == "A") %>%
+  filter(is_empirical == TRUE) %>%
+  mutate(sample_id = ifelse(sample_id == "both", "Random", sample_id)) %>%
+  ggplot() +
+  geom_bar(
+    mapping = aes(x = has_ppc, fill = sample_id),
+    stat = "count",
+    position = position_dodge(width = 0.8),  # Use position = "dodge" to create side-by-side bars
+    colour = "black",
+    alpha = 0.7,
+    width = 0.7,
+    na.rm = FALSE,
+    orientation = "vertical",
+    show.legend = TRUE,
+    inherit.aes = TRUE
+  ) +
+  geom_text(
+    aes(x = has_ppc, y = ..count.., label = ..count.., group = sample_id),
+    stat = "count",
+    position = position_dodge(width = 0.8),
+    vjust = -0.5,  # Adjust the vertical position of the labels
+    size = 6
+  ) +
+  theme_bw() +
+  ylim(0, 100) +
+  scale_fill_brewer(palette = "Set2") +
+  labs(title = "Journal PPC Acceptance by Sample",
+       x = "Accepts PPC",
+       y = "Count",
+       fill = "Sample"  # Customize the legend title here
+  ) + 
+  theme(
+    text = element_text(size = 18)  # Increase the font size here
+  )
 
-chisq.test(x=dj_prom$has_ppc, y=dj_rand$has_ppc)
-
-prop.test()
-
+ggsave(filename = "PPCbySample.png", plot = last_plot(), device = "png")
 ```
-```{r}
-# Sample data
-yes_prom <- 38  # Number of "yes" responses in Sample 1 (dj_prom)
-yes_rand <- 23  # Number of "yes" responses in Sample 2 (dj_rand)
-
-# Total number of observations in each sample (assuming 100)
-n_prom <- 100
-n_rand <- 100
-
-# Perform the proportion test
-test_result <- prop.test(x = c(yes_prom, yes_rand), n = c(n_prom, n_rand), alternative = "two.sided")
-
-# Print the test result
-print(test_result)
-
-```

### 2023-12-22 analysis/practiceCoding_AW.Rmd
code cleaning and manuscript
removed irrelevant code from 'practiceCoding_AW'. Drafting up a manuscript for NHB as an .rmd file.

@@
 library(dplyr)
+library(binom)
 library(kableExtra) # for tables
@@
 
-d_journals <- read_csv(here('data','processed','d_journals.csv'))
-d_articles <- read_csv(here('data','processed','d_articles.csv'))
+d_articles <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique', 'data','processed','d_articles.csv'), show_col_types = F) # article data 
+d_journals <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique','data','processed','d_journals.csv'), show_col_types = F) # journal data 
+```
 
-```
 # Create separate tibbles for Prominent and Randomly-selected journal samples
@@
 ```{r}
-library(binom)
 
 # Prominent Sample data
-prominentSuccess <- 1
-randomSuccess <- 23
-totalSuccess <- 57
+prominentSuccess <- dj_prominent %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES") %>%
+  count()
+randomSuccess <- dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES") %>%
+  count()
 
 sample_size <- 100
-totalSample <- 189
 confidence_level <- 0.95
@@
 ci_random <- binom.confint(randomSuccess, sample_size, method = "wilson", conf.level = confidence_level)
-ci_total <- binom.confint(totalSuccess, totalSample, method = "wilson", conf.level = confidence_level)
 
@@
 print(ci_random)
-print(ci_total)
-```
-
-# Calculate CIs for NO [**EDIT TO DERIVE NUMBERS FROM DATA**]
-```{r}
-library(binom)
-
-# Prominent Sample data
-prominentNO <- 77
-randomNO <- 74
-totalNO <- 123
-
-# Calculate the Wilson confidence interval
-ci_prominentNO <- binom.confint(prominentNO, sample_size, method = "wilson", conf.level = confidence_level)
-ci_randomNO <- binom.confint(randomNO, sample_size, method = "wilson", conf.level = confidence_level)
-ci_totalNO <- binom.confint(totalNO, totalSample, method = "wilson", conf.level = confidence_level)
-
-# Print the confidence interval
-print(ci_prominentNO)
-print(ci_randomNO)
-print(ci_totalNO)
 ```
@@
 # Filter and transform restrictions for ppc_length
-ppc_length_data <- dj_prominent %>%
+prominent_length_data <- dj_prominent %>%
   filter(!is.na(ppc_name)) %>%
@@
 # Filter and transform restrictions for ppc_time
-ppc_time_data <- dj_prominent %>%
+prominent_time_data <- dj_prominent %>%
   filter(!is.na(ppc_name)) %>%
@@
 combined_data <- bind_rows(
-  ppc_length_data %>% mutate(Code = "Length"),
-  ppc_time_data %>% mutate(Code = "Time-to-submit")
+  prominent_length_data %>% mutate(Code = "Length"),
+  prominent_time_data %>% mutate(Code = "Time-to-submit")
 ) %>%
@@
 ```
+
+```{r}
+# Load the dplyr package
+library(dplyr)
+
+# Calculate the count and percentage for "Quantitative"
+quantitative_data <- prominent_length_data %>%
+ filter(ppc_length == "Quantitative") %>%
+ summarise(count = sum(count), percentage = sum(count) / sum(prominent_length_data$count) * 100)
+
+# Print the count and percentage for "Quantitative"
+print(paste(quantitative_data$count, "(", round(quantitative_data$percentage, 2), "%)", sep = ""))
+
+```
+
 # Create and combine restiction statement graphs with ppc acceptance (random sample)
@@
 # Filter and process data for ppc_length
-ppc_length_random <- d_journals %>%
+random_length_data <- d_journals %>%
   filter(sample_id %in% c("random", "both")) %>%
@@
 # Filter and process data for ppc_time
-ppc_time_random<- d_journals %>%
+random_time_data <- d_journals %>%
   filter(sample_id %in% c("random", "both")) %>%
@@
 combined_data_random <- bind_rows(
-  ppc_length_random %>% mutate(Code = "Length"),
-  ppc_time_random %>% mutate(Code = "Time-to-submit")
+  random_length_data %>% mutate(Code = "Length"),
+  random_time_data %>% mutate(Code = "Time-to-submit")
 ) %>%

### 2023-12-22 manuscript_PPC_AW(NHB).qmd
code cleaning and manuscript
removed irrelevant code from 'practiceCoding_AW'. Drafting up a manuscript for NHB as an .rmd file.

---
title: A Descriptive Analysis of How Psychology Journals Handle Post-Publication
  Critiques
format:
  pdf: default
  journal: sn-nature-human-behaviour
  keep-tex: true
author:
  - name: Annie Whamond
    affiliations:
      - name: University of Melbounre
        id: 1
        department: Melbourne School of Psychological Sciences
        address: 161 Barry St
        city: Carlton
        state: VIC
        postal-code: 3010
    email: whamonda@unimelb.edu.au
    corresponding: true
  - name: Simine Vazire
    affiliations:
      - ref: 1
  - name: Beth Clarke
    affiliations:
      - ref: 1
  - name: Nicholas Moodie
    affiliations:
      - ref: 1
  - name: Sarah Schiavone
    affiliations:
      - ref: 1
  - name: Robert T. Thibault
    affiliations:
      - name: Stanford University
        id: 2
        department: Meta Research Innovation Centre
        address: 450 Jane Stanford Way
        city: Stanford
        state: CA
        postal-code: 94305
  - name: Tom E. Hardwicke
    affiliations:
      - ref: 1
abstract: >
  Fostering critical discussion is essential to upholding the ethos of
  science as an unbiased, collaborative, and self-correcting endeavor. Journals
  can support this by offering options for post-publication critique, such as
  commentaries or letters, allowing peers to voice substantiated concerns of
  empirical articles. We provide a descriptive, cross-sectional analysis of
  post-publication critique policies and prevalence across both prominent
  randomly-selected and psychology journals. We found that, overall, the
  majority of psychology journals do not offer explicit options for
  post-publication critique. When they did, length and time-to-submit limits
  were often not stated. Critique prevalence was rare with only a single event
  identified. Given the widespread recognition of the replication crisis in
  psychology, allowing avenues for criticisms to be voiced may help increase the
  credibility within the field. To support transparency and self-correction,
  psychology journals should offer clearly stated post-publication critique
  options and encourage their use.
keywords:
  - metascience
  - post-publication cretique
  - psychology
  - credibility
bibliography: bibliography.bib

---
null

# Introduction {#sec-intro}

The Introduction section, of referenced text @greenwade93 expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.

Springer Nature does not impose a strict layout as standard however authors are advised to check the individual requirements for the journal they are planning to submit to as there may be journal-level preferences. When preparing your text please also be aware that some stylistic choices are not supported in full text XML (publication version), including coloured font. These will not be replicated in the typeset article if it is accepted.

# Using this template {#sec-template}

This Quarto template is unofficial and built out of Springer Nature's template. Some examples of commonly used commands and features are listed below, to help you get started.

As seen below, you can mix markdown and Latex with each other, though it's likely best to mostly use markdown.

## Cross Referencing

To reference a figure with example label "plot", use `@fig-plot`. Analogously, to reference a table with example label "data", use `@tbl-data`. To reference a section, such as the Introduction (@sec-intro), use `@sec-intro`.

For complete information on cross referencing with Quarto, see <https://quarto.org/docs/authoring/cross-references.html>.

## Citations

Quarto formats citations and references automatically using the bibliography records in your .bib file. For a citation in parentheses use [@greenwade93] and for a text citation: @greenwade93. Multiple citations can be given as [@greenwade93; @knuth1984texbook]. Drop the author like so [-@greenwade93].

# Tables and Figures

To include figures, you can use Quarto syntax.

![An example figure (an empty plot)](fig.eps){#fig-plot}

For both figures and tables, you can use LaTeX syntax if you need additional customizability.

For example, to use footnotes within a table, you may want to use LaTeX.

```{=tex}
\begin{table}[h]
\caption{LaTeX caption text}\label{tbl-data}%
\begin{tabular}{@{}llll@{}}
\toprule
Column 1 & Column 2  & Column 3 & Column 4\\
\midrule
row 1    & data 1   & data 2  & data 3  \\
row 2    & data 4   & data 5\footnotemark[1]  & data 6  \\
row 3    & data 7   & data 8  & data 9\footnotemark[2]  \\
\botrule
\end{tabular}
\footnotetext{Source: This is an example of table footnote. This is an example of table footnote.}
\footnotetext[1]{Example for a first table footnote. This is an example of table footnote.}
\footnotetext[2]{Example for a second table footnote. This is an example of table footnote.}
\end{table}
```
# References

<!-- the pattern below controls the placement of the references -->

::: {#refs}
:::

### 2023-12-22 manuscript_NHB.Rmd
Create manuscript_NHB.Rmd

---
title: A Descriptive Analysis of How Psychology Journals Handle Post-Publication
  Critiques
format:
  pdf: default
  journal: "sn-nature-human-behaviour"
  keep-tex: true
author:
  - name: Annie Whamond
    affiliations:
      - name: University of Melbounre
        id: 1
        department: Melbourne School of Psychological Sciences
        address: 161 Barry St
        city: Carlton
        state: VIC
        postal-code: 3010
    email: whamonda@unimelb.edu.au
    corresponding: true
  - name: Simine Vazire
    affiliations:
      - ref: 1
  - name: Beth Clarke
    affiliations:
      - ref: 1
  - name: Nicholas Moodie
    affiliations:
      - ref: 1
  - name: Sarah Schiavone
    affiliations:
      - ref: 1
  - name: Robert T. Thibault
    affiliations:
      - name: Stanford University
        id: 2
        department: Meta Research Innovation Centre
        address: 450 Jane Stanford Way
        city: Stanford
        state: CA
        postal-code: 94305
  - name: Tom E. Hardwicke
    affiliations:
      - ref: 1
abstract: >
  Fostering critical discussion is essential to upholding the ethos of
  science as an unbiased, collaborative, and self-correcting endeavor. Journals
  can support this by offering options for post-publication critique, such as
  commentaries or letters, allowing peers to voice substantiated concerns of
  empirical articles. We provide a descriptive, cross-sectional analysis of
  post-publication critique policies and prevalence across both prominent
  randomly-selected and psychology journals. We found that, overall, the
  majority of psychology journals do not offer explicit options for
  post-publication critique. When they did, length and time-to-submit limits
  were often not stated. Critique prevalence was rare with only a single event
  identified. Given the widespread recognition of the replication crisis in
  psychology, allowing avenues for criticisms to be voiced may help increase the
  credibility within the field. To support transparency and self-correction,
  psychology journals should offer clearly stated post-publication critique
  options and encourage their use.
keywords:
  - metascience
  - post-publication cretique
  - psychology
  - credibility
bibliography: bibliography.bib

---

```{r}
library(papaja) # article template
library(tidyverse)
library(ggplot2) # figure creation
library(RColorBrewer) # data visualisation
library(dplyr)
library(kableExtra) # for tables
library(knitr) # for literate programming
library(janitor) # for data munging
library(tidylog) # for inline code feedback
library(here) # for finding files
```

```{r}
source(here('analysis','functions.R')) # load custom functions
source(here('analysis','raw_to_primary.R')) # converts raw data to primary data
```

```{r}
# Load processed data files

d_articles <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique', 'data','processed','d_articles.csv'), show_col_types = F) # article data 
d_journals <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique','data','processed','d_journals.csv'), show_col_types = F) # journal data 
```

```{r}
# Create separate tibbles for Prominent and Randomly-selected journal samples

dj_prominent <- d_journals %>%
  filter(sample_id != "random") %>%
  filter(is_empirical == TRUE)

dj_random <- d_journals %>%
  filter(sample_id != "prominent") %>%
  filter(is_empirical == TRUE)
```

# Main

# Results

## Journal Policy

For descriptive statistics on journal subdisciplines, post-publication critique acceptance, and COPE membership for both prominent and randomly-selected samples, see Supplemetary Information ##. A full list of the journals included in this study, along with their post-publication critique options and restrictions, is provided in Supplemetary Information ##.

## Prominent Psychology Journals

```{r journal-characteristics}

# below we ascertain journal JIF characteristics

promJournalCharacteristics <- dj_prominent %>% 
  filter(ppc_type == "A") %>%
  summarise(promMedian_jif = round(median(jif),2),
            promMin_jif = round(min(jif),2),
            promMax_jif = round(max(jif),2),
            promIQR_jif = round(IQR(jif),2)
  )

```

In our sample of 100 prominent journals, the median 2021 Journal Impact Factor was `r promJournalCharacteristics %>% pull(promMedian_jif)` (IQR = `r promJournalCharacteristics %>% pull(promIQR_jif)`, range = `r promJournalCharacteristics %>% pull(promMin_jif)` - `r promJournalCharacteristics %>% pull(promMax_jif)`). As this represents the entire population of interest for this section of the study, confidence intervals (CIs) are not included for this section of the study. Figure *XX* shows theobserved journal policies and, of the explicitly offered critique options identified, how restrictions on length and time-to-submit were stated.

### *Post-Publication Critique Policy and Restriction Statements in Prominent Psychology Journals*

```{r, echo = FALSE}
# Filter and transform restrictions for ppc_length
prominent_length_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>% # removes Archive Only PPC types
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all length limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>% 
  group_by(ppc_length) %>%
  summarise(count = n())

# Filter and transform restrictions for ppc_time
prominent_time_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>%
  group_by(ppc_time) %>%
  summarise(count = n())

# Combine the data and unite the columns
combined_data <- bind_rows(
  prominent_length_data %>% mutate(Code = "Length"),
  prominent_time_data %>% mutate(Code = "Time-to-submit")
) %>%
unite(limits, ppc_length, ppc_time) %>%
  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
                   limits == "Qualitative_NA" ~ "Qualitative",
                   limits == "Quantitative_NA" ~ "Quantitative",
                   limits == "NA_Not Stated" ~ "Not Stated",
                   limits == "NA_Qualitative" ~ "Qualitative",
                   limits == "NA_Quantitative" ~ "Quantitative",
                   TRUE ~ as.character(limits)
                   ))

# Create the first graph
graph1 <- ggplot(combined_data, aes(x = Code, y = count, fill = limits)) +
  geom_bar(stat = "identity", 
           position = "stack",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(x = "Restriction Type", y = "Count", fill = "Restrictions")

# Create the second graph
graph2 <- dj_prominent %>%
  filter(ppc_type == "A") %>% # Keeps only first PPC row for each journal
  filter(!is.na(has_ppc)) %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'Archive',
    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
    has_ppc == 'YES' ~ 'Yes',
    TRUE ~ has_ppc
  )) %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ggplot(aes(x = "", y = count, fill = has_ppc)) +
  geom_bar(stat = "identity",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Oranges") +
  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")

# Arrange both graphs in the same figure
combined_plots <- graph2 + graph1
combined_plots

```

*Note.* PPC = post-publication critique. Orange bar (left) indicates policy statements for each journal included in sample (n = 100). Blue bars (right) indicate how length and time-to-submit restrictions were stated in cases where journals had explicit post-publication critique policies in place (n = 41). Implicit acceptance denoted by archival examples of critiques despite absence of stated policy.

```{r}
# Length restriction statement types of explicit PPC types (prominent sample)

# Calculate the count and percentage for "Quantitative"
prom_quantitative_length <- prominent_length_data %>%
 filter(ppc_length == "Quantitative") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(prominent_length_data$count) * 100)

# Calculate the count and percentage for "Qualitative"
prom_qualitative_length <- prominent_length_data %>%
 filter(ppc_length == "Qualitative") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(prominent_length_data$count) * 100)

# Calculate the count and percentage for "Not Stated"
prom_notStated_length <- prominent_length_data %>%
 filter(ppc_length == "Not Stated") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(prominent_length_data$count) * 100)

# Range
prom_length_range <- dj_prominent %>%
  filter(!is.na(ppc_length)) %>%
  filter(ppc_length != "Qualitative") %>%
  filter(ppc_length != "NOT STATED") %>%
  mutate(ppc_length = as.numeric(ppc_length)) %>%
  summarise(prom_median_length = median(ppc_length),
            prom_min_length = min(ppc_length),
            prom_max_length = max(ppc_length)
            )

# Time-to-submit restriction statement types of explicit PPC types (prominent sample)

# Calculate the count and percentage for "Quantitative"
prom_quantitative_time <- prominent_time_data %>%
 filter(ppc_time == "Quantitative") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(prominent_time_data$count) * 100)

# Calculate the count and percentage for "Qualitative"
prom_qualitative_time <- prominent_time_data %>%
 filter(ppc_time == "Qualitative") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(prominent_time_data$count) * 100)

# Calculate the count and percentage for "Not Stated"
prom_notStated_time <- prominent_time_data %>%
 filter(ppc_time == "Not Stated") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(prominent_time_data$count) * 100)

# Range
prom_time_range <- dj_prominent %>%
  filter(!is.na(ppc_time)) %>%
  filter(ppc_time != "Qualitative") %>%
  filter(ppc_time != "NOT STATED") %>%
  mutate(ppc_time = as.numeric(ppc_time)) %>%
  summarise(prom_median_time = median(ppc_time),
            prom_min_time = min(ppc_time),
            prom_max_time = max(ppc_time)
            )

# Reference restriction statement types of explicit PPC types (prominent sample)
prominent_ref_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>% # keep only entries that identify PPC option
  filter(has_ppc != "ARCHIVE") %>% # remove implicit yes examples
  mutate(ppc_ref = case_when(
    ppc_ref %in% c(10, 15, 20, 5) ~ 'Quantitative',
    ppc_ref == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>%
  group_by(ppc_ref) %>%
  summarise(count = n()) %>%
  ungroup()

# Calculate the count and percentage for "Quantitative"
prom_quantitative_ref <- prominent_ref_data %>%
 filter(ppc_ref == "Quantitative") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(prominent_ref_data$count) * 100)

# Calculate the count and percentage for "Not Stated"
prom_notStated_ref <- prominent_ref_data %>%
 filter(ppc_ref == "Not Stated") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(prominent_ref_data$count) * 100)

# Range
prom_ref_range <- dj_prominent %>%
  filter(!is.na(ppc_ref)) %>%
  filter(ppc_ref != "Qualitative") %>%
  filter(ppc_ref != "NOT STATED") %>%
  mutate(ppc_ref = as.numeric(ppc_ref)) %>%
  summarise(prom_median_ref = median(ppc_ref),
            prom_min_ref = min(ppc_ref),
            prom_max_ref = max(ppc_ref)
            )

# Peer-review statements of explicit PPC types (prominent sample)
prominent_review_data <- dj_prominent %>%
  filter(!is.na(ppc_review)) %>% # keep only entries that identify PPC option
  filter(has_ppc != "ARCHIVE") %>% # remove implicit yes examples
  mutate(ppc_review = case_when(
    ppc_review == 'YES' ~ 'Yes',
    ppc_review == 'NO' ~ 'No',
    ppc_review == "NOT STATED" ~ "Not Stated"
  )) %>%
  group_by(ppc_review) %>%
  summarise(count = n()) %>%
  ungroup()

# Calculate the count and percentage for "Yes"
prom_yes_review <- prominent_review_data %>%
 filter(ppc_review == "Yes") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(prominent_review_data$count) * 100)

# Calculate the count and percentage for "No"
prom_no_review <- prominent_review_data %>%
 filter(ppc_review == "No") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(prominent_review_data$count) * 100)

# Calculate the count and percentage for "Not Stated"
prom_notStated_review <- prominent_review_data %>%
 filter(ppc_review == "Not Stated") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(prominent_review_data$count) * 100)

```

  As shown in Figure *XX*, post-publication critique policies were explicitly stated by `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "YES") / n() * 100)` of journals, and we inferred that they were implicitly accepted (as denoted by archival examples) in `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "ARCHIVE") / n() * 100)` of journals. `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "NO IMPLICIT") / n() * 100)` had no advertised post-publication critique policy, and `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "NO EXPLICIT") / n() * 100)` of journals explicitly stated that they did not accept critiques (*Clinical Psychology: Science and Practice and Psychological Bulletin*). `r dj_prominent %>% filter(ppc_type == "B" & !is.na(ppc_name)) %>% summarise(percentage = sum(!is.na(ppc_name) / n() * 100))` of journals accepted two types (commentaries and letters); *International Journal of Mental Health and Addiction*, *Journal of Environmental Psychology*, and *Psychological Science*. 
    Among the 41 explicitly stated post-publication critique options, restrictions on length were quantitatively stated (e.g., '1,000 words') in `r print(paste(prom_quantitative_length$count, "(", round(prom_quantitative_length$percentage), "%)", sep = ""))` cases, qualitatively stated (e.g. 'brief') in  `r print(paste(prom_qualitative_length$count, "(", round(prom_qualitative_length$percentage), "%)", sep = ""))` cases, and not stated in `r print(paste(prom_notStated_length$count, "(", round(prom_notStated_length$percentage), "%)", sep = ""))` cases. Time-to-submit was quantitatively stated (e.g., '4 weeks') in `r print(paste(prom_quantitative_time$count, "(", round(prom_quantitative_time$percentage), "%)", sep = ""))` cases, qualitatively stated (e.g., 'timely') in `r print(paste(prom_qualitative_time$count, "(", round(prom_qualitative_time$percentage), "%)", sep = ""))` cases, and not stated in `r print(paste(prom_notStated_time$count, "(", round(prom_notStated_time$percentage), "%)", sep = ""))` cases. Number of references allowed was quantitatively stated (e.g., 'max 20') in `r print(paste(prom_quantitative_ref$count, "(", round(prom_quantitative_ref$percentage), "%)", sep = ""))` cases and not stated in `r print(paste(prom_notStated_ref$count, "(", round(prom_notStated_ref$percentage), "%)", sep = ""))`. Whether critiques were sent for external peer-review was only stated in `r print(paste((prom_yes_review$count + prom_no_review$count), "(", round(prom_yes_review$percentage + prom_no_review$percentage), "%)", sep = ""))` cases, in `r print(paste(prom_yes_review$count, "(", round(prom_yes_review$percentage), "%)", sep = ""))` cases this was in the affirmative. 
    When stated quantitatively, length limits ranged from `r prom_length_range %>% pull(prom_min_length)` - `r prom_length_range %>% pull(prom_max_length)` words, time-to-submit limits ranged from `r prom_time_range %>% pull(prom_min_time)` -`r prom_time_range %>% pull(prom_max_time)` weeks, reference limits ranged between `r prom_ref_range %>% pull(prom_min_ref)` -`r prom_ref_range %>% pull(prom_max_ref)`. Table *XX* shows descriptive statistics for stated quantitative restrictions, broken down by critique type.

### Table *XX*

As expected, results in Table 1 show that commentaries were generally less restrictive on length with the median word limit being 2.5 times that of letters. The median number of references allowed was 1.5 times greater in commentaries compared to letters. Commentaries were also 3.3 times more likely to be sent for peer-review. Interestingly, time-to-submit was less restrictive for letters than commentaries, however, this was only reported in two and four cases (respectively) so limited inferences can be made from this.

## Randomly-selected Psychology Journals
```{r journal-characteristics}

# below we ascertain journal JIF characteristics

randJournalCharacteristics <- dj_random %>% 
  filter(ppc_type == "A") %>%
  filter(!is.na(jif)) %>%
  summarise(randMedian_jif = round(median(jif),2),
            randMin_jif = round(min(jif),2),
            randMax_jif = round(max(jif),2),
            randIQR_jif = round(IQR(jif),2)
  )

```
Amongst our sample of 100 randomly-selected psychology journals, Journal Impact Factor data was unavailable for 25 journals. Median 2021 Journal Impact Factor was `r randJournalCharacteristics %>% pull(randMedian_jif)` (IQR = `r randJournalCharacteristics %>% pull(randIQR_jif)`, range = `r randJournalCharacteristics %>% pull(randMin_jif)` - `r randJournalCharacteristics %>% pull(randMax_jif)`). Figure *XX* shows the observed journal policies and, of the explicitly offered critique options identified, how restrictions on length and time-to-submit were stated.

### Figure *XX*: *Post-Publication Critique Policy and Restriction Statements in Randomly-selected Psychology Journals*
```{r}
# Create and combine restiction statement graphs with ppc acceptance (random sample)

# Filter and process data for ppc_length
random_length_data <- d_journals %>%
  filter(sample_id %in% c("random", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_length) %>%
  summarise(count = n())

# Filter and process data for ppc_time
random_time_data <- d_journals %>%
  filter(sample_id %in% c("random", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_time) %>%
  summarise(count = n())

# Combine the data and unite the columns
combined_data_random <- bind_rows(
  random_length_data %>% mutate(Code = "Length"),
  random_time_data %>% mutate(Code = "Time-to-submit")
) %>%
unite(limits, ppc_length, ppc_time) %>%
  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
                   limits == "Qualitative_NA" ~ "Qualitative",
                   limits == "Quantitative_NA" ~ "Quantitative",
                   limits == "NA_Not Stated" ~ "Not Stated",
                   limits == "NA_Qualitative" ~ "Qualitative",
                   limits == "NA_Quantitative" ~ "Quantitative",
                   TRUE ~ as.character(limits)
                   ))

# Create the first graph
graph4 <- ggplot(combined_data_random, aes(x = Code, y = count, fill = limits)) +
  geom_bar(stat = "identity", 
           position = "stack",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(x = "Restriction Type", y = "Count", fill = "Restrictions")

# Create the second graph
graph3 <- d_journals %>%
  filter(sample_id == "random" | sample_id == "both") %>%
  filter(ppc_type == "A") %>%
  filter(!is.na(has_ppc)) %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'Archive',
    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
    has_ppc == 'YES' ~ 'Yes',
    TRUE ~ has_ppc
  )) %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ggplot(aes(x = "", y = count, fill = has_ppc)) +
  geom_bar(stat = "identity",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Oranges") +
  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")

# Arrange both graphs in the same figure
combined_plots <- graph3 + graph4
combined_plots

ggsave(filename = "Random_statements.png", plot = last_plot(), device = "png")

```
*Note.* PPC = post-publication critique. Orange bar (left) indicates policy statements for each journal included in sample (n = 100). Blue bars (right) indicate how length and time-to-submit restrictions were stated in cases where journals had explicit post-publication critique policies in place (n = 25).

```{r}
# Length restriction statement types of explicit PPC types (random sample)

# Calculate the count and percentage for "Quantitative"
rand_quantitative_length <- random_length_data %>%
 filter(ppc_length == "Quantitative") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(random_length_data$count) * 100)

# Calculate the count and percentage for "Qualitative"
rand_qualitative_length <- random_length_data %>%
 filter(ppc_length == "Qualitative") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(random_length_data$count) * 100)

# Calculate the count and percentage for "Not Stated"
rand_notStated_length <- random_length_data %>%
 filter(ppc_length == "Not Stated") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(random_length_data$count) * 100)

# Range
rand_length_range <- dj_random %>%
  filter(!is.na(ppc_length)) %>%
  filter(ppc_length != "Qualitative") %>%
  filter(ppc_length != "NOT STATED") %>%
  mutate(ppc_length = as.numeric(ppc_length)) %>%
  summarise(prom_median_length = median(ppc_length),
            rand_min_length = min(ppc_length),
            rand_max_length = max(ppc_length)
            )

# Time-to-submit restriction statement types of explicit PPC types (prominent sample)

# Calculate the count and percentage for "Quantitative"
rand_quantitative_time <- random_time_data %>%
 filter(ppc_time == "Quantitative") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(random_time_data$count) * 100)

# Calculate the count and percentage for "Qualitative"
rand_qualitative_time <- random_time_data %>%
 filter(ppc_time == "Qualitative") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(random_time_data$count) * 100)

# Calculate the count and percentage for "Not Stated"
rand_notStated_time <- random_time_data %>%
 filter(ppc_time == "Not Stated") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(random_time_data$count) * 100)

# Range
rand_time_range <- dj_random %>%
  filter(!is.na(ppc_time)) %>%
  filter(ppc_time != "Qualitative") %>%
  filter(ppc_time != "NOT STATED") %>%
  mutate(ppc_time = as.numeric(ppc_time)) %>%
  summarise(rand_median_time = median(ppc_time),
            rand_min_time = min(ppc_time),
            rand_max_time = max(ppc_time)
            )

# Reference restriction statement types of explicit PPC types (prominent sample)
random_ref_data <- dj_random %>%
  filter(!is.na(ppc_name)) %>% # keep only entries that identify PPC option
  filter(has_ppc != "ARCHIVE") %>% # remove implicit yes examples
  mutate(ppc_ref = case_when(
    ppc_ref %in% c(10, 15, 20, 5) ~ 'Quantitative',
    ppc_ref == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>%
  group_by(ppc_ref) %>%
  summarise(count = n()) %>%
  ungroup()

# Calculate the count and percentage for "Quantitative"
rand_quantitative_ref <- random_ref_data %>%
 filter(ppc_ref == "Quantitative") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(random_ref_data$count) * 100)

# Calculate the count and percentage for "Not Stated"
rand_notStated_ref <- random_ref_data %>%
 filter(ppc_ref == "Not Stated") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(random_ref_data$count) * 100)

# Range
rand_ref_range <- dj_random %>%
  filter(!is.na(ppc_ref)) %>%
  filter(ppc_ref != "Qualitative") %>%
  filter(ppc_ref != "NOT STATED") %>%
  mutate(ppc_ref = as.numeric(ppc_ref)) %>%
  summarise(rand_median_ref = median(ppc_ref),
            rand_min_ref = min(ppc_ref),
            rand_max_ref = max(ppc_ref)
            )

# Peer-review statements of explicit PPC types (prominent sample)
random_review_data <- dj_random %>%
  filter(!is.na(ppc_review)) %>% # keep only entries that identify PPC option
  filter(has_ppc != "ARCHIVE") %>% # remove implicit yes examples
  mutate(ppc_review = case_when(
    ppc_review == 'YES' ~ 'Yes',
    ppc_review == 'NO' ~ 'No',
    ppc_review == "NOT STATED" ~ "Not Stated"
  )) %>%
  group_by(ppc_review) %>%
  summarise(count = n()) %>%
  ungroup()

# Calculate the count and percentage for "Yes"
rand_yes_review <- random_review_data %>%
 filter(ppc_review == "Yes") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(random_review_data$count) * 100)

# Calculate the count and percentage for "No"
rand_no_review <- random_review_data %>%
 filter(ppc_review == "No") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(random_review_data$count) * 100)

# Calculate the count and percentage for "Not Stated"
rand_notStated_review <- random_review_data %>%
 filter(ppc_review == "Not Stated") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(random_review_data$count) * 100)

```
  As shown in Figure *XX*, post-publication critique policies were explicitly stated by `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "YES") / n() * 100)`% of journals (95% CI [15.8%, 32.2%]), and we inferred that they were implicitly accepted (as denoted by archival examples) in `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "ARCHIVE") / n() * 100)`% of journals (95% CI [1.0%, 8.5%]). `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "NO IMPLICIT") / n() * 100)`% of journals (95% CI [63.6%, 80.7%]) had no advertised post-publication critique policy, and `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "NO EXPLICIT") / n() * 100)` of journals (95% CI [0.2%, 5.4%]) explicitly stated that they did not accept critiques (*Clinical Psychology: Science and Practice and Psychological Bulletin*, also included in sample for prominent journals). `r dj_random %>% filter(ppc_type == "B" & !is.na(ppc_name)) %>% summarise(percentage = sum(!is.na(ppc_name) / n() * 100))` of journals accepted two types (95% CI [0.0%, 7.0%]); *Cortex* offered commentaries and 'verification reports' (Chambers, 2020) and *Journal of Cognition and Culture* offered commentaries and letters.

**ABOVE EDIT: insert code for CIs**

  Among the 25 cases of explicitly accepted post-publication critiques, restrictions on length were quantitatively stated in `r print(paste(rand_quantitative_length$count, "(", round(rand_quantitative_length$percentage), "%)", sep = ""))` cases, and not stated in `r print(paste(rand_notStated_length$count, "(", round(rand_notStated_length$percentage), "%)", sep = ""))` cases. Time-to-submit was quantitatively stated in `r print(paste(rand_quantitative_time$count, "(", round(rand_quantitative_time$percentage), "%)", sep = ""))` case, and qualitatively stated in `r print(paste(rand_qualitative_time$count, "(", round(rand_qualitative_time$percentage), "%)", sep = ""))`, and not stated in `r print(paste(rand_notStated_time$count, "(", round(rand_notStated_time$percentage), "%)", sep = ""))` cases. Number of references allowed was stated quantitatively in `r print(paste(rand_quantitative_ref$count, "(", round(rand_quantitative_ref$percentage), "%)", sep = ""))` cases, and not stated in `r print(paste(rand_notStated_ref$count, "(", round(rand_notStated_ref$percentage), "%)", sep = ""))` cases. Whether critiques were peer-reviewed was stated in `r print(paste((rand_yes_review$count + rand_no_review$count), "(", round(rand_yes_review$percentage + rand_no_review$percentage), "%)", sep = ""))` cases, in `r print(paste(rand_yes_review$count, "(", round(rand_yes_review$percentage), "%)", sep = ""))` cases this was in the affirmative. When stated quantitatively, length limits ranged from `r rand_length_range %>% pull(rand_min_length)` - `r rand_length_range %>% pull(rand_max_length)` words, time-to-submit limits were only stated by one journal (as 9 months), references ranged between `r rand_ref_range %>% pull(rand_min_ref)` - `r rand_ref_range %>% pull(rand_max_ref)`. Table *XX* shows descriptive statistics for these restrictions, broken down by critique type.

### Table *XX*

As expected, Table *XX* shows that commentaries were overall less restrictive on length with the median word limit being double that of letters. Commentaries were also three times more likely to state quantitative length restrictions than letters. Restrictions on time-to-submit, references, and whether critiques would be sent for peer-review were not stated for any policies on letters. Similarly, no details on restrictions or peer-review were stated for 'verification reports' (the one 'other' critique type included in this sample).

## PPC Prevalence (results cont.)

# Discussion

# Data Availability

# Code Availability

### 2023-12-25 manuscript_NHB.Rmd
Updated manuscript
replaced .qmd script with .rmd version

@@
 
-d_articles <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique', 'data','processed','d_articles.csv'), show_col_types = F) # article data 
-d_journals <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique','data','processed','d_journals.csv'), show_col_types = F) # journal data 
+d_articles <- read_csv(here('data','processed','d_articles.csv'), show_col_types = F) # article data 
+d_journals <- read_csv(here('data','processed','d_journals.csv'), show_col_types = F) # journal data 
 ```

### 2023-12-26 manuscript_NHB.Rmd
remove .png files update manuscript
Removed unnecessary images. Updated manuscript to version that knits successfully

@@
 ---
-title: A Descriptive Analysis of How Psychology Journals Handle Post-Publication
-  Critiques
-format:
-  pdf: default
-  journal: "sn-nature-human-behaviour"
-  keep-tex: true
-author:
-  - name: Annie Whamond
-    affiliations:
-      - name: University of Melbounre
-        id: 1
-        department: Melbourne School of Psychological Sciences
-        address: 161 Barry St
-        city: Carlton
-        state: VIC
-        postal-code: 3010
-    email: whamonda@unimelb.edu.au
-    corresponding: true
-  - name: Simine Vazire
-    affiliations:
-      - ref: 1
-  - name: Beth Clarke
-    affiliations:
-      - ref: 1
-  - name: Nicholas Moodie
-    affiliations:
-      - ref: 1
-  - name: Sarah Schiavone
-    affiliations:
-      - ref: 1
-  - name: Robert T. Thibault
-    affiliations:
-      - name: Stanford University
-        id: 2
-        department: Meta Research Innovation Centre
-        address: 450 Jane Stanford Way
-        city: Stanford
-        state: CA
-        postal-code: 94305
-  - name: Tom E. Hardwicke
-    affiliations:
-      - ref: 1
-abstract: >
-  Fostering critical discussion is essential to upholding the ethos of
-  science as an unbiased, collaborative, and self-correcting endeavor. Journals
-  can support this by offering options for post-publication critique, such as
-  commentaries or letters, allowing peers to voice substantiated concerns of
-  empirical articles. We provide a descriptive, cross-sectional analysis of
-  post-publication critique policies and prevalence across both prominent
-  randomly-selected and psychology journals. We found that, overall, the
-  majority of psychology journals do not offer explicit options for
-  post-publication critique. When they did, length and time-to-submit limits
-  were often not stated. Critique prevalence was rare with only a single event
-  identified. Given the widespread recognition of the replication crisis in
-  psychology, allowing avenues for criticisms to be voiced may help increase the
-  credibility within the field. To support transparency and self-correction,
-  psychology journals should offer clearly stated post-publication critique
-  options and encourage their use.
-keywords:
-  - metascience
-  - post-publication cretique
-  - psychology
-  - credibility
-bibliography: bibliography.bib
-
+title: "A Descriptive Analysis of How Psychology Journals Handle Post-Publication Critiques"
+author: "Whamond, A., Vazire, S., Clarke, B., Moodie, N., Schiavone, S., Thibault, R. T., & Hardwicke, T. E."
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+output: pdf_document
 ---
 
-```{r}
+```{r setup, include = FALSE}
+renv::activate()
+
 library(papaja) # article template
@@
 library(ggplot2) # figure creation
+library(ggrepel) # for ggplot text labels
+library(patchwork) # for multipanel plot layouts
 library(RColorBrewer) # data visualisation
@@
 
-```{r}
-source(here('analysis','functions.R')) # load custom functions
-source(here('analysis','raw_to_primary.R')) # converts raw data to primary data
+```{r echo=FALSE, message=FALSE}
+# Load processed data files
+
+d_articles <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique', 'data','processed','d_articles.csv'), show_col_types = F) # article data 
+d_journals <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique', 'data','processed','d_journals.csv'), show_col_types = F) # journal data 
 ```
 
-```{r}
-# Load processed data files
-
-d_articles <- read_csv(here('data','processed','d_articles.csv'), show_col_types = F) # article data 
-d_journals <- read_csv(here('data','processed','d_journals.csv'), show_col_types = F) # journal data 
-```
-
-```{r}
+```{r echo=FALSE, message=FALSE}
 # Create separate tibbles for Prominent and Randomly-selected journal samples
@@
 dj_prominent <- d_journals %>%
-  filter(sample_id != "random") %>%
-  filter(is_empirical == TRUE)
+  filter(sample_id != "random") %>% # remove entries from the random sample
+  filter(is_empirical == TRUE) # remove ineligible (non-empirical) journals
 
 dj_random <- d_journals %>%
-  filter(sample_id != "prominent") %>%
-  filter(is_empirical == TRUE)
+  filter(sample_id != "prominent") %>% # remove entries from the prominent sample
+  filter(is_empirical == TRUE) # remove ineligible (non-empirical) journals
 ```
@@
 # Main
+*Add 'Introduction' section*
 
@@
 
-```{r journal-characteristics}
+```{r prominent journal-characteristics, echo=FALSE, message=FALSE}
 
-# below we ascertain journal JIF characteristics
+# Ascertain prominent journal JIF characteristics
 
 promJournalCharacteristics <- dj_prominent %>% 
-  filter(ppc_type == "A") %>%
+  filter(ppc_type == "A") %>%       # Keep only single entry for each journal
   summarise(promMedian_jif = round(median(jif),2), 
@@
 
-```{r, echo = FALSE}
+```{r, echo = FALSE, message=FALSE}
 # Filter and transform restrictions for ppc_length
@@
   filter(!is.na(ppc_name)) %>%
-  filter(has_ppc != "ARCHIVE") %>% # removes Archive Only PPC types
+  filter(has_ppc != "ARCHIVE") %>% # removes 'Archive Only' PPC types
   mutate(ppc_length = case_when(
@@
   filter(!is.na(ppc_name)) %>%
-  filter(has_ppc != "ARCHIVE") %>%
+  filter(has_ppc != "ARCHIVE") %>% # removes 'Archive Only' PPC types
   mutate(ppc_time = case_when(
@@
 graph2 <- dj_prominent %>%
-  filter(ppc_type == "A") %>% # Keeps only first PPC row for each journal
-  filter(!is.na(has_ppc)) %>%
+  filter(ppc_type == "A") %>% # Keeps only first entry for each journal
+  filter(!is.na(has_ppc)) %>% # Remove journal rows with no (NA) PPC options 
   mutate(has_ppc = case_when(
@@
 
-```{r}
+```{r echo=FALSE, message=FALSE}
 # Length restriction statement types of explicit PPC types (prominent sample)
@@
     ppc_review == 'NO' ~ 'No',
-    ppc_review == "NOT STATED" ~ "Not Stated"
-  )) %>%
+    ppc_review == "NOT STATED" ~ "Not Stated")
+  ) %>%
   group_by(ppc_review) %>%
@@
 ## Randomly-selected Psychology Journals
-```{r journal-characteristics}
+```{r randomly-selected journal-characteristics, echo=FALSE, message=FALSE}
 
-# below we ascertain journal JIF characteristics
+# Ascertain randonly-selected journal JIF characteristics
 
@@
 ```
-Amongst our sample of 100 randomly-selected psychology journals, Journal Impact Factor data was unavailable for 25 journals.
+Among our sample of 100 randomly-selected psychology journals, Journal Impact Factor data was unavailable for 25 journals.
 Median 2021 Journal Impact Factor was `r randJournalCharacteristics %>% pull(randMedian_jif)` (IQR = `r randJournalCharacteristics %>% pull(randIQR_jif)`, range = `r randJournalCharacteristics %>% pull(randMin_jif)` - `r randJournalCharacteristics %>% pull(randMax_jif)`).
@@
 ### Figure *XX*: *Post-Publication Critique Policy and Restriction Statements in Randomly-selected Psychology Journals*
-```{r}
-# Create and combine restiction statement graphs with ppc acceptance (random sample)
+```{r echo=FALSE, message=FALSE}
+# Create and combine restriction statement graphs with PPC acceptance (random sample)
 
@@
 ```
+
 *Note.* PPC = post-publication critique.
@@
 
-```{r}
+```{r echo=FALSE, message=FALSE}
 # Length restriction statement types of explicit PPC types (random sample)
@@
 # Discussion
+*Add 'Discussion' section*
+
+# Methods
+*Add 'Methods' section*
 
 # Data Availability
+The data used for this paper are available from the project’s OSF repository (link: [https://osf.io/8k7m4/](https://osf.io/8k7m4/))
 
 # Code Availability
+The analysis code for all results reported in this paper are available from the project’s OSF repository (link: [https://osf.io/8k7m4/](https://osf.io/8k7m4/))

### 2024-01-03 manuscript_NHB.Rmd
Added CIs in code
Updated to calculate CIs and include in-text through code

@@
 ```{r setup, include = FALSE}
-renv::activate()
+#renv::activate()
 
@@
 library(here) # for finding files
+library(binom) # for calculating CIs
 ```
@@
 # Load processed data files
-
-d_articles <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique', 'data','processed','d_articles.csv'), show_col_types = F) # article data 
-d_journals <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique', 'data','processed','d_journals.csv'), show_col_types = F) # journal data 
+#'ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique',
+d_articles <- read_csv(here('data','processed','d_articles.csv'), show_col_types = F) # article data 
+d_journals <- read_csv(here('data','processed','d_journals.csv'), show_col_types = F) # journal data 
 ```
@@
   mutate(has_ppc = case_when(
-    has_ppc == 'ARCHIVE' ~ 'Archive',
+    has_ppc == 'ARCHIVE' ~ 'Yes Implicit',
     has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
     has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
-    has_ppc == 'YES' ~ 'Yes',
+    has_ppc == 'YES' ~ 'Yes Explicit',
     TRUE ~ has_ppc
@@
 
+# Calculate the count and percentage for 2 types
+prominent2types <- dj_prominent %>%
+  filter(ppc_type == "B") %>%
+  filter(!is.na(ppc_name)) %>%
+  count()
+
 ```
 
-  As shown in Figure *XX*, post-publication critique policies were explicitly stated by `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "YES") / n() * 100)` of journals, and we inferred that they were implicitly accepted (as denoted by archival examples) in `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "ARCHIVE") / n() * 100)` of journals.
-`r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "NO IMPLICIT") / n() * 100)` had no advertised post-publication critique policy, and `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "NO EXPLICIT") / n() * 100)` of journals explicitly stated that they did not accept critiques (*Clinical Psychology: Science and Practice and Psychological Bulletin*).
-`r dj_prominent %>% filter(ppc_type == "B" & !is.na(ppc_name)) %>% summarise(percentage = sum(!is.na(ppc_name) / n() * 100))` of journals accepted two types (commentaries and letters); *International Journal of Mental Health and Addiction*, *Journal of Environmental Psychology*, and *Psychological Science*.
+  As shown in Figure *XX*, post-publication critique policies were explicitly stated by `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "YES") / n() * 100, "%"))` of journals, and we inferred that they were implicitly accepted (as denoted by archival examples) in `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "ARCHIVE") / n() * 100, "%"))` of journals.
+`r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO IMPLICIT") / n() * 100, "%"))` had no advertised post-publication critique policy, and `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO EXPLICIT") / n() * 100, "%"))` of journals explicitly stated that they did not accept critiques (*Clinical Psychology: Science and Practice and Psychological Bulletin*).
+`r paste0(prominent2types, "%")` of journals accepted two types (commentaries and letters); *International Journal of Mental Health and Addiction*, *Journal of Environmental Psychology*, and *Psychological Science*.
     Among the 41 explicitly stated post-publication critique options, restrictions on length were quantitatively stated (e.g., '1,000 words') in `r print(paste(prom_quantitative_length$count, "(", round(prom_quantitative_length$percentage), "%)", sep = ""))` cases, qualitatively stated (e.g.
@@
 combined_plots
+```
 
-ggsave(filename = "Random_statements.png", plot = last_plot(), device = "png")
+``` {r echo = FALSE, message = FALSE}
 
+# Calculate Wilson Confidence Intervals
+sample_size <- 100
+confidence_level <- 0.95
+
+#CIs for 'Yes Explicit'
+randomYes <- dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES") %>%
+  count()
+
+ci_yesE <- binom.confint(randomYes$n, sample_size, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_yesE_LL <- round(ci_yesE$lower*100, 1)
+ci_yesE_UL <- round(ci_yesE$upper*100, 1)
+
+#CIs for 'Yes Implicit'
+randomArchive <- dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "ARCHIVE") %>%
+  count()
+
+ci_yesI <- binom.confint(randomArchive$n, sample_size, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_yesI_LL <- round(ci_yesI$lower*100, 1)
+ci_yesI_UL <- round(ci_yesI$upper*100, 1)
+
+#CIs for 'No Implicit'
+randomNoImp <- dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "NO IMPLICIT") %>%
+  count()
+
+ci_noI <- binom.confint(randomNoImp$n, sample_size, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_noI_LL <- round(ci_noI$lower*100, 1)
+ci_noI_UL <- round(ci_noI$upper*100, 1)
+
+#CIs for 'No Explicit'
+randomNoExp <- dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "NO EXPLICIT") %>%
+  count()
+
+ci_noE <- binom.confint(randomNoExp$n, sample_size, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_noE_LL <- round(ci_noE$lower*100, 1)
+ci_noE_UL <- round(ci_noE$upper*100, 1)
+
+# CIs for 2 types
+random2types <- dj_random %>%
+  filter(ppc_type == "B") %>%
+  filter(!is.na(ppc_name)) %>%
+  count()
+
+ci_2typ <- binom.confint(random2types$n, sample_size, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_2typ_LL <- round(ci_2typ$lower*100, 1)
+ci_2typ_UL <- round(ci_2typ$upper*100, 1)
 ```
@@
 ```
-  As shown in Figure *XX*, post-publication critique policies were explicitly stated by `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "YES") / n() * 100)`% of journals (95% CI [15.8%, 32.2%]), and we inferred that they were implicitly accepted (as denoted by archival examples) in `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "ARCHIVE") / n() * 100)`% of journals (95% CI [1.0%, 8.5%]).
-`r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "NO IMPLICIT") / n() * 100)`% of journals (95% CI [63.6%, 80.7%]) had no advertised post-publication critique policy, and `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = sum(has_ppc == "NO EXPLICIT") / n() * 100)` of journals (95% CI [0.2%, 5.4%]) explicitly stated that they did not accept critiques (*Clinical Psychology: Science and Practice and Psychological Bulletin*, also included in sample for prominent journals).
-`r dj_random %>% filter(ppc_type == "B" & !is.na(ppc_name)) %>% summarise(percentage = sum(!is.na(ppc_name) / n() * 100))` of journals accepted two types (95% CI [0.0%, 7.0%]); *Cortex* offered commentaries and 'verification reports' (Chambers, 2020) and *Journal of Cognition and Culture* offered commentaries and letters.
-
-**ABOVE EDIT: insert code for CIs**
+  As shown in Figure *XX*, post-publication critique policies were explicitly stated by `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "YES") / n() * 100, "%"))` of journals (`r paste0(round(confidence_level*100), "% CI [", ci_yesE_LL, "%, ", ci_yesE_UL, "%]")`), and we inferred that they were implicitly accepted (as denoted by archival examples) in `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "ARCHIVE") / n() * 100, "%"))` of journals (`r paste0(round(confidence_level*100), "% CI [", ci_yesI_LL, "%, ", ci_yesI_UL, "%]")`).
+`r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO IMPLICIT") / n() * 100, "%"))` of journals (`r paste0(round(confidence_level*100), "% CI [", ci_noI_LL, "%, ", ci_noI_UL, "%]")`) had no advertised post-publication critique policy, and `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO EXPLICIT") / n() * 100, "%"))` of journals (`r paste0(round(confidence_level*100), "% CI [", ci_noE_LL, "%, ", ci_noE_UL, "%]")`) explicitly stated that they did not accept critiques (*Clinical Psychology: Science and Practice and Psychological Bulletin*, also included in sample for prominent journals).
+`r paste0(random2types, "%")` of journals accepted two types (`r paste0(round(confidence_level*100), "% CI [", ci_2typ_LL, "%, ", ci_2typ_UL, "%]")`); *Cortex* offered commentaries and 'verification reports' (Chambers, 2020) and *Journal of Cognition and Culture* offered commentaries and letters.
 

### 2024-01-03 manuscript_NHB.Rmd
Minor formatting changes
removed in-text print() functions where followed by paste as this for some reason decided to stop showing in pdf knit. Whole text changed due to folder name change leading to altering wrong manuscript copy so full text copy-pasted over.

@@
 `r paste0(prominent2types, "%")` of journals accepted two types (commentaries and letters); *International Journal of Mental Health and Addiction*, *Journal of Environmental Psychology*, and *Psychological Science*.
-    Among the 41 explicitly stated post-publication critique options, restrictions on length were quantitatively stated (e.g., '1,000 words') in `r print(paste(prom_quantitative_length$count, "(", round(prom_quantitative_length$percentage), "%)", sep = ""))` cases, qualitatively stated (e.g.
-'brief') in  `r print(paste(prom_qualitative_length$count, "(", round(prom_qualitative_length$percentage), "%)", sep = ""))` cases, and not stated in `r print(paste(prom_notStated_length$count, "(", round(prom_notStated_length$percentage), "%)", sep = ""))` cases.
-Time-to-submit was quantitatively stated (e.g., '4 weeks') in `r print(paste(prom_quantitative_time$count, "(", round(prom_quantitative_time$percentage), "%)", sep = ""))` cases, qualitatively stated (e.g., 'timely') in `r print(paste(prom_qualitative_time$count, "(", round(prom_qualitative_time$percentage), "%)", sep = ""))` cases, and not stated in `r print(paste(prom_notStated_time$count, "(", round(prom_notStated_time$percentage), "%)", sep = ""))` cases.
-Number of references allowed was quantitatively stated (e.g., 'max 20') in `r print(paste(prom_quantitative_ref$count, "(", round(prom_quantitative_ref$percentage), "%)", sep = ""))` cases and not stated in `r print(paste(prom_notStated_ref$count, "(", round(prom_notStated_ref$percentage), "%)", sep = ""))`.
-Whether critiques were sent for external peer-review was only stated in `r print(paste((prom_yes_review$count + prom_no_review$count), "(", round(prom_yes_review$percentage + prom_no_review$percentage), "%)", sep = ""))` cases, in `r print(paste(prom_yes_review$count, "(", round(prom_yes_review$percentage), "%)", sep = ""))` cases this was in the affirmative.
-    When stated quantitatively, length limits ranged from `r prom_length_range %>% pull(prom_min_length)` - `r prom_length_range %>% pull(prom_max_length)` words, time-to-submit limits ranged from `r prom_time_range %>% pull(prom_min_time)` -`r prom_time_range %>% pull(prom_max_time)` weeks, reference limits ranged between `r prom_ref_range %>% pull(prom_min_ref)` -`r prom_ref_range %>% pull(prom_max_ref)`.
+
+Among the 41 explicitly stated post-publication critique options, restrictions on length were quantitatively stated (e.g., '1,000 words') in `r paste(prom_quantitative_length$count, "(", round(prom_quantitative_length$percentage), "%)", sep = "")` cases, qualitatively stated (e.g.
+'brief') in  `r paste(prom_qualitative_length$count, "(", round(prom_qualitative_length$percentage), "%)", sep = "")` cases, and not stated in `r paste(prom_notStated_length$count, "(", round(prom_notStated_length$percentage), "%)", sep = "")` cases.
+Time-to-submit was quantitatively stated (e.g., '4 weeks') in `r paste(prom_quantitative_time$count, "(", round(prom_quantitative_time$percentage), "%)", sep = "")` cases, qualitatively stated (e.g., 'timely') in `r paste(prom_qualitative_time$count, "(", round(prom_qualitative_time$percentage), "%)", sep = "")` cases, and not stated in `r paste(prom_notStated_time$count, "(", round(prom_notStated_time$percentage), "%)", sep = "")` cases.
+Number of references allowed was quantitatively stated (e.g., 'max 20') in `r paste(prom_quantitative_ref$count, "(", round(prom_quantitative_ref$percentage), "%)", sep = "")` cases and not stated in `r paste(prom_notStated_ref$count, "(", round(prom_notStated_ref$percentage), "%)", sep = "")`.
+Whether critiques were sent for external peer-review was only stated in `r paste((prom_yes_review$count + prom_no_review$count), "(", round(prom_yes_review$percentage + prom_no_review$percentage), "%)", sep = "")` cases, in `r paste(prom_yes_review$count, "(", round(prom_yes_review$percentage), "%)", sep = "")` cases this was in the affirmative.
+
+When stated quantitatively, length limits ranged from `r prom_length_range %>% pull(prom_min_length)` - `r prom_length_range %>% pull(prom_max_length)` words, time-to-submit limits ranged from `r prom_time_range %>% pull(prom_min_time)` - `r prom_time_range %>% pull(prom_max_time)` weeks, reference limits ranged between `r prom_ref_range %>% pull(prom_min_ref)` -`r prom_ref_range %>% pull(prom_max_ref)`.
 Table *XX* shows descriptive statistics for stated quantitative restrictions, broken down by critique type.
@@
 
-  Among the 25 cases of explicitly accepted post-publication critiques, restrictions on length were quantitatively stated in `r print(paste(rand_quantitative_length$count, "(", round(rand_quantitative_length$percentage), "%)", sep = ""))` cases, and not stated in `r print(paste(rand_notStated_length$count, "(", round(rand_notStated_length$percentage), "%)", sep = ""))` cases.
-Time-to-submit was quantitatively stated in `r print(paste(rand_quantitative_time$count, "(", round(rand_quantitative_time$percentage), "%)", sep = ""))` case, and qualitatively stated in `r print(paste(rand_qualitative_time$count, "(", round(rand_qualitative_time$percentage), "%)", sep = ""))`, and not stated in `r print(paste(rand_notStated_time$count, "(", round(rand_notStated_time$percentage), "%)", sep = ""))` cases.
-Number of references allowed was stated quantitatively in `r print(paste(rand_quantitative_ref$count, "(", round(rand_quantitative_ref$percentage), "%)", sep = ""))` cases, and not stated in `r print(paste(rand_notStated_ref$count, "(", round(rand_notStated_ref$percentage), "%)", sep = ""))` cases.
-Whether critiques were peer-reviewed was stated in `r print(paste((rand_yes_review$count + rand_no_review$count), "(", round(rand_yes_review$percentage + rand_no_review$percentage), "%)", sep = ""))` cases, in `r print(paste(rand_yes_review$count, "(", round(rand_yes_review$percentage), "%)", sep = ""))` cases this was in the affirmative.
+Among the 25 cases of explicitly accepted post-publication critiques, restrictions on length were quantitatively stated in `r paste(rand_quantitative_length$count, "(", round(rand_quantitative_length$percentage), "%)", sep = "")` cases, and not stated in `r paste(rand_notStated_length$count, "(", round(rand_notStated_length$percentage), "%)", sep = "")` cases.
+Time-to-submit was quantitatively stated in `r paste(rand_quantitative_time$count, "(", round(rand_quantitative_time$percentage), "%)", sep = "")` case, and qualitatively stated in `r paste(rand_qualitative_time$count, "(", round(rand_qualitative_time$percentage), "%)", sep = "")`, and not stated in `r paste(rand_notStated_time$count, "(", round(rand_notStated_time$percentage), "%)", sep = "")` cases.
+Number of references allowed was stated quantitatively in `r paste(rand_quantitative_ref$count, "(", round(rand_quantitative_ref$percentage), "%)", sep = "")` cases, and not stated in `r paste(rand_notStated_ref$count, "(", round(rand_notStated_ref$percentage), "%)", sep = "")` cases.
+Whether critiques were peer-reviewed was stated in `r paste((rand_yes_review$count + rand_no_review$count), "(", round(rand_yes_review$percentage + rand_no_review$percentage), "%)", sep = "")` cases, in `r paste(rand_yes_review$count, "(", round(rand_yes_review$percentage), "%)", sep = "")` cases this was in the affirmative.
+
 When stated quantitatively, length limits ranged from `r rand_length_range %>% pull(rand_min_length)` - `r rand_length_range %>% pull(rand_max_length)` words, time-to-submit limits were only stated by one journal (as 9 months), references ranged between `r rand_ref_range %>% pull(rand_min_ref)` - `r rand_ref_range %>% pull(rand_max_ref)`.

### 2024-01-05 analysis/preprocessing.Rmd
Corrected logic coding error
Noticed T/F coding for d_articles$ppc_linked was inverted.

@@
          exclude_reason = factor(exclusion_reason_final),
-         ppc_linked = as.logical(fct_recode(ppc_linked_final, T = "NO", F = "YES"))) %>%
+         ppc_linked = as.logical(fct_recode(ppc_linked_final, F = "NO", T = "YES"))) %>%
   select(sample_id, article_id, exclude, exclude_reason, ppc_linked)

### 2024-01-05 manuscript/manuscript_NHB.Rmd
manuscript draft
updating changes

--- 2024-01-03 manuscript_NHB.Rmd
@@
 ---
-title: "A Descriptive Analysis of How Psychology Journals Handle Post-Publication Critiques"
-author: "Whamond, A., Vazire, S., Clarke, B., Moodie, N., Schiavone, S., Thibault, R. T., & Hardwicke, T. E."
+title: "A Descriptive Analysis of How Psychology Journals Handle Post-Publication
+  Critiques"
+author: Whamond, A., Vazire, S., Clarke, B., Moodie, N., Schiavone, S., Thibault,
+  R. T., & Hardwicke, T. E.
 date: "`r format(Sys.time(), '%d %B, %Y')`"
-output: pdf_document
+output:
+  pdf_document: default
+  word_document: default
+abstract: "Fostering critical discussion is essential to upholding the ethos of science
+  as an unbiased, collaborative, and self-correcting endeavor. Journals can support
+  this by offering options for post-publication critique, such as commentaries or
+  letters, allowing peers to voice substantiated concerns of empirical articles. We
+  provide a descriptive, cross-sectional analysis of post-publication critique policies
+  and prevalence across both prominent randomly-selected and psychology journals.
+  We found that 38% of prominent and 23% of randomly-selected psychology journals
+  offered explicit options for post-publication critique. Length and time-to-submit
+  limits were often not stated. Critique prevalence was rare with only a single event
+  identified among two samples of 101 articles. Given the widespread recognition of
+  the replication crisis in psychology, allowing avenues for criticisms to be voiced
+  may help increase the credibility within the field. To support transparency and
+  self-correction, psychology journals should offer clearly stated post-publication
+  critique options and encourage their use.\n"
+keywords: "post-publication critique, peer review, psychology, meta-research, journal
+  policy, self-correction, scientific criticism"
+
+bibliography: references.bib
+link-citations: true
+csl: nature.csl
+
+floatsintext: false
+figurelist: false
+tablelist: false
+footnotelist: false
+linenumbers: true
+mask: true
+draft: true
+always_allow_html: true
+urlcolor: blue
 ---
@@
 ```{r setup, include = FALSE}
-#renv::activate()
 
@@
 library(binom) # for calculating CIs
+library(citation) # for organizing citations
+library(tinytex)
 ```
@@
 #'ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique',
-d_articles <- read_csv(here('data','processed','d_articles.csv'), show_col_types = F) # article data 
-d_journals <- read_csv(here('data','processed','d_journals.csv'), show_col_types = F) # journal data 
+d_articles <- read_csv(here('data', 'processed', 'd_articles.csv'), show_col_types = F) # article data 
+d_journals <- read_csv(here('data', 'processed', 'd_journals.csv'), show_col_types = F) # journal data
+
 ```
@@
 
+```{r echo = FALSE, message = FALSE}
+# Create Table for describing the different common PPC types and restrictions (based on Hardwicke et al., 2022 findings)
+Type <- c("Letters", "Commentaries", "Web Comments")
+MedianLength <- c("500", "1200", "600")
+MedianTime <- c("8", "26", "NA")
+MedianRefs <- c("6", "15", "8")
+PeerReview <- c("20%", "55%", "0%")
+DOIs <- c("Yes", "Yes", "No")
+Utility <- c("Concise criticisms submitted shortly after target article published", "More in-depth critical reviews", "Flexible length with almost immediate visibility to readership")
+
+PPCtypes <- data.frame(Type, MedianLength, MedianTime, MedianRefs, PeerReview, DOIs, Utility)
+```
+
+``` {r echo = FALSE, results = 'asis'}
+PPCtypes %>%
+  kbl(align = c(rep("l", 1), rep("c", 5), rep("l", 1)), caption = "Common post-publication critique types including median restrictions, peer review policies, and descriptions",
+      col.names = c("Type", "Length", "Time-to-submit", "References", "Peer-review", "DOI", "Description")) %>%
+  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = TRUE) %>%
+  row_spec(0, bold = TRUE, align = "c")
+
+```
+
 # Results
 
-## Journal Policy
+## Part 1: Post-Publication Critique Policies
 
-For descriptive statistics on journal subdisciplines, post-publication critique acceptance, and COPE membership for both prominent and randomly-selected samples, see Supplemetary Information ##.
-A full list of the journals included in this study, along with their post-publication critique options and restrictions, is provided in Supplemetary Information ##.
+For descriptive statistics on journal subdisciplines, post-publication critique acceptance, and COPE membership for both prominent and randomly-selected samples, see Supplementary Information ##.
+A full list of the journals included in this study, along with their post-publication critique options and restrictions, is provided in Supplementary Information ##.
 
@@
 As this represents the entire population of interest for this section of the study, confidence intervals (CIs) are not included for this section of the study.
-Figure *XX* shows theobserved journal policies and, of the explicitly offered critique options identified, how restrictions on length and time-to-submit were stated.
+Figure *XX* shows the observed journal policies and, of the explicitly offered critique options identified, how restrictions on length and time-to-submit were stated.
 
@@
 `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO IMPLICIT") / n() * 100, "%"))` of journals (`r paste0(round(confidence_level*100), "% CI [", ci_noI_LL, "%, ", ci_noI_UL, "%]")`) had no advertised post-publication critique policy, and `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO EXPLICIT") / n() * 100, "%"))` of journals (`r paste0(round(confidence_level*100), "% CI [", ci_noE_LL, "%, ", ci_noE_UL, "%]")`) explicitly stated that they did not accept critiques (*Clinical Psychology: Science and Practice and Psychological Bulletin*, also included in sample for prominent journals).
-`r paste0(random2types, "%")` of journals accepted two types (`r paste0(round(confidence_level*100), "% CI [", ci_2typ_LL, "%, ", ci_2typ_UL, "%]")`); *Cortex* offered commentaries and 'verification reports' (Chambers, 2020) and *Journal of Cognition and Culture* offered commentaries and letters.
+`r paste0(random2types, "%")` of journals accepted two types (`r paste0(round(confidence_level*100), "% CI [", ci_2typ_LL, "%, ", ci_2typ_UL, "%]")`); *Cortex* offered commentaries and 'verification reports' [@Chambers2020] and *Journal of Cognition and Culture* offered commentaries and letters.
 
@@
 
-## PPC Prevalence (results cont.)
+## Part 2: Post-Publication Critique Prevalence
+```{r echo = FALSE, message=FALSE}
+# Filter articles by sample and calculate CIs
+
+# For articles randomly sampled from prominent psychology journals
+da_prominent <- d_articles %>%
+  filter(exclude == "RETAIN") %>% # remove excluded articles
+  filter(sample_id == "prominent") # keep only articles from prominent journals
+
+sample_size_a <- 101
+
+# Linked PPCs
+prominent_linked <- da_prominent %>% # counts number of linked PPC events
+  filter(ppc_linked == "TRUE") %>%
+  count()
+
+ci_linked <- binom.confint(prominent_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_linked_LL <- round(ci_linked$lower*100, 1)
+ci_linked_UL <- round(ci_linked$upper*100, 1)
+
+# Instance PPCs
+prominent_instance <- da_prominent %>% # counts number of linked PPC events
+  filter(exclude_reason == "IS PPC") %>%
+  count()
+
+ci_instance <- binom.confint(prominent_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_instance_LL <- round(ci_instance$lower*100, 1)
+ci_instance_UL <- round(ci_instance$upper*100, 1)
+
+# For articles randomly sampled from all psychology journals
+da_random <- d_articles %>%
+  filter(exclude == "RETAIN") %>% # remove excluded articles
+  filter(sample_id == "random") # keep only randomly-selected articles
+
+# Linked PPCs
+random_linked <- da_random %>%
+  filter(ppc_linked == "TRUE") %>%
+  count()
+
+ci_linkedR <- binom.confint(random_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_linkedR_LL <- round(ci_linkedR$lower*100, 1)
+ci_linkedR_UL <- round(ci_linkedR$upper*100, 1)
+
+# Instance PPCs
+random_instance <- da_random %>% # counts number of linked PPC events
+  filter(exclude_reason == "IS PPC") %>%
+  count()
+
+ci_instanceR <- binom.confint(random_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_instanceR_LL <- round(ci_instanceR$lower*100, 1)
+ci_instanceR_UL <- round(ci_instanceR$upper*100, 1)
+```
+**2a) Articles Published in Prominent Psychology Journals**
+
+Prevalence was defined in two ways: linked critiques (links to critiques appearing on same webpage as target article) and instances of critiques (articles that are themselves critiques).
+Only one linked post-publication critique event was found within our sample of 101 articles published in prominent psychology journals, yielding a prevalence estimate of `r da_prominent %>% summarise(percentage = paste0(round(sum(as.integer(ppc_linked == "TRUE")) / n() * 100, 1), "%"))` (`r paste0(round(confidence_level*100), "% CI [", ci_linked_LL, "%, ", ci_linked_UL, "%]")`).
+No instances of post-publication critiques were found (0%, `r paste0(round(confidence_level*100), "% CI [", ci_instance_LL, "%, ", ci_instance_UL, "%]")`).
+
+The single linked critique found appeared under the 'Recommended articles' sidebar of an article published in the Journal of Environmental Psychology webpage (for a depiction of how the article was linked, see Appendix F).
+This example was published as a letter[@Berto2020] and addressed concerns over incorrect citation of the critiquing author’s previous work and methodology used in the target article [@Hicks2020].
+
+**2b) Articles Published in Any Psychology Journal**
+
+No events of either linked or instances of post-publication critiques were identified in our random sample of 101 articles, resulting in a prevalence estimate of 0% (`r paste0(round(confidence_level*100), "% CI [", ci_instanceR_LL, "%, ", ci_instanceR_UL, "%]")`) for both classifications.
 
@@
 The analysis code for all results reported in this paper are available from the project’s OSF repository (link: [https://osf.io/8k7m4/](https://osf.io/8k7m4/))
+
+# References

### 2024-01-05 manuscript/manuscript_NHB.Rmd
Added COPE data
updated to include COPE results coded in-text

@@
 library(tinytex)
+library(english) # for displaying code generated numbers as written 
 ```
@@
 ### Table *XX*
+[*Insert table of results*]
 
@@
 Interestingly, time-to-submit was less restrictive for letters than commentaries, however, this was only reported in two and four cases (respectively) so limited inferences can be made from this.
+
+```{r COPE status in prominent sample, echo=FALSE, message=FALSE}
+# COPE membership status among prominent journals accepting PPC
+prominent_PPCy <- dj_prominent %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>% # keep only journals that accept PPC
+  summarise(count = n()) # total number journals accepting PPC
+
+prom_copeY_PPC <- dj_prominent %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>%
+  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
+  summarise(count = n()) # number of COPE journals accepting PPC
+
+prom_copeN_PPC <- dj_prominent %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>%
+  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
+  summarise(count = n()) # number of non-COPE journals accepting PPC
+
+# COPE membership status among prominent journals NOT accepting PPC
+prominent_PPCn <- dj_prominent %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>% # keep only journals that accept PPC
+  summarise(count = n()) # total number journals accepting PPC
+
+prom_copeY_PPCn <- dj_prominent %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
+  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
+  summarise(count = n()) # number of COPE journals accepting PPC
+
+prom_copeN_PPCn <- dj_prominent %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
+  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
+  summarise(count = n()) # number of non-COPE journals accepting PPC
+
+```
+
+Of the `r paste(prominent_PPCy$count)` journals that accepted post-publication critiques (including the six implicitly implied through archive examples), `r paste(prom_copeY_PPC$count, "(", round((prom_copeY_PPC$count / prominent_PPCy$count) * 100, 1), "%)", sep = "")` were COPE members and `r paste(as.english(prom_copeN_PPC$count), " (", round((prom_copeN_PPC$count / prominent_PPCy$count) * 100, 1), "%)", sep = "")` were not.
+Of the `r paste(prominent_PPCn$count)` journals that had no critique policy, `r paste(prom_copeY_PPCn$count, "(", round((prom_copeY_PPCn$count / prominent_PPCn$count) * 100, 1), "%)", sep = "")` were COPE members, including both of those with explicit statements that they do not accept unsolicited critiques.
 
@@
 Similarly, no details on restrictions or peer-review were stated for 'verification reports' (the one 'other' critique type included in this sample).
+
+```{r COPE status in random sample, echo=FALSE, message=FALSE}
+# COPE membership status among randomly-sampled journals accepting PPC
+random_PPCy <- dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>% # keep only journals that accept PPC
+  summarise(count = n()) # total number journals accepting PPC
+
+rand_copeY_PPC <- dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>%
+  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
+  summarise(count = n()) # number of COPE journals accepting PPC
+
+rand_copeN_PPC <- dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>%
+  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
+  summarise(count = n()) # number of non-COPE journals accepting PPC
+
+# COPE membership status among prominent journals NOT accepting PPC
+random_PPCn <- dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>% # keep only journals that accept PPC
+  summarise(count = n()) # total number journals accepting PPC
+
+rand_copeY_PPCn <- dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
+  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
+  summarise(count = n()) # number of COPE journals accepting PPC
+
+rand_copeN_PPCn <- dj_random %>%
+  filter(ppc_type == "A") %>%
+  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
+  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
+  summarise(count = n()) # number of non-COPE journals accepting PPC
+
+```
+
+Of the `r paste(random_PPCy$count)` journals that accepted post-publication critiques (including the three implicitly implied through archive examples), `r paste(rand_copeY_PPC$count, "(", round((rand_copeY_PPC$count / random_PPCy$count) * 100, 1), "%)", sep = "")` were COPE members and `r paste(as.english(rand_copeN_PPC$count), " (", round((rand_copeN_PPC$count / random_PPCy$count) * 100, 1), "%)", sep = "")` were not.
+Of the `r paste(random_PPCn$count)` journals that had no critique policy, `r paste(rand_copeY_PPCn$count, "(", round((rand_copeY_PPCn$count / random_PPCn$count) * 100, 1), "%)", sep = "")` were COPE members, including the one with an explicit statement that they do not accept unsolicited critiques.
 

### 2024-01-05 manuscript/manuscript_NHB.Rmd
Corrected # COPE code descriptions

@@
   filter(ppc_type == "A") %>%
-  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>% # keep only journals that accept PPC
-  summarise(count = n()) # total number journals accepting PPC
+  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>% # keep only journals that do not accept PPC
+  summarise(count = n()) # total number journals not accepting PPC
 
@@
   filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
-  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
+  filter(cope == "TRUE") %>% # Keep only COPE journals (that do not accept PPC)
   summarise(count = n()) # number of COPE journals accepting PPC
@@
   filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
-  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
-  summarise(count = n()) # number of non-COPE journals accepting PPC
+  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that do not accept PPC)
+  summarise(count = n()) # number of non-COPE journals not accepting PPC
 

### 2024-01-05 manuscript/manuscript_NHB.Rmd
edited Abstract

@@
   provide a descriptive, cross-sectional analysis of post-publication critique policies
-  and prevalence across both prominent randomly-selected and psychology journals.
+  and prevalence across samples of a) 100 prominent and b) 100 randomly-selected and psychology journals.
   We found that 38% of prominent and 23% of randomly-selected psychology journals
-  offered explicit options for post-publication critique. Length and time-to-submit
+  offered explicit critique options. Length and time-to-submit
   limits were often not stated. Critique prevalence was rare with only a single event
@@
   the replication crisis in psychology, allowing avenues for criticisms to be voiced
-  may help increase the credibility within the field. To support transparency and
+  may help increase credibility within the field. To support transparency and
   self-correction, psychology journals should offer clearly stated post-publication

### 2024-01-05 manuscript/manuscript_NHB.Rmd
Edited figures
minor edits to text size and colours to improve readability

@@
 
-``` {r echo = FALSE, results = 'asis'}
+``` {r echo = FALSE, message = FALSE}
+#ERR: Table currently inserts under results in PDF. Format is horrendous in Word.
+
 PPCtypes %>%
@@
   scale_fill_brewer(palette = "Blues") +
-  labs(x = "Restriction Type", y = "Count", fill = "Restrictions")
+  labs(x = "Restriction Type", y = "Count", fill = "Restrictions") +
+  theme(axis.text.x = element_text(size = 7))
 
@@
   geom_bar(stat = "identity",
-           colour = "black") +
+           colour = "black",
+           width = 0.8) +
   theme_bw() +
-  scale_fill_brewer(palette = "Oranges") +
+  scale_fill_brewer(palette = "YlOrRd", direction = -1) +
   labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")

### 2024-01-12 manuscript/manuscript_NHB.Rmd
removed broken table

@@
 *Add 'Introduction' section*
-
-```{r echo = FALSE, message = FALSE}
-# Create Table for describing the different common PPC types and restrictions (based on Hardwicke et al., 2022 findings)
-Type <- c("Letters", "Commentaries", "Web Comments")
-MedianLength <- c("500", "1200", "600")
-MedianTime <- c("8", "26", "NA")
-MedianRefs <- c("6", "15", "8")
-PeerReview <- c("20%", "55%", "0%")
-DOIs <- c("Yes", "Yes", "No")
-Utility <- c("Concise criticisms submitted shortly after target article published", "More in-depth critical reviews", "Flexible length with almost immediate visibility to readership")
-
-PPCtypes <- data.frame(Type, MedianLength, MedianTime, MedianRefs, PeerReview, DOIs, Utility)
-```
 

### 2024-04-05 analysis/preprocessing.Rmd
Update preprocessing.Rmd

@@
          has_ppc = fct_recode(anyPPC, 
-                             "ARCHIVE" = "ARCHIVE ONLY", 
                              "NO IMPLICIT" = "NO (there are no PPC options)",

### 2024-04-11 analysis/resultsAnalysis.Rmd
Create resultsAnalysis.Rmd

---
title: "Results Analysis"
author: "Annie Whamond"
date: "2024-04-10"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r}
# Load libraries
library(here)
library(lsr)
library(tidyverse)
library(tidylog)
library(binom)
library(ggplot2)
library(RColorBrewer)
```

# Load data

```{r}
# Load preprocessed data
d_articles <- read_csv(here('data', 'processed', 'd_articles.csv'), show_col_types = F) # article data 
d_journals <- read_csv(here('data', 'processed', 'd_journals.csv'), show_col_types = F) # journal data
```

# STUDY ONE: JOURNAL POLICY

Remove excluded journals and create separate tibbles for prominent and randomly sampled journals
```{r}
dj_prominent <- d_journals %>%
  filter(sample_id != "random") %>%
  filter(is_empirical == TRUE)

dj_random <- d_journals %>%
  filter(sample_id != "prominent") %>%
  filter(is_empirical == TRUE)
```
## Journal characteristics
Descriptive statistics

Calculate JIF median and IQR for prominent journals
```{r}
# Prominent journal sample
prominentJIF <- dj_prominent %>% 
  filter(ppc_type == "A") %>%      # Keep only single entry for each journal
  summarise(promMedian_jif = round(median(jif),2), 
            promMin_jif = round(min(jif),2),
            promMax_jif = round(max(jif),2),
            promIQR_jif = round(IQR(jif),2)
  )

prominentJIF
```

Calculate JIF median and IQR for random journals
```{r}
randomJIF <- dj_random %>% 
  filter(ppc_type == "A") %>%
  filter(!is.na(jif)) %>%
  summarise(randMedian_jif = round(median(jif),2),
            randMin_jif = round(min(jif),2),
            randMax_jif = round(max(jif),2),
            randIQR_jif = round(IQR(jif),2)
  )

randomJIF
```

Count prominent journals listed as COPE members 
```{r}
prominentCOPE <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  filter(cope == TRUE) %>%
  summarise(count = n())

prominentCOPE
```

Count randomly sampled journals listed as COPE members 
```{r}
randomCOPE <- dj_random %>%
  filter(ppc_type == 'A') %>%
  filter(cope == TRUE) %>%
  summarise(count = n())

randomCOPE
```

Prominent journals Web Of Science categories
```{r}
prominentCategory <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  group_by(field) %>%
  summarise(count = n()) %>%
  ungroup()

prominentCategory
```
Random journals Web Of Science categories
```{r}
randomCategory <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(field) %>%
  summarise(count = n()) %>%
  ungroup()

randomCategory
```
## How many journals offer post-publication critique?

Inspect how frequently post-publication critique policies were stated for prominent journals 
```{r}
prominentPPC <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

prominentPPC
```
*Note: This may change once ARCHIVE ONLY coding is removed*

Inspect post-publication critique types at prominent journals
```{r}
prominentTypes <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  group_by(ppc_name) %>%
  summarise(count = n()) %>%
  ungroup()

prominentTypes
```

Inspect how frequently post-publication critique policies were stated for randomly sampled journals 
```{r}
randomPPC <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

randomPPC
```

Calculate confidence interval for explicitly stated post-publication critique policies among randomly sampled journals
```{r}

randomPPCyes <- dj_random %>%
  filter(ppc_type == 'A', !is.na(ppc_name)) %>%
  summarise(count = n())

# Calculate Wilson confidence intervals
sample_size <- 100
confidence_level <- 0.95

#CIs for 'Yes Explicit'
randomPPC_CI <- binom.confint(randomPPCyes, sample_size, method = "wilson", conf.level = confidence_level)

randomPPC_CI
```

Inspect post-publication critique types at randomly sampled journals
```{r}
randomTypes <- dj_random %>%
  filter(!is.na(ppc_name)) %>%
  group_by(ppc_name) %>%
  summarise(count = n()) %>%
  ungroup()

randomTypes
```

### 2024-04-24 analysis/resultsAnalysis.Rmd
added limits analysis
Now contains all the analysis code for limitations in both journal samples

@@
 library(RColorBrewer)
+library(assertthat) 
 ```
@@
 
-Remove excluded journals and create separate tibbles for prominent and randomly sampled journals
+Remove excluded journals and create separate tibbles for prominent and randomly selected journals
 ```{r}
@@
 ```
+```{r}
+# Run a test to ensure all randomly-selected and non-empirical journals removed from dj_prominent
+assert_that(
+  all(dj_prominent$sample_id == "prominent" | dj_prominent$sample_id == "both" 
+      & dj_prominent$is_empirical == TRUE),
+  msg = "Found unexpected values in the sample_id or is_empirical columns"
+  )
+
+# Run a test to ensure all prominent sample and non-empirical journals removed from dj_prominent
+assert_that(
+  all(dj_random$sample_id == "random" | 
+        dj_random$sample_id == "both" 
+      & dj_random$is_empirical == TRUE),
+  msg = "Found unexpected values in the sample_id or is_empirical columns"
+  )
+
+```
+
 ## Journal characteristics
@@
 
-Count randomly sampled journals listed as COPE members 
+Count randomly selected journals listed as COPE members 
 ```{r}
@@
 ```
-*Note: This may change once ARCHIVE ONLY coding is removed*
+Get the names of the prominent journals that have 'NO EXPLICIT' PPC options
+```{r}
+dj_prominent %>%
+  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
+  print()
+```
+Get how many prominent journals offered more than one type
+```{r}
+# Return all rows with ppc_name values for ppc_type B and C
+dj_prominent %>%
+  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name)))
+
+# Return count
+dj_prominent %>%
+  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
+  summarise(count = n())
+```
 
@@
 ```{r}
-prominentTypes <- dj_prominent %>%
+# Counts for all types of PPC, commentary only, and letters only
+promAllTypes <- dj_prominent %>%
   filter(!is.na(ppc_name)) %>%
-  group_by(ppc_name) %>%
-  summarise(count = n()) %>%
+  summarise(n())
+
+promCommentary <- dj_prominent %>%
+  filter(ppc_name == "Commentary") %>%
+  summarise(n())
+
+promLetters <- dj_prominent %>%
+  filter(ppc_name == "Letters") %>%
+  summarise(n())
+
+# These numbers will be used in percentage calculations for limits
+promAllTypes # Total number of PPC options found in prominent journals
+promCommentary # Total number of 'Commentary' options
+promLetters # Total number of 'Letters' options
+```
+Inspect the COPE status of prominent journals with and without PPC policies
+```{r}
+promCOPEtable <- dj_prominent %>%
+ filter(ppc_type == "A") %>%
+ mutate(has_ppc = case_when(
+    has_ppc == "NO EXPLICIT" ~ "NO",
+    has_ppc == "NO IMPLICIT" ~ "NO",
+    TRUE ~ has_ppc
+ )) %>%
+ group_by(has_ppc) %>%
+ summarise(
+    total_count = n(),
+    COPE_count = sum(cope == TRUE)
+ ) %>%
+ mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
  ungroup()
 
-prominentTypes
+promCOPEtable
 ```
 
-Inspect how frequently post-publication critique policies were stated for randomly sampled journals 
+Inspect how frequently post-publication critique policies were stated for randomly selected journals 
 ```{r}
@@
 
-Calculate confidence interval for explicitly stated post-publication critique policies among randomly sampled journals
+Calculate confidence interval for explicitly stated post-publication critique policies among randomly selected journals
 ```{r}
@@
 ```
+Get how many randomly selected journals offered more than one type
+```{r}
+# Return all rows with ppc_name values for ppc_type B and C
+dj_random %>%
+  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name)))
 
-Inspect post-publication critique types at randomly sampled journals
+# Return count
+dj_random %>%
+  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
+  summarise(count = n())
+```
+
+Get the names of the randomly samples journals that have 'NO EXPLICIT' PPC options
+```{r}
+dj_random %>%
+  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
+  print()
+```
+
+Inspect post-publication critique types at randomly selected journals
 ```{r}
@@
 ```
+
+Inspect the COPE status of randomly selected journals with and without PPC policies
+```{r}
+randCOPEtable <- dj_random %>%
+ filter(ppc_type == "A") %>%
+ mutate(has_ppc = case_when(
+    has_ppc == "NO EXPLICIT" ~ "NO",
+    has_ppc == "NO IMPLICIT" ~ "NO",
+    TRUE ~ has_ppc
+ )) %>%
+ group_by(has_ppc) %>%
+ summarise(
+    total_count = n(),
+    COPE_count = sum(cope == TRUE)
+ ) %>%
+ mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
+ ungroup()
+
+randCOPEtable
+```
+
+# What limits did journals place on post-publication critique?
+Find the most restrictive limits of any journal
+```{r}
+# Find the lowest length limit
+minLength <- d_journals %>%
+ select(c(sample_id, journal_name, ppc_name, ppc_length)) %>%
+ filter(!is.na(ppc_name),
+         ppc_length != "NOT STATED" & ppc_length != "Qualitative") %>%
+ mutate(quantLength = as.numeric(ppc_length)) %>%
+ slice_min(quantLength, n = 1) %>% # Select the row with the minimum quantLength
+ ungroup()
+
+minLength
+```
+
+``` {r}
+# Find the lowest time-to-submit limit
+minTime <- d_journals %>%
+ select(c(sample_id, journal_name, ppc_name, ppc_time)) %>%
+ filter(!is.na(ppc_name),
+         ppc_time != "NOT STATED" & ppc_time != "Qualitative") %>%
+ mutate(quantTime = as.numeric(ppc_time)) %>%
+ slice_min(quantTime, n = 1) %>% # Select the row with the minimum quantTime
+ ungroup()
+
+minTime
+```
+
+## Calculations for Table 1: Prominent journals
+Check length limits placed on PPC options in prominent journals
+```{r}
+# Summarise length statistics for All Types
+prominentLengthAll <- dj_prominent %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_length)) %>%
+ mutate(quantLength = case_when(
+    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
+  )) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_length == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianLength = median(quantLength, na.rm = TRUE),
+    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
+    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
+    IQR = Q3 - Q1 
+ )
+
+prominentLengthAll
+```
+
+``` {r}
+# Summarise length Statistics for each PPC type
+prominentLengthType <- dj_prominent %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_length)) %>%
+ mutate(quantLength = case_when(
+    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
+  )) %>%
+ group_by(ppc_name) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_length == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianLength = median(quantLength, na.rm = TRUE),
+    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
+    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
+    IQR = Q3 - Q1 
+ ) %>%
+  ungroup()
+
+prominentLengthType
+```
+Check time-to-submit limits placed on PPC options in prominent journals
+```{r}
+# Summarise time-to-submit statistics for All Types
+prominentTimeAll <- dj_prominent %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_time)) %>%
+ mutate(quantTime = case_when(
+    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
+  )) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_time == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianTime = median(quantTime, na.rm = TRUE),
+    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
+    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
+    IQR = Q3 - Q1 
+ )
+
+prominentTimeAll
+```
+
+``` {r}
+# Summarise time-to-submit Statistics for each PPC type
+prominentTimeType <- dj_prominent %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_time)) %>%
+ mutate(quantTime = case_when(
+    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
+  )) %>%
+  group_by(ppc_name) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_time == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianTime = median(quantTime, na.rm = TRUE),
+    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
+    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
+    IQR = Q3 - Q1 
+ ) %>%
+  ungroup()
+
+prominentTimeType
+```
+Check reference limits placed on PPC options in prominent journals
+```{r}
+# Summarise reference statistics for All Types
+prominentRefAll <- dj_prominent %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_ref)) %>%
+ mutate(quantRef = case_when(
+    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
+  )) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianRef = median(quantRef, na.rm = TRUE),
+    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
+    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
+    IQR = Q3 - Q1 
+ )
+
+prominentRefAll
+```
+
+```{r}
+# Summarise reference statistics by type
+prominentRefType <- dj_prominent %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_ref)) %>%
+ mutate(quantRef = case_when(
+    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
+  )) %>%
+  group_by(ppc_name) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianRef = median(quantRef, na.rm = TRUE),
+    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
+    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
+    IQR = Q3 - Q1 
+ ) %>%
+  ungroup()
+
+prominentRefType
+```
+Check how many PPC options are sent for external peer review in prominent journals
+```{r}
+# Peer review statistics for All Types
+prominentReviewAll <- dj_prominent %>%
+  select(c(journal_name, ppc_name, ppc_review)) %>%
+  filter(!is.na(ppc_name)) %>%
+  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
+            yesReview = anyReview - sum(ppc_review == "NO"),
+            yesPercent = round((yesReview / n()) * 100)   # Percentage reviewed from All Types 
+  )
+
+prominentReviewAll
+
+```
+
+```{r}
+# Peer review statistics by types
+prominentReviewAll <- dj_prominent %>%
+  select(c(journal_name, ppc_name, ppc_review)) %>%
+  filter(!is.na(ppc_name)) %>%
+  group_by(ppc_name) %>%
+  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
+            yesReview = anyReview - sum(ppc_review == "NO"),
+            yesPercent = round((yesReview / n()) * 100)
+  ) %>%
+  ungroup()
+
+prominentReviewAll
+
+```
+
+## Calculations for Table 2: Randomly selected journals
+
+Check length limits placed on PPC options in randomly selected journals
+```{r}
+# Summarise length statistics for All Types
+randomLengthAll <- dj_random %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_length)) %>%
+ mutate(quantLength = case_when(
+    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
+  )) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_length == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianLength = median(quantLength, na.rm = TRUE),
+    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
+    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
+    IQR = Q3 - Q1 
+ )
+
+randomLengthAll
+```
+
+``` {r}
+# Summarise length Statistics for each PPC type
+randomLengthType <- dj_random %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_length)) %>%
+ mutate(quantLength = case_when(
+    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
+  )) %>%
+ group_by(ppc_name) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_length == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianLength = median(quantLength, na.rm = TRUE),
+    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
+    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
+    IQR = Q3 - Q1 
+ ) %>%
+  ungroup()
+
+randomLengthType
+```
+Check time-to-submit limits placed on PPC options in prominent journals
+```{r}
+# Summarise time-to-submit statistics for All Types
+randomTimeAll <- dj_random %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_time)) %>%
+ mutate(quantTime = case_when(
+    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
+  )) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_time == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianTime = median(quantTime, na.rm = TRUE),
+    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
+    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
+    IQR = Q3 - Q1 
+ )
+
+randomTimeAll
+```
+
+``` {r}
+# Summarise time-to-submit Statistics for each PPC type
+randomTimeType <- dj_random %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_time)) %>%
+ mutate(quantTime = case_when(
+    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
+  )) %>%
+  group_by(ppc_name) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_time == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianTime = median(quantTime, na.rm = TRUE),
+    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
+    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
+    IQR = Q3 - Q1 
+ ) %>%
+  ungroup()
+
+randomTimeType
+```
+Check reference limits placed on PPC options in prominent journals
+```{r}
+# Summarise reference statistics for All Types
+randomRefAll <- dj_random %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_ref)) %>%
+ mutate(quantRef = case_when(
+    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
+  )) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianRef = median(quantRef, na.rm = TRUE),
+    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
+    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
+    IQR = Q3 - Q1 
+ )
+
+randomRefAll
+```
+
+```{r}
+# Summarise reference statistics by type
+randomRefType <- dj_random %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_ref)) %>%
+ mutate(quantRef = case_when(
+    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
+  )) %>%
+  group_by(ppc_name) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianRef = median(quantRef, na.rm = TRUE),
+    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
+    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
+    IQR = Q3 - Q1 
+ ) %>%
+  ungroup()
+
+randomRefType
+```
+Check how many PPC options are sent for external peer review in prominent journals
+```{r}
+# Peer review statistics for All Types
+randomReviewAll <- dj_random %>%
+  select(c(journal_name, ppc_name, ppc_review)) %>%
+  filter(!is.na(ppc_name)) %>%
+  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
+            yesReview = anyReview - sum(ppc_review == "NO"),
+            yesPercent = round((yesReview / n()) * 100)   # Percentage reviewed from All Types 
+  )
+
+randomReviewAll
+
+```
+
+```{r}
+# Peer review statistics by types
+randomReviewAll <- dj_random %>%
+  select(c(journal_name, ppc_name, ppc_review)) %>%
+  filter(!is.na(ppc_name)) %>%
+  group_by(ppc_name) %>%
+  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
+            yesReview = anyReview - sum(ppc_review == "NO"),
+            yesPercent = round((yesReview / n()) * 100)
+  ) %>%
+  ungroup()
+
+randomReviewAll
+
+```

### 2024-04-24 analysis/resultsAnalysis.Rmd
added article analyses

@@
 library(lsr)
+library(dplyr)
 library(tidyverse)
@@
 ```
+
+*Note.* PPC = post-publication critique
 
@@
 
-# Run a test to ensure all prominent sample and non-empirical journals removed from dj_prominent
+# Run a test to ensure all prominent sample and non-empirical journals removed from dj_random
 assert_that(
@@
 
-Inspect how frequently post-publication critique policies were stated for prominent journals 
+Inspect how frequently PPC policies were stated for prominent journals 
 ```{r}
@@
 ```
-Get how many prominent journals offered more than one type
+Get how many prominent journals offered more than one type of PPC
 ```{r}
@@
 
-Inspect post-publication critique types at prominent journals
+Inspect PPC types at prominent journals
 ```{r}
@@
 
-Inspect how frequently post-publication critique policies were stated for randomly selected journals 
+Inspect how frequently PPC policies were stated for randomly selected journals 
 ```{r}
@@
 
-Calculate confidence interval for explicitly stated post-publication critique policies among randomly selected journals
+Calculate confidence interval for explicitly stated PPC policies among randomly selected journals
 ```{r}
@@
 ```
-Get how many randomly selected journals offered more than one type
+Get how many randomly selected journals offered more than one type of PPC
 ```{r}
@@
 
-Inspect post-publication critique types at randomly selected journals
+Inspect PPC types at randomly selected journals
 ```{r}
@@
 # What limits did journals place on post-publication critique?
+
 Find the most restrictive limits of any journal
@@
 ## Calculations for Table 1: Prominent journals
+
 Check length limits placed on PPC options in prominent journals
@@
 ```
+
 Check time-to-submit limits placed on PPC options in prominent journals
@@
 ```
+
 Check reference limits placed on PPC options in prominent journals
@@
 ```
+
 Check how many PPC options are sent for external peer review in prominent journals
@@
 randomReviewAll
+```
+# STUDY 2: PREVALENCE
 
+Look for links to PPC in articles published in prominent journals
+```{r}
+d_articles %>%
+  filter(sample_id == "prominent",
+         ppc_linked == TRUE) %>%
+  summarise(n = n())
 ```
+
+Calculate CIs for Linked PPC 
+```{r}
+sample_size_a <- 101
+
+# Linked PPCs
+prominent_linked <- d_articles %>% # counts number of linked PPC events
+  filter(sample_id == "prominent",
+         ppc_linked == TRUE) %>%
+  count()
+
+ci_linked <- binom.confint(prominent_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_promLinked_LL <- round(ci_linked$lower*100, 1)
+ci_promLinked_UL <- round(ci_linked$upper*100, 1)
+
+ci_promLinked_LL
+ci_promLinked_UL
+```
+
+Look for instances of PPC in articles published in prominent journals
+```{r}
+d_articles %>%
+  filter(sample_id == "prominent",
+         exclude_reason == "IS ITSELF PPC") %>%
+  summarise(n = n())
+```
+Calculate CIs for Instance PPC in prominent journals
+```{r}
+# Instance PPCs
+prominent_instance <- d_articles %>% # counts number of linked PPC events
+  filter(sample_id == "prominent",
+    exclude_reason == "IS ITSELF PPC") %>%
+  count()
+
+ci_instance <- binom.confint(prominent_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_promInstance_LL <- round(ci_instance$lower*100, 1)
+ci_promIinstance_UL <- round(ci_instance$upper*100, 1)
+
+ci_promInstance_LL
+ci_promIinstance_UL
+```
+Look for linked PPC in articles in random sample
+```{r}
+d_articles %>%
+  filter(sample_id == "random",
+         ppc_linked == TRUE) %>%
+  summarise(n = n())
+```
+
+Calculate CIs for linked PPC in articles in random sample
+```{r}
+# Linked PPCs
+random_linked <- d_articles %>% # counts number of linked PPC events
+  filter(sample_id == "random",
+         ppc_linked == TRUE) %>%
+  count()
+
+ci_Rlinked <- binom.confint(random_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_randLinked_LL <- round(ci_Rlinked$lower*100, 1)
+ci_randLinked_UL <- round(ci_Rlinked$upper*100, 1)
+
+ci_randLinked_LL
+ci_randLinked_UL
+```
+Look for instances of PPC in articles in random sample
+```{r}
+d_articles %>%
+  filter(sample_id == "random",
+         exclude_reason == "IS ITSELF PPC") %>%
+  summarise(n = n())
+```
+
+Calculate CIs for Instance PPC in random sample
+```{r}
+# Instance PPCs
+random_instance <- d_articles %>% # counts number of linked PPC events
+  filter(sample_id == "random",
+    exclude_reason == "IS ITSELF PPC") %>%
+  count()
+
+ci_Rinstance <- binom.confint(random_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_randInstance_LL <- round(ci_Rinstance$lower*100, 1)
+ci_randIinstance_UL <- round(ci_Rinstance$upper*100, 1)
+
+ci_randInstance_LL
+ci_randIinstance_UL
+```

### 2024-04-24 manuscript/manuscript_NHB.Rmd
added article analyses

@@
   policy, self-correction, scientific criticism"
-
 bibliography: references.bib
@@
 csl: nature.csl
-
 floatsintext: false
@@
 ```{r setup, include = FALSE}
-
 library(papaja) # article template
@@
 *Add 'Introduction' section*
-
-``` {r echo = FALSE, message = FALSE}
-#ERR: Table currently inserts under results in PDF. Format is horrendous in Word.
-
-PPCtypes %>%
-  kbl(align = c(rep("l", 1), rep("c", 5), rep("l", 1)), caption = "Common post-publication critique types including median restrictions, peer review policies, and descriptions",
-      col.names = c("Type", "Length", "Time-to-submit", "References", "Peer-review", "DOI", "Description")) %>%
-  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = TRUE) %>%
-  row_spec(0, bold = TRUE, align = "c")
-
-```
 
@@
 
+ggsave("ProminentJournalPolicies.png", plot = last_plot(), device = "png")
 ```
@@
 combined_plots
+
+ggsave("RandomJournalPolicies.png", plot = last_plot(), device = "png")
 ```

### 2024-04-24 analysis/resultsAnalysis.Rmd
added figures

@@
 ```
+Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
+```{r}
+dj_random %>%
+  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
+  print()
+```
 
@@
 ```{r}
-
 randomPPCyes <- dj_random %>%
@@
 ```
+
+# FIGURES
+
+```{r}
+quantLength <- d_journals %>%
+ select(c(sample_id, ppc_name, ppc_length)) %>%
+ filter(!is.na(ppc_length),
+         ppc_length != "NOT STATED",
+         ppc_length != "Qualitative") %>%
+ mutate(Length = as.numeric(ppc_length))
+
+quantLength %>%  
+ ggplot(mapping = aes(x = ppc_name, y = Length, colour = sample_id)) +
+ geom_boxplot(
+    color = "black",
+    fill = "lightblue",
+    alpha = 0.5
+ ) +
+ geom_jitter(width = 0.2) + 
+ coord_flip() +
+ theme_bw() +
+ labs(Title = "Length Limits", x = "Post-publication critique type", y = "Length limits (words)")
+
+```
+
+```{r}
+quantTime <- d_journals %>%
+ select(c(sample_id, ppc_name, ppc_time)) %>%
+ filter(!is.na(ppc_time),
+         ppc_time != "NOT STATED",
+         ppc_time != "Qualitative") %>%
+ mutate(Time = as.numeric(ppc_time))
+
+quantTime %>%  
+ ggplot(mapping = aes(x = ppc_name, y = Time, colour = sample_id)) +
+ geom_boxplot(
+    color = "black",
+    fill = "lightblue",
+    alpha = 0.5
+ ) +
+ geom_jitter(width = 0.2) + 
+ coord_flip() +
+ theme_bw() +
+ labs(Title = "Time Limits", x = "Post-publication critique type", y = "Time limits (weeks)")
+```

### 2024-04-25 analysis/resultsAnalysis.Rmd
Updated analysis plots
Also simplified some analysis code.

--- 2024-04-24 analysis/resultsAnalysis.Rmd
@@
 ```
-Get how many prominent journals offered more than one type of PPC
+Get names for prominent journals that offered more than one type of PPC
 ```{r}
-# Return all rows with ppc_name values for ppc_type B and C
-dj_prominent %>%
-  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name)))
-
 # Return count
@@
   filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
-  summarise(count = n())
+  print()
 ```
@@
 ```{r}
-# Counts for all types of PPC, commentary only, and letters only
-promAllTypes <- dj_prominent %>%
-  filter(!is.na(ppc_name)) %>%
-  summarise(n())
-
-promCommentary <- dj_prominent %>%
-  filter(ppc_name == "Commentary") %>%
-  summarise(n())
-
-promLetters <- dj_prominent %>%
-  filter(ppc_name == "Letters") %>%
-  summarise(n())
-
-# These numbers will be used in percentage calculations for limits
-promAllTypes # Total number of PPC options found in prominent journals
-promCommentary # Total number of 'Commentary' options
-promLetters # Total number of 'Letters' options
+table(dj_prominent$ppc_name)
 ```
@@
 ```{r}
-promCOPEtable <- dj_prominent %>%
+promCOPE <- dj_prominent %>%
  filter(ppc_type == "A") %>%
@@
 
-promCOPEtable
+promCOPE
 ```
@@
 ```
-Get how many randomly selected journals offered more than one type of PPC
+Get names for randomly selected journals that offered more than one type of PPC
 ```{r}
@@
 dj_random %>%
-  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name)))
-
-# Return count
-dj_random %>%
   filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
-  summarise(count = n())
+  print()
 ```
 
-Get the names of the randomly samples journals that have 'NO EXPLICIT' PPC options
+Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
 ```{r}
@@
 ```{r}
-randomTypes <- dj_random %>%
-  filter(!is.na(ppc_name)) %>%
-  group_by(ppc_name) %>%
-  summarise(count = n()) %>%
-  ungroup()
-
-randomTypes
+table(dj_random$ppc_name)
 ```
@@
 ```{r}
-randCOPEtable <- dj_random %>%
+randomCOPE <- dj_random %>%
  filter(ppc_type == "A") %>%
@@
 
-randCOPEtable
+randomCOPE
 ```
@@
 
-## Calculations for Table 1: Prominent journals
+## Calculations for Table 1: PPC limits in prominent journals
 
@@
 
-## Calculations for Table 2: Randomly selected journals
+## Calculations for Table 2: PPC limits in randomly selected journals
 
@@
 ```
+
+# FIGURES
+Boxplot of quantitative length limits
+```{r}
+quantLength <- d_journals %>%
+ select(c(sample_id, ppc_name, ppc_length)) %>%
+ filter(!is.na(ppc_length),
+         ppc_length != "NOT STATED",
+         ppc_length != "Qualitative") %>%
+ mutate(Length = as.numeric(ppc_length))
+
+quantLength %>%  
+ ggplot(mapping = aes(x = ppc_name, y = Length, colour = sample_id)) +
+ geom_violin(
+    color = "black",
+    fill = "lightblue",
+    alpha = 0.5
+ ) +
+ geom_jitter(width = 0.1,
+             alpha = 0.8) + 
+ scale_fill_brewer(palette = "Set2") +
+ scale_color_brewer(palette = "Set2") +
+ coord_flip() +
+ theme_bw() +
+ labs(title = "All stated quantitative length Limits", x = "Post-publication critique type", y = "Length limits (words)")
+
+```
+Boxplot of quantitative time limits
+```{r}
+quantTime <- d_journals %>%
+ select(c(sample_id, ppc_name, ppc_time)) %>%
+ filter(!is.na(ppc_time),
+         ppc_time != "NOT STATED",
+         ppc_time != "Qualitative") %>%
+ mutate(Time = as.numeric(ppc_time))
+
+quantTime %>%  
+ ggplot(mapping = aes(x = ppc_name, y = Time, colour = sample_id)) +
+ geom_boxplot(
+    color = "black",
+    fill = "lightblue",
+    alpha = 0.5
+ ) +
+ geom_jitter(width = 0.2) + 
+ scale_fill_brewer(palette = "Set2") +
+ scale_color_brewer(palette = "Set2") +
+ coord_flip() +
+ theme_bw() +
+ labs(title = "All stated quantitative time limits", x = "Post-publication critique type", y = "Time limits (weeks)")
+```
+### *Post-Publication Critique Policy and Restriction Statements in Prominent Psychology Journals*
+
+```{r, echo = FALSE, message=FALSE}
+# Filter and transform restrictions for ppc_length
+prominent_length_data <- dj_prominent %>%
+  filter(!is.na(ppc_name)) %>%
+  filter(has_ppc != "ARCHIVE") %>% # removes 'Archive Only' PPC types
+  mutate(ppc_length = case_when(
+    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
+    ppc_length == "NOT STATED" ~ "Not Stated",
+    TRUE ~ 'Qualitative' # Summarises all length limits as 'Quantitative', 'Qualitative', or 'Not Stated'
+  )) %>% 
+  group_by(ppc_length) %>%
+  summarise(count = n())
+
+# Filter and transform restrictions for ppc_time
+prominent_time_data <- dj_prominent %>%
+  filter(!is.na(ppc_name)) %>%
+  filter(has_ppc != "ARCHIVE") %>% # removes 'Archive Only' PPC types
+  mutate(ppc_time = case_when(
+    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
+    ppc_time == "NOT STATED" ~ "Not Stated",
+    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
+  )) %>%
+  group_by(ppc_time) %>%
+  summarise(count = n())
+
+# Combine the data and unite the columns
+combined_data <- bind_rows(
+  prominent_length_data %>% mutate(Code = "Length"),
+  prominent_time_data %>% mutate(Code = "Time-to-submit")
+) %>%
+unite(limits, ppc_length, ppc_time) %>%
+  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
+                   limits == "Qualitative_NA" ~ "Qualitative",
+                   limits == "Quantitative_NA" ~ "Quantitative",
+                   limits == "NA_Not Stated" ~ "Not Stated",
+                   limits == "NA_Qualitative" ~ "Qualitative",
+                   limits == "NA_Quantitative" ~ "Quantitative",
+                   TRUE ~ as.character(limits)
+                   ))
+
+# Create the first graph
+graph1 <- ggplot(combined_data, aes(x = Code, y = count, fill = limits)) +
+  geom_bar(stat = "identity", 
+           position = "stack",
+           colour = "black") +
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues") +
+  labs(x = "Restriction Type", y = "Count", fill = "Restrictions") +
+  theme(axis.text.x = element_text(size = 7))
+
+# Create the second graph
+graph2 <- dj_prominent %>%
+  filter(ppc_type == "A") %>% # Keeps only first entry for each journal
+  filter(!is.na(has_ppc)) %>% # Remove journal rows with no (NA) PPC options 
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'Yes Implicit',
+    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
+    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
+    has_ppc == 'YES' ~ 'Yes Explicit',
+    TRUE ~ has_ppc
+  )) %>%
+  group_by(has_ppc) %>%
+  summarise(count = n()) %>%
+  mutate(percentage = count / sum(count) * 100) %>%
+  ggplot(aes(x = "", y = count, fill = has_ppc)) +
+  geom_bar(stat = "identity",
+           colour = "black",
+           width = 0.8) +
+  theme_bw() +
+  scale_fill_brewer(palette = "YlOrRd", direction = -1) +
+  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")
+
+# Arrange both graphs in the same figure
+combined_plots <- graph2 + graph1
+combined_plots
+
+#ggsave("ProminentJournalPolicies.png", plot = last_plot(), device = "png")
+```
+
+### *Post-Publication Critique Policy and Restriction Statements in Randomly-selected Psychology Journals*
+```{r echo=FALSE, message=FALSE}
+# Create and combine restriction statement graphs with PPC acceptance (random sample)
+
+# Filter and process data for ppc_length
+random_length_data <- d_journals %>%
+  filter(sample_id %in% c("random", "both")) %>%
+  filter(!is.na(ppc_name)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_length = case_when(
+    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
+    ppc_length == "NOT STATED" ~ "Not Stated",
+    TRUE ~ 'Qualitative'
+  )) %>%
+  group_by(ppc_length) %>%
+  summarise(count = n())
+
+# Filter and process data for ppc_time
+random_time_data <- d_journals %>%
+  filter(sample_id %in% c("random", "both")) %>%
+  filter(!is.na(ppc_name)) %>%
+  filter(has_ppc != "ARCHIVE") %>%
+  mutate(ppc_time = case_when(
+    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
+    ppc_time == "NOT STATED" ~ "Not Stated",
+    TRUE ~ 'Qualitative'
+  )) %>%
+  group_by(ppc_time) %>%
+  summarise(count = n())
+
+# Combine the data and unite the columns
+combined_data_random <- bind_rows(
+  random_length_data %>% mutate(Code = "Length"),
+  random_time_data %>% mutate(Code = "Time-to-submit")
+) %>%
+unite(limits, ppc_length, ppc_time) %>%
+  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
+                   limits == "Qualitative_NA" ~ "Qualitative",
+                   limits == "Quantitative_NA" ~ "Quantitative",
+                   limits == "NA_Not Stated" ~ "Not Stated",
+                   limits == "NA_Qualitative" ~ "Qualitative",
+                   limits == "NA_Quantitative" ~ "Quantitative",
+                   TRUE ~ as.character(limits)
+                   ))
+
+# Create the first graph
+graph4 <- ggplot(combined_data_random, aes(x = Code, y = count, fill = limits)) +
+  geom_bar(stat = "identity", 
+           position = "stack",
+           colour = "black") +
+  theme_bw() +
+  scale_fill_brewer(palette = "Blues") +
+  labs(x = "Restriction Type", y = "Count", fill = "Restrictions") +
+  theme(axis.text.x = element_text(size = 7))
+
+# Create the second graph
+graph3 <- d_journals %>%
+  filter(sample_id == "random" | sample_id == "both") %>%
+  filter(ppc_type == "A") %>%
+  filter(!is.na(has_ppc)) %>%
+  mutate(has_ppc = case_when(
+    has_ppc == 'ARCHIVE' ~ 'Yes Implicit',
+    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
+    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
+    has_ppc == 'YES' ~ 'Yes Explicit',
+    TRUE ~ has_ppc
+  )) %>%
+  group_by(has_ppc) %>%
+  summarise(count = n()) %>%
+  mutate(percentage = count / sum(count) * 100) %>%
+  ggplot(aes(x = "", y = count, fill = has_ppc)) +
+  geom_bar(stat = "identity",
+           colour = "black",
+           width = 0.8) +
+  theme_bw() +
+  scale_fill_brewer(palette = "YlOrRd", direction = -1) +
+  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")
+
+# Arrange both graphs in the same figure
+combined_plots <- graph3 + graph4
+combined_plots
+
+#ggsave("RandomJournalPolicies.png", plot = last_plot(), device = "png")
+```

### 2024-06-04 analysis/resultsAnalysis.Rmd
Plot changes
Superficial alterations to plots

@@
  ggplot(mapping = aes(x = ppc_name, y = Length, colour = sample_id)) +
- geom_violin(
+ geom_boxplot(
     color = "black",
     fill = "lightblue",
-    alpha = 0.5
+    alpha = 0.4
  ) +
- geom_jitter(width = 0.1,
-             alpha = 0.8) + 
- scale_fill_brewer(palette = "Set2") +
- scale_color_brewer(palette = "Set2") +
+ geom_jitter(width = 0.3,
+             alpha = 0.8,
+             size = 2) + 
+ scale_color_manual(values = c("prominent" =  "#ff6347", 
+                              "random" =   "#8db600",
+                              "both" = "#000080")
+                    ) +
  coord_flip() +
+ scale_y_continuous(n.breaks = 8) +
  theme_bw() +
- labs(title = "All stated quantitative length Limits", x = "Post-publication critique type", y = "Length limits (words)")
+ theme(axis.text.y = element_text(angle = 90, hjust = 0.5)) +
+ labs(title = "All stated quantitative length limits", 
+      x = "Post-publication critique type", 
+      y = "Length limits (words)", 
+      colour = "Sample")
 
+ggsave("lengthLimits.png", plot = last_plot(), device = "png")
 ```
@@
     fill = "lightblue",
-    alpha = 0.5
+    alpha = 0.4
  ) +
- geom_jitter(width = 0.2) + 
- scale_fill_brewer(palette = "Set2") +
- scale_color_brewer(palette = "Set2") +
+ geom_jitter(width = 0.2,
+             alpha = 0.8,
+             size = 2) + 
+ scale_color_manual(values = c("prominent" =  "#ff6347", 
+                              "random" =   "#8db600",
+                              "both" = "#000080")
+                    ) +
  coord_flip() +
  theme_bw() +
- labs(title = "All stated quantitative time limits", x = "Post-publication critique type", y = "Time limits (weeks)")
+ theme(axis.text.y = element_text(angle = 90, hjust = 0.5)) +
+ labs(title = "All stated quantitative time limits", 
+      x = "Post-publication critique type", 
+      y = "Time limits (weeks)", 
+      colour = "Sample")
+
+ggsave("timeLimits.png", plot = last_plot(), device = "png")
 ```
@@
 
-#ggsave("ProminentJournalPolicies.png", plot = last_plot(), device = "png")
+ggsave("ProminentJournalPolicies.png", plot = last_plot(), device = "png")
 ```
@@
 
-#ggsave("RandomJournalPolicies.png", plot = last_plot(), device = "png")
+ggsave("RandomJournalPolicies.png", plot = last_plot(), device = "png")
 ```

### 2024-10-23 analysis/resultsAnalysis.Rmd
Updated via the Open Science Framework

@@
 output:
-  pdf_document: default
   html_document: default
@@
 
-Remove excluded journals and create separate tibbles for prominent and randomly selected journals
+Remove excluded, non-empirical, journals and create separate tibbles for prominent and randomly selected journals
 ```{r}
@@
 ```
+Run assertion checks for both samples
 ```{r}
-# Run a test to ensure all randomly-selected and non-empirical journals removed from dj_prominent
+# Check all randomly-selected and non-empirical journals have been removed from dj_prominent
 assert_that(
@@
 
-# Run a test to ensure all prominent sample and non-empirical journals removed from dj_random
+# Check all prominent sample and non-empirical journals have been removed from dj_random
 assert_that(
@@
 ```
+
 Random journals Web Of Science categories
@@
 
+PROMINENT SAMPLE
 Inspect how frequently PPC policies were stated for prominent journals 
@@
 ```
+
 Get the names of the prominent journals that have 'NO EXPLICIT' PPC options
@@
 ```
+
 Get names for prominent journals that offered more than one type of PPC
@@
 ```
+
 Inspect the COPE status of prominent journals with and without PPC policies
@@
 ```
-
+RANDOMLY-SELECTED SAMPLE
 Inspect how frequently PPC policies were stated for randomly selected journals 
@@
 ```
+
 Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
@@
 
+randomPPCno <- dj_random %>%
+  filter(ppc_type == 'A', is.na(ppc_name)) %>%
+  summarise(count = n())
+
 # Calculate Wilson confidence intervals
@@
 
-#CIs for 'Yes Explicit'
+# CIs for 'Yes Explicit'
 randomPPC_CI <- binom.confint(randomPPCyes, sample_size, method = "wilson", conf.level = confidence_level)
 
+# CIs for 'No' (both explicit and Implicit)
+randomPPC_CI_neg <- binom.confint(randomPPCno, sample_size, method = "wilson", conf.level = confidence_level)
+
+# View results
 randomPPC_CI
+randomPPC_CI_neg
 ```
+*Note.* CIs were not calculated for the prominent sample of journals as they represented our entire population of interest.
+
 Get names for randomly selected journals that offered more than one type of PPC
@@
 # Peer review statistics by types
-prominentReviewAll <- dj_prominent %>%
+prominentReviewType <- dj_prominent %>%
   select(c(journal_name, ppc_name, ppc_review)) %>%
@@
 
-prominentReviewAll
-
+prominentReviewType
 ```
@@
 randomReviewAll
-
 ```
@@
 # Peer review statistics by types
-randomReviewAll <- dj_random %>%
+randomReviewType <- dj_random %>%
   select(c(journal_name, ppc_name, ppc_review)) %>%
@@
 
-randomReviewAll
+randomReviewType
 ```
+
 # STUDY 2: PREVALENCE
@@
 ```
+
 Calculate CIs for Instance PPC in prominent journals
@@
 ```
+
 Look for linked PPC in articles in random sample
@@
 ```
+
 Look for instances of PPC in articles in random sample
@@
 # FIGURES
+*Note.* These figures are not included in the final article as they do not offer additional informative informative beyond what was reported in the tables.
+
 Boxplot of quantitative length limits
@@
 ```
+
 Boxplot of quantitative time limits
@@
 ```
+
 ### *Post-Publication Critique Policy and Restriction Statements in Prominent Psychology Journals*
-
 ```{r, echo = FALSE, message=FALSE}

### 2024-11-02 analysis/Updated-ResultsAnalysis.Rmd
Created limit tables
The Updated-resultsAnalysis file was includes stitched tables of our limitations results. Can replace the resultsAnalysis.Rmd

---
title: "Results Analysis"
author: "Annie Whamond"
date: "2024-04-10"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r}
# Load libraries
library(here)
library(lsr)
library(dplyr)
library(tidyverse)
library(tidylog)
library(binom)
library(ggplot2)
library(RColorBrewer)
library(assertthat)
library(kableExtra)
library(webshot2)
```

# Load data

```{r}
# Load preprocessed data
d_articles <- read_csv(here('data', 'processed', 'd_articles.csv'), show_col_types = F) # article data 
d_journals <- read_csv(here('data', 'processed', 'd_journals.csv'), show_col_types = F) # journal data
```

*Note.* PPC = post-publication critique

# STUDY ONE: JOURNAL POLICY

Remove excluded, non-empirical, journals and create separate tibbles for prominent and randomly selected journals
```{r}
dj_prominent <- d_journals %>%
  filter(sample_id != "random") %>%
  filter(is_empirical == TRUE)

dj_random <- d_journals %>%
  filter(sample_id != "prominent") %>%
  filter(is_empirical == TRUE)
```
Run assertion checks for both samples
```{r}
# Check all randomly-selected and non-empirical journals have been removed from dj_prominent
assert_that(
  all(dj_prominent$sample_id == "prominent" | dj_prominent$sample_id == "both" 
      & dj_prominent$is_empirical == TRUE),
  msg = "Found unexpected values in the sample_id or is_empirical columns"
  )

# Check all prominent sample and non-empirical journals have been removed from dj_random
assert_that(
  all(dj_random$sample_id == "random" | 
        dj_random$sample_id == "both" 
      & dj_random$is_empirical == TRUE),
  msg = "Found unexpected values in the sample_id or is_empirical columns"
  )

```

## Journal characteristics
Descriptive statistics

Calculate JIF median and IQR for prominent journals
```{r}
# Prominent journal sample
prominentJIF <- dj_prominent %>% 
  filter(ppc_type == "A") %>%      # Keep only single entry for each journal
  summarise(promMedian_jif = round(median(jif),2), 
            promMin_jif = round(min(jif),2),
            promMax_jif = round(max(jif),2),
            promIQR_jif = round(IQR(jif),2)
  )

prominentJIF
```

Calculate JIF median and IQR for random journals
```{r}
randomJIF <- dj_random %>% 
  filter(ppc_type == "A") %>%
  filter(!is.na(jif)) %>%
  summarise(randMedian_jif = round(median(jif),2),
            randMin_jif = round(min(jif),2),
            randMax_jif = round(max(jif),2),
            randIQR_jif = round(IQR(jif),2)
  )

randomJIF
```

Count prominent journals listed as COPE members 
```{r}
prominentCOPE <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  filter(cope == TRUE) %>%
  summarise(count = n())

prominentCOPE
```

Count randomly selected journals listed as COPE members 
```{r}
randomCOPE <- dj_random %>%
  filter(ppc_type == 'A') %>%
  filter(cope == TRUE) %>%
  summarise(count = n())

randomCOPE
```

Prominent journals Web Of Science categories
```{r}
prominentCategory <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  group_by(field) %>%
  summarise(count = n()) %>%
  ungroup()

prominentCategory
```

Random journals Web Of Science categories
```{r}
randomCategory <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(field) %>%
  summarise(count = n()) %>%
  ungroup()

randomCategory
```

## How many journals offer post-publication critique?

RANDOMLY-SELECTED SAMPLE

Inspect how frequently PPC policies were stated for randomly selected journals 
```{r}
randomPPC <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

randomPPC
```

Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
```{r}
dj_random %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```

Calculate confidence interval for explicitly stated PPC policies among randomly selected journals
```{r}
randomPPCyes <- dj_random %>%
  filter(ppc_type == 'A', !is.na(ppc_name)) %>%
  summarise(count = n())

randomPPCno <- dj_random %>%
  filter(ppc_type == 'A', is.na(ppc_name)) %>%
  summarise(count = n())

# Calculate Wilson confidence intervals
sample_size <- 100
confidence_level <- 0.95

# CIs for 'Yes Explicit'
randomPPC_CI <- binom.confint(randomPPCyes, sample_size, method = "wilson", conf.level = confidence_level)

# CIs for 'No' (both explicit and Implicit)
randomPPC_CI_neg <- binom.confint(randomPPCno, sample_size, method = "wilson", conf.level = confidence_level)

# View results
randomPPC_CI
randomPPC_CI_neg
```
*Note.* CIs were not calculated for the prominent sample of journals as they represented our entire population of interest.

Get names for randomly selected journals that offered more than one type of PPC
```{r}
# Return all rows with ppc_name values for ppc_type B and C
dj_random %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
  print()
```

Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
```{r}
dj_random %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```

Inspect PPC types at randomly selected journals
```{r}
table(dj_random$ppc_name)
```

Inspect the COPE status of randomly selected journals with and without PPC policies
```{r}
randomCOPE <- dj_random %>%
 filter(ppc_type == "A") %>%
 mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
 )) %>%
 group_by(has_ppc) %>%
 summarise(
    total_count = n(),
    COPE_count = sum(cope == TRUE)
 ) %>%
 mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
 ungroup()

randomCOPE
```

PROMINENT SAMPLE

Inspect how frequently PPC policies were stated for prominent journals 
```{r}
prominentPPC <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

prominentPPC
```

Get the names of the prominent journals that have 'NO EXPLICIT' PPC options
```{r}
dj_prominent %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```

Get names for prominent journals that offered more than one type of PPC
```{r}
# Return count
dj_prominent %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
  print()
```

Inspect PPC types at prominent journals
```{r}
table(dj_prominent$ppc_name)
```

Inspect the COPE status of prominent journals with and without PPC policies
```{r}
promCOPE <- dj_prominent %>%
 filter(ppc_type == "A") %>%
 mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
 )) %>%
 group_by(has_ppc) %>%
 summarise(
    total_count = n(),
    COPE_count = sum(cope == TRUE)
 ) %>%
 mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
 ungroup()

promCOPE
```

# What limits did journals place on post-publication critique?

Find the most restrictive limits of any journal
```{r}
# Find the lowest length limit
minLength <- d_journals %>%
 select(c(sample_id, journal_name, ppc_name, ppc_length)) %>%
 filter(!is.na(ppc_name),
         ppc_length != "NOT STATED" & ppc_length != "Qualitative") %>%
 mutate(quantLength = as.numeric(ppc_length)) %>%
 slice_min(quantLength, n = 1) %>% # Select the row with the minimum quantLength
 ungroup()

minLength
```

``` {r}
# Find the lowest time-to-submit limit
minTime <- d_journals %>%
 select(c(sample_id, journal_name, ppc_name, ppc_time)) %>%
 filter(!is.na(ppc_name),
         ppc_time != "NOT STATED" & ppc_time != "Qualitative") %>%
 mutate(quantTime = as.numeric(ppc_time)) %>%
 slice_min(quantTime, n = 1) %>% # Select the row with the minimum quantTime
 ungroup()

minTime
```

## Calculations for Table 1: PPC limits in randomly selected journals

Check length limits placed on PPC options in randomly selected journals
```{r}
# Summarise length statistics for All Types
randomLengthAll <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
    IQR = round(Q3 - Q1)
 )

# Put results into desired table format
randomLengthAll_1 <- randomLengthAll %>% 
  mutate('Post-publication critique type' = "All types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", IQR, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise length Statistics for each PPC type
randomLengthType <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
    IQR = Q3 - Q1 
 ) %>%
  ungroup()

# Put results into desired table format
randomLengthType_1 <- randomLengthType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", IQR, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all time limits into single table
randomLength_combo <- bind_rows(
  randomLengthType_1,
  randomLengthAll_1
)
```

Check time-to-submit limits placed on PPC options in prominent journals
```{r}
# Summarise time-to-submit statistics for All Types
randomTimeAll <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = median(quantTime, na.rm = TRUE),
    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
    IQR = Q3 - Q1 
 )

# Put results into desired table format
randomTimeAll_1 <- randomTimeAll %>% 
  mutate('Post-publication critique type' = "All Types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianTime, " (", IQR, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise time-to-submit Statistics for each PPC type
randomTimeType <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = median(quantTime, na.rm = TRUE),
    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
randomTimeType_1 <- randomTimeType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianTime, " (", IQR, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all time limits into single table
randomTime_combo <- bind_rows(
  randomTimeType_1,
  randomTimeAll_1
)
```

Check reference limits placed on PPC options in prominent journals
```{r}
# Summarise reference statistics for All Types
randomRefAll <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
    IQR = round(Q3 - Q1)
 )

# Put results into desired table format
randomRefAll_1 <- randomRefAll %>% 
  mutate('Post-publication critique type' = "All types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianRef, " (", IQR, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Summarise reference statistics by type
randomRefType <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
randomRefType_1 <- randomRefType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianRef, " (", IQR, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
randomRef_combo <- bind_rows(
  randomRefType_1,
  randomRefAll_1
)
```

Check how many PPC options are sent for external peer review in prominent journals
```{r}
# Peer review statistics for All Types
randomReviewAll <- dj_random %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)   # Percentage reviewed from All Types 
  )

# Put results into desired table format
randomReviewAll_1 <- randomReviewAll %>%
  mutate('Post-publication critique type' = "All types") %>%
  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
  select('Post-publication critique type', 'YES n (%)')
```

```{r}
# Peer review statistics by types
randomReviewType <- dj_random %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  group_by(ppc_name) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)
  ) %>%
  ungroup()

# Put results into desired table format
randomReviewType_1 <- randomReviewType %>%
  mutate('Post-publication critique type' = ppc_name) %>%
  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
  select('Post-publication critique type', 'YES n (%)')
```

```{r}
# Combine all peer review into single table
randomReview_combo <- bind_rows(
  randomReviewType_1,
  randomReviewAll_1
)
```

**Table 1.** Post-publication critique types identified in randomly selected psychology journals and their length, time-to-submit, and reference limits.

``` {r}
# Give each table a separate header for results
randomLengthTable <- randomLength_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Length limits" = 3))

randomTimeTable <- randomTime_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Time limits" = 3))

randomRefTable <- randomRef_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Reference limits" = 3))

randomReviewTable <- randomReview_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "YES n (%)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Peer review" = 1))
```

```{r}
# Combine the random sample limitations data frames
combined_df <- bind_cols(
  randomLength_combo %>% select(-`Post-publication critique type`),
  randomTime_combo %>% select(-`Post-publication critique type`),
  randomRef_combo %>% select(-`Post-publication critique type`),
  randomReview_combo %>% select(-`Post-publication critique type`)
)

# Add the 'Post-publication critique type' column back to the combined data frame
combined_df <- bind_cols(randomLength_combo %>% select(`Post-publication critique type`), combined_df)

# Create the table with kableExtra
randomLimits_Table <- combined_df %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "YES n (%)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Length limits" = 3, "Time limits" = 3, "Reference limits" = 3, "Peer review" = 1))

randomLimits_Table

save_kable(randomLimits_Table, here("analysis/randomLimits_Table.png"))
```

## Calculations for Table 2: PPC limits in prominent journals

Check length limits placed on PPC options in prominent journals
```{r}
# Summarise length statistics for All Types
prominentLengthAll <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
    IQR = round(Q3 - Q1)
 )

# Put results into desired table format
prominentLengthAll_1 <- prominentLengthAll %>% 
  mutate('Post-publication critique type' = "All types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", IQR, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise length Statistics for each PPC type
prominentLengthType <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
prominentLengthType_1 <- prominentLengthType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", IQR, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
prominentLength_combo <- bind_rows(
  prominentLengthType_1,
  prominentLengthAll_1
)
```

Check time-to-submit limits placed on PPC options in prominent journals
```{r}
# Summarise time-to-submit statistics for All Types
prominentTimeAll <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = round(median(quantTime, na.rm = TRUE)),
    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
    IQR = round(Q3 - Q1) 
 )

# Put results into desired table format
prominentTimeAll_1 <- prominentTimeAll %>%
  mutate('Post-publication critique type' = "All types") %>%
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
  mutate('median (IQR)' = paste(medianTime, " (", IQR, ")", sep = "")) %>%
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise time-to-submit Statistics for each PPC type
prominentTimeType <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = round(median(quantTime, na.rm = TRUE)),
    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
prominentTimeType_1 <- prominentTimeType %>%
  mutate('Post-publication critique type' = ppc_name) %>%
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
  mutate('median (IQR)' = paste(medianTime, " (", IQR, ")", sep = "")) %>%
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
prominentTime_combo <- bind_rows(
  prominentTimeType_1,
  prominentTimeAll_1
)
```

Check reference limits placed on PPC options in prominent journals
```{r}
# Summarise reference statistics for All Types
prominentRefAll <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
    IQR = round(Q3 - Q1)
 )

# Put results into desired table format
prominentRefAll_1 <- prominentRefAll %>%
  mutate('Post-publication critique type' = "All types") %>%
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
  mutate('median (IQR)' = paste(medianRef, " (", IQR, ")", sep = "")) %>%
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Summarise reference statistics by type
prominentRefType <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
prominentRefType_1 <- prominentRefType %>%
  mutate('Post-publication critique type' = ppc_name) %>%
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
  mutate('median (IQR)' = paste(medianRef, " (", IQR, ")", sep = "")) %>%
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
prominentRef_combo <- bind_rows(
  prominentRefType_1,
  prominentRefAll_1
)
```

Check how many PPC options are sent for external peer review in prominent journals
```{r}
# Peer review statistics for All Types
prominentReviewAll <- dj_prominent %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)   # Percentage reviewed from All Types 
  )

# Put results into desired table format
prominentReviewAll_1 <- prominentReviewAll %>%
  mutate('Post-publication critique type' = "All types") %>%
  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
  select('Post-publication critique type', 'YES n (%)')
```

```{r}
# Peer review statistics by types
prominentReviewType <- dj_prominent %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  group_by(ppc_name) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)
  ) %>%
  ungroup()

# Put results into desired table format
prominentReviewType_1 <- prominentReviewType %>%
  mutate('Post-publication critique type' = ppc_name) %>%
  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
  select('Post-publication critique type', 'YES n (%)')
```

```{r}
# Combine all peer review into single table
prominentReview_combo <- bind_rows(
  prominentReviewType_1,
  prominentReviewAll_1
)
```

**Table 2.** Post-publication critique types identified in prominent psychology journals and their length, time-to-submit, and reference limits.

``` {r}
# Give each table a separate header for results
prominentLengthTable <- prominentLength_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Length limits" = 3))

prominentTimeTable <- prominentTime_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Time limits" = 3))

prominentRefTable <- prominentRef_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Reference limits" = 3))

prominentReviewTable <- prominentReview_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "YES n (%)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Peer review" = 1))

```

```{r}
# Combine the prominent limitations data frames
combined_df <- bind_cols(
  prominentLength_combo %>% select(-`Post-publication critique type`),
  prominentTime_combo %>% select(-`Post-publication critique type`),
  prominentRef_combo %>% select(-`Post-publication critique type`),
  prominentReview_combo %>% select(-`Post-publication critique type`)
)

# Add the 'Post-publication critique type' column back to the combined data frame
combined_df <- bind_cols(prominentLength_combo %>% select(`Post-publication critique type`), combined_df)

# Create the table with kableExtra
prominentLimits_Table <- combined_df %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "YES n (%)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Length limits" = 3, "Time limits" = 3, "Reference limits" = 3, "Peer review" = 1))

prominentLimits_Table

save_kable(prominentLimits_Table, here("analysis/prominentLimits_Table.png"))
```

# STUDY 2: PREVALENCE

## Prevalence in randomly selected journals

Look for linked PPC in articles in random sample
```{r}
d_articles %>%
  filter(sample_id == "random",
         ppc_linked == TRUE) %>%
  summarise(n = n())
```

Calculate CIs for linked PPC in articles in random sample
```{r}
# Linked PPCs
random_linked <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "random",
         ppc_linked == TRUE) %>%
  count()

ci_Rlinked <- binom.confint(random_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)

# Convert the lower and upper limits to percentages and round them to one decimal place
ci_randLinked_LL <- round(ci_Rlinked$lower*100, 1)
ci_randLinked_UL <- round(ci_Rlinked$upper*100, 1)

ci_randLinked_LL
ci_randLinked_UL
```

Look for instances of PPC in articles in random sample
```{r}
d_articles %>%
  filter(sample_id == "random",
         exclude_reason == "IS ITSELF PPC") %>%
  summarise(n = n())
```

Calculate CIs for Instance PPC in random sample
```{r}
# Instance PPCs
random_instance <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "random",
    exclude_reason == "IS ITSELF PPC") %>%
  count()

ci_Rinstance <- binom.confint(random_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)

# Convert the lower and upper limits to percentages and round them to one decimal place
ci_randInstance_LL <- round(ci_Rinstance$lower*100, 1)
ci_randIinstance_UL <- round(ci_Rinstance$upper*100, 1)

ci_randInstance_LL
ci_randIinstance_UL
```

## Prevalence in prominent journals

Look for links to PPC in articles published in prominent journals
```{r}
d_articles %>%
  filter(sample_id == "prominent",
         ppc_linked == TRUE) %>%
  summarise(n = n())
```

Calculate CIs for Linked PPC 
```{r}
sample_size_a <- 101

# Linked PPCs
prominent_linked <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "prominent",
         ppc_linked == TRUE) %>%
  count()

ci_linked <- binom.confint(prominent_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)

# Convert the lower and upper limits to percentages and round them to one decimal place
ci_promLinked_LL <- round(ci_linked$lower*100, 1)
ci_promLinked_UL <- round(ci_linked$upper*100, 1)

ci_promLinked_LL
ci_promLinked_UL
```

Look for instances of PPC in articles published in prominent journals
```{r}
d_articles %>%
  filter(sample_id == "prominent",
         exclude_reason == "IS ITSELF PPC") %>%
  summarise(n = n())
```

Calculate CIs for Instance PPC in prominent journals
```{r}
# Instance PPCs
prominent_instance <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "prominent",
    exclude_reason == "IS ITSELF PPC") %>%
  count()

ci_instance <- binom.confint(prominent_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)

# Convert the lower and upper limits to percentages and round them to one decimal place
ci_promInstance_LL <- round(ci_instance$lower*100, 1)
ci_promIinstance_UL <- round(ci_instance$upper*100, 1)

ci_promInstance_LL
ci_promIinstance_UL
```

\end

### 2024-11-02 analysis/Updated-ResultsAnalysis.Rmd
Updated results order
Ensured results reflects same order as manuscript

@@
 output:
+  html_document: default
   pdf_document: default
-  html_document: default
 ---
@@
 library(binom)
-library(ggplot2)
-library(RColorBrewer)
 library(assertthat)
@@
 ```
+
 Run assertion checks for both samples
@@
   )
-
 ```
@@
 ## Journal characteristics
-Descriptive statistics
+
+*Descriptive statistics*
+
+Calculate JIF median and IQR for random journals
+```{r}
+randomJIF <- dj_random %>% 
+  filter(ppc_type == "A") %>%
+  filter(!is.na(jif)) %>%
+  summarise(randMedian_jif = round(median(jif),2),
+            randMin_jif = round(min(jif),2),
+            randMax_jif = round(max(jif),2),
+            randIQR_jif = round(IQR(jif),2)
+  )
+
+randomJIF
+```
 
@@
 ```
-
-Calculate JIF median and IQR for random journals
-```{r}
-randomJIF <- dj_random %>% 
-  filter(ppc_type == "A") %>%
-  filter(!is.na(jif)) %>%
-  summarise(randMedian_jif = round(median(jif),2),
-            randMin_jif = round(min(jif),2),
-            randMax_jif = round(max(jif),2),
-            randIQR_jif = round(IQR(jif),2)
-  )
-
-randomJIF
+Count randomly selected journals listed as COPE members 
+```{r}
+randomCOPE <- dj_random %>%
+  filter(ppc_type == 'A') %>%
+  filter(cope == TRUE) %>%
+  summarise(count = n())
+
+randomCOPE
 ```
@@
 
-Count randomly selected journals listed as COPE members 
-```{r}
-randomCOPE <- dj_random %>%
+*Supplementary Information I: Descriptive statistics for both journal samples*
+
+Random journals Web Of Science categories
+```{r}
+randomCategory <- dj_random %>%
   filter(ppc_type == 'A') %>%
-  filter(cope == TRUE) %>%
-  summarise(count = n())
-
-randomCOPE
+  group_by(field) %>%
+  summarise(count = n()) %>%
+  ungroup()
+
+randomCategory
 ```
@@
 
-Random journals Web Of Science categories
-```{r}
-randomCategory <- dj_random %>%
-  filter(ppc_type == 'A') %>%
-  group_by(field) %>%
-  summarise(count = n()) %>%
-  ungroup()
-
-randomCategory
-```
-
 ## How many journals offer post-publication critique?
 
-RANDOMLY-SELECTED SAMPLE
+**RANDOMLY-SELECTED SAMPLE**
 
@@
 
-PROMINENT SAMPLE
+**PROMINENT SAMPLE**
 
@@
 
-Find the most restrictive limits of any journal
+Find the most restrictive length limit of any journal
 ```{r}
@@
 
+Find the most restrictive time limit of any journal
 ``` {r}
@@
 ```{r}
+# Specify sample size for articles (same for both samples)
+sample_size_a <- 101
+
 # Linked PPCs
@@
 ```{r}
-sample_size_a <- 101
-
 # Linked PPCs

### 2024-11-12 manuscript/manuscript_NHB.Rmd
Added via the Open Science Framework

@@
 ---
-title: "A Descriptive Analysis of How Psychology Journals Handle Post-Publication
-  Critiques"
-author: Whamond, A., Vazire, S., Clarke, B., Moodie, N., Schiavone, S., Thibault,
-  R. T., & Hardwicke, T. E.
+title: "How do psychology journals handle post-publication critique? A cross-sectional study of policy and practice."
+author: Whamond, A., Vazire, S., Clarke, B., Moodie, N., Schiavone, S., Thibault, R. T., & Hardwicke, T. E.
 date: "`r format(Sys.time(), '%d %B, %Y')`"
@@
   word_document: default
-abstract: "Fostering critical discussion is essential to upholding the ethos of science
-  as an unbiased, collaborative, and self-correcting endeavor. Journals can support
-  this by offering options for post-publication critique, such as commentaries or
-  letters, allowing peers to voice substantiated concerns of empirical articles. We
-  provide a descriptive, cross-sectional analysis of post-publication critique policies
-  and prevalence across samples of a) 100 prominent and b) 100 randomly-selected and psychology journals.
-  We found that 38% of prominent and 23% of randomly-selected psychology journals
-  offered explicit critique options. Length and time-to-submit
-  limits were often not stated. Critique prevalence was rare with only a single event
-  identified among two samples of 101 articles. Given the widespread recognition of
-  the replication crisis in psychology, allowing avenues for criticisms to be voiced
-  may help increase credibility within the field. To support transparency and
-  self-correction, psychology journals should offer clearly stated post-publication
-  critique options and encourage their use.\n"
-keywords: "post-publication critique, peer review, psychology, meta-research, journal
-  policy, self-correction, scientific criticism"
+abstract: "Post-publication critique, such as letters-to-the-editor, can contribute
+  to the validity and trustworthiness of scientific research. We conducted a cross-sectional
+  and (b) prominent psychology journals. In 2023, an explicit submission option for
+  post-publication critique was available at 23% (95% CI [16% to 32%]) of randomly
+  sampled psychology journals (N = 100) and 38% of the most prominent psychology journals
+  (N = 100). Journals sometimes imposed limits on the length and time allowed to submit
+  critiques. We manually inspected two random samples of empirical articles published
+  in 2020 (N = 101 articles per sample), estimating the prevalence of post-publication
+  critique to be 0% (95% CI [0% to 3.7%]) in psychology journals generally and 1%
+  (95% CI [0.2% to 5.4%]) in the most prominent psychology journals. The policy and
+  practice of post-publication critique is seriously neglected in psychology journals.\n"
+keywords: "post-publication critique, meta-research, journal policy, self-correction,
+  peer review"
 bibliography: references.bib
 link-citations: true
-csl: nature.csl
-floatsintext: false
-figurelist: false
-tablelist: false
-footnotelist: false
-linenumbers: true
-mask: true
-draft: true
+csl: "CSL-apa.csl"
 always_allow_html: true
 urlcolor: blue
+header-includes:
+- \usepackage{float}
+- \usepackage{pdflscape}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
 ---
 
-```{r setup, include = FALSE}
-library(papaja) # article template
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+```
+
+```{r}
+#library(papaja) # article template
 library(tidyverse)
-library(ggplot2) # figure creation
-library(ggrepel) # for ggplot text labels
-library(patchwork) # for multipanel plot layouts
-library(RColorBrewer) # data visualisation
 library(dplyr)
@@
 library(knitr) # for literate programming
-library(janitor) # for data munging
 library(tidylog) # for inline code feedback
@@
 
-```{r echo=FALSE, message=FALSE}
+```{r}
 # Load processed data files
@@
 
-```{r echo=FALSE, message=FALSE}
+```{r}
+# Custom function to convert text to sentence case
+sentence_case <- function(x) {
+  s <- tolower(x)
+  substr(s, 1, 1) <- toupper(substr(s, 1, 1))
+  s
+}
+```
+
+```{r}
 # Create separate tibbles for Prominent and Randomly-selected journal samples
@@
 
-# Main
-*Add 'Introduction' section*
-
-# Results
-
-## Part 1: Post-Publication Critique Policies
-
-For descriptive statistics on journal subdisciplines, post-publication critique acceptance, and COPE membership for both prominent and randomly-selected samples, see Supplementary Information ##.
-A full list of the journals included in this study, along with their post-publication critique options and restrictions, is provided in Supplementary Information ##.
-
-## Prominent Psychology Journals
-
-```{r prominent journal-characteristics, echo=FALSE, message=FALSE}
-
-# Ascertain prominent journal JIF characteristics
-
-promJournalCharacteristics <- dj_prominent %>% 
+\newpage
+
+# Research transparency statement
+
+**Conflicts of interest:** All authors declare no conflicts of interest.
+**Funding:** This research was supported by Australian Research Council grant FT210100652.
+**Artificial intelligence:** No artificial intelligence assisted technologies were used in this research or the creation of this article.
+**Ethics:** Not applicable.
+**Preregistration:** The study protocol (aims, methods, and analyses) was preregistered [(https://osf.io/d6xf2)](https://osf.io/d6xf2) on April 19th 2023, prior to data collection which began on May 10th 2023.
+There were no major deviations from the preregistered protocol; minor deviations are reported in Supplementary Table A1.
+**Materials:** All study materials are publicly available [(https://osf.io/8k7m4/)](https://osf.io/8k7m4/).
+**Data:** All primary data are publicly available [(https://osf.io/8k7m4/)](https://osf.io/8k7m4/).
+**Analysis scripts:** All analysis scripts are publicly available [(https://osf.io/8k7m4/)](https://osf.io/8k7m4/).
+**Computational reproducibility:** The analysis code is available in a Code Ocean container [(https://codeocean.com/capsule/4794801/tree)](https://codeocean.com/capsule/4794801/tree) which re-creates the software environment in which the original analyses were performed.
+
+# Introduction
+
+Critical discourse can contribute to the validity and trustworthiness of scientific research [@robertk.merton1973; @vazire2022].
+Criticism can highlight errors, limitations, and alternative interpretations, helping research consumers to calibrate their beliefs in scientific claims.
+However, the proliferation of poor-quality research in psychology (and other fields) indicates that the dominant mode of critical discourse, conventional peer review, is not sufficient to maintain high standards in the scientific literature [@hardwicke2020; @nosek2022].
+
+Scientific journals can support the ongoing critical scrutiny of research by offering avenues for post-publication critique, such as letters to the editor [@altman2002].
+Journals’ obligation to facilitate post-publication critique is explicitly codified in the principles of the Committee on Publication Ethics (COPE), an organisation that most prominent journals are members of [@committeeonpublicationethics2021; @hardwicke2022].
+However, prior research indicates that many (37%) of the most prominent academic journals across a broad range of scientific disciplines do not explicitly allow submissions of post-publication critique [@hardwicke2022].
+Moreover, journals that do allow post-publication critiques in principle rarely publish them in practice, and often impose restrictive limits on length and time-to-submit.
+The present research closely follows the methods used in @hardwicke2022 but extends this prior work by providing a focused evaluation of how psychology journals in particular handle post-publication critique (Hardwicke et al.
+examined 15 journals in a combined psychiatry and psychology category, along with 315 journals from other disciplines).
+
+For the purposes of the present study, we operationally defined post-publication critique as any journal-based avenue for sharing peer-initiated critical discourse related to specific research articles previously published in the same journal (see Supplementary Information B for a complete operational definition).
+A prototypical example of post-publication critique is a letter to the editor, though there are other variations, such as commentary articles and website comments.
+
+Our study was conducted in two parts.
+The first part aimed to describe policies related to post-publication critique at: (a) all psychology journals publishing empirical research (via a random sample of 100 journals), and (b) the 100 most prominent^[There is no agreed upon or objective measure of journal prominence.
+To avoid an entirely subjective and arbitrary definition, we used Journal Impact Factor as a proxy for journal prominence.
+Journal Impact Factor, like all journal metrics, has limitations (especially when used as a proxy for quality, which is not what we are doing here), but using this method yields a collection of journals that we believe has good face validity in terms of prominence.] psychology journals publishing empirical research.
+Specifically, we identified whether options for submitting critiques (e.g., letters to the editor) are available, and whether limits are imposed in terms of length, time-to-submit since publication of the target article, number of references, and whether critiques were sent for independent peer review.
+The second part of our study aimed to estimate the prevalence of post-publication critiques published in: (a) all psychology journals (via a random sample of 100 empirical psychology articles), and (b) the 100 most prominent psychology journals (via a random sample of 100 empirical articles published in these journals).
+
+# Part One: Post-Publication Critique Policies
+
+## Method
+
+The methods and analysis plan were preregistered [(https://osf.io/d6xf2)](https://osf.io/d6xf2).
+All deviations from the preregistered protocol were considered minor and are detailed in Supplementary Information A and, where relevant, mentioned below.
+
+### Design
+
+This investigation had a cross-sectional design.
+All measured variables are described in detail in Supplementary Table C1.
+In brief, we extracted and described journal policies related to post-publication critique (according to our operational definition, Supplementary Information B) provided on journal websites in 2023.
+We recorded the name and description of any options for post-publication critique offered by each journal (e.g., article types such as ‘letters’ or ‘commentaries’, or web comments) or any explicit statement that the journal does not accept post-publication critique; limits imposed on post-publication critique in terms of length (e.g., number of words), time-to-submit (e.g., weeks since publication of the target article) and/ or number of references; and whether it was stated that post-publication critiques would be sent for independent external peer review (i.e., reviews solicited from individuals who were not members of the editorial team or authors of the target article).
+We recorded qualitative as well as quantitative limits; for example, a length limit might be stated as “500 words” or “short”.
+We also identified whether journals were members of COPE, an organisation which outlines several core publishing practices, including the importance of facilitating post-publication critique [@committeeonpublicationethics2021].
+
+### Sample
+
+*Target populations*
+
+The target populations of the two samples of journals were: (a) all psychology journals publishing empirical research in 2023; and (b) prominent journals in psychology publishing empirical research in 2023.
+We were only interested in legitimate (non-predatory), peer-reviewed journals.
+
+*Sample sizes*
+
+The sample consisted of 100 randomly selected journals and 100 prominent journals.
+Justification for these sample sizes was based on a precision analysis (details provided in Supplementary Information E).
+Eleven journals appeared in both samples and were not replaced in order to maintain the random sampling scheme.
+
+*Preparing samples (inclusion/exclusion criteria)*
+
+We only included journals that were in the Web of Science Core Collection, meaning they met 24 basic quality criteria, such as having a peer-review policy and publishing scholarly content (for details see https://perma.cc/C5J3-V7C4).
+As of 15th March 2023, there were 867 unique journals included in this database that were classified as belonging to a subject category related to ‘psychology’.
+Of these 867 journals, 115 were classified by Web of Science as non-English language and excluded, leaving 752 journals remaining.
+For the random sample of psychology journals, a list of all included 752 psychology journals was randomly shuffled using the R function ‘sample’ and we selected the first 600 on the shuffled list (to allow for exclusions).
+For the prominent journals sample, we sorted journals in order of their 2021 Clarivate Journal Impact Factors (https://jcr.clarivate.com/) and selected the first 600 journals (to allow for exclusions).
+The list of these journals is available at https://osf.io/k6yx5.
+For both samples, journals were then evaluated sequentially from the top of their respective list until the target of 100 eligible journals in each sample was reached.
+If a journal needed to be excluded after manual inspection, it was replaced with the next available journal in its list, thus maintaining the respective sampling schemes.
+We excluded an additional 6 journals from the randomly-selected journal list and 15 from the prominent list because they did not publish empirical research.
+This determination involved some degree of subjective judgement and was primarily based on each journal’s scope as defined on its website.
+If the journal’s description of its scope was ambiguous, we searched the journal's archive for examples of empirical articles to inform our determination.
+This represented a slight deviation from the preregistered protocol (for details see Supplementary Information A).
+
+### Procedure
+
+*Piloting and training*
+
+The data extraction procedures were piloted with 10  journals that were not included in the sample.
+All investigators were trained and familiarised with the data extraction process and practised with positive and negative training examples.
+
+*Collating journal policy information*
+
+One investigator (AW or NM) identified, downloaded, and archived the ‘scope’ and ‘article types’ sections (or equivalent) provided on each journal’s website [(https://osf.io/8k7m4/)](https://osf.io/8k7m4/).
+This information was used to determine whether the journal published empirical articles and, if so, whether post-publication critique article types were accepted by the journal.
+If these sections could not be found, a second investigator (TEH) double-checked.
+
+*Data extraction*
+
+The policy information (outlined in Supplementary Information C using a Goole Form [(https://osf.io/d6uzj)](https://osf.io/d6uzj) was extracted and classified for each journal by two investigators.
+Primary coding was conducted by AW (n = 183) and NM (n = 37).
+Secondary coding was conducted by RTT (n = 82), SV (n = 80), and TEH (n = 41).
+Disagreements between primary and secondary coders, usually arising due to unclear descriptions of article types, were resolved by TEH.
+This was necessary for 40 journals (for details see Supplementary Information H).
+For coding whether journals provided an option for post-publication critique, we first examined the journal website’s description of the journal’s article types (typically found in journals’ submission guidelines or instructions to authors).
+If a journal’s description of its article types was not provided or unclear, we searched the journal's archive to see if any examples of articles meeting our operational definition of post-publication critique (Supplementary Information B) had been published within the last five years (i.e., since the beginning of 2019).
+Note that if a journal had an article type that sounded like it might be used for post-publication critique (e.g., "Commentary"), that was not sufficient for a positive classification; the description of the article type, or examples of that article type, also had to meet our operational definition of post-publication critique (see Supplementary Information B).
+
+*Data harmonization*
+
+Journals used various naming conventions for similar types of post-publication critique and various units (e.g., characters, words or pages for length limits) to specify limits.
+To address this, we harmonised the various names used for critique formats to four types (letters [to the editor], commentaries, web comments, and other) and transformed length limit units to words and time-to-submit limit units to weeks (for details see Supplementary Information G).
+
+## Results
+
+### Journal characteristics
+
+```{r}
+# Calculate JIF median and IQR for random journals
+randomJIF <- dj_random %>% 
+  filter(ppc_type == "A") %>%
+  filter(!is.na(jif)) %>%
+  summarise(Median = round(median(jif),2),
+            Q1 = round(quantile(jif, .25),2),
+            Q3 = round(quantile(jif, .75),2),
+            IQR = round(IQR(jif),2)
+  )
+```
+
+```{r}
+# Calculate JIF median and IQR for prominent journals
+prominentJIF <- dj_prominent %>% 
   filter(ppc_type == "A") %>%      # Keep only single entry for each journal
-  summarise(promMedian_jif = round(median(jif),2), 
-            promMin_jif = round(min(jif),2),
-            promMax_jif = round(max(jif),2),
-            promIQR_jif = round(IQR(jif),2)
-  )
-
-```
-
-In our sample of 100 prominent journals, the median 2021 Journal Impact Factor was `r promJournalCharacteristics %>% pull(promMedian_jif)` (IQR = `r promJournalCharacteristics %>% pull(promIQR_jif)`, range = `r promJournalCharacteristics %>% pull(promMin_jif)` - `r promJournalCharacteristics %>% pull(promMax_jif)`).
-As this represents the entire population of interest for this section of the study, confidence intervals (CIs) are not included for this section of the study.
-Figure *XX* shows the observed journal policies and, of the explicitly offered critique options identified, how restrictions on length and time-to-submit were stated.
-
-### *Post-Publication Critique Policy and Restriction Statements in Prominent Psychology Journals*
-
-```{r, echo = FALSE, message=FALSE}
-# Filter and transform restrictions for ppc_length
-prominent_length_data <- dj_prominent %>%
-  filter(!is.na(ppc_name)) %>%
-  filter(has_ppc != "ARCHIVE") %>% # removes 'Archive Only' PPC types
-  mutate(ppc_length = case_when(
-    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
-    ppc_length == "NOT STATED" ~ "Not Stated",
-    TRUE ~ 'Qualitative' # Summarises all length limits as 'Quantitative', 'Qualitative', or 'Not Stated'
-  )) %>% 
-  group_by(ppc_length) %>%
+  summarise(Median = round(median(jif),2), 
+            Q1 = round(quantile(jif, .25),2),
+            Q3 = round(quantile(jif, .75),2),
+            IQR = round(IQR(jif),2)
+  )
+```
+
+```{r}
+# Count randomly selected journals listed as COPE members
+randomCOPE <- dj_random %>%
+  filter(ppc_type == 'A') %>%
+  filter(cope == TRUE) %>%
   summarise(count = n())
-
-# Filter and transform restrictions for ppc_time
-prominent_time_data <- dj_prominent %>%
-  filter(!is.na(ppc_name)) %>%
-  filter(has_ppc != "ARCHIVE") %>% # removes 'Archive Only' PPC types
-  mutate(ppc_time = case_when(
-    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
-    ppc_time == "NOT STATED" ~ "Not Stated",
-    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
-  )) %>%
-  group_by(ppc_time) %>%
+```
+
+```{r}
+# Count prominent journals listed as COPE members 
+prominentCOPE <- dj_prominent %>%
+  filter(ppc_type == 'A') %>%
+  filter(cope == TRUE) %>%
   summarise(count = n())
-
-# Combine the data and unite the columns
-combined_data <- bind_rows(
-  prominent_length_data %>% mutate(Code = "Length"),
-  prominent_time_data %>% mutate(Code = "Time-to-submit")
-) %>%
-unite(limits, ppc_length, ppc_time) %>%
-  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
-                   limits == "Qualitative_NA" ~ "Qualitative",
-                   limits == "Quantitative_NA" ~ "Quantitative",
-                   limits == "NA_Not Stated" ~ "Not Stated",
-                   limits == "NA_Qualitative" ~ "Qualitative",
-                   limits == "NA_Quantitative" ~ "Quantitative",
-                   TRUE ~ as.character(limits)
-                   ))
-
-# Create the first graph
-graph1 <- ggplot(combined_data, aes(x = Code, y = count, fill = limits)) +
-  geom_bar(stat = "identity", 
-           position = "stack",
-           colour = "black") +
-  theme_bw() +
-  scale_fill_brewer(palette = "Blues") +
-  labs(x = "Restriction Type", y = "Count", fill = "Restrictions") +
-  theme(axis.text.x = element_text(size = 7))
-
-# Create the second graph
-graph2 <- dj_prominent %>%
-  filter(ppc_type == "A") %>% # Keeps only first entry for each journal
-  filter(!is.na(has_ppc)) %>% # Remove journal rows with no (NA) PPC options 
-  mutate(has_ppc = case_when(
-    has_ppc == 'ARCHIVE' ~ 'Yes Implicit',
-    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
-    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
-    has_ppc == 'YES' ~ 'Yes Explicit',
-    TRUE ~ has_ppc
-  )) %>%
+```
+
+The median 2021 Journal Impact Factor was `r randomJIF$randMedian_jif` (interquartile range = `r randomJIF$Q1` - `r randomJIF$Q3`) for the randomly sampled journals (NB.
+25 of the randomly selected journals did not have Journal Impact Factors) and `r prominentJIF$Median` (interquartile range = `r prominentJIF$Q1` - `r prominentJIF$Q3`) for the prominent journals.
+`r randomCOPE` of the `r dj_random %>% filter(ppc_type == 'A') %>% nrow()` randomly sampled journals, and `r prominentCOPE` of the `r dj_prominent %>% filter(ppc_type == 'A') %>% nrow()` prominent journals, were members of COPE.
+Journal characteristics stratified by psychology sub-field are available in Supplementary Information I.
+
+### How many journals offer post-publication critique?
+
+```{r}
+# Inspect how frequently PPC policies were stated for randomly selected journals 
+randomPPC <- dj_random %>%
+  filter(ppc_type == 'A') %>%
   group_by(has_ppc) %>%
   summarise(count = n()) %>%
-  mutate(percentage = count / sum(count) * 100) %>%
-  ggplot(aes(x = "", y = count, fill = has_ppc)) +
-  geom_bar(stat = "identity",
-           colour = "black",
-           width = 0.8) +
-  theme_bw() +
-  scale_fill_brewer(palette = "YlOrRd", direction = -1) +
-  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")
-
-# Arrange both graphs in the same figure
-combined_plots <- graph2 + graph1
-combined_plots
-
-ggsave("ProminentJournalPolicies.png", plot = last_plot(), device = "png")
-```
-
-*Note.* PPC = post-publication critique.
-Orange bar (left) indicates policy statements for each journal included in sample (n = 100).
-Blue bars (right) indicate how length and time-to-submit restrictions were stated in cases where journals had explicit post-publication critique policies in place (n = 41).
-Implicit acceptance denoted by archival examples of critiques despite absence of stated policy.
-
-```{r echo=FALSE, message=FALSE}
-# Length restriction statement types of explicit PPC types (prominent sample)
-
-# Calculate the count and percentage for "Quantitative"
-prom_quantitative_length <- prominent_length_data %>%
- filter(ppc_length == "Quantitative") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(prominent_length_data$count) * 100)
-
-# Calculate the count and percentage for "Qualitative"
-prom_qualitative_length <- prominent_length_data %>%
- filter(ppc_length == "Qualitative") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(prominent_length_data$count) * 100)
-
-# Calculate the count and percentage for "Not Stated"
-prom_notStated_length <- prominent_length_data %>%
- filter(ppc_length == "Not Stated") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(prominent_length_data$count) * 100)
-
-# Range
-prom_length_range <- dj_prominent %>%
-  filter(!is.na(ppc_length)) %>%
-  filter(ppc_length != "Qualitative") %>%
-  filter(ppc_length != "NOT STATED") %>%
-  mutate(ppc_length = as.numeric(ppc_length)) %>%
-  summarise(prom_median_length = median(ppc_length),
-            prom_min_length = min(ppc_length),
-            prom_max_length = max(ppc_length)
-            )
-
-# Time-to-submit restriction statement types of explicit PPC types (prominent sample)
-
-# Calculate the count and percentage for "Quantitative"
-prom_quantitative_time <- prominent_time_data %>%
- filter(ppc_time == "Quantitative") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(prominent_time_data$count) * 100)
-
-# Calculate the count and percentage for "Qualitative"
-prom_qualitative_time <- prominent_time_data %>%
- filter(ppc_time == "Qualitative") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(prominent_time_data$count) * 100)
-
-# Calculate the count and percentage for "Not Stated"
-prom_notStated_time <- prominent_time_data %>%
- filter(ppc_time == "Not Stated") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(prominent_time_data$count) * 100)
-
-# Range
-prom_time_range <- dj_prominent %>%
-  filter(!is.na(ppc_time)) %>%
-  filter(ppc_time != "Qualitative") %>%
-  filter(ppc_time != "NOT STATED") %>%
-  mutate(ppc_time = as.numeric(ppc_time)) %>%
-  summarise(prom_median_time = median(ppc_time),
-            prom_min_time = min(ppc_time),
-            prom_max_time = max(ppc_time)
-            )
-
-# Reference restriction statement types of explicit PPC types (prominent sample)
-prominent_ref_data <- dj_prominent %>%
-  filter(!is.na(ppc_name)) %>% # keep only entries that identify PPC option
-  filter(has_ppc != "ARCHIVE") %>% # remove implicit yes examples
-  mutate(ppc_ref = case_when(
-    ppc_ref %in% c(10, 15, 20, 5) ~ 'Quantitative',
-    ppc_ref == "NOT STATED" ~ "Not Stated",
-    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
-  )) %>%
-  group_by(ppc_ref) %>%
-  summarise(count = n()) %>%
-  ungroup()
-
-# Calculate the count and percentage for "Quantitative"
-prom_quantitative_ref <- prominent_ref_data %>%
- filter(ppc_ref == "Quantitative") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(prominent_ref_data$count) * 100)
-
-# Calculate the count and percentage for "Not Stated"
-prom_notStated_ref <- prominent_ref_data %>%
- filter(ppc_ref == "Not Stated") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(prominent_ref_data$count) * 100)
-
-# Range
-prom_ref_range <- dj_prominent %>%
-  filter(!is.na(ppc_ref)) %>%
-  filter(ppc_ref != "Qualitative") %>%
-  filter(ppc_ref != "NOT STATED") %>%
-  mutate(ppc_ref = as.numeric(ppc_ref)) %>%
-  summarise(prom_median_ref = median(ppc_ref),
-            prom_min_ref = min(ppc_ref),
-            prom_max_ref = max(ppc_ref)
-            )
-
-# Peer-review statements of explicit PPC types (prominent sample)
-prominent_review_data <- dj_prominent %>%
-  filter(!is.na(ppc_review)) %>% # keep only entries that identify PPC option
-  filter(has_ppc != "ARCHIVE") %>% # remove implicit yes examples
-  mutate(ppc_review = case_when(
-    ppc_review == 'YES' ~ 'Yes',
-    ppc_review == 'NO' ~ 'No',
-    ppc_review == "NOT STATED" ~ "Not Stated")
+  ungroup()
+```
+
+```{r}
+# Calculate confidence interval for explicitly stated PPC policies among randomly selected journals
+randomPPCyes <- dj_random %>%
+  filter(ppc_type == 'A', !is.na(ppc_name)) %>%
+  summarise(count = n())
+
+randomPPCno <- dj_random %>%
+  filter(ppc_type == 'A', is.na(ppc_name)) %>%
+  summarise(count = n())
+
+# Sepcify sample size and confidence interval of 95%
+sample_size <- 100
+confidence_level <- 0.95
+
+# CIs for 'Yes Explicit'
+randomPPC_CI <- binom.confint(randomPPCyes, sample_size, method = "wilson", conf.level = confidence_level)
+
+# CIs for 'No' (both explicit and Implicit)
+randomPPC_CI_neg <- binom.confint(randomPPCno, sample_size, method = "wilson", conf.level = confidence_level)
+```
+
+```{r}
+# Return all rows with ppc_name values for ppc_type B and C indicating > 1 PPC type
+random_multiPPC <- dj_random %>%
+  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) 
+```
+
+```{r}
+# Inspect the COPE status of randomly selected journals with and without PPC policies
+randomCOPE <- dj_random %>%
+ filter(ppc_type == "A") %>%
+ mutate(has_ppc = case_when(
+    has_ppc == "NO EXPLICIT" ~ "NO",
+    has_ppc == "NO IMPLICIT" ~ "NO",
+    TRUE ~ has_ppc
+ )) %>%
+ group_by(has_ppc) %>%
+ summarise(
+    total_count = n(),
+    COPE_count = sum(cope == TRUE)
  ) %>%
-  group_by(ppc_review) %>%
-  summarise(count = n()) %>%
-  ungroup()
-
-# Calculate the count and percentage for "Yes"
-prom_yes_review <- prominent_review_data %>%
- filter(ppc_review == "Yes") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(prominent_review_data$count) * 100)
-
-# Calculate the count and percentage for "No"
-prom_no_review <- prominent_review_data %>%
- filter(ppc_review == "No") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(prominent_review_data$count) * 100)
-
-# Calculate the count and percentage for "Not Stated"
-prom_notStated_review <- prominent_review_data %>%
- filter(ppc_review == "Not Stated") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(prominent_review_data$count) * 100)
-
-# Calculate the count and percentage for 2 types
-prominent2types <- dj_prominent %>%
-  filter(ppc_type == "B") %>%
-  filter(!is.na(ppc_name)) %>%
-  count()
-
-```
-
-As shown in Figure *XX*, post-publication critique policies were explicitly stated by `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "YES") / n() * 100, "%"))` of journals, and we inferred that they were implicitly accepted (as denoted by archival examples) in `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "ARCHIVE") / n() * 100, "%"))` of journals.
-`r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO IMPLICIT") / n() * 100, "%"))` had no advertised post-publication critique policy, and `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO EXPLICIT") / n() * 100, "%"))` of journals explicitly stated that they did not accept critiques (*Clinical Psychology: Science and Practice and Psychological Bulletin*).
-`r paste0(prominent2types, "%")` of journals accepted two types (commentaries and letters); *International Journal of Mental Health and Addiction*, *Journal of Environmental Psychology*, and *Psychological Science*.
-
-Among the 41 explicitly stated post-publication critique options, restrictions on length were quantitatively stated (e.g., '1,000 words') in `r paste(prom_quantitative_length$count, "(", round(prom_quantitative_length$percentage), "%)", sep = "")` cases, qualitatively stated (e.g.
-'brief') in  `r paste(prom_qualitative_length$count, "(", round(prom_qualitative_length$percentage), "%)", sep = "")` cases, and not stated in `r paste(prom_notStated_length$count, "(", round(prom_notStated_length$percentage), "%)", sep = "")` cases.
-Time-to-submit was quantitatively stated (e.g., '4 weeks') in `r paste(prom_quantitative_time$count, "(", round(prom_quantitative_time$percentage), "%)", sep = "")` cases, qualitatively stated (e.g., 'timely') in `r paste(prom_qualitative_time$count, "(", round(prom_qualitative_time$percentage), "%)", sep = "")` cases, and not stated in `r paste(prom_notStated_time$count, "(", round(prom_notStated_time$percentage), "%)", sep = "")` cases.
-Number of references allowed was quantitatively stated (e.g., 'max 20') in `r paste(prom_quantitative_ref$count, "(", round(prom_quantitative_ref$percentage), "%)", sep = "")` cases and not stated in `r paste(prom_notStated_ref$count, "(", round(prom_notStated_ref$percentage), "%)", sep = "")`.
-Whether critiques were sent for external peer-review was only stated in `r paste((prom_yes_review$count + prom_no_review$count), "(", round(prom_yes_review$percentage + prom_no_review$percentage), "%)", sep = "")` cases, in `r paste(prom_yes_review$count, "(", round(prom_yes_review$percentage), "%)", sep = "")` cases this was in the affirmative.
-
-When stated quantitatively, length limits ranged from `r prom_length_range %>% pull(prom_min_length)` - `r prom_length_range %>% pull(prom_max_length)` words, time-to-submit limits ranged from `r prom_time_range %>% pull(prom_min_time)` - `r prom_time_range %>% pull(prom_max_time)` weeks, reference limits ranged between `r prom_ref_range %>% pull(prom_min_ref)` -`r prom_ref_range %>% pull(prom_max_ref)`.
-Table *XX* shows descriptive statistics for stated quantitative restrictions, broken down by critique type.
-
-### Table *XX*
-[*Insert table of results*]
-
-As expected, results in Table 1 show that commentaries were generally less restrictive on length with the median word limit being 2.5 times that of letters.
-The median number of references allowed was 1.5 times greater in commentaries compared to letters.
-Commentaries were also 3.3 times more likely to be sent for peer-review.
-Interestingly, time-to-submit was less restrictive for letters than commentaries, however, this was only reported in two and four cases (respectively) so limited inferences can be made from this.
-
-```{r COPE status in prominent sample, echo=FALSE, message=FALSE}
-# COPE membership status among prominent journals accepting PPC
-prominent_PPCy <- dj_prominent %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>% # keep only journals that accept PPC
-  summarise(count = n()) # total number journals accepting PPC
-
-prom_copeY_PPC <- dj_prominent %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>%
-  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
-  summarise(count = n()) # number of COPE journals accepting PPC
-
-prom_copeN_PPC <- dj_prominent %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>%
-  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
-  summarise(count = n()) # number of non-COPE journals accepting PPC
-
-# COPE membership status among prominent journals NOT accepting PPC
-prominent_PPCn <- dj_prominent %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>% # keep only journals that accept PPC
-  summarise(count = n()) # total number journals accepting PPC
-
-prom_copeY_PPCn <- dj_prominent %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
-  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
-  summarise(count = n()) # number of COPE journals accepting PPC
-
-prom_copeN_PPCn <- dj_prominent %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
-  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
-  summarise(count = n()) # number of non-COPE journals accepting PPC
-
-```
-
-Of the `r paste(prominent_PPCy$count)` journals that accepted post-publication critiques (including the six implicitly implied through archive examples), `r paste(prom_copeY_PPC$count, "(", round((prom_copeY_PPC$count / prominent_PPCy$count) * 100, 1), "%)", sep = "")` were COPE members and `r paste(as.english(prom_copeN_PPC$count), " (", round((prom_copeN_PPC$count / prominent_PPCy$count) * 100, 1), "%)", sep = "")` were not.
-Of the `r paste(prominent_PPCn$count)` journals that had no critique policy, `r paste(prom_copeY_PPCn$count, "(", round((prom_copeY_PPCn$count / prominent_PPCn$count) * 100, 1), "%)", sep = "")` were COPE members, including both of those with explicit statements that they do not accept unsolicited critiques.
-
-## Randomly-selected Psychology Journals
-```{r randomly-selected journal-characteristics, echo=FALSE, message=FALSE}
-
-# Ascertain randonly-selected journal JIF characteristics
-
-randJournalCharacteristics <- dj_random %>% 
-  filter(ppc_type == "A") %>%
-  filter(!is.na(jif)) %>%
-  summarise(randMedian_jif = round(median(jif),2),
-            randMin_jif = round(min(jif),2),
-            randMax_jif = round(max(jif),2),
-            randIQR_jif = round(IQR(jif),2)
-  )
-
-```
-Among our sample of 100 randomly-selected psychology journals, Journal Impact Factor data was unavailable for 25 journals.
-Median 2021 Journal Impact Factor was `r randJournalCharacteristics %>% pull(randMedian_jif)` (IQR = `r randJournalCharacteristics %>% pull(randIQR_jif)`, range = `r randJournalCharacteristics %>% pull(randMin_jif)` - `r randJournalCharacteristics %>% pull(randMax_jif)`).
-Figure *XX* shows the observed journal policies and, of the explicitly offered critique options identified, how restrictions on length and time-to-submit were stated.
-
-### Figure *XX*: *Post-Publication Critique Policy and Restriction Statements in Randomly-selected Psychology Journals*
-```{r echo=FALSE, message=FALSE}
-# Create and combine restriction statement graphs with PPC acceptance (random sample)
-
-# Filter and process data for ppc_length
-random_length_data <- d_journals %>%
-  filter(sample_id %in% c("random", "both")) %>%
-  filter(!is.na(ppc_name)) %>%
-  filter(has_ppc != "ARCHIVE") %>%
-  mutate(ppc_length = case_when(
-    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
-    ppc_length == "NOT STATED" ~ "Not Stated",
-    TRUE ~ 'Qualitative'
-  )) %>%
-  group_by(ppc_length) %>%
-  summarise(count = n())
-
-# Filter and process data for ppc_time
-random_time_data <- d_journals %>%
-  filter(sample_id %in% c("random", "both")) %>%
-  filter(!is.na(ppc_name)) %>%
-  filter(has_ppc != "ARCHIVE") %>%
-  mutate(ppc_time = case_when(
-    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
-    ppc_time == "NOT STATED" ~ "Not Stated",
-    TRUE ~ 'Qualitative'
-  )) %>%
-  group_by(ppc_time) %>%
-  summarise(count = n())
-
-# Combine the data and unite the columns
-combined_data_random <- bind_rows(
-  random_length_data %>% mutate(Code = "Length"),
-  random_time_data %>% mutate(Code = "Time-to-submit")
-) %>%
-unite(limits, ppc_length, ppc_time) %>%
-  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
-                   limits == "Qualitative_NA" ~ "Qualitative",
-                   limits == "Quantitative_NA" ~ "Quantitative",
-                   limits == "NA_Not Stated" ~ "Not Stated",
-                   limits == "NA_Qualitative" ~ "Qualitative",
-                   limits == "NA_Quantitative" ~ "Quantitative",
-                   TRUE ~ as.character(limits)
-                   ))
-
-# Create the first graph
-graph4 <- ggplot(combined_data_random, aes(x = Code, y = count, fill = limits)) +
-  geom_bar(stat = "identity", 
-           position = "stack",
-           colour = "black") +
-  theme_bw() +
-  scale_fill_brewer(palette = "Blues") +
-  labs(x = "Restriction Type", y = "Count", fill = "Restrictions") +
-  theme(axis.text.x = element_text(size = 7))
-
-# Create the second graph
-graph3 <- d_journals %>%
-  filter(sample_id == "random" | sample_id == "both") %>%
-  filter(ppc_type == "A") %>%
-  filter(!is.na(has_ppc)) %>%
-  mutate(has_ppc = case_when(
-    has_ppc == 'ARCHIVE' ~ 'Yes Implicit',
-    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
-    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
-    has_ppc == 'YES' ~ 'Yes Explicit',
-    TRUE ~ has_ppc
-  )) %>%
+ mutate(COPEpercent = round((COPE_count / total_count) * 100)) %>%
+ ungroup()
+```
+
+A full list of journals and their post-publication critique options and limits is provided in Supplementary Information J (raw data available at [https://osf.io/8k7m4/](https://osf.io/8k7m4/)).
+Among the 100 randomly-selected journals, `r randomPPC$count[randomPPC$has_ppc == "YES"]` (`r randomPPC$count[randomPPC$has_ppc == "YES"]`%, 95% CI [`r round(randomPPC_CI[1,5]*100)`%, `r round(randomPPC_CI[1,6]*100)`%]) explicitly stated that they allowed submissions of post-publication critique.
+Of these `r randomPPC$count[randomPPC$has_ppc == "YES"]` journals, `r print(as.character(english(nrow(random_multiPPC))))` had two types of critique formats and the other `r (randomPPC$count[randomPPC$has_ppc == "YES"] - nrow(random_multiPPC))` each had one critique format.
+`r print(as.character(english(randomPPC$count[randomPPC$has_ppc == "NO EXPLICIT"])))` journal (*Clinical Psychology: Science and Practice*, also included in the prominent journals sample) stated explicitly that they did not accept post-publication critique.
+`r dj_random %>% filter(ppc_name == "Commentary") %>% nrow()` journals offered commentaries, `r dj_random %>% filter(ppc_name == "Letters") %>% nrow()` journals offered letters, `r dj_random %>% filter(ppc_name == "Web comments") %>% nrow()` journals offered web comments, and `r print(as.character(english(nrow(dj_random %>% filter(ppc_name == "Other")))))` journal (*Cortex*) offered a format called 'verification reports' which we classified as ‘other’.
+Of the `r randomPPC$count[randomPPC$has_ppc == "YES"]` journals that explicitly accepted post-publication critique, `r randomCOPE$COPE_count[randomCOPE$has_ppc == "YES"]` (`r randomCOPE$COPEpercent[randomCOPE$has_ppc == "YES"]`%) were COPE members.
+Of the `r randomCOPE$COPE_count[randomCOPE$has_ppc == "NO"]` journals that did not have a policy related to post-publication critique, `r randomCOPE$COPE_count[randomCOPE$has_ppc == "NO"]` (`r randomCOPE$COPEpercent[randomCOPE$has_ppc == "NO"]`%) were COPE members.
+
+```{r}
+# Inspect how frequently PPC policies were stated for prominent journals 
+prominentPPC <- dj_prominent %>%
+  filter(ppc_type == 'A') %>%
   group_by(has_ppc) %>%
   summarise(count = n()) %>%
-  mutate(percentage = count / sum(count) * 100) %>%
-  ggplot(aes(x = "", y = count, fill = has_ppc)) +
-  geom_bar(stat = "identity",
-           colour = "black",
-           width = 0.8) +
-  theme_bw() +
-  scale_fill_brewer(palette = "YlOrRd", direction = -1) +
-  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")
-
-# Arrange both graphs in the same figure
-combined_plots <- graph3 + graph4
-combined_plots
-
-ggsave("RandomJournalPolicies.png", plot = last_plot(), device = "png")
-```
-
-``` {r echo = FALSE, message = FALSE}
-
-# Calculate Wilson Confidence Intervals
-sample_size <- 100
-confidence_level <- 0.95
-
-#CIs for 'Yes Explicit'
-randomYes <- dj_random %>%
+  ungroup()
+```
+
+```{r}
+# Get names for prominent journals that offered more than one type of PPC
+prom_multiPPC <- dj_prominent %>%
+  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) 
+```
+
+```{r}
+# Inspect the COPE status of prominent journals with and without PPC policies
+promCOPE <- dj_prominent %>%
  filter(ppc_type == "A") %>%
-  filter(has_ppc == "YES") %>%
-  count()
-
-ci_yesE <- binom.confint(randomYes$n, sample_size, method = "wilson", conf.level = confidence_level)
+ mutate(has_ppc = case_when(
+    has_ppc == "NO EXPLICIT" ~ "NO",
+    has_ppc == "NO IMPLICIT" ~ "NO",
+    TRUE ~ has_ppc
+ )) %>%
+ group_by(has_ppc) %>%
+ summarise(
+    total_count = n(),
+    COPE_count = sum(cope == TRUE)
+ ) %>%
+ mutate(COPEpercent = round((COPE_count / total_count) * 100)) %>%
+ ungroup()
+```
+
+Among the 100 prominent journals, `r prominentPPC$count[prominentPPC$has_ppc == "YES"]` (`r prominentPPC$count[prominentPPC$has_ppc == "YES"]`%) explicitly stated that they allowed submissions of post-publication critique^[Confidence intervals are not included for the prominent psychology journals as this sample represents our entire population of interest, negating the need for inferential statistical calculations.].
+Of these `r prominentPPC$count[prominentPPC$has_ppc == "YES"]` journals, `r print(as.character(english(nrow(prom_multiPPC))))` had two types of critique format and the other `r (prominentPPC$count[prominentPPC$has_ppc == "YES"] - nrow(prom_multiPPC))` journals had one critique format.
+`r print(as.character(english(prominentPPC$count[prominentPPC$has_ppc == "NO EXPLICIT"])))` journals (*Clinical Psychology: Science and Practice* and *Psychological Bulletin*) stated explicitly that they did not accept post-publication critiques.
+No reason was provided.
+`r dj_prominent %>% filter(ppc_name == "Commentary") %>% nrow()` journals offered commentaries, `r dj_prominent %>% filter(ppc_name == "Letters") %>% nrow()` journals offered letters, and `r dj_prominent %>% filter(ppc_name == "Web comments") %>% nrow()` journals offered web comments.
+Of the `r prominentPPC$count[prominentPPC$has_ppc == "YES"]` journals that explicitly accepted post-publication critique, `r promCOPE$COPE_count[promCOPE$has_ppc == "YES"]` (`r promCOPE$COPEpercent[promCOPE$has_ppc == "YES"]`%) were COPE members.
+Of the `r promCOPE$COPE_count[promCOPE$has_ppc == "NO"]` journals that did not have a policy related to post-publication critique, `r promCOPE$COPE_count[promCOPE$has_ppc == "NO"]` (`r promCOPE$COPEpercent[promCOPE$has_ppc == "NO"]`%) were COPE members.
+
+### What limits did journals place on post-publication critique?
+
+```{r}
+# Find the most restrictive length limit of any journal
+minLength <- d_journals %>%
+ select(c(sample_id, journal_name, ppc_name, ppc_length)) %>%
+ filter(!is.na(ppc_name),
+         ppc_length != "NOT STATED" & ppc_length != "Qualitative") %>%
+ mutate(quantLength = as.numeric(ppc_length)) %>%
+ slice_min(quantLength, n = 1) %>% # Select the row with the minimum quantLength
+ ungroup()
+
+# Find the most restrictive time limit of any journal
+minTime <- d_journals %>%
+ select(c(sample_id, journal_name, ppc_name, ppc_time)) %>%
+ filter(!is.na(ppc_name),
+         ppc_time != "NOT STATED" & ppc_time != "Qualitative") %>%
+ mutate(quantTime = as.numeric(ppc_time)) %>%
+ slice_min(quantTime, n = 1) %>% # Select the row with the minimum quantTime
+ ungroup()
+```
+
+Table 1 (randomly selected journals) and Table 2 (prominent journals) show the limits journals imposed on post-publication critique in terms of length, time-to-submit, and number of references.
+The tables also show whether a peer review policy for critiques was stated.
+Length limits were stated for most critique formats, especially those in prominent journals.
+Length limits were usually stated quantitatively (e.g., “1,000 words”).
+A few formats had qualitative limits (e.g., “brief”).
+Letters had tighter length limits than commentaries on average.
+The most restrictive length limit was `r minLength$quantLength` words at the *Journal of Adolescent Health*.
+Time-to-submit limits were not stated for most critique formats; they were somewhat more common in prominent journals.
+Time-to-submit limits, when present, were often stated qualitatively (e.g., “brief”) and sometimes quantitatively (e.g., “3 months”).
+The most restrictive time-to-submit limit was `r minTime$quantTime` weeks at the *Journal of Applied Psychology*.
+For most critique formats, journals did not state whether they would be sent for independent peer review or not.
+For a full list of stated limits at each journal, see Supplementary Information J.
+
+\newpage
+\begin{landscape}
+
+\textbf{Table 1.} Post-publication critique types identified in randomly selected psychology journals and their length, time-to-submit, and reference limits. 
+```{r}
+# Check length limits placed on PPC options in randomly selected journals
+
+# Summarise length statistics for All Types
+randomLengthAll <- dj_random %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_length)) %>%
+ mutate(quantLength = case_when(
+    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
+  )) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_length == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianLength = median(quantLength, na.rm = TRUE),
+    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ )
+
+# Put results into desired table format
+randomLengthAll_1 <- randomLengthAll %>% 
+  mutate('Post-publication critique type' = "All types") %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+``` {r}
+# Summarise length Statistics for each PPC type
+randomLengthType <- dj_random %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_length)) %>%
+ mutate(quantLength = case_when(
+    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
+  )) %>%
+ group_by(ppc_name) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_length == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianLength = round(median(quantLength, na.rm = TRUE)),
+    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1) 
+ ) %>%
+  ungroup()
+
+# Put results into desired table format
+randomLengthType_1 <- randomLengthType %>% 
+  mutate('Post-publication critique type' = ppc_name) %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Combine all time limits into single table
+randomLength_combo <- bind_rows(
+  randomLengthType_1,
+  randomLengthAll_1
+)
+```
+
+```{r}
+# Check time-to-submit limits placed on PPC options in prominent journals
+
+# Summarise time-to-submit statistics for All Types
+randomTimeAll <- dj_random %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_time)) %>%
+ mutate(quantTime = case_when(
+    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
+  )) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_time == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianTime = round(median(quantTime, na.rm = TRUE)),
+    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1) 
+ )
+
+# Put results into desired table format
+randomTimeAll_1 <- randomTimeAll %>% 
+  mutate('Post-publication critique type' = "All Types") %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+``` {r}
+# Summarise time-to-submit Statistics for each PPC type
+randomTimeType <- dj_random %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_time)) %>%
+ mutate(quantTime = case_when(
+    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
+  )) %>%
+  group_by(ppc_name) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_time == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianTime = round(median(quantTime, na.rm = TRUE)),
+    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ ) %>%
+  ungroup()
+
+# Put results into desired table format
+randomTimeType_1 <- randomTimeType %>% 
+  mutate('Post-publication critique type' = ppc_name) %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Combine all time limits into single table
+randomTime_combo <- bind_rows(
+  randomTimeType_1,
+  randomTimeAll_1
+)
+```
+
+```{r}
+# Check reference limits placed on PPC options in prominent journals
+
+# Summarise reference statistics for All Types
+randomRefAll <- dj_random %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_ref)) %>%
+ mutate(quantRef = case_when(
+    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
+  )) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianRef = median(quantRef, na.rm = TRUE),
+    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ )
+
+# Put results into desired table format
+randomRefAll_1 <- randomRefAll %>% 
+  mutate('Post-publication critique type' = "All types") %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Summarise reference statistics by type
+randomRefType <- dj_random %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_ref)) %>%
+ mutate(quantRef = case_when(
+    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
+  )) %>%
+  group_by(ppc_name) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianRef = median(quantRef, na.rm = TRUE),
+    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ ) %>%
+  ungroup()
+
+# Put results into desired table format
+randomRefType_1 <- randomRefType %>% 
+  mutate('Post-publication critique type' = ppc_name) %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Combine all peer review into single table
+randomRef_combo <- bind_rows(
+  randomRefType_1,
+  randomRefAll_1
+)
+```
+
+```{r}
+# Check how many PPC options are sent for external peer review in prominent journals
+
+# Peer review statistics for All Types
+randomReviewAll <- dj_random %>%
+  select(c(journal_name, ppc_name, ppc_review)) %>%
+  filter(!is.na(ppc_name)) %>%
+  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
+            yesReview = anyReview - sum(ppc_review == "NO"),
+            yesPercent = round((yesReview / n()) * 100)   # Percentage reviewed from All Types 
+  )
+
+# Put results into desired table format
+randomReviewAll_1 <- randomReviewAll %>%
+  mutate('Post-publication critique type' = "All types") %>%
+  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
+  select('Post-publication critique type', 'YES n (%)')
+```
+
+```{r}
+# Peer review statistics by types
+randomReviewType <- dj_random %>%
+  select(c(journal_name, ppc_name, ppc_review)) %>%
+  filter(!is.na(ppc_name)) %>%
+  group_by(ppc_name) %>%
+  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
+            yesReview = anyReview - sum(ppc_review == "NO"),
+            yesPercent = round((yesReview / n()) * 100)
+  ) %>%
+  ungroup()
+
+# Put results into desired table format
+randomReviewType_1 <- randomReviewType %>%
+  mutate('Post-publication critique type' = ppc_name) %>%
+  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
+  select('Post-publication critique type', 'YES n (%)')
+```
+
+```{r}
+# Combine all peer review into single table
+randomReview_combo <- bind_rows(
+  randomReviewType_1,
+  randomReviewAll_1
+)
+```
+
+``` {r}
+# Give each table a separate header for results
+randomLengthTable <- randomLength_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", 
+                              "quantitative n (%)", 
+                              "median (IQR)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Length limits" = 3))
+
+randomTimeTable <- randomTime_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", 
+                              "quantitative n (%)", 
+                              "median (IQR)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Time limits" = 3))
+
+randomRefTable <- randomRef_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", 
+                              "quantitative n (%)", 
+                              "median (IQR)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Reference limits" = 3))
+
+randomReviewTable <- randomReview_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "YES n (%)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Peer review" = 1))
+```
+
+```{r}
+# Combine the random sample limitations data frames
+combined_df <- bind_cols(
+  randomLength_combo %>% select(-`Post-publication critique type`),
+  randomTime_combo %>% select(-`Post-publication critique type`),
+  randomRef_combo %>% select(-`Post-publication critique type`),
+  randomReview_combo %>% select(-`Post-publication critique type`)
+)
+
+# Add the 'Post-publication critique type' column back to the combined data frame
+combined_df <- bind_cols(randomLength_combo %>% select(`Post-publication critique type`),
+                         combined_df)
+
+# Create the table with kableExtra
+randomLimits_Table <- combined_df %>%
+  kable("latex", col.names = c("Post-publication critique type", 
+                      "any n (%)", "quantitative n (%)", "Median (IQR)",
+                      "any n (%)", "quantitative n (%)", "Median (IQR)",
+                      "any n (%)", "quantitative n (%)", "Median (IQR)",
+                      "'Yes' n (%)")
+        ) %>%
+  column_spec(1, width = "2.6cm") %>% 
+  column_spec(c(2, 5, 8), width = "1.6cm") %>% 
+  column_spec(c(3, 6, 9), width = "2cm") %>% 
+  column_spec(c(4, 7, 10), width = "1.5cm") %>% 
+  column_spec(c(11), width = "1.2cm") %>% 
+  kable_styling("scale_down", latex_options = "H") %>%
+  add_header_above(c(" " = 1, 
+                     "Length limits" = 3, 
+                     "Time limits" = 3, 
+                     "Reference limits" = 3, 
+                     "Peer review" = 1)
+                   ) 
+```
+`r randomLimits_Table`\textit{Note.} This table also indicates whether the journal states that critiques will be sent for independent external peer review.
+IQR = Interquartile Range.
+Note that n’s refer to number of critique formats, not number of journals (some journals had more than one format of post publication critique).
+All results rounded to the nearest integer.
+
+\textbf{Table 2.} Post-publication critique types identified in prominent psychology journals and their length, time-to-submit, and reference limits.
+
+```{r}
+# Check length limits placed on PPC options in prominent journals
+
+# Summarise length statistics for All Types
+prominentLengthAll <- dj_prominent %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_length)) %>%
+ mutate(quantLength = case_when(
+    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
+  )) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_length == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianLength = median(quantLength, na.rm = TRUE),
+    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ )
+
+# Put results into desired table format
+prominentLengthAll_1 <- prominentLengthAll %>% 
+  mutate('Post-publication critique type' = "All types") %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+``` {r}
+# Summarise length Statistics for each PPC type
+prominentLengthType <- dj_prominent %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_length)) %>%
+ mutate(quantLength = case_when(
+    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
+  )) %>%
+ group_by(ppc_name) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_length == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianLength = median(quantLength, na.rm = TRUE),
+    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ ) %>%
+  ungroup()
+
+# Put results into desired table format
+prominentLengthType_1 <- prominentLengthType %>% 
+  mutate('Post-publication critique type' = ppc_name) %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Combine all peer review into single table
+prominentLength_combo <- bind_rows(
+  prominentLengthType_1,
+  prominentLengthAll_1
+)
+```
+
+```{r}
+# Check time-to-submit limits placed on PPC options in prominent journals
+
+# Summarise time-to-submit statistics for All Types
+prominentTimeAll <- dj_prominent %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_time)) %>%
+ mutate(quantTime = case_when(
+    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
+  )) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_time == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianTime = round(median(quantTime, na.rm = TRUE)),
+    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1) 
+ )
+
+# Put results into desired table format
+prominentTimeAll_1 <- prominentTimeAll %>%
+  mutate('Post-publication critique type' = "All types") %>%
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
+  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>%
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+``` {r}
+# Summarise time-to-submit Statistics for each PPC type
+prominentTimeType <- dj_prominent %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_time)) %>%
+ mutate(quantTime = case_when(
+    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
+  )) %>%
+  group_by(ppc_name) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_time == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianTime = round(median(quantTime, na.rm = TRUE)),
+    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ ) %>%
+  ungroup()
+
+# Put results into desired table format
+prominentTimeType_1 <- prominentTimeType %>%
+  mutate('Post-publication critique type' = ppc_name) %>%
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
+  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>%
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Combine all peer review into single table
+prominentTime_combo <- bind_rows(
+  prominentTimeType_1,
+  prominentTimeAll_1
+)
+```
+
+```{r}
+# Check reference limits placed on PPC options in prominent journals
+
+# Summarise reference statistics for All Types
+prominentRefAll <- dj_prominent %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_ref)) %>%
+ mutate(quantRef = case_when(
+    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
+  )) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianRef = median(quantRef, na.rm = TRUE),
+    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ )
+
+# Put results into desired table format
+prominentRefAll_1 <- prominentRefAll %>%
+  mutate('Post-publication critique type' = "All types") %>%
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
+  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>%
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Summarise reference statistics by type
+prominentRefType <- dj_prominent %>%
+ filter(!is.na(ppc_name)) %>% 
+ select(c(journal_name, ppc_name, ppc_ref)) %>%
+ mutate(quantRef = case_when(
+    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
+    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
+  )) %>%
+  group_by(ppc_name) %>%
+ summarise(
+    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
+    anyPercent = round((anyLimit / n()) * 100),
+    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
+    quantPercent = round((quantLimit / n()) * 100),
+    medianRef = median(quantRef, na.rm = TRUE),
+    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ ) %>%
+  ungroup()
+
+# Put results into desired table format
+prominentRefType_1 <- prominentRefType %>%
+  mutate('Post-publication critique type' = ppc_name) %>%
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
+  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>%
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Combine all peer review into single table
+prominentRef_combo <- bind_rows(
+  prominentRefType_1,
+  prominentRefAll_1
+)
+```
+
+```{r}
+# Check how many PPC options are sent for external peer review in prominent journals
+
+# Peer review statistics for All Types
+prominentReviewAll <- dj_prominent %>%
+  select(c(journal_name, ppc_name, ppc_review)) %>%
+  filter(!is.na(ppc_name)) %>%
+  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
+            yesReview = anyReview - sum(ppc_review == "NO"),
+            yesPercent = round((yesReview / n()) * 100)   # Percentage reviewed from All Types 
+  )
+
+# Put results into desired table format
+prominentReviewAll_1 <- prominentReviewAll %>%
+  mutate('Post-publication critique type' = "All types") %>%
+  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
+  select('Post-publication critique type', 'YES n (%)')
+```
+
+```{r}
+# Peer review statistics by types
+prominentReviewType <- dj_prominent %>%
+  select(c(journal_name, ppc_name, ppc_review)) %>%
+  filter(!is.na(ppc_name)) %>%
+  group_by(ppc_name) %>%
+  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
+            yesReview = anyReview - sum(ppc_review == "NO"),
+            yesPercent = round((yesReview / n()) * 100)
+  ) %>%
+  ungroup()
+
+# Put results into desired table format
+prominentReviewType_1 <- prominentReviewType %>%
+  mutate('Post-publication critique type' = ppc_name) %>%
+  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
+  select('Post-publication critique type', 'YES n (%)')
+```
+
+```{r}
+# Combine all peer review into single table
+prominentReview_combo <- bind_rows(
+  prominentReviewType_1,
+  prominentReviewAll_1
+)
+```
+
+``` {r}
+# Give each table a separate header for results
+prominentLengthTable <- prominentLength_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", 
+                              "quantitative n (%)", 
+                              "median (IQR)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Length limits" = 3))
+
+prominentTimeTable <- prominentTime_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", 
+                              "quantitative n (%)", 
+                              "median (IQR)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Time limits" = 3))
+
+prominentRefTable <- prominentRef_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", 
+                              "quantitative n (%)", 
+                              "median (IQR)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Reference limits" = 3))
+
+prominentReviewTable <- prominentReview_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "YES n (%)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Peer review" = 1))
+
+```
+
+```{r}
+# Combine the prominent limitations data frames
+combined_df <- bind_cols(
+  prominentLength_combo %>% select(-`Post-publication critique type`),
+  prominentTime_combo %>% select(-`Post-publication critique type`),
+  prominentRef_combo %>% select(-`Post-publication critique type`),
+  prominentReview_combo %>% select(-`Post-publication critique type`)
+)
+
+# Add the 'Post-publication critique type' column back to the combined data frame
+combined_df <- bind_cols(prominentLength_combo %>% select(`Post-publication critique type`), combined_df)
+
+# Create the table with kableExtra
+prominentLimits_Table <- combined_df %>%
+  kable("latex", col.names = c("Post-publication critique type", 
+                      "any n (%)", "quantitative n (%)", "Median (IQR)",
+                      "any n (%)", "quantitative n (%)", "Median (IQR)",
+                      "any n (%)", "quantitative n (%)", "Median (IQR)",
+                      "'Yes' n (%)") 
+        ) %>%
+ column_spec(1, width = "2.6cm") %>% 
+  column_spec(c(2, 5, 8), width = "1.6cm") %>% 
+  column_spec(c(3, 6, 9), width = "2cm") %>% 
+  column_spec(c(4, 7, 10), width = "1.5cm") %>% 
+  column_spec(c(11), width = "1.2cm") %>% 
+  kable_styling("basic", latex_options = "H") %>%
+  add_header_above(c(" " = 1, 
+                     "Length limits" = 3, 
+                     "Time limits" = 3, 
+                     "Reference limits" = 3, 
+                     "Peer review" = 1)
+                   ) 
+```
+`r prominentLimits_Table`\textit{Note.} This table also indicates whether the journal states that the critiques will be sent for independent external peer review.
+IQR = Interquartile Range.
+Note that n’s refer to number of critique formats, not number of journals (some journals had more than one format of post publication critique).
+All results rounded to the nearest integer.
+
+\end{landscape}
+\newpage
+
+# Part Two: Post-Publication Critique Prevalence
+
+## Method
+
+The methods and analysis plan were preregistered [(https://osf.io/d6xf2)](https://osf.io/d6xf2).
+All deviations from the preregistered protocol were considered minor and are detailed in Supplementary Information A and, where relevant, mentioned below.
+
+### Design
+
+This investigation had an cross-sectional design.
+All measured variables are described in detail in Supplementary Information C2.
+In brief, we estimated the prevalence of post-publication critique among empirical articles published in 2020 using two methods: (a) we identified whether sampled articles contained a link to a post-publication critique of the article (“Linked Method”); and (b) we identified whether sampled articles were themselves examples of post-publication critique (“Instance Method”)^[In Hardwicke et al.
+(2022), the Linked Method and Instance Method of prevalence estimation were called the ‘primary’ and ‘secondary’ method respectively.
+We changed the terminology because we do not want to imply that one method is necessarily superior to the other.].
+These two methods of estimating prevalence have complementary strengths and weaknesses; for more details, see Supplementary Information D.
+
+### Sample
+
+*Target populations*
+
+The target populations were (a) all empirical articles published in 2020 in all psychology journals; and (b) all empirical articles published in 2020 in the 100 most prominent psychology journals identified in Part One.
+We were only interested in articles published in legitimate (non-predatory), peer-reviewed journals.
+
+*Sample sizes*
+
+We examined 101 randomly selected empirical articles published in psychology journals and 101 randomly selected empirical articles published in prominent psychology journals (our target sample size was 100 articles in each sample, but, deviating from our preregistration, we accidently examined one additional article in each sample, see Supplementary Information A for details).
+Justification for these sample sizes is provided in Supplementary Information E.
+
+*Preparing Samples (inclusion/exclusion criteria)*
+
+For the random sample of articles published in psychology journals, we used the Web of Science Core Collection to download bibliographic classified with a Web of Science document type of ‘Article’, ‘Discussion’, ‘Editorial material’, or ‘Letter’ published in 2020 and classified as belonging to a psychology research area.
+The search returned 61,735 records (for exact search string, see Supplementary Information F).
+
+For the random sample of articles published in the most prominent psychology journals, we used the Web of Science Core Collection to download bibliographic records classified with a Web of Science document type of ‘Article’, ‘Discussion’, ‘Editorial material’, or ‘Letter’ published in 2020 in the 100 most prominent psychology journals (identified in Part One).
+The search returned 12,255 records (for exact search string, see Supplementary Information F).
+
+The two lists of sampled articles were each randomly shuffled using the R function ‘sample’ and the top 600 entries in each shuffled list were selected (to allow for exclusions).
+Articles were then evaluated sequentially until the target of 100 eligible articles in each sample was reached.
+Articles were excluded because they: (i) could not be accessed (n = 9); (ii) were non-English language (n = 4); (iii) indicated they had been retracted (n = 2), (iv) were non-empirical (n = 55), or (v) were conference abstracts or ‘supplement’ articles rather than complete articles (n = 9).
+Assessing whether an article is empirical involved some subjective judgement, but we used the following guidelines: empirical research must include some analysis of quantitative or qualitative data and the following do not count as empirical research: news, book reviews, editorials, previews, opinion pieces, simulations, proofs, theoretical papers, and reviews.
+We included primary research, secondary data analysis, and meta-analyses.
+If an article needed to be excluded after manual inspection, it was replaced with the next available article in its list, thus maintaining the random sampling scheme.
+
+Note, the above applies to the Linked Method for calculating prevalence; for the Instance Method for calculating prevalence estimates, articles that were themselves post-publication critique (e.g.
+'Letters') were included, but they did not count towards the 100 empirical articles sample size target.
+
+### Procedure
+
+*Piloting and training*
+
+The data extraction procedures were piloted with 10 articles that were not included in the sample.
+All investigators were trained and familiarised with the data extraction process and practised with positive and negative training examples.
+
+*Data extraction*
+
+To code whether sampled articles were linked to post-publication critique (Linked Method), two investigators independently viewed each article on the journal’s website, assessed if the article met the eligibility criteria, and if it did, thoroughly checked the page for any linked post-publication critique.
+
+To code whether the sampled article itself was an example of post-publication critique (Instance Method), the same two coders also read the title and, if necessary, the abstract of the sampled article.
+
+Primary coding was conducted by AW (n = 246) and NM (n = 35).
+Secondary coding was conducted by BC (n = 122), SS (n = 110), and TEH (n = 49).
+Data extraction/classification disagreements were resolved by TEH, which was necessary for 15 articles (for details see Supplementary Information H).
+
+## Results
+
+```{r}
+# Look for linked PPC in articles in random sample
+random_linked <- d_articles %>%
+  filter(sample_id == "random",
+         ppc_linked == TRUE) %>%
+  summarise(n = n())
+```
+
+```{r}
+# Calculate CIs for linked PPC in articles in random sample
+
+# Specify sample size for articles (same for both samples)
+sample_size_a <- 101
+
+ci_Rlinked <- binom.confint(random_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)
 
 # Convert the lower and upper limits to percentages and round them to one decimal place
-ci_yesE_LL <- round(ci_yesE$lower*100, 1)
-ci_yesE_UL <- round(ci_yesE$upper*100, 1)
-
-#CIs for 'Yes Implicit'
-randomArchive <- dj_random %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "ARCHIVE") %>%
-  count()
-
-ci_yesI <- binom.confint(randomArchive$n, sample_size, method = "wilson", conf.level = confidence_level)
+ci_randLinked_LL <- round(ci_Rlinked$lower*100, 1)
+ci_randLinked_UL <- round(ci_Rlinked$upper*100, 1)
+```
+
+```{r}
+# Look for instances of PPC in articles in random sample
+random_instance <- d_articles %>%
+  filter(sample_id == "random",
+         exclude_reason == "IS ITSELF PPC") %>%
+  summarise(n = n())
+```
+
+```{r}
+# Calculate CIs for Instance PPC in random sample
+ci_Rinstance <- binom.confint(random_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)
 
 # Convert the lower and upper limits to percentages and round them to one decimal place
-ci_yesI_LL <- round(ci_yesI$lower*100, 1)
-ci_yesI_UL <- round(ci_yesI$upper*100, 1)
-
-#CIs for 'No Implicit'
-randomNoImp <- dj_random %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "NO IMPLICIT") %>%
-  count()
-
-ci_noI <- binom.confint(randomNoImp$n, sample_size, method = "wilson", conf.level = confidence_level)
+ci_randInstance_LL <- round(ci_Rinstance$lower*100, 1)
+ci_randIinstance_UL <- round(ci_Rinstance$upper*100, 1)
+```
+
+Among the 101 empirical articles randomly sampled from all psychology journals, we did not find any examples of post-publication critiques based on the Linked Method nor the Instance Method, resulting in a prevalence estimate of `r random_linked`% (95% CI [`r ci_randInstance_LL`%, `r ci_randIinstance_UL`%]) for both methods.
+
+```{r}
+# Look for links to PPC in articles published in prominent journals
+prominent_linked <- d_articles %>%
+  filter(sample_id == "prominent",
+         ppc_linked == TRUE) %>%
+  summarise(n = n())
+```
+
+```{r}
+ci_linked <- binom.confint(prominent_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)
 
 # Convert the lower and upper limits to percentages and round them to one decimal place
-ci_noI_LL <- round(ci_noI$lower*100, 1)
-ci_noI_UL <- round(ci_noI$upper*100, 1)
-
-#CIs for 'No Explicit'
-randomNoExp <- dj_random %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "NO EXPLICIT") %>%
-  count()
-
-ci_noE <- binom.confint(randomNoExp$n, sample_size, method = "wilson", conf.level = confidence_level)
+ci_promLinked_LL <- round(ci_linked$lower*100, 1)
+ci_promLinked_UL <- round(ci_linked$upper*100, 1)
+```
+
+```{r}
+# Look for instances of PPC in articles published in prominent journals
+prominent_instance <- d_articles %>%
+  filter(sample_id == "prominent",
+         exclude_reason == "IS ITSELF PPC") %>%
+  summarise(n = n())
+```
+
+```{r}
+# Calculate CIs for Instance PPC in prominent journals
+ci_instance <- binom.confint(prominent_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)
 
 # Convert the lower and upper limits to percentages and round them to one decimal place
-ci_noE_LL <- round(ci_noE$lower*100, 1)
-ci_noE_UL <- round(ci_noE$upper*100, 1)
-
-# CIs for 2 types
-random2types <- dj_random %>%
-  filter(ppc_type == "B") %>%
-  filter(!is.na(ppc_name)) %>%
-  count()
-
-ci_2typ <- binom.confint(random2types$n, sample_size, method = "wilson", conf.level = confidence_level)
-
-# Convert the lower and upper limits to percentages and round them to one decimal place
-ci_2typ_LL <- round(ci_2typ$lower*100, 1)
-ci_2typ_UL <- round(ci_2typ$upper*100, 1)
-```
-
-*Note.* PPC = post-publication critique.
-Orange bar (left) indicates policy statements for each journal included in sample (n = 100).
-Blue bars (right) indicate how length and time-to-submit restrictions were stated in cases where journals had explicit post-publication critique policies in place (n = 25).
-
-```{r echo=FALSE, message=FALSE}
-# Length restriction statement types of explicit PPC types (random sample)
-
-# Calculate the count and percentage for "Quantitative"
-rand_quantitative_length <- random_length_data %>%
- filter(ppc_length == "Quantitative") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(random_length_data$count) * 100)
-
-# Calculate the count and percentage for "Qualitative"
-rand_qualitative_length <- random_length_data %>%
- filter(ppc_length == "Qualitative") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(random_length_data$count) * 100)
-
-# Calculate the count and percentage for "Not Stated"
-rand_notStated_length <- random_length_data %>%
- filter(ppc_length == "Not Stated") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(random_length_data$count) * 100)
-
-# Range
-rand_length_range <- dj_random %>%
-  filter(!is.na(ppc_length)) %>%
-  filter(ppc_length != "Qualitative") %>%
-  filter(ppc_length != "NOT STATED") %>%
-  mutate(ppc_length = as.numeric(ppc_length)) %>%
-  summarise(prom_median_length = median(ppc_length),
-            rand_min_length = min(ppc_length),
-            rand_max_length = max(ppc_length)
-            )
-
-# Time-to-submit restriction statement types of explicit PPC types (prominent sample)
-
-# Calculate the count and percentage for "Quantitative"
-rand_quantitative_time <- random_time_data %>%
- filter(ppc_time == "Quantitative") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(random_time_data$count) * 100)
-
-# Calculate the count and percentage for "Qualitative"
-rand_qualitative_time <- random_time_data %>%
- filter(ppc_time == "Qualitative") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(random_time_data$count) * 100)
-
-# Calculate the count and percentage for "Not Stated"
-rand_notStated_time <- random_time_data %>%
- filter(ppc_time == "Not Stated") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(random_time_data$count) * 100)
-
-# Range
-rand_time_range <- dj_random %>%
-  filter(!is.na(ppc_time)) %>%
-  filter(ppc_time != "Qualitative") %>%
-  filter(ppc_time != "NOT STATED") %>%
-  mutate(ppc_time = as.numeric(ppc_time)) %>%
-  summarise(rand_median_time = median(ppc_time),
-            rand_min_time = min(ppc_time),
-            rand_max_time = max(ppc_time)
-            )
-
-# Reference restriction statement types of explicit PPC types (prominent sample)
-random_ref_data <- dj_random %>%
-  filter(!is.na(ppc_name)) %>% # keep only entries that identify PPC option
-  filter(has_ppc != "ARCHIVE") %>% # remove implicit yes examples
-  mutate(ppc_ref = case_when(
-    ppc_ref %in% c(10, 15, 20, 5) ~ 'Quantitative',
-    ppc_ref == "NOT STATED" ~ "Not Stated",
-    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
-  )) %>%
-  group_by(ppc_ref) %>%
-  summarise(count = n()) %>%
-  ungroup()
-
-# Calculate the count and percentage for "Quantitative"
-rand_quantitative_ref <- random_ref_data %>%
- filter(ppc_ref == "Quantitative") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(random_ref_data$count) * 100)
-
-# Calculate the count and percentage for "Not Stated"
-rand_notStated_ref <- random_ref_data %>%
- filter(ppc_ref == "Not Stated") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(random_ref_data$count) * 100)
-
-# Range
-rand_ref_range <- dj_random %>%
-  filter(!is.na(ppc_ref)) %>%
-  filter(ppc_ref != "Qualitative") %>%
-  filter(ppc_ref != "NOT STATED") %>%
-  mutate(ppc_ref = as.numeric(ppc_ref)) %>%
-  summarise(rand_median_ref = median(ppc_ref),
-            rand_min_ref = min(ppc_ref),
-            rand_max_ref = max(ppc_ref)
-            )
-
-# Peer-review statements of explicit PPC types (prominent sample)
-random_review_data <- dj_random %>%
-  filter(!is.na(ppc_review)) %>% # keep only entries that identify PPC option
-  filter(has_ppc != "ARCHIVE") %>% # remove implicit yes examples
-  mutate(ppc_review = case_when(
-    ppc_review == 'YES' ~ 'Yes',
-    ppc_review == 'NO' ~ 'No',
-    ppc_review == "NOT STATED" ~ "Not Stated"
-  )) %>%
-  group_by(ppc_review) %>%
-  summarise(count = n()) %>%
-  ungroup()
-
-# Calculate the count and percentage for "Yes"
-rand_yes_review <- random_review_data %>%
- filter(ppc_review == "Yes") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(random_review_data$count) * 100)
-
-# Calculate the count and percentage for "No"
-rand_no_review <- random_review_data %>%
- filter(ppc_review == "No") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(random_review_data$count) * 100)
-
-# Calculate the count and percentage for "Not Stated"
-rand_notStated_review <- random_review_data %>%
- filter(ppc_review == "Not Stated") %>%
- summarise(count = sum(count), percentage = sum(count) / sum(random_review_data$count) * 100)
-
-```
-As shown in Figure *XX*, post-publication critique policies were explicitly stated by `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "YES") / n() * 100, "%"))` of journals (`r paste0(round(confidence_level*100), "% CI [", ci_yesE_LL, "%, ", ci_yesE_UL, "%]")`), and we inferred that they were implicitly accepted (as denoted by archival examples) in `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "ARCHIVE") / n() * 100, "%"))` of journals (`r paste0(round(confidence_level*100), "% CI [", ci_yesI_LL, "%, ", ci_yesI_UL, "%]")`).
-`r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO IMPLICIT") / n() * 100, "%"))` of journals (`r paste0(round(confidence_level*100), "% CI [", ci_noI_LL, "%, ", ci_noI_UL, "%]")`) had no advertised post-publication critique policy, and `r dj_random %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO EXPLICIT") / n() * 100, "%"))` of journals (`r paste0(round(confidence_level*100), "% CI [", ci_noE_LL, "%, ", ci_noE_UL, "%]")`) explicitly stated that they did not accept critiques (*Clinical Psychology: Science and Practice and Psychological Bulletin*, also included in sample for prominent journals).
-`r paste0(random2types, "%")` of journals accepted two types (`r paste0(round(confidence_level*100), "% CI [", ci_2typ_LL, "%, ", ci_2typ_UL, "%]")`); *Cortex* offered commentaries and 'verification reports' [@Chambers2020] and *Journal of Cognition and Culture* offered commentaries and letters.
-
-Among the 25 cases of explicitly accepted post-publication critiques, restrictions on length were quantitatively stated in `r paste(rand_quantitative_length$count, "(", round(rand_quantitative_length$percentage), "%)", sep = "")` cases, and not stated in `r paste(rand_notStated_length$count, "(", round(rand_notStated_length$percentage), "%)", sep = "")` cases.
-Time-to-submit was quantitatively stated in `r paste(rand_quantitative_time$count, "(", round(rand_quantitative_time$percentage), "%)", sep = "")` case, and qualitatively stated in `r paste(rand_qualitative_time$count, "(", round(rand_qualitative_time$percentage), "%)", sep = "")`, and not stated in `r paste(rand_notStated_time$count, "(", round(rand_notStated_time$percentage), "%)", sep = "")` cases.
-Number of references allowed was stated quantitatively in `r paste(rand_quantitative_ref$count, "(", round(rand_quantitative_ref$percentage), "%)", sep = "")` cases, and not stated in `r paste(rand_notStated_ref$count, "(", round(rand_notStated_ref$percentage), "%)", sep = "")` cases.
-Whether critiques were peer-reviewed was stated in `r paste((rand_yes_review$count + rand_no_review$count), "(", round(rand_yes_review$percentage + rand_no_review$percentage), "%)", sep = "")` cases, in `r paste(rand_yes_review$count, "(", round(rand_yes_review$percentage), "%)", sep = "")` cases this was in the affirmative.
-
-When stated quantitatively, length limits ranged from `r rand_length_range %>% pull(rand_min_length)` - `r rand_length_range %>% pull(rand_max_length)` words, time-to-submit limits were only stated by one journal (as 9 months), references ranged between `r rand_ref_range %>% pull(rand_min_ref)` - `r rand_ref_range %>% pull(rand_max_ref)`.
-Table *XX* shows descriptive statistics for these restrictions, broken down by critique type.
-
-### Table *XX*
-[*Insert table of results*]
-
-As expected, Table *XX* shows that commentaries were overall less restrictive on length with the median word limit being double that of letters.
-Commentaries were also three times more likely to state quantitative length restrictions than letters.
-Restrictions on time-to-submit, references, and whether critiques would be sent for peer-review were not stated for any policies on letters.
-Similarly, no details on restrictions or peer-review were stated for 'verification reports' (the one 'other' critique type included in this sample).
-
-```{r COPE status in random sample, echo=FALSE, message=FALSE}
-# COPE membership status among randomly-sampled journals accepting PPC
-random_PPCy <- dj_random %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>% # keep only journals that accept PPC
-  summarise(count = n()) # total number journals accepting PPC
-
-rand_copeY_PPC <- dj_random %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>%
-  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
-  summarise(count = n()) # number of COPE journals accepting PPC
-
-rand_copeN_PPC <- dj_random %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>%
-  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
-  summarise(count = n()) # number of non-COPE journals accepting PPC
-
-# COPE membership status among prominent journals NOT accepting PPC
-random_PPCn <- dj_random %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>% # keep only journals that do not accept PPC
-  summarise(count = n()) # total number journals not accepting PPC
-
-rand_copeY_PPCn <- dj_random %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
-  filter(cope == "TRUE") %>% # Keep only COPE journals (that do not accept PPC)
-  summarise(count = n()) # number of COPE journals accepting PPC
-
-rand_copeN_PPCn <- dj_random %>%
-  filter(ppc_type == "A") %>%
-  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
-  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that do not accept PPC)
-  summarise(count = n()) # number of non-COPE journals not accepting PPC
-
-```
-
-Of the `r paste(random_PPCy$count)` journals that accepted post-publication critiques (including the three implicitly implied through archive examples), `r paste(rand_copeY_PPC$count, "(", round((rand_copeY_PPC$count / random_PPCy$count) * 100, 1), "%)", sep = "")` were COPE members and `r paste(as.english(rand_copeN_PPC$count), " (", round((rand_copeN_PPC$count / random_PPCy$count) * 100, 1), "%)", sep = "")` were not.
-Of the `r paste(random_PPCn$count)` journals that had no critique policy, `r paste(rand_copeY_PPCn$count, "(", round((rand_copeY_PPCn$count / random_PPCn$count) * 100, 1), "%)", sep = "")` were COPE members, including the one with an explicit statement that they do not accept unsolicited critiques.
-
-## Part 2: Post-Publication Critique Prevalence
-```{r echo = FALSE, message=FALSE}
-# Filter articles by sample and calculate CIs
-
-# For articles randomly sampled from prominent psychology journals
-da_prominent <- d_articles %>%
-  filter(exclude == "RETAIN") %>% # remove excluded articles
-  filter(sample_id == "prominent") # keep only articles from prominent journals
-
-sample_size_a <- 101
-
-# Linked PPCs
-prominent_linked <- da_prominent %>% # counts number of linked PPC events
-  filter(ppc_linked == "TRUE") %>%
-  count()
-
-ci_linked <- binom.confint(prominent_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)
-
-# Convert the lower and upper limits to percentages and round them to one decimal place
-ci_linked_LL <- round(ci_linked$lower*100, 1)
-ci_linked_UL <- round(ci_linked$upper*100, 1)
-
-# Instance PPCs
-prominent_instance <- da_prominent %>% # counts number of linked PPC events
-  filter(exclude_reason == "IS PPC") %>%
-  count()
-
-ci_instance <- binom.confint(prominent_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)
-
-# Convert the lower and upper limits to percentages and round them to one decimal place
-ci_instance_LL <- round(ci_instance$lower*100, 1)
-ci_instance_UL <- round(ci_instance$upper*100, 1)
-
-# For articles randomly sampled from all psychology journals
-da_random <- d_articles %>%
-  filter(exclude == "RETAIN") %>% # remove excluded articles
-  filter(sample_id == "random") # keep only randomly-selected articles
-
-# Linked PPCs
-random_linked <- da_random %>%
-  filter(ppc_linked == "TRUE") %>%
-  count()
-
-ci_linkedR <- binom.confint(random_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)
-
-# Convert the lower and upper limits to percentages and round them to one decimal place
-ci_linkedR_LL <- round(ci_linkedR$lower*100, 1)
-ci_linkedR_UL <- round(ci_linkedR$upper*100, 1)
-
-# Instance PPCs
-random_instance <- da_random %>% # counts number of linked PPC events
-  filter(exclude_reason == "IS PPC") %>%
-  count()
-
-ci_instanceR <- binom.confint(random_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)
-
-# Convert the lower and upper limits to percentages and round them to one decimal place
-ci_instanceR_LL <- round(ci_instanceR$lower*100, 1)
-ci_instanceR_UL <- round(ci_instanceR$upper*100, 1)
-```
-**2a) Articles Published in Prominent Psychology Journals**
-
-Prevalence was defined in two ways: linked critiques (links to critiques appearing on same webpage as target article) and instances of critiques (articles that are themselves critiques).
-Only one linked post-publication critique event was found within our sample of 101 articles published in prominent psychology journals, yielding a prevalence estimate of `r da_prominent %>% summarise(percentage = paste0(round(sum(as.integer(ppc_linked == "TRUE")) / n() * 100, 1), "%"))` (`r paste0(round(confidence_level*100), "% CI [", ci_linked_LL, "%, ", ci_linked_UL, "%]")`).
-No instances of post-publication critiques were found (0%, `r paste0(round(confidence_level*100), "% CI [", ci_instance_LL, "%, ", ci_instance_UL, "%]")`).
-
-The single linked critique found appeared under the 'Recommended articles' sidebar of an article published in the Journal of Environmental Psychology webpage (for a depiction of how the article was linked, see Appendix F).
-This example was published as a letter[@Berto2020] and addressed concerns over incorrect citation of the critiquing author’s previous work and methodology used in the target article [@Hicks2020].
-
-**2b) Articles Published in Any Psychology Journal**
-
-No events of either linked or instances of post-publication critiques were identified in our random sample of 101 articles, resulting in a prevalence estimate of 0% (`r paste0(round(confidence_level*100), "% CI [", ci_instanceR_LL, "%, ", ci_instanceR_UL, "%]")`) for both classifications.
-
-# Discussion
-*Add 'Discussion' section*
-
-# Methods
-*Add 'Methods' section*
-
-# Data Availability
-The data used for this paper are available from the project’s OSF repository (link: [https://osf.io/8k7m4/](https://osf.io/8k7m4/))
-
-# Code Availability
-The analysis code for all results reported in this paper are available from the project’s OSF repository (link: [https://osf.io/8k7m4/](https://osf.io/8k7m4/))
-
-# References
+ci_promInstance_LL <- round(ci_instance$lower*100, 1)
+ci_promIinstance_UL <- round(ci_instance$upper*100, 1)
+```
+
+Among the 101 empirical articles randomly sampled from prominent psychology journals, we found only one post-publication critique using the Linked Method (i.e., one sampled article was associated with a linked post-publication critique), yielding a prevalence estimate of `r prominent_linked`% (95% CI [`r ci_promLinked_LL`%, `r `ci_promLinked_UL`%]).
+Using the Instance Method, we found no post-publication critiques (`r `prominent_instance`%, 95% CI [`r ci_promInstance_LL`%, `r ci_promIinstance_UL`%]) (i.e., none of the sampled articles were themselves instances of post-publication critique).
+
+# General Discussion
+
+Post-publication critique is often viewed as an important mechanism of scientific self-correction [@robertk.merton1973; @vazire2022].
+However, our study found that across the field of psychology only a minority of journals (`r randomPPC$count[randomPPC$has_ppc == "YES"]`, `r randomPPC$count[randomPPC$has_ppc == "YES"]`%, 95% CI [`r round(randomPPC_CI[1,5]*100)`%, `r round(randomPPC_CI[1,6]*100)`%]) had an explicit submission format for post-publication critique, and actual examples of post-publication critique are extremely rare.
+Prominent psychology journals were more likely to have an explicit format for post-publication critique according to their policies (38%), but the majority still did not.
+No journals in either sample supported web comments.
+Journals that did allow submission of post-publication critique sometimes imposed restrictions on length and time-to-submit.
+Occasionally, these limits were quite restrictive; the strictest length limit was 400 words and the strictest time-to-submit limit was 4 weeks after the target article was published.
+In practice, post-publication critiques were rare with only a single Linked example found within the articles sampled from prominent journals.
+Overall, our findings suggest that the policy and practice of post-publication critique is seriously neglected in psychology journals.
+
+Should all journals offer an explicit avenue for post-publication critique?
+Post-publication critique is recognized as an important mechanism of scientific self-correction [@robertk.merton1973; @vazire2022] and facilitating critique is often considered to be a journal’s responsibility (e.g., according to @committeeonpublicationethics2021).
+Interestingly, in both the randomly selected and prominent samples, most (`r randomCOPE$COPEpercent[randomCOPE$has_ppc == "NO"]`% and `r promCOPE$COPEpercent[promCOPE$has_ppc == "NO"]`%, respectively) of the journals that did not offer post-publication critique were members of COPE^[COPE guidelines explicitly recommend that journals allow post-publication critique “on their site, through letters to the editor, or on external moderated website such as PubPeer” (COPE Council, 2021).
+Technically, a journal does not need to do anything to comply with this recommendation because PubPeer is an independent platform.].
+It is unclear if publishers or journal editors have principled reasons for not explicitly offering post-publication critique.
+
+It could be argued that post-publication critique can take place in other contexts, such as social media or dedicated platforms like PubPeer [@bastian2014]; however, journals are in a privileged position to encourage, curate, and publish critiques in the scientific record, which improves      permanence and discoverability (i.e., by linking to critiques on the same webpage as the target article).
+Critiques posted informally on external platforms may be overlooked by journals and readers [@allison2016].
+There is also a risk that third party sites will become defunct — as in the case of PubMed Commons, which was shut down in 2018 [ncbiinsights2018].
+Some prominent psychologists have even argued that critiques should appear only in venues subject to editorial oversight (e.g., @fiske2016).
+
+Are journal limits on post-publication critique justifiable?
+Length limits may promote concision; however, strict limits (e.g., a few hundred words) are likely to seriously reduce the scope and substance of critiques [@altman2005].
+There is no obvious justification for imposing time-to-submit limits.
+Such limits imply that there is effectively a “statute of limitations” on scientific critique once a paper has been published for a given time (often no more than a few months).
+Only a few policies stated that critiques would be sent for independent external peer-review.
+It was unclear whether journals routinely send critiques to the original authors for review, but anecdotally, we know this can occur.
+Independent peer-review can provide more impartial assessment of critiques and bolster their legitimacy @schriger2010.
+Without independent review, the decision about whether to publish a critique may be based solely on the perspectives of individuals with a conflict of interest, namely the journal editors and the original authors.
+
+Though our data indicate that post-publication critique is neglected in psychology journals, they do not provide insight into why this is the case.
+Potential reasons could be cultural (e.g., disciplines have different attitudes towards scientific criticism and how to handle it), pragmatic (e.g., some disciplines have a greater need for critique than others because of lower quality standards), bureaucratic (e.g., availability of resources to support post-publication critique), historic (e.g., particular individuals or events that have highlighted the value of post-publication critique), or reputational (e.g., a perception that post-publication critique could damage journal reputation).
+Other factors which may deter submission of post-publication critique include fear of retaliation, such as public defamation and legal threats from those whose research they questioned [@besancon2021].
+
+Our research has several limitations.
+First, our operational definition of post-publication critique was intentionally focused on journal accountability and therefore some types of critical discourse (such as externally hosted critiques or criticisms embedded in research or review articles that do not target a specific article) were beyond the scope of this study.
+Our definition also excluded errata, corrections, and retractions, some of which may have been motivated by post-publication critiques that were eventually not published.
+Second, we relied on information explicitly published on journal websites; it is possible that some journals accept post-publication critique, even though they do not have an explicit policy saying so on their website.
+Third, it is possible that we missed some examples of post-publication critique because they were not clearly linked to the target article; we did our best to minimize this possibility by having two coders independently assess the presence of critique for each article.
+Fourth, our study focused on constraints  imposed by journals on post-publication critique; however, there are likely many contributing factors to the low prevalence of critique, such as authors’ ability and willingness to write and submit critiques, and the extent to which critiques are recognized in hiring, promotion, and funding decisions.
+
+## Conclusion
+
+Since 2011, psychology has been navigating a period of considerable epistemological turmoil, with serious concerns raised about research quality [@nosek2022].
+Post-publication critique is a valuable mechanism for identifying problems in published research and highlighting them to readers [@hardwicke2022; @robertk.merton1973; @vazire2022].
+The present study shows that post-publication critique is seriously neglected in policy and practice at psychology journals.
+Most journals do not have explicit formats for the submission of post-publication critiques and critiques are very rarely published.
+In Box 1, we provide some tentative policy suggestions that may help to improve this situation.
+
+**INSERT BOX 1**
+
+## Author contributions
+
+Conceptualization: T.E.H., A.W., S.V.
+Data curation: A.W.
+and T.E.H.
+Formal analysis: A.W.
+and T.E.H.
+Investigation: A.W., B.C., N.M., S.S., S.V, R.T.T., and T.E.H.
+Methodology: T.E.H.
+Project administration: A.W.
+and T.E.H.
+Resources: T.E.H.
+Software: T.E.H.
+Supervision: T.E.H.
+and S.V.
+Validation: A.W.
+and T.E.H.
+Visualization: A.W.
+Writing - original draft: A.W.
+Writing - review & editing: A.W., S.V., and T.E.H.
+
+## Acknowledgements
+
+AW would like to thank her father, Robert Whamond, for providing technical assistance and support with software issues that arose during this project.
+
+\newpage
+
+## References

### 2024-11-12 analysis/resultsAnalysis.Rmd
Moved via the Open Science Framework

@@
   html_document: default
+  pdf_document: default
 ---
@@
 library(binom)
-library(ggplot2)
-library(RColorBrewer)
 library(assertthat)
+library(kableExtra)
+library(webshot2)
 ```
@@
 
-Random journals Web Of Science categories
-```{r}
-randomCategory <- dj_random %>%
+## How many journals offer post-publication critique?
+
+**RANDOMLY-SELECTED SAMPLE**
+
+Inspect how frequently PPC policies were stated for randomly selected journals 
+```{r}
+randomPPC <- dj_random %>%
   filter(ppc_type == 'A') %>%
-  group_by(field) %>%
+  group_by(has_ppc) %>%
   summarise(count = n()) %>%
@@
 
-randomCategory
-```
-## How many journals offer post-publication critique?
-
-PROMINENT SAMPLE
+randomPPC
+```
+
+Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
+```{r}
+dj_random %>%
+  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
+  print()
+```
+
+Calculate confidence interval for explicitly stated PPC policies among randomly selected journals
+```{r}
+randomPPCyes <- dj_random %>%
+  filter(ppc_type == 'A', !is.na(ppc_name)) %>%
+  summarise(count = n())
+
+randomPPCno <- dj_random %>%
+  filter(ppc_type == 'A', is.na(ppc_name)) %>%
+  summarise(count = n())
+
+# Calculate Wilson confidence intervals
+sample_size <- 100
+confidence_level <- 0.95
+
+# CIs for 'Yes Explicit'
+randomPPC_CI <- binom.confint(randomPPCyes, sample_size, method = "wilson", conf.level = confidence_level)
+
+# CIs for 'No' (both explicit and Implicit)
+randomPPC_CI_neg <- binom.confint(randomPPCno, sample_size, method = "wilson", conf.level = confidence_level)
+
+# View results
+randomPPC_CI
+randomPPC_CI_neg
+```
+*Note.* CIs were not calculated for the prominent sample of journals as they represented our entire population of interest.
+
+Get names for randomly selected journals that offered more than one type of PPC
+```{r}
+# Return all rows with ppc_name values for ppc_type B and C
+dj_random %>%
+  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
+  print()
+```
+
+Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
+```{r}
+dj_random %>%
+  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
+  print()
+```
+
+Inspect PPC types at randomly selected journals
+```{r}
+table(dj_random$ppc_name)
+```
+
+Inspect the COPE status of randomly selected journals with and without PPC policies
+```{r}
+randomCOPE <- dj_random %>%
+ filter(ppc_type == "A") %>%
+ mutate(has_ppc = case_when(
+    has_ppc == "NO EXPLICIT" ~ "NO",
+    has_ppc == "NO IMPLICIT" ~ "NO",
+    TRUE ~ has_ppc
+ )) %>%
+ group_by(has_ppc) %>%
+ summarise(
+    total_count = n(),
+    COPE_count = sum(cope == TRUE)
+ ) %>%
+ mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
+ ungroup()
+
+randomCOPE
+```
+
+**PROMINENT SAMPLE**
+
 Inspect how frequently PPC policies were stated for prominent journals 
@@
 ```
-RANDOMLY-SELECTED SAMPLE
-Inspect how frequently PPC policies were stated for randomly selected journals 
-```{r}
-randomPPC <- dj_random %>%
-  filter(ppc_type == 'A') %>%
-  group_by(has_ppc) %>%
-  summarise(count = n()) %>%
-  ungroup()
-
-randomPPC
-```
-
-Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
-```{r}
-dj_random %>%
-  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
-  print()
-```
-
-Calculate confidence interval for explicitly stated PPC policies among randomly selected journals
-```{r}
-randomPPCyes <- dj_random %>%
-  filter(ppc_type == 'A', !is.na(ppc_name)) %>%
-  summarise(count = n())
-
-randomPPCno <- dj_random %>%
-  filter(ppc_type == 'A', is.na(ppc_name)) %>%
-  summarise(count = n())
-
-# Calculate Wilson confidence intervals
-sample_size <- 100
-confidence_level <- 0.95
-
-# CIs for 'Yes Explicit'
-randomPPC_CI <- binom.confint(randomPPCyes, sample_size, method = "wilson", conf.level = confidence_level)
-
-# CIs for 'No' (both explicit and Implicit)
-randomPPC_CI_neg <- binom.confint(randomPPCno, sample_size, method = "wilson", conf.level = confidence_level)
-
-# View results
-randomPPC_CI
-randomPPC_CI_neg
-```
-*Note.* CIs were not calculated for the prominent sample of journals as they represented our entire population of interest.
-
-Get names for randomly selected journals that offered more than one type of PPC
-```{r}
-# Return all rows with ppc_name values for ppc_type B and C
-dj_random %>%
-  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
-  print()
-```
-
-Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
-```{r}
-dj_random %>%
-  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
-  print()
-```
-
-Inspect PPC types at randomly selected journals
-```{r}
-table(dj_random$ppc_name)
-```
-
-Inspect the COPE status of randomly selected journals with and without PPC policies
-```{r}
-randomCOPE <- dj_random %>%
- filter(ppc_type == "A") %>%
- mutate(has_ppc = case_when(
-    has_ppc == "NO EXPLICIT" ~ "NO",
-    has_ppc == "NO IMPLICIT" ~ "NO",
-    TRUE ~ has_ppc
- )) %>%
- group_by(has_ppc) %>%
- summarise(
-    total_count = n(),
-    COPE_count = sum(cope == TRUE)
- ) %>%
- mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
- ungroup()
-
-randomCOPE
-```
 
@@
 
-## Calculations for Table 1: PPC limits in prominent journals
-
-Check length limits placed on PPC options in prominent journals
+## Calculations for Table 1: PPC limits in randomly selected journals
+
+Check length limits placed on PPC options in randomly selected journals
 ```{r}
 # Summarise length statistics for All Types
-prominentLengthAll <- dj_prominent %>%
+randomLengthAll <- dj_random %>%
  filter(!is.na(ppc_name)) %>% 
@@
     medianLength = median(quantLength, na.rm = TRUE),
-    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
-    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
-    IQR = Q3 - Q1 
- )
-
-prominentLengthAll
+    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ )
+
+# Put results into desired table format
+randomLengthAll_1 <- randomLengthAll %>% 
+  mutate('Post-publication critique type' = "All types") %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
 ```
@@
 # Summarise length Statistics for each PPC type
-prominentLengthType <- dj_prominent %>%
+randomLengthType <- dj_random %>%
  filter(!is.na(ppc_name)) %>% 
@@
     medianLength = median(quantLength, na.rm = TRUE),
-    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
-    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
+    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
     IQR = Q3 - Q1 
@@
 
-prominentLengthType
+# Put results into desired table format
+randomLengthType_1 <- randomLengthType %>% 
+  mutate('Post-publication critique type' = ppc_name) %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Combine all time limits into single table
+randomLength_combo <- bind_rows(
+  randomLengthType_1,
+  randomLengthAll_1
+)
 ```
@@
 # Summarise time-to-submit statistics for All Types
-prominentTimeAll <- dj_prominent %>%
+randomTimeAll <- dj_random %>%
  filter(!is.na(ppc_name)) %>% 
@@
     medianTime = median(quantTime, na.rm = TRUE),
-    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
-    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
+    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
     IQR = Q3 - Q1 
@@
 
-prominentTimeAll
+# Put results into desired table format
+randomTimeAll_1 <- randomTimeAll %>% 
+  mutate('Post-publication critique type' = "All Types") %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
 ```
@@
 # Summarise time-to-submit Statistics for each PPC type
-prominentTimeType <- dj_prominent %>%
+randomTimeType <- dj_random %>%
  filter(!is.na(ppc_name)) %>% 
@@
     medianTime = median(quantTime, na.rm = TRUE),
-    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
-    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
-    IQR = Q3 - Q1 
+    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
  ) %>%
@@
 
-prominentTimeType
+# Put results into desired table format
+randomTimeType_1 <- randomTimeType %>% 
+  mutate('Post-publication critique type' = ppc_name) %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Combine all time limits into single table
+randomTime_combo <- bind_rows(
+  randomTimeType_1,
+  randomTimeAll_1
+)
 ```
@@
 # Summarise reference statistics for All Types
-prominentRefAll <- dj_prominent %>%
+randomRefAll <- dj_random %>%
  filter(!is.na(ppc_name)) %>% 
@@
     medianRef = median(quantRef, na.rm = TRUE),
-    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
-    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
-    IQR = Q3 - Q1 
- )
-
-prominentRefAll
+    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ )
+
+# Put results into desired table format
+randomRefAll_1 <- randomRefAll %>% 
+  mutate('Post-publication critique type' = "All types") %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
 ```
@@
 # Summarise reference statistics by type
-prominentRefType <- dj_prominent %>%
+randomRefType <- dj_random %>%
  filter(!is.na(ppc_name)) %>% 
@@
     medianRef = median(quantRef, na.rm = TRUE),
-    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
-    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
-    IQR = Q3 - Q1 
+    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
  ) %>%
@@
 
-prominentRefType
+# Put results into desired table format
+randomRefType_1 <- randomRefType %>% 
+  mutate('Post-publication critique type' = ppc_name) %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Combine all peer review into single table
+randomRef_combo <- bind_rows(
+  randomRefType_1,
+  randomRefAll_1
+)
 ```
@@
 # Peer review statistics for All Types
-prominentReviewAll <- dj_prominent %>%
+randomReviewAll <- dj_random %>%
   select(c(journal_name, ppc_name, ppc_review)) %>%
@@
 
-prominentReviewAll
-
+# Put results into desired table format
+randomReviewAll_1 <- randomReviewAll %>%
+  mutate('Post-publication critique type' = "All types") %>%
+  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
+  select('Post-publication critique type', 'YES n (%)')
 ```
@@
 # Peer review statistics by types
-prominentReviewType <- dj_prominent %>%
+randomReviewType <- dj_random %>%
   select(c(journal_name, ppc_name, ppc_review)) %>%
@@
 
-prominentReviewType
-```
-
-## Calculations for Table 2: PPC limits in randomly selected journals
-
-Check length limits placed on PPC options in randomly selected journals
+# Put results into desired table format
+randomReviewType_1 <- randomReviewType %>%
+  mutate('Post-publication critique type' = ppc_name) %>%
+  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
+  select('Post-publication critique type', 'YES n (%)')
+```
+
+```{r}
+# Combine all peer review into single table
+randomReview_combo <- bind_rows(
+  randomReviewType_1,
+  randomReviewAll_1
+)
+```
+
+**Table 1.** Post-publication critique types identified in randomly selected psychology journals and their length, time-to-submit, and reference limits.
+
+``` {r}
+# Give each table a separate header for results
+randomLengthTable <- randomLength_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", 
+                              "quantitative n (%)", 
+                              "median (IQR)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Length limits" = 3))
+
+randomTimeTable <- randomTime_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", 
+                              "quantitative n (%)", 
+                              "median (IQR)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Time limits" = 3))
+
+randomRefTable <- randomRef_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", 
+                              "quantitative n (%)", 
+                              "median (IQR)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Reference limits" = 3))
+
+randomReviewTable <- randomReview_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "YES n (%)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Peer review" = 1))
+```
+
+```{r}
+# Combine the random sample limitations data frames
+combined_df <- bind_cols(
+  randomLength_combo %>% select(-`Post-publication critique type`),
+  randomTime_combo %>% select(-`Post-publication critique type`),
+  randomRef_combo %>% select(-`Post-publication critique type`),
+  randomReview_combo %>% select(-`Post-publication critique type`)
+)
+
+# Add the 'Post-publication critique type' column back to the combined data frame
+combined_df <- bind_cols(randomLength_combo %>% select(`Post-publication critique type`), combined_df)
+
+# Create the table with kableExtra
+randomLimits_Table <- combined_df %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", "quantitative n (%)", "median (IQR)",
+                              "any n (%)", "quantitative n (%)", "median (IQR)",
+                              "any n (%)", "quantitative n (%)", "median (IQR)",
+                              "YES n (%)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Length limits" = 3, "Time limits" = 3, "Reference limits" = 3, "Peer review" = 1))
+
+randomLimits_Table
+
+save_kable(randomLimits_Table, here("analysis/randomLimits_Table.png"))
+```
+
+## Calculations for Table 2: PPC limits in prominent journals
+
+Check length limits placed on PPC options in prominent journals
 ```{r}
 # Summarise length statistics for All Types
-randomLengthAll <- dj_random %>%
+prominentLengthAll <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>% 
@@
     medianLength = median(quantLength, na.rm = TRUE),
-    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
-    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
-    IQR = Q3 - Q1 
- )
-
-randomLengthAll
+    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ )
+
+# Put results into desired table format
+prominentLengthAll_1 <- prominentLengthAll %>% 
+  mutate('Post-publication critique type' = "All types") %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
 ```
@@
 # Summarise length Statistics for each PPC type
-randomLengthType <- dj_random %>%
+prominentLengthType <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>% 
@@
     medianLength = median(quantLength, na.rm = TRUE),
-    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
-    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
-    IQR = Q3 - Q1 
+    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
  ) %>%
@@
 
-randomLengthType
-```
+# Put results into desired table format
+prominentLengthType_1 <- prominentLengthType %>% 
+  mutate('Post-publication critique type' = ppc_name) %>% 
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
+  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Combine all peer review into single table
+prominentLength_combo <- bind_rows(
+  prominentLengthType_1,
+  prominentLengthAll_1
+)
+```
+
 Check time-to-submit limits placed on PPC options in prominent journals
@@
 # Summarise time-to-submit statistics for All Types
-randomTimeAll <- dj_random %>%
+prominentTimeAll <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>% 
@@
     quantPercent = round((quantLimit / n()) * 100),
-    medianTime = median(quantTime, na.rm = TRUE),
-    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
-    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
-    IQR = Q3 - Q1 
- )
-
-randomTimeAll
+    medianTime = round(median(quantTime, na.rm = TRUE)),
+    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1) 
+ )
+
+# Put results into desired table format
+prominentTimeAll_1 <- prominentTimeAll %>%
+  mutate('Post-publication critique type' = "All types") %>%
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
+  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>%
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
 ```
@@
 # Summarise time-to-submit Statistics for each PPC type
-randomTimeType <- dj_random %>%
+prominentTimeType <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>% 
@@
     quantPercent = round((quantLimit / n()) * 100),
-    medianTime = median(quantTime, na.rm = TRUE),
-    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
-    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
-    IQR = Q3 - Q1 
+    medianTime = round(median(quantTime, na.rm = TRUE)),
+    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
  ) %>%
@@
 
-randomTimeType
-```
+# Put results into desired table format
+prominentTimeType_1 <- prominentTimeType %>%
+  mutate('Post-publication critique type' = ppc_name) %>%
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
+  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>%
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Combine all peer review into single table
+prominentTime_combo <- bind_rows(
+  prominentTimeType_1,
+  prominentTimeAll_1
+)
+```
+
 Check reference limits placed on PPC options in prominent journals
@@
 # Summarise reference statistics for All Types
-randomRefAll <- dj_random %>%
+prominentRefAll <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>% 
@@
     medianRef = median(quantRef, na.rm = TRUE),
-    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
-    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
-    IQR = Q3 - Q1 
- )
-
-randomRefAll
+    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
+    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
+    IQR = round(Q3 - Q1)
+ )
+
+# Put results into desired table format
+prominentRefAll_1 <- prominentRefAll %>%
+  mutate('Post-publication critique type' = "All types") %>%
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
+  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>%
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
 ```
@@
 # Summarise reference statistics by type
-randomRefType <- dj_random %>%
+prominentRefType <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>% 
@@
 
-randomRefType
-```
+# Put results into desired table format
+prominentRefType_1 <- prominentRefType %>%
+  mutate('Post-publication critique type' = ppc_name) %>%
+  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
+  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
+  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>%
+  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
+```
+
+```{r}
+# Combine all peer review into single table
+prominentRef_combo <- bind_rows(
+  prominentRefType_1,
+  prominentRefAll_1
+)
+```
+
 Check how many PPC options are sent for external peer review in prominent journals
@@
 # Peer review statistics for All Types
-randomReviewAll <- dj_random %>%
+prominentReviewAll <- dj_prominent %>%
   select(c(journal_name, ppc_name, ppc_review)) %>%
@@
 
-randomReviewAll
+# Put results into desired table format
+prominentReviewAll_1 <- prominentReviewAll %>%
+  mutate('Post-publication critique type' = "All types") %>%
+  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
+  select('Post-publication critique type', 'YES n (%)')
 ```
@@
 # Peer review statistics by types
-randomReviewType <- dj_random %>%
+prominentReviewType <- dj_prominent %>%
   select(c(journal_name, ppc_name, ppc_review)) %>%
@@
 
-randomReviewType
+# Put results into desired table format
+prominentReviewType_1 <- prominentReviewType %>%
+  mutate('Post-publication critique type' = ppc_name) %>%
+  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
+  select('Post-publication critique type', 'YES n (%)')
+```
+
+```{r}
+# Combine all peer review into single table
+prominentReview_combo <- bind_rows(
+  prominentReviewType_1,
+  prominentReviewAll_1
+)
+```
+
+**Table 2.** Post-publication critique types identified in prominent psychology journals and their length, time-to-submit, and reference limits.
+
+``` {r}
+# Give each table a separate header for results
+prominentLengthTable <- prominentLength_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", 
+                              "quantitative n (%)", 
+                              "median (IQR)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Length limits" = 3))
+
+prominentTimeTable <- prominentTime_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", 
+                              "quantitative n (%)", 
+                              "median (IQR)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Time limits" = 3))
+
+prominentRefTable <- prominentRef_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", 
+                              "quantitative n (%)", 
+                              "median (IQR)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Reference limits" = 3))
+
+prominentReviewTable <- prominentReview_combo %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "YES n (%)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Peer review" = 1))
+
+```
+
+```{r}
+# Combine the prominent limitations data frames
+combined_df <- bind_cols(
+  prominentLength_combo %>% select(-`Post-publication critique type`),
+  prominentTime_combo %>% select(-`Post-publication critique type`),
+  prominentRef_combo %>% select(-`Post-publication critique type`),
+  prominentReview_combo %>% select(-`Post-publication critique type`)
+)
+
+# Add the 'Post-publication critique type' column back to the combined data frame
+combined_df <- bind_cols(prominentLength_combo %>% select(`Post-publication critique type`), combined_df)
+
+# Create the table with kableExtra
+prominentLimits_Table <- combined_df %>%
+  kable("html", col.names = c("Post-publication critique type", 
+                              "any n (%)", "quantitative n (%)", "median (IQR)",
+                              "any n (%)", "quantitative n (%)", "median (IQR)",
+                              "any n (%)", "quantitative n (%)", "median (IQR)",
+                              "YES n (%)")) %>%
+  kable_styling(full_width = F) %>%
+  add_header_above(c(" " = 1, "Length limits" = 3, "Time limits" = 3, "Reference limits" = 3, "Peer review" = 1))
+
+prominentLimits_Table
+
+save_kable(prominentLimits_Table, here("analysis/prominentLimits_Table.png"))
 ```
@@
 # STUDY 2: PREVALENCE
+
+## Prevalence in randomly selected journals
+
+Look for linked PPC in articles in random sample
+```{r}
+d_articles %>%
+  filter(sample_id == "random",
+         ppc_linked == TRUE) %>%
+  summarise(n = n())
+```
+
+Calculate CIs for linked PPC in articles in random sample
+```{r}
+# Specify sample size for articles (same for both samples)
+sample_size_a <- 101
+
+# Linked PPCs
+random_linked <- d_articles %>% # counts number of linked PPC events
+  filter(sample_id == "random",
+         ppc_linked == TRUE) %>%
+  count()
+
+ci_Rlinked <- binom.confint(random_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_randLinked_LL <- round(ci_Rlinked$lower*100, 1)
+ci_randLinked_UL <- round(ci_Rlinked$upper*100, 1)
+
+ci_randLinked_LL
+ci_randLinked_UL
+```
+
+Look for instances of PPC in articles in random sample
+```{r}
+d_articles %>%
+  filter(sample_id == "random",
+         exclude_reason == "IS ITSELF PPC") %>%
+  summarise(n = n())
+```
+
+Calculate CIs for Instance PPC in random sample
+```{r}
+# Instance PPCs
+random_instance <- d_articles %>% # counts number of linked PPC events
+  filter(sample_id == "random",
+    exclude_reason == "IS ITSELF PPC") %>%
+  count()
+
+ci_Rinstance <- binom.confint(random_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)
+
+# Convert the lower and upper limits to percentages and round them to one decimal place
+ci_randInstance_LL <- round(ci_Rinstance$lower*100, 1)
+ci_randIinstance_UL <- round(ci_Rinstance$upper*100, 1)
+
+ci_randInstance_LL
+ci_randIinstance_UL
+```
+
+## Prevalence in prominent journals
 
@@
 
-Look for linked PPC in articles in random sample
-```{r}
-d_articles %>%
-  filter(sample_id == "random",
-         ppc_linked == TRUE) %>%
-  summarise(n = n())
-```
-
-Calculate CIs for linked PPC in articles in random sample
-```{r}
-# Linked PPCs
-random_linked <- d_articles %>% # counts number of linked PPC events
-  filter(sample_id == "random",
-         ppc_linked == TRUE) %>%
-  count()
-
-ci_Rlinked <- binom.confint(random_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)
-
-# Convert the lower and upper limits to percentages and round them to one decimal place
-ci_randLinked_LL <- round(ci_Rlinked$lower*100, 1)
-ci_randLinked_UL <- round(ci_Rlinked$upper*100, 1)
-
-ci_randLinked_LL
-ci_randLinked_UL
-```
-
-Look for instances of PPC in articles in random sample
-```{r}
-d_articles %>%
-  filter(sample_id == "random",
-         exclude_reason == "IS ITSELF PPC") %>%
-  summarise(n = n())
-```
-
-Calculate CIs for Instance PPC in random sample
-```{r}
-# Instance PPCs
-random_instance <- d_articles %>% # counts number of linked PPC events
-  filter(sample_id == "random",
-    exclude_reason == "IS ITSELF PPC") %>%
-  count()
-
-ci_Rinstance <- binom.confint(random_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)
-
-# Convert the lower and upper limits to percentages and round them to one decimal place
-ci_randInstance_LL <- round(ci_Rinstance$lower*100, 1)
-ci_randIinstance_UL <- round(ci_Rinstance$upper*100, 1)
-
-ci_randInstance_LL
-ci_randIinstance_UL
-```
-
-# FIGURES
-*Note.* These figures are not included in the final article as they do not offer additional informative informative beyond what was reported in the tables.
-
-Boxplot of quantitative length limits
-```{r}
-quantLength <- d_journals %>%
- select(c(sample_id, ppc_name, ppc_length)) %>%
- filter(!is.na(ppc_length),
-         ppc_length != "NOT STATED",
-         ppc_length != "Qualitative") %>%
- mutate(Length = as.numeric(ppc_length))
-
-quantLength %>%  
- ggplot(mapping = aes(x = ppc_name, y = Length, colour = sample_id)) +
- geom_boxplot(
-    color = "black",
-    fill = "lightblue",
-    alpha = 0.4
+\end
+
+## Journal Policy Figures for Conference Presentation
+
+```{r}
+dj_prominent %>% 
+  filter(ppc_type == "A") %>% 
+  mutate(has_ppc = case_when(
+    has_ppc == "NO EXPLICIT" ~ "NO",
+    has_ppc == "NO IMPLICIT" ~ "NO",
+    TRUE ~ has_ppc
+  )) %>% 
+  ggplot(aes(x = has_ppc, fill = has_ppc)) +
+  geom_bar(alpha = 0.7,
+           colour = "black",
+           width = 0.9,
+           show.legend = F
            ) +
- geom_jitter(width = 0.3,
-             alpha = 0.8,
-             size = 2) + 
- scale_color_manual(values = c("prominent" =  "#ff6347", 
-                              "random" =   "#8db600",
-                              "both" = "#000080")
-                    ) +
- coord_flip() +
- scale_y_continuous(n.breaks = 8) +
- theme_bw() +
- theme(axis.text.y = element_text(angle = 90, hjust = 0.5)) +
- labs(title = "All stated quantitative length limits", 
-      x = "Post-publication critique type", 
-      y = "Length limits (words)", 
-      colour = "Sample")
-
-ggsave("lengthLimits.png", plot = last_plot(), device = "png")
-```
-
-Boxplot of quantitative time limits
-```{r}
-quantTime <- d_journals %>%
- select(c(sample_id, ppc_name, ppc_time)) %>%
- filter(!is.na(ppc_time),
-         ppc_time != "NOT STATED",
-         ppc_time != "Qualitative") %>%
- mutate(Time = as.numeric(ppc_time))
-
-quantTime %>%  
- ggplot(mapping = aes(x = ppc_name, y = Time, colour = sample_id)) +
- geom_boxplot(
-    color = "black",
-    fill = "lightblue",
-    alpha = 0.4
- ) +
- geom_jitter(width = 0.2,
-             alpha = 0.8,
-             size = 2) + 
- scale_color_manual(values = c("prominent" =  "#ff6347", 
-                              "random" =   "#8db600",
-                              "both" = "#000080")
-                    ) +
- coord_flip() +
- theme_bw() +
- theme(axis.text.y = element_text(angle = 90, hjust = 0.5)) +
- labs(title = "All stated quantitative time limits", 
-      x = "Post-publication critique type", 
-      y = "Time limits (weeks)", 
-      colour = "Sample")
-
-ggsave("timeLimits.png", plot = last_plot(), device = "png")
-```
-
-### *Post-Publication Critique Policy and Restriction Statements in Prominent Psychology Journals*
-```{r, echo = FALSE, message=FALSE}
-# Filter and transform restrictions for ppc_length
-prominent_length_data <- dj_prominent %>%
-  filter(!is.na(ppc_name)) %>%
-  filter(has_ppc != "ARCHIVE") %>% # removes 'Archive Only' PPC types
-  mutate(ppc_length = case_when(
-    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
-    ppc_length == "NOT STATED" ~ "Not Stated",
-    TRUE ~ 'Qualitative' # Summarises all length limits as 'Quantitative', 'Qualitative', or 'Not Stated'
-  )) %>% 
-  group_by(ppc_length) %>%
-  summarise(count = n())
-
-# Filter and transform restrictions for ppc_time
-prominent_time_data <- dj_prominent %>%
-  filter(!is.na(ppc_name)) %>%
-  filter(has_ppc != "ARCHIVE") %>% # removes 'Archive Only' PPC types
-  mutate(ppc_time = case_when(
-    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
-    ppc_time == "NOT STATED" ~ "Not Stated",
-    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
-  )) %>%
-  group_by(ppc_time) %>%
-  summarise(count = n())
-
-# Combine the data and unite the columns
-combined_data <- bind_rows(
-  prominent_length_data %>% mutate(Code = "Length"),
-  prominent_time_data %>% mutate(Code = "Time-to-submit")
+  theme(aspect.ratio = 2/1) +
+  labs(title = "Prominent Journals", x = "", y ="Number of Journals (N = 100)") +
+  scale_fill_brewer(palette = "Paired") +
+  scale_y_continuous(limits = c(0, 100)) +
+  theme(
+    axis.text.x = element_text(size = 14),  
+    axis.text.y = element_text(size = 14)
+  )
+
+ggsave("prom_plot.png", plot = last_plot())
+```
+
+```{r}
+# Calculate Wilson confidence intervals
+dj_random_sum <- dj_random %>% 
+  filter(ppc_type == "A") %>% 
+  mutate(has_ppc = case_when(
+    has_ppc == "NO EXPLICIT" ~ "NO",
+    has_ppc == "NO IMPLICIT" ~ "NO",
+    TRUE ~ has_ppc)
   ) %>% 
-unite(limits, ppc_length, ppc_time) %>%
-  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
-                   limits == "Qualitative_NA" ~ "Qualitative",
-                   limits == "Quantitative_NA" ~ "Quantitative",
-                   limits == "NA_Not Stated" ~ "Not Stated",
-                   limits == "NA_Qualitative" ~ "Qualitative",
-                   limits == "NA_Quantitative" ~ "Quantitative",
-                   TRUE ~ as.character(limits)
-                   ))
-
-# Create the first graph
-graph1 <- ggplot(combined_data, aes(x = Code, y = count, fill = limits)) +
-  geom_bar(stat = "identity", 
-           position = "stack",
-           colour = "black") +
-  theme_bw() +
-  scale_fill_brewer(palette = "Blues") +
-  labs(x = "Restriction Type", y = "Count", fill = "Restrictions") +
-  theme(axis.text.x = element_text(size = 7))
-
-# Create the second graph
-graph2 <- dj_prominent %>%
-  filter(ppc_type == "A") %>% # Keeps only first entry for each journal
-  filter(!is.na(has_ppc)) %>% # Remove journal rows with no (NA) PPC options 
-  mutate(has_ppc = case_when(
-    has_ppc == 'ARCHIVE' ~ 'Yes Implicit',
-    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
-    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
-    has_ppc == 'YES' ~ 'Yes Explicit',
-    TRUE ~ has_ppc
-  )) %>%
   group_by(has_ppc) %>% 
    summarise(count = n()) %>% 
-  mutate(percentage = count / sum(count) * 100) %>%
-  ggplot(aes(x = "", y = count, fill = has_ppc)) +
+  mutate(
+    LL = case_when(
+      has_ppc == "YES" ~ 16,
+      has_ppc == "NO" ~ 68
+    ),
+    UL = case_when(
+      has_ppc == "YES" ~ 32,
+      has_ppc == "NO" ~ 84
+    )
+  )
+
+# Plot with error bars
+dj_random_sum %>% 
+  ggplot(aes(x = has_ppc, y = count, fill = has_ppc)) +
   geom_bar(stat = "identity", 
+           alpha = 0.7, 
            colour = "black",
-           width = 0.8) +
-  theme_bw() +
-  scale_fill_brewer(palette = "YlOrRd", direction = -1) +
-  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")
-
-# Arrange both graphs in the same figure
-combined_plots <- graph2 + graph1
-combined_plots
-
-ggsave("ProminentJournalPolicies.png", plot = last_plot(), device = "png")
-```
-
-### *Post-Publication Critique Policy and Restriction Statements in Randomly-selected Psychology Journals*
-```{r echo=FALSE, message=FALSE}
-# Create and combine restriction statement graphs with PPC acceptance (random sample)
-
-# Filter and process data for ppc_length
-random_length_data <- d_journals %>%
-  filter(sample_id %in% c("random", "both")) %>%
-  filter(!is.na(ppc_name)) %>%
-  filter(has_ppc != "ARCHIVE") %>%
-  mutate(ppc_length = case_when(
-    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
-    ppc_length == "NOT STATED" ~ "Not Stated",
-    TRUE ~ 'Qualitative'
-  )) %>%
-  group_by(ppc_length) %>%
-  summarise(count = n())
-
-# Filter and process data for ppc_time
-random_time_data <- d_journals %>%
-  filter(sample_id %in% c("random", "both")) %>%
-  filter(!is.na(ppc_name)) %>%
-  filter(has_ppc != "ARCHIVE") %>%
-  mutate(ppc_time = case_when(
-    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
-    ppc_time == "NOT STATED" ~ "Not Stated",
-    TRUE ~ 'Qualitative'
-  )) %>%
-  group_by(ppc_time) %>%
-  summarise(count = n())
-
-# Combine the data and unite the columns
-combined_data_random <- bind_rows(
-  random_length_data %>% mutate(Code = "Length"),
-  random_time_data %>% mutate(Code = "Time-to-submit")
-) %>%
-unite(limits, ppc_length, ppc_time) %>%
-  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
-                   limits == "Qualitative_NA" ~ "Qualitative",
-                   limits == "Quantitative_NA" ~ "Quantitative",
-                   limits == "NA_Not Stated" ~ "Not Stated",
-                   limits == "NA_Qualitative" ~ "Qualitative",
-                   limits == "NA_Quantitative" ~ "Quantitative",
-                   TRUE ~ as.character(limits)
-                   ))
-
-# Create the first graph
-graph4 <- ggplot(combined_data_random, aes(x = Code, y = count, fill = limits)) +
-  geom_bar(stat = "identity", 
-           position = "stack",
-           colour = "black") +
-  theme_bw() +
-  scale_fill_brewer(palette = "Blues") +
-  labs(x = "Restriction Type", y = "Count", fill = "Restrictions") +
-  theme(axis.text.x = element_text(size = 7))
-
-# Create the second graph
-graph3 <- d_journals %>%
-  filter(sample_id == "random" | sample_id == "both") %>%
-  filter(ppc_type == "A") %>%
-  filter(!is.na(has_ppc)) %>%
-  mutate(has_ppc = case_when(
-    has_ppc == 'ARCHIVE' ~ 'Yes Implicit',
-    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
-    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
-    has_ppc == 'YES' ~ 'Yes Explicit',
-    TRUE ~ has_ppc
-  )) %>%
-  group_by(has_ppc) %>%
-  summarise(count = n()) %>%
-  mutate(percentage = count / sum(count) * 100) %>%
-  ggplot(aes(x = "", y = count, fill = has_ppc)) +
-  geom_bar(stat = "identity",
-           colour = "black",
-           width = 0.8) +
-  theme_bw() +
-  scale_fill_brewer(palette = "YlOrRd", direction = -1) +
-  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")
-
-# Arrange both graphs in the same figure
-combined_plots <- graph3 + graph4
-combined_plots
-
-ggsave("RandomJournalPolicies.png", plot = last_plot(), device = "png")
-```
+           width = 0.9,
+           show.legend = F
+           ) +
+   theme(aspect.ratio = 2/1) +
+  geom_errorbar(aes(ymin = LL, ymax = UL), width = 0.2) +
+  labs(title = "Randomly Selected Journals", x = "", y = "Number of Journals  (N = 100)") +
+  scale_fill_brewer(palette = "Greens") +
+  scale_y_continuous(limits = c(0, 100)) +
+  theme(
+    axis.text.x = element_text(size = 14),  
+    axis.text.y = element_text(size = 14)
+  )
+
+ggsave("random_plot.png", plot = last_plot())
+```
